### 2017-06-10 Draft/Draft0.1.tex
minor changes

\documentclass[useAMS,usenatbib]{mnras}
\usepackage{color}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{bm}
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage[T1]{fontenc}
\usepackage{aecompl}

\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm
        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$~}\fi}} 
\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title[Constraining CPL via clustering shells of BOSS]{Cosmological constraints via clustering shells: 
constraining the Chevallier-Polarski-Linder parametrization using the SDSS-III BOSS data}

\author[X-D. Li, C.G. Sabiu,  C. Park, Y. Wang,  G. Zhao, H. Park, A. Shafieloo, J. Kim, S.E. Hong]
{ Xiao-Dong Li,$^{1,\dagger}$
Cristiano G. Sabiu,$^{2}$
Changbom Park,$^{1}$
Yuting Wang,$^{3,\star}$
Gong-bo Zhao,$^{3}$
Hyunbae Park,$^{2}$
Arman Shafieloo,$^{2}$
Juhan Kim,$^{4,1}$
and Sungwook E. Hong$^{2}$
\\
$^1$School of Physics, Korea Institute for Advanced Study, 85 Heogi-ro, Dongdaemun-gu, Seoul 130-722, Korea\\
$^2$Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 305-348, Korea\\
$^3$NAOC\\
$^4$Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 130-722, Korea\\
$^{\dagger}$xiaodongli@kias.re.kr\\
$\star$Corresponding Author: ***}

%\date{Accepted 1988 December 15. Received 1988 December 14; in original form 1988 October 11}

% \begin{keywords}
% methods: data analysis -- methods: statistical -- Galaxies:
% kinematics and dynamics -- Cosmology: observations -- large-scale
% structure of universe
% \end{keywords}

\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2002}

\maketitle

\label{firstpage}

\begin{abstract}
We use the anisotropic clustering of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
12 spanning the redshift range $0.15<z<0.69$ to place constraints on the expansion history of the Universe. 
Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy $w=w_0+w_a\frac{z}{1+z}$,
while improving upon earlier works (Li et al. 2016), 
we present a novel use of the Alcock-Paczynski (AP) test via the small scales clustering difference between redshift bins. 
This differential measure appears to be a robust statistical tool which mitigates many systematic effect, 
allowing for competitive and unbiased constrains. 
A combination of CMB+BAO+SNIa+$H_0$+AP yields
$\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ w_a = -0.07 \pm 0.29$ (68.3\% CL).
Adding the AP method reduces the $w_0-w_a$ contour area by 50\%.
The method can be combined with the BAO method, 
increasing the science output of ongoing and future galaxy surveys by a factor of 2.
\end{abstract}

% \begin{keywords}
% circumstellar matter -- infrared: stars.
% \end{keywords}

\section{Introduction}
The  origin  of  the  accelerating  expansion  of  the  universe  is  one of  the  most  salient  questions  in  contemporary cosmology. 
Proposed mechanisms include  evolving  scalar  fields  remnant  from  the  big  bang, 
modifications to gravity,  and a  non-zero  vacuum energy \cite[see][for a comprehensive review]{2012IJMPD..2130002Y}. 
It is, therefore, crucial to obtain precise and unbiased measurements of the expansion history of the Universe allowing us to 
differentiate between competing dark energy models.

In recent years the Alcock-Paczynski (AP) test \citep{AP1979} applied to galaxy redshift samples \citep{Outram2004,Blake2011,Alam2016}, 
has allowed tight constraints to be placed on the background averaged distance scales, $D_A(z)$ and $H^{-1}(z)$.  
Assuming an incorrect cosmological model for the coordinate transformation from redshift space to comoving space produces residual geometric distortions. 
These distortions are induced by the fact that measured distances along 
and perpendicular to the line of sight are fundamentally different. 
Measuring the ratio of galaxy clustering in the radial and transverse directions provides a probe of this AP effect.

%The BAO standard ruler method for obtaining estimates of $D_A(z)$ and $H^{-1}(z)$ is widely used and accepted by the community.
%However, since these measurements are made on large scales (~$120$Mpc), 
%they require large comoving volumes and wide redshift bins to reduce cosmic variance. 
%This results in estimates of the cosmic observables at fewer redshifts and with access to fewer Fourier modes. 
%This reduction of information hinders our attempts to test dark energy models.

The main caveat of AP test is that,
because the radial distances of galaxies are inferred from observed redshifts,
AP tests are inevitably limited by peculiar motions of galaxies,
which leads to apparent anisotropy even if the adopted cosmology is correct.
The effect, known as redshift-space distortions (RSD),
is very difficult to be accurately modeled in the 2-point statistics of galaxy clustering \citep{Ballinger1996}.

As alternative methods, \cite{Marinoni2010} proposed using the symmetry properties of galaxy pairs;
%Unfortunately this method is also seriously limited by RSD.
however, since the peculiar velocity distorts the redshifts and changes the apparent tilt angles of galaxy pairs,
this method is also seriously limited by RSD \citep{Jennings2011}.
\cite{Ryden1995} and \cite{LavausWandelt1995} proposed another method using the apparent stretching of voids.
This approach has the advantage that the void regions are easier to model compared with dense regions,
but has limitations in that it utilizes only low density regions of the LSS and requires large samples to achieve good statistics \citep{Qingqing2016}.

%In an effort to overcome the RSD problem, 
%\citep{Li2016} proposed to apply the AP effect to clustering on small scales. 
%However, redshift space distortions affect the angular clustering of galaxies, mimicking a signal similar to the AP effect, 
%thus contaminating the cosmological information.

In an effort to mitigate the RSD effect, \cite{Li2014} proposed utilizing the {\it redshift dependence} of the AP effect. 
The anisotropies produced by the RSD effect are, although large, close to uniform in magnitude over a wide range in redshift. 
However, if cosmological parameters are incorrectly chosen resulting in an AP effect, 
the anisotropy in the clustering signal has a clear redshift dependence. 
In a later work, \cite{Li2015} developed the AP methodology 
which investigates the redshift dependence of galaxy 2-point correlation function (2pCF), 
measured as a function of angle between the galaxy pair and line-of-sight (LoS).

\begin{figure*}
   \centering{
   \includegraphics[height=5cm]{fig_xy.eps}
   %\includegraphics[height=8cm]{fig4_1.eps}
   %\includegraphics[height=7cm]{FVol.eps}
   %\includegraphics[height=8cm]{xy.eps}
   %\includegraphics[height=8cm]{smu.eps}
   }
   \caption{\label{fig_xy}
   The distance dependence of shape distortion in four wrongly assumed cosmologies,
   assuming a true cosmology of $\Omega_m=0.31$, $w=-1$.
   There are four perfect squares with their true shapes plotted in blue dashed lines.
   They are measured by an observer located at the origin, and the distances are computed in the two wrong cosmologies.
   The apparently distorted shapes are plotted in red solid lines.
   }
\end{figure*}

%$\xi_{\Delta s}(\mu)\equiv \int_{s_{\rm min}}^{s_{\rm max}} xi(s,\mu) ds$
%($s$ is the clustering scale).
%The RSD effect significantly distorts the shape of $\xi_{\Delta s}(mu)$ but exhibits much less redshift evolution 
%compared to the amount of change in due to incorrectly adopted cosmologies .

%When incorrect cosmological parameters are adopted, the shape of $\xi(\mu)$
%appears anisotropic due to the AP effect, and the amplitude
%is shifted by the change in comoving volume; both effects
%have significant redshift dependence. We test the method
%using the 2pCF on mock surveys drawn from HR3 and
%find the constraints obtained are tighter than those from
%the methodology of Li et al. (2014).

\cite{Li2016} applied the AP method to galaxies from the 3rd incarnation of the Sloan Digital Sky Survey (SDSS-III).
Combining the method with measurements of Cosmic Microwave Background (CMB), type Ia supernovae (SNIa), 
baryon acoustic oscialltions (BAO), and $H_0$,
they obtained very tight constraints of $ \Omega_m = 0.301 \pm 0.006,\ w=-1.054 \pm 0.025$.
By reducing the RSD effect, 
they are able to use the galaxy clustering down to 6 $h^{-1}$Mpc,
which is a major advance in extracting the cosmological information 
on small scales where galaxy clustering is strong and there are a lot of independent structures.

In this work as a continuation of the serious work we move forward to infer the constraints on dynamical dark energy.
We will present a slightly improved methodology to that of \citep{Li2016}, 
allowing for faster likelihood estimation and thus the exploration of larger parameter spaces. 
The methodology we will present here, can be applied to any model of dynamical dark energy, 
or indeed any appropriately chosen non-parametric approach could also be considered. 
However, as a first step, in this paper we will focus on the widely used Chevallier-Polarski-Linder (CPL) parametrization
$w(z) = w_0 + w_a \frac{z}{1+z}$. 
As an illustration, Fig.\ref{fig_xy} shows how the shape distortion of objects varies with distance
in case of wrongly adopted $w_0$ or $w_a$.

The paper is organised as follows; 
in \S\ref{sec:method} we will briefly review the {\em clustering shells} method as proposed by \citet{Li2016} 
and then discuss some improvements that allow us to extend and generalise the analysis for any dark energy model. 
%In \S\ref{wcdm_constraint} we perform a consistency check with our pervious work using the same SDSS DR12 galaxies 
%and focusing on a constant dark energy e.o.s parameter, $w$. 
The results are presented in \S\ref{sec:results}, showing the constraints on the expansion history in terms of CPL parameters, $w_0, w_a$. 
In \S\ref{sec:test} we perform test on the robustness of our results. 
We then conclude in \S\ref{sec:conclusion}.

\section{Methodology}\label{sec:method}

The spectroscopic sample of SDSS-III BOSS (Baryon Oscillation Spectroscopic Survey) has two primary catalogues:
%the LOWZ at $z\leq0.4$, and CMASS covering $0.4\leq z \leq 0.7$. %of galaxies.
the LOWZ sample, designed as an extension of the SDSS-I/II luminous red galaxy sample to $z\approx 0.4$ and fainter luminosities,
and the CMASS sample covers a higher redshift ($0.4\lesssim z \lesssim 0.7$),
targeted to be an approximately stellar mass limited sample of massive, luminous galaxies \cite{Reidetal:2016}.
In the clustering analysis we use 1,133,326 galaxies, split into six, non-overlapping redshift bins, 
$0.150<z_1<0.274<z_2<0.351<z_3<0.430<z_4<0.511<z_5<0.572<z_6<0.693$.
The number density of galaxies and the redshift binning scheme is plotted in the left panel of Fig.\ref{fig_TPCF}.

Following our previous methodology \citep{Li2016}, the information of small-scale anisotropic clustering is computed
\footnote{These correlations were computed using the public, kd-tree + MPI code called KSTAT \citep{kstat}.} 
as $\xi_{\Delta s} (\mu) \equiv \int_{s_{\rm min}}^{s_{\rm max}} \xi (s,\mu)\ ds$, 
with $s_{\rm min}=6 h^{-1} {\rm Mpc},\ s_{\rm max}=40 h^{-1} {\rm Mpc}$.
We then normalise these {\em clustering shells} as 
$\hat\xi_{\Delta s}(\mu) \equiv \frac{\xi_{\Delta s}(\mu)}{\int_{0}^{\mu_{\rm max}}\xi_{\Delta s}(\mu)\ d\mu}$
to nullify the amplitude information of the clustering signal, 
which is not associated with the Alcock-Paczynski test and is mostly sensitive to the galaxy bias.

The right panel of Fig.\ref{fig_TPCF} shows the contour map of $\xi(s,\mu)$ measured in the six redshift bins.
The contour lines are not horizontal due to the effects of peculiar velocity,
and the RSD effect clearly manifest itself through the tilting of contour lines.
But the shape of the tilted lines remain similar at different redshifts, which enables us avoiding RSD by looking at the redshift dependence.
The ``correct'' cosmological model is selected by minimising the amount of redshift evolution of $\hat\xi_{\Delta s}$,
via a $\chi^2$ function of 
\begin{equation}
 \chi^2\equiv \sum_{i=2}^{6} \sum_{j_1=1}^{n_{\mu}} \sum_{j_2=1}^{n_{\mu}} {\bf p}(z_i,\mu_{j_1}) ({\bf Cov}_{i}^{-1})_{j_1,j_2}  {\bf p}(z_i,\mu_{j_2})
\end{equation}
where ${\bf p}(z_i,\mu_{j})$ is the redshift evolution of clustering with respective to the lowest redshift bin,
with systematic effects subtracted:
$ {\bf p}(z_i,\mu_{j}) \equiv\  \left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right] - \left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right]_{\rm sys}$.
We use a number of $n_{\mu}$=20, 21, ... 25 bins for the value of $\hat\xi_{\Delta s}(\mu)$ at $0<\mu<\mu_{\rm max}$.
For the removal of fiber collision and the strong FoG effect near the LOS we take a cut $\mu_{\rm max} = 0.97$.

Systematics effects are estimated using mock catalogues derived from Horizon Run 4 (HR4) \cite{HR4},
an N-body simulation with box size $L={3150}$ $h^{-1}$Mpc, number of particles $6300^3$,   
initial redshift $z_{i}=100$, and WMAP5 cosmological parameters 
$(\Omega_{b},\Omega_{m},\Omega_\Lambda,h,\sigma_8,n_s)$  = (0.044, 0.26, 0.74, 0.72, 0.79, 0.96) \citep[]{komatsu 2011}. 
Mock galaxy samples are produced using a modified version of the one-to-one correspondence scheme \citep{hong2016}. 
The covariance matrix ${\bf Cov}$ is computed from the 2,000 sets of MultiDark PATCHY mock catalogues \citep{MDPATCHY}.
The statistical bias and scattering in the likelihood function (due to the finite number of mocks in covariance estimation) 
are corrected following \citet{Hartlap} and \citet{Percival2014}.

In \cite{Li2016} the likelihood contour of $\Omega_m-w$ was constructed by
measuring the 2PCF 3,375 times,
using 3D positions of BOSS galaxies computed in 71$\times$45 sets of cosmological parameters.
%with $0.06\leq \Omega_m\leq 0.41$, $-1.5 \leq w \leq -0.4$.
This procedure took 1 month using 500 cores of the KIAS {\texttt baekdu} cluster.
It would be too expensive to do such a computation on a 3D grid of $\Omega_m-w_0-w_a$,
so here we take an approach  of ``approximate 2PCF'', described as follows.

The number of pairs are only counted in a fiducial cosmology
-- which is taken as the $\Omega_m=0.26$ $\Lambda$CDM --
and ``translated'' to the measurements in a ``target'' cosmology using the realtion of 
\begin{eqnarray}
 s_{\rm target} = s_{\rm fiducial} \sqrt{\alpha_{\parallel}^2 \mu_{\rm fiducial}+\alpha_{\bot}(1-\mu_{\rm fiducial}^2)}, \\
 \mu_{\rm target} = \mu_{\rm fiducial} \frac{\alpha_\parallel}
 {\sqrt{\alpha_{\parallel}^2 \mu_{\rm fiducial} +\alpha_{\bot}(1-\mu_{\rm fiducial}^2)}}
\end{eqnarray}
where $\alpha_{\bot}\equiv D_{A,\rm target}/D_{A,\rm fiducial}$,
$\alpha_{\parallel}\equiv H_{\rm fiducial}/H_{\rm target}$.
and values of $D_A$ and $H$ are computed in the effective redshifts of the six redshift bins.
In the fiducial cosmology
we measure $\xi(s,\mu)$ in an ultra high resolution of
$\Delta s = 0.2 {\rm Mpc/h}$, $\Delta \mu = 1/600$,
%Let us call this ``approximate 2pCF'' method.
%to obtain the accurate number counts 
and these small ``pixels'' are grouped to infer 
the number counts in other cosmologies, 
in large pixels of $\Delta s = 1 {\rm Mpc/h}$, $\Delta \mu = 1/120$.
%in the fiducial cosmology and group the bins in the target cosmology.
The ``edge effects'' in case of one small pixel belonging to more than one large pixel
are treated by computing the fraction of the area.
We found that using the approximated method the computed 
$\hat\xi_{\Delta s}(\mu)$ in non-fiducial cosmologies suffer from
an error of $\approx0.5\%$, which is 10 times smaller than 
the statistical noise in the 2pCF.

%\section{Reproducing wCDM Constraints}\label{wcdm_constraint}
%As a first trial, we firstly try to reproduce the constraints on $\Omega_m$ and $w$ in \citep{Li2016}:
%As a first trial of reproduce the $\Omega_m-w$ constraints presented in \citep{Li2016},
%we obtains
%\begin{equation}
%\Omega_m = 0.301 \pm 0.008,\ w=-1.053\pm 0.034\ (w\rm CDM).
%    1  0.3010870E+00  0.7818562E-02  0.2973018E+00  0.3045011E+00  0.2883318E+00  0.3150334E+00   \Omega_m
%    2  0.6886453E+00  0.8507156E-02  0.6802557E+00  0.6975813E+00  0.6708444E+00  0.7047652E+00   h
%    3 -0.1053343E+01  0.3395215E-01 -0.1087474E+01 -0.1020395E+01 -0.1121890E+01 -0.9819443E+00   w
%\end{equation}
%The results are rather insensitive to the choice of fiducial cosmology.
%while taking a different fiducial cosmology yields
%\begin{eqnarray}
%\Omega_m = 0.300 \pm 0.008,\ w=-1.057\pm 0.034\ (\rm fid:\ \Omega_m=0.26, w=-0.6),\\    
%\Omega_m = 0.301 \pm 0.009,\ w=-1.055\pm 0.039\ (\rm fid:\ \Omega_m=0.31, w=-1.0),\\
%\Omega_m = 0.302 \pm 0.008,\ w=-1.050\pm 0.035\ (\rm fid:\ \Omega_m=0.31, w=-0.6),\\
%\Omega_m = 0.301 \pm 0.009,\ w=-1.052\pm 0.038\ (\rm fid:\ \Omega_m=0.31, w=-1.4),\\
%\Omega_m = 0.304 \pm 0.008,\ w=-1.037\pm 0.034\ (\rm fid:\ \Omega_m=0.11, w=-2.0).
%\end{eqnarray}
%so the derived constraints are rather insensitive to the fiducial cosmology.
%Even when adopting an extremely unlikely fiducial cosmological model, such as $\Omega_m=0.11, w=-2.0$, 
%yields correct estimation of parameters of $\Omega_m = 0.304 \pm 0.008,\ w=-1.037\pm 0.034$.
%For consideration of safety, when using the approxmiated method we slightly reduced the number of binning in $\hat\xi_{\Delta s}(\mu)$,
%so the error bars are slightly larger than \citep{Li2016} %due to the limitation of approximation method
%\footnote{We use $n_{\mu}$=20-25, while \citep{Li2016} adopted $n_{\mu}$=25-35.
%The approximate 2pCF contour begins to be noisy if using such a large number of $n_\mu$.}.
%from the 
%The approximate 2pCF may not be accurate enough }

%Using other fiducial cosmologies we derive similar cosmological constraints...
%We simply adopt the $\Omega_m=0.26, w=-1$ as the fiducial cosmology in the following analysis...

\section{Results}\label{sec:results}

\begin{figure*}
   \centering{
   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
   \includegraphics[height=5.3cm]{fig_nbar.eps}
   \includegraphics[width=7cm,]{fig_2pcf.eps}
   }
   \caption{\label{fig_TpCF}
   Left panel: We split the BOSS DR12 galaxies into six redshift bins to measure the evolution of shape distortion.
   The blue and green solid histograms show the redshift density distribution of LOWZ and CMASS galaxies in the $\Omega_m=0.31$ $\Lambda$CDM. 
   The vertical dashed lines define the six redshift bins that are used to cut the samples.
%   Their redshift ranges are listed.                                       .
   The number of LOWZ/CMASS galaxies in the three low/high redshift bins are listed.
   Right panel: 2D contour map of measured $\xi$ as a function of $\mu$ and $s$, from the six redshift bins of LOWZ and CMASS samples, 
      in the cosmology of $\Omega_m=0.31$ $\Lambda$CDM model.
    The black dashed lines mark the clustering region 6-40\ Mpc/h studied in the AP method.
    %The correlation functions have rather large values on small sales such as $s=5$ $h^{-1}$Mpc,
    %  and monotonically decreases to smaller values on larger scales due to weaker clustering.
    The six contour maps have rather similar appearance, implying small redshift evolution of $\xi$ from RSD.
   }
\end{figure*}

The Planck team has released the {\texttt {COSMOMC}} \citep{LB2002} outputs of four ``chains'' in the CPL model, 
using a combination of four techniques:
the full-mission Planck observations of CMB temperature and polarization anisotropies \cite{Planck2015},
the BAO distance priors measured from SDSS DR11 \citep{Anderson2013}, 6dFGS \citep{6dFGS} and SDSS MGS \citep{MGS},
the ``JLA'' SNIa sample \citep{JLA},
and the Hubble Space Telescope measurement of $H_0=70.6\pm3.3$ \cite{Riess2011,E14H0}.
\footnote{http://pla.esac.esa.int/pla/\#cosmology}.
These chains contain the CMB+BAO+SNIa+$H_0$ likelihood computed at $\sim$37 thounsands sets of cosmological parameters,
yielding constraints of 
\begin{equation}
 \Omega_m = 0.309 \pm 0.010, w_0 = -0.938 \pm 0.109, w_a = -0.38 \pm 0.41.
\end{equation}
%To include the AP method into the constraints,
We then compute the likelihood of AP method at these parameters, 
multiplying the sample likelihoods with ours and also correspondingly changing the sample weights,
and derive the CMB+BAO+SNIa+$H_0$+AP constraints on CPL parameters
\begin{equation}
%\Omega_m = 0.300 \pm 0.008, w_0 = -1.056 \pm 0.061, w_a = -0.04 \pm 0.27,
    %1  0.2999656E+00  0.7616334E-02  0.2958745E+00  0.3035033E+00  0.2878169E+00  0.3132870E+00   \Omega_m
    %2  0.6904801E+00  0.8675444E-02  0.6808558E+00  0.6993898E+00  0.6722945E+00  0.7052207E+00   h
    %3 -0.1056468E+01  0.6096323E-01 -0.1116874E+01 -0.9965903E+00 -0.1175041E+01 -0.9287388E+00   w
    %4 -0.3808376E-01  0.2716607E+00 -0.3105235E+00  0.2321461E+00 -0.6033103E+00  0.4782076E+00   w_a    
\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29,    
%    1  0.3014353E+00  0.7759923E-02  0.2974325E+00  0.3048882E+00  0.2889838E+00  0.3152269E+00   \Omega_m
%    2  0.6887652E+00  0.8760036E-02  0.6797134E+00  0.6978279E+00  0.6703971E+00  0.7044224E+00   h
%    3 -0.1041626E+01  0.6732817E-01 -0.1107730E+01 -0.9768319E+00 -0.1172149E+01 -0.8979017E+00   w
%    4 -0.7173374E-01  0.2860547E+00 -0.3572176E+00  0.2107347E+00 -0.6775045E+00  0.4558817E+00   w_a    
\end{equation}
%$$.
While the central values of parameters do not shift significantly,
the erro bars of $w_0$ and $w_a$ are reduced by 38.4\% and 29.7\%, respectively.% $$-40\%$ by adding our method into the analysis.

The marginalised constraints on $w_0-w_a$ are shown in the left panel of Fig.\ref{fig_con}, 
Adding our new AP constraints significantly reduces the allowable parameter space. 
We can also visualise this as allowable bands in $w(z)$ as can be seen in the right panel of Fig.\ref{fig_con}.

The derived cosmological constraints are fully consistent with a cosmological constant dark energy component having no evolution.
Adding the AP method reduces the statistical errors by $\sim$30-40\%,
reduces the 95.4\% CL $w_0-w_a$ contour by 50\%.
This reveals the power of the our method in constraining the redshift evolution of dark energy.

%\cite{Li2016} shows that the AP method outperforms SNIa in constraining the parameter space of $\Omega_m-w$.
%Similarly we find it outperforms in constraining $w_0-w_a$, as shown in the middle panel of Fig.\ref{fig_TpCF}.

\begin{figure*}
   \centering{
   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
   \includegraphics[height=5cm,natwidth=6,natheight=4.5]{figCPL_b.pdf}
   %\includegraphics[width=5.5cm,natwidth=4,natheight=4]{figCPL_b_BAOSNIaAP.pdf}
   \includegraphics[height=5cm,natwidth=6,natheight=4.5]{figCPL_d.pdf}
   %\includegraphics[height=8cm]{fig2b.pdf}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}
   }
   \caption{\label{fig_con}
   Left panel: 68.3\%, 95.4\% CL likelihood contours in the  $w_0-w_a$ plane.
   %Results are consistent with $\Lambda$CDM.
   The constrained area is significantly reduced after combined with the AP method.
   %This shows the power of the AP method in constraining dynamical dark energy.
   %Middle panel: $w_0-w_a$ likelihood contours using datasets of CMB+BAO, CMB+BAO+SNIa+$H_0$ and CMB+BAO+AP+$H_0$.
   %When combined with CMB+BAO, AP method yields much tighter constraints than SNIa.
   Right panel: Redshift evolution of $w(z)$, with/without adding the AP constraint.
   Adding AP tightens the constraints and reduces the redshift evolution of $w$ (tilt of $w(z)$).
   }
\end{figure*}

In this short paper we have chosen to focus on the popular CPL parameterisation of dark energy, 
however our methodology could be used with any model of cosmic expansion history.

%%% To be written!!!
\section{Robustness Test}\label{sec:test}

Analysing the same DR12 BOSS data, \citet{Li2016} obtained constraints on $\Omega_m$ and $w$
\begin{equation}\label{eq:wcdm_constrain_default}
\Omega_m=0.301\pm 0.006, w=-1.054\pm 0.025.
\end{equation}
In our new ``approximate 2pCF'' approach, while taking a fiducial cosmological model of $\Omega_m=0.26, w=-1$, we obtain consistent results of,
\begin{equation}
\Omega_m = 0.301 \pm 0.008,\ w=-1.053\pm 0.034.
%    1  0.3010870E+00  0.7818562E-02  0.2973018E+00  0.3045011E+00  0.2883318E+00  0.3150334E+00   \Omega_m
%    2  0.6886453E+00  0.8507156E-02  0.6802557E+00  0.6975813E+00  0.6708444E+00  0.7047652E+00   h
%    3 -0.1053343E+01  0.3395215E-01 -0.1087474E+01 -0.1020395E+01 -0.1121890E+01 -0.9819443E+00   w
\end{equation}
Since we use a smaller $n_{\mu}$ value than that adopted by \citep{Li2016}
\footnote{\citep{Li2016} adopted $n_{\mu}=25-35$ to achieve tighter constraints.
Since we are using an approximate 2pCF, for robustness considerations we use $n_{\mu}=20-25$.}, 
resulting in a slightly enlarged error bar. 
The central values of the parameters agree quite well, demonstrating the reliability of the approximate 2pCF method.

%\begin{figure*}
%   \centering{
%   \includegraphics[width=6cm]{figIO.eps}
%   %\includegraphics[width=9cm,natwidth=4,natheight=4]{fig2b.pdf}
%   %\includegraphics[height=8cm]{fig2b.pdf}
%   %   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%   %    \includegraphics[height=8cm]{smu.eps}
%   }
%   \caption{\label{fig_IO}
%   Input-output test of the AP method. 
%   The input cosmology (marker by green plus) is recovered at $\sim$0.5$\sigma$ 
%   using 4 realizations.
%   }
%\end{figure*}

We also performed an input-output test on four realizations of the HR4 mock catalogues \cite{hr4}.
%In the framework of $w$CDM cosmology, %Figure \ref{fig_IO} shows 
The input cosmology $\Omega_m=0.26$, $w=-1$ is recovered well, lying within the $\sim$0.5$\sigma$ CL region.

Finally, we performed a thorough test of all the possible variables in our methodology.
Figure \ref{fig_contest} shows that,
the result does not change if 
we adopt $\mu_{\rm max}=0.99\ (0.85)$ to include more (less) near-LOS regions in the analysis,
decrease the number of bins to $n_{\mu}=15-20$,
change the range of clustering to $8-30 \rm Mpc/h$,
change the fiducial cosmology to $\Omega_m=0.26,\ w=-0.6$,
exclude 1 or 2 high redshift bins,
or reduce the number of mocks to 1000.
%Constraints get weaker if increase $s_{\rm min}$,
%but are consistent with the original one.
%Even if we choose an extremely unrealistic fiducial cosmology, i.e. 
% $\Omega_m=0.11,\ w=-2.0$, the change in contour is still mild.
The most striking point to note in our testing is that the 
shift in contour position is very small even when we do not include the systematic correction.
This is reassuring, since we may have worried that {\it cosmological dependence} on the systematic correction could influence on our final results.

%We measure the evolution of $\hat\xi_{\Delta s}$ in six redshift bins.
%on scales of $s_{\rm min}=6$, $s_{\rm max}=40$.
%Systematics subtracted with the help of HR4 simulation.
%Covariance matrix

\begin{figure*}
   \centering{
   \includegraphics[width=16cm,natwidth=6,natheight=5]{fig_con_tests.pdf}
   %\includegraphics[width=9cm,natwidth=4,natheight=4]{fig2b.pdf}
   %\includegraphics[height=8cm]{fig2b.pdf}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}
   }
   \caption{\label{fig_contest}
   Robustness test of the AP method. 
   For the ``default'' constraints (pink contours) are derived using six redshift bins, 
   $\mu_{\rm max}=0.97$, $n_{\mu}=15-20$, $s=6-40 \rm Mpc/h$,
   a fiducial cosmology $\Omega_m=0.26,\ w=-1.0$ for the measurement of 2pCF,
   systematic effects estimated from HR4 simulations, 
   and covariance estimated using 2,000 PATCHY mocks.
   When altering these options, the results remain robust (black contours).
   }
\end{figure*}

\section{Conclusion}\label{sec:conclusion}

In \cite{Li2016} we proposed to constrain cosmological parameters via 
the redshift dependence of galaxy anisotropic clustering. 
This enables a robust Alcock-Paczynski test on relatively small scales.
In this paper we improved the methodology and obtained tight constraints on the CPL parametrization of dark energy. 
Adding our constraints to the CMB+SNIa+BAO+$H_0$ combination, the $w_0-w_a$ contour was reduced by $\sim50$\%.

The AP method presented in this work has many advantages over the 'traditional' galaxy clustering method.
Since it works with the redshift evolution of the anisotropic clustering signal it significantly reduces the effect of systematics. 
It avoids the great difficulty in accurate modelling of the RSD, non-linear clustering and galaxy bias.
It is applicable on much smaller scales, allowing for the inclusion of more $k$-modes and hence more information.

%By reducing the RSD effect the method enables using clustering information on scales of $s<6 \rm Mpc/h$.
%This is a major advance in extracting cosmological information on relatively small scales clustering.

%In sum, our AP method have many advantages:
%\begin{itemize}
%\item {\it It leads to very tight cosmological constraints (powerful)}. The 
% \item {\it Focusing on the redshift evolution of anisotropy it successfully overcome the problem of RSD, 
% which has long time been a limitation to the application of AP to LSS (successful).}
% In traditional approaches it is very challenging to model the RSD and enable a robust AP test.
% \item {\it It is robust against systematics (reliable)}. 
% \cite{Li2016} shows that $\hat\xi_{\Delta s}$ is insensitive to RSD or galaxy bias.
% Figure \ref{fig_con_tests} shows that the change in results is small even if we do not correct the systematics at all.
% \item {\it It is a major advance in extracting cosmological information on relatively small scales clustering (unique).} 
% Clustering of galaxies happen on all scales,
%but the size and shape of BAO ring only captures information mostly on scales of $s=100-120 {\rm Mpc/h}$.
%In the analysis of correlation function shape, people mostly use $s\gtrsim 40$ Mpc/h.
%Our AP method enters much smaller scales.
%
% \item {\it It does not require complicate modeling of non-linear structure growth and RSD (simple).}
% \item {\it It is complimentary to BAO (useful).}
% The method explores much smaller clustering scales than BAO. 
% \cite{Li2016} shows that, actually the directions of $\Omega_m-w$ contours of the two methods are orthogonal to each other.
%\end{itemize}

%While it is of essential importance to build larger experiments to 
%explore more of our Universe,
%the physical interpretation of the data is of equal importance.
%Considering our method enables {\it twice as much as before} information about the cosmic expansion history extracted from LSS data.
%This, in a way, significantly enhances the valuable data obtained from the very expensive experiments costing billions of dollars.

The presented method of clustering shells can be applied to many spectroscopic galaxy surveys. 
The method is complimentary to the BAO method and the two methods can be combined together, 
increasing (by roughly twice) the science output of ongoing and future surveys, with little to no additional cost.
We expect it play an important role in helping us unveiling the mystery of dark energy.

\section*{Acknowledgments}

We thank the Korea Institute for Advanced Study for providing computing resources (KIAS Center for Advanced Computation Linux Cluster System). CGS acknowledges support from the National Research Foundation (NRF,  \#2017R1D1A1B03034900). 
We thank Stephen Appleby, Seokcheon Lee, van putten Maurice, Graziano Rossi and Yi Wang for helpful discussions.

\begin{thebibliography}{}

\bibitem[Ade et al. (2015)]{Planck2015}
Ade, P.A.R., Aghanim, N., \& Arnaud, M., et al. arXiv:1502.01589

\bibitem[Alam et al.(2016)]{Alam2016}
Alam, S., Ata, M., \& Bailey, S., et al. 2016,
submitted to MNRAS (arXiv:1607.03155)

\bibitem[{{Alam} {et~al}\mbox{.}(2015{\natexlab{a}}){Alam}, {Albareti},
  {Allende Prieto}, {Anders}, {Anderson}, {Anderton}, {Andrews}, {Armengaud},
  {Aubourg}, {Bailey}, \& et~al.}]{dr12}
{Alam} S., Albareti, F.D.,\& Allende Prieto, C., {et~al.}, 2015,  ApJS, 219, 12

\bibitem[Alcock \& Paczynski(1979)]{AP1979}
Alcock, C., \& Paczynski, B. 1979, Nature, 281, 358

%\bibitem[Anderson et al.(2012)]{2012MNRAS.427.3435A} 
%Anderson, L., Aubourg, E., Bailey, S., et al.\ 2012, MNRAS, 427, 3435

\bibitem[Anderson et al.(2013)]{Anderson2013}
Anderson, L., Aubourg, \'E., \& Bailey, S. et al. 2014, MNRAS, 441, 24

%\bibitem[Bassett et al.(2002)]{Bassett2002}
%Bassett, B.A., Kunz, M., Silk, J., \& Ungarelli, C. 2002, MNRAS, 336, 1217

\bibitem[Ballinger, Peacock \& Heavens 1996]{Ballinger1996}
Ballinger, W.E., Peacock, J.A., \& Heavens, A.F. 1996, MNRAS, 282, 877

\bibitem[Betoule et al.(2014)]{JLA}
Betoule, M., Kessler, R., \& Guy, J., et al. 2014, A\&A, 568, 32

\bibitem[Beutler et al.(2011)]{6dFGS}
Beutler, F., Blake, C., \& Colless, M., et al. 2011, MNRAS, 416, 3017

\bibitem[Beutler et al.(2013)]{Beutler2013}
Beutler, F., Saito, S., \& Seo, H.-J., et al. 2013, MNRAS, 443, 1065

\bibitem[Beutler et al.(2016)]{Beutler2016}
Beutler, F., Seo, H.-J., \& Saito, S., et al. 2016,
arXiv:1607.03150

\bibitem[Blake et al.(2011)]{Blake2011}
Blake, C., Glazebrook, K., \& Davis, T. M., 2011, MNRAS, 418, 1725

\bibitem[Blake et al.(2013)]{WiggleZtopoloy}
Blake, C., James, J.B., \& Poole, G.B. 2013, MNRAS, 437, 2488

\bibitem[Bolton et al.(2012)]{Bolton2012}
Bolton, A.S., Schlegel, \& D.J., Aubourg E., et al. 2012, AJ, 144, 144

\bibitem[Boylan-Kolchin et al.(2008)]{B08}
Boylan-Kolchin, M., Ma, C.-P., \& Quataert, E. 2008, MNRAS, 383, 93

%\bibitem[Bueno Belloso et al. (2012)]{BB2012}
%Bueno Belloso, A., Pettinari, G.W., Meures, N., \& Percival, W.J. 2012, Phys. Rev. D, 86, 023530

%\bibitem[Chevallier \& Polarski(2001)]{CP2001}
%Chevallier, M., Polarski, D. 2001, Int. J. Mod. Phys. D, 10, 213

%\bibitem[Choi et al.(2010)]{choi 2010}
%Choi, Y.-Y., Park, C., Kim, J., Gott, J.R., 
%Weinberg, D.H., Vogeley, M.S., \& Kim, S.S. 2010, ApJS, 190, 181

\bibitem[Christensen et al.(2001)]{Bayesian}
Christensen, N., Meyer, R., Knox, L., \& Luey, B. 2001, Class. Quant. Grav., 18, 2677

%\bibitem[Chuang et al.(2013)]{Chuang2013}
%Chuang, C.-H., Prada, F., Beutler, F., et al. 2013, arXiv:1312.4889

\bibitem[Chuang \& Wang(2012)]{ChuangWang2012}
Chuang, C.-H., \& Wang, Y. 2012, MNRAS, 426, 226

%\bibitem[Corasaniti \& Copeland(2003)]{Corasaniti2003}
%Corasaniti, P.S., Copeland, E.J. 2003, Phys. Rev. D, 67, 063521

%eBOSS: 
%http://arxiv.org/abs/1508.04473
\bibitem[Dawson et al.(2015)]{eBOSS}
Dawson, K.S., Kneib, J.P., \& Percival, W.J., et al. 2015, accepted AJ

\bibitem[Dawson et al.(2012)]{Dawson et al. 2012}
Dawson, K.S., Schlegel, D.J., \& Ahn, C.P., et al. 2012, AJ, 145, 10

\bibitem[Efstathiou (2014)]{E14H0}
Efstathiou, G. 2014, MNRAS, 440, 1138

\bibitem[Eisenstein et al.(2011)]{Eisenstein et al. 2011}
Eisenstein, D.J.,  Weinberg, D.H., \& Agolet, E., et al. 2011, AJ, 142, 72

\bibitem[Feldman, Kaiser \& Peacock (1994)]{1994ApJ...426...23F} 
Feldman, H.A., Kaiser, N., \& Peacock, J.A.\ 1994, ApJ, 426, 23

\bibitem[Fukugita et al. (1996)]{Fukugita1996}
Fukugita, M., Ichikawa, T., \& Gunn, J.E., et al. 1996, AJ, 111, 1748
%Publication:	
%Astronomical Journal v.111, p.1748

%\bibitem[Gingold \& Monaghan(1977)]{GM1977}
%Gingold, R.A., \& Monaghan, J.J. 1977, MNRAS, 181, 375

%\bibitem[Gott et al.(2009)]{gott 2009}
%Gott, J.R., Choi, Y.-Y., Park, C., \& Kim, J. 2009, ApJ, 695, L45

%\bibitem[Gott et al.(2008)]{gott 2008}
%Gott, J.R., Hambrick, D.C., Vogeley, M.S., Kim, J., Park, C., Choi, Y.-Y.,
%Cen, R., Ostriker, J.P., \& Nagamine, K. 2008, ApJ, 675, 16

\bibitem[Gunn et al. (1998)]{Gunn1998}	
Gunn, J.E., Carr, M., \& Rockosi, C. et al. 1998, AJ, 116, 3040

\bibitem[Gunn et al.(2006)]{Gunn et al. 2006}
Gunn, J.E., Siegmund, W.A., \& Mannery, E.J., et al. 2006, AJ, 131, 2332

\bibitem[Guzzo et al.(2008)]{Guzzo2008}
Guzzo, L., Pierleoni, M., \& Meneux, B., et al. 2008, Nature, 451, 541

\bibitem[Hartlap et al.(2006)]{Hartlap}
Hartlap J., Simon P. \& Schneider P. [astro-ph/0608064].

\bibitem[Hong et al.(2016)]{hong2016}
Hong, S.E., Park, C.,\&  Kim, J. 2016, ApJ, 823, 103

\bibitem[Jackson (1972)]{FOG}
Jackson, J., 1972, MNRAS, 156, 1

\bibitem[Jennings et al.(2011)]{Jennings2011}
Jennings, E., Baugh, C.M., \& Pascoli, S. 2011, MNRAS, 420, 1079

%\bibitem[Jeong et al.(2014)]{Jeong2014}
%Jeong, D., Dai, L., Kamionkowski, M., \& Szalay, A.S. 2014, arXiv:1408.4648

\bibitem[Jiang et al.(2008)]{jiang2008}
Jiang, C.Y., Jing, Y. P., \& Faltenbacher, A., et al. 2008, ApJ, 675, 1095

\bibitem[Kaiser (1987)]{Kaiser1987}
Kaiser, N. 1987, MNRAS, 227, 1

\bibitem[Kim \& Park(2006)]{kim and park 2006}
Kim, J., \& Park, C. 2006, ApJ, 639, 600

\bibitem[Kim et al.(2009)]{2009ApJ...701.1547K} 
Kim, J., Park, C., Gott, J.R., III, \& Dubinski, J.\ 2009, ApJ, 701, 1547

\bibitem[Kim et al.(2015)]{hr4}
Kim, J., Park, C., L'Huillier, B., \& Hong, S. E. 2015, JKAS, 48, 213

\bibitem[Kim et al.(2011)]{horizonrun}
Kim, J., Park, C., Rossi, G., Lee, S.M., \& Gott, J.R. 2011, JKAS, 44, 217

\bibitem[Kitaura et al.(2015)]{MDPATCHY}
Kitaura, F.S., Rodrı\'{i}guez-Torres, S., Chuang, C.-H., et al. arXiv:1509.06400

\bibitem[Komatsu et al.(2011)]{komatsu 2011}
Komatsu, E., Smith, K. M., \& Dunkley, J., et al. 2011, ApJS, 192, 18

\bibitem[Lacey \& Cole(1993)]{LC93}
Lacey, C., \& Cole, S. 1993, MNRAS, 262, 627

\bibitem[Landy \& Szalay(1993)]{1993ApJ...412...64L} 
Landy, S.D., \& Szalay, A.S.\ 1993, ApJ, 412, 64

%EUCLID:
%http://arxiv.org/abs/1110.3193
\bibitem[Laureijs et al.(2011)]{EUCLID}
Laureijs, R., Amiaux, J., \& Arduini, S., et al. 2011, arXiv:1110.3193

\bibitem[Lavaux \& Wandelt(2012)]{LavausWandelt1995}
Lavaux, G., \& Wandelt, B.D. 2012, ApJ, 754, 109

%\bibitem[Levi et al.(2013)]{2013arXiv1308.0847L} 
%Levi, M., Bebek, C., Beers, T., et al.\ 2013, arXiv:1308.0847

\bibitem[Lewis \& Bridle (2002)]{LB2002}
Lewis, A., \& Bridle, S. 2002, Phys. Rev. D, 66, 103511

\bibitem[L'Huillier et al.(2014)]{2014NewA...30...79L} 
L'Huillier, B., Park, C., \& Kim, J.\ 2014, New Astronomy, 30, 79

\bibitem[Li et al.(2011)]{Li2011}
Li, M., Li, X.-D., Wang, S., \& Wang, Y. 2011, Commun. Theor. Phys., 56, 525

\bibitem[Li et al.(2014)]{Li2014}
Li, X.-D., Park, C., Forero-Romero, J., \& Kim, J. 2014, ApJ, 796, 137

\bibitem[Li et al.(2015)]{Li2015}
Li, X.-D., Park, C., Sabiu, C.G., \& Kim, J. 2015, MNRAS, 450, 807

\bibitem[Li et al.(2016)]{Li2016}
Li, X.-D., Park, C., \& Sabiu, C.G., et al. 2016, ApJ, 832, 103

%\bibitem[Linder(2003)]{Linder2003}
%Linder, E.V. 2003, Phys. Rev. Lett., 90, 091301

\bibitem[Linder et al.(2014)]{Linder2013}
Linder, E.V., Minji, O., Okumura, T., Sabiu, C.G., \& Song, Y.-S. 2014, Phys. Rev. D, 89, 063525

\bibitem[L{\'o}pez-Corredoira(2014)]{2014ApJ...781...96L} 
L{\'o}pez-Corredoira, M.\ 2014, ApJ, 781, 96

\bibitem[Mao et al. (2016)]{Qingqing2016}
Mao, Q., Berlind, A.A., Scherrer, R.J., et al. 2016, submitted to ApJ

\bibitem[Marinoni \& Buzzi(2010)]{Marinoni2010}
Marinoni, C., \& Buzzi, A. 2010, Nature, 468, 539

\bibitem[Matsubara \& Suto(1996)]{Matsubara1996}
Matsubara T., \& Suto, Y. 1996, ApJ, 470, L1

\bibitem[McCavana et al.(2012)]{M12}
McCavana, T., Micic, M., Lewis, G. F., et al. 2012, MNRAS, 424, 361

\bibitem[Morandi \& Sun (2016)]{MS2016}
Morandi, A., \& Sun, M. arXiv:1601.03741

\bibitem[Outram et al.(2004)]{Outram2004}
Outram, P.J., Shanks, T., Boyle, B.J., Croom, S.M., Hoyle, F., Loaring, N.S., 
Miller, L., \& Smith, R.J. 2004, MNRAS, 348, 745

%\bibitem[Parejko et al.(2013)]{Parejko2013}
%Parejko, J. K., Sunayama, T., Padmanabhan, N., et al. 2013, MNRAS, 429, 98

\bibitem[Parejko et al.(2013)]{Parejko2013}
Parejko J.K., et al., 2013, MNRAS, 429, 98

\bibitem[Parihar et al. (2014)]{CMASSLSS2014}
Parihar, P., Vogeley, M.S., \& Gott, J.R., et al. 2014, ApJ, 796, 86

\bibitem[Park et al.(2005)]{park 2005}
Park, C., Kim, J., \& Gott, J.R. 2005, ApJ, 633, 1

\bibitem[Park \& Kim(2010)]{topology}
Park, C., \& Kim, Y.-R. 2010, ApJL, 715, L185

\bibitem[Park et al. (2012)]{Park2012}
Park, C., Choi, Y.-Y., Kim, J., Gott, J.R., Kim, S.S., \&
Kim, K.-S. 2012, ApJ, 759, 7

\bibitem[Park et al. (2015)]{Park2015}
Park, C., Song, H., Einasto, M., Lietzen, H., \&
Heinamaki, P. 2015, JKAS, 48, 75

\bibitem[Peebles \& Ratra(2003)]{PR2003}
Peebles, P.J.E., \& Ratra, B. 2003, Reviews of Modern Physics, 75, 559

\bibitem[Percival et al.(2014)]{Percival2014}
Percival, W.J., Ross, A.J., \& S\'{a}nchez, A.G., et al. 2014, MNRAS, 439, 2531

\bibitem[Perlmutter et al.(1999)]{Perl1999}
Perlmutter, S., Aldering, G., \& Goldhaber, G., et al. 1999, ApJ, 517, 565

\bibitem[Press \& Shechter(1974)]{PS1974}
Press, W.H., \& Schechter, P.L. 1974, ApJ, 187, 425

\bibitem[Reid et al.(2012)]{Reid2012}
Reid, B., Samushia, L., \& White, M., et al. 2012, MNRAS, 426, 2719

\bibitem[Reid et al.(2016)]{Reidetal:2016}
Reid, B., Ho, S., \& Padmanabhan, N., et al.  2016, MNRAS, 455, 1553

\bibitem[Riess et al.(1998)]{Riess1998}
Riess, A.G., Filippenko, A.V., \& Challis, P., et al. 1998, AJ, 116, 1009

\bibitem[Riess et al.(2011)]{Riess2011}
Riess, A.G., Macri, L., \& Casertano, S., et al. 2011, ApJ, 730, 119
%A 3\% Solution: Determination of the Hubble Constant with the Hubble Space Telescope and Wide Field Camera

\bibitem[Ross et al.(2012)]{2012MNRAS.424..564R} 
Ross, A.J., Percival, W.J., \& S{\'a}nchez, A.G. et al.\ 2012, MNRAS, 424, 564

\bibitem[Ross et al.(2015)]{MGS}
Ross, A.J., Samushia, L., \& Howlett, C., et al. 2015, MNRAS, 449, 835

\bibitem[Ryden(1995)]{Ryden1995}
Ryden, B.S. 1995, ApJ, 452, 25

%\bibitem[Samushia et al.(2014)]{Samushia2014}
%Samushia, L., Reid, B. A., White, M., et al. 2014, MNRAS, 439, 3504

%\bibitem[Sanchez et al.(2013)]{Sanchez2013}
%Sanchez, A. G., Kazin, E. A., Beutler, F., et al. 2013, MNRAS, 433, 1202

%\bibitem[Sutter et al.(2014)]{Sutter2014}
%Sutter, P.M., Pisani, A., Wandelt, B.D., \& Weinberg, D.H. 2014, MNRAS, 443, 2983

\bibitem[Sabiu (2013)]{kstat}
C.G. Sabiu 2013
https://bitbucket.org/csabiu/kstat
http://ascl.net/code/v/1634

\bibitem[Sanchez et al.(2016)]{Sanchez2016}
Sanchez, A. G., Scoccimarro, R., \& Crocce, M., et al.
arXiv:1607.03147

\bibitem[Schlafly et al.(2010)]{Schlafly2010}
Schlafly E.F., Finkbeiner D.P., Schlegel D.J., et al. 2010, ApJ, 725, 1175

\bibitem[Schlafly \& Finkbeiner(2011)]{SF2011}
Schlafly E.F., \& Finkbeiner D.P. 2011, ApJ, 737, 103

%DESI:
%http://arxiv.org/abs/1106.1706
\bibitem[Schlegel et al.(2011)]{DESI}
Schlegel, D., Abdalla, F., \& Abraham, T., et al. 2011, arXiv:1106.1706

\bibitem[Smee et al.(2013)]{Smee2013}
Smee, S.A., Gunn, J.E., \& Uomoto, A., et al. 2013, AJ, 146, 32

\bibitem[Song et al.(2014)]{2014arXiv1407.2257S} 
Song, Y.S., Sabiu, C.G., 
Okumura, T., Oh, M., \& Linder, E.V.\ 2014, JCAP, 12, 005

\bibitem[Speare et al. (2015)]{Speare2015}
Speare, R., Gott, J.R., Kim, J., \& Park, C.
2015, ApJ, 799, 176

%\bibitem[Tojeiro \& Percival(2011)]{Tojeiro2011}
%Tojeiro R., \& Percivial W.J. 2011, MNRAS, 417, 1114

%\bibitem[Tojeiro et al.(2012)]{Tojeiro2012}
%Tojeiro, R., Percival, W. J., Wake, D. A., et al. 2012, MNRAS, 424, 136

\bibitem[Viana \& Liddle(1996)]{VL1996}
Viana, P.T.P., \& Liddle, A.R. 1996, MNRAS, 281, 323

\bibitem[Villalobos et al.(2013)]{V13}
Villalobos, \'{A}., ́De Lucia, G., Weinmann, S.M., Borgani, S., \& Murante, G. 2013, MNRAS, 433, L49

\bibitem[Weinberg (1989)]{SW1989}
Weinberg, S. 1989, Reviews of Modern Physics, 61, 1

\bibitem[White (2011)]{White2011}
White M., et al. 2011, ApJ, 728, 126

\bibitem[Yoo \& Watanabe(2012)]{2012IJMPD..2130002Y} Yoo, J., \& Watanabe, Y.\ 2012, International Journal of Modern Physics D, 21, 1230002

\bibitem[York et al.(2000)]{York et al. 2000}
York, D.G., Adelman, J., \& Anderson, J.E., et al. 2000, AJ, 120, 1579

\bibitem[Zehavi et al.(2011)]{zehavi2011}
Zehavi, I., Zheng, Z., \& Weinberg, D.H., et al. 2011, ApJ, 736, 59

\end{thebibliography}

\bsp

\label{lastpage}

\end{document}

### 2017-06-10 Draft/Draft_20160910.tex
minor changes

%%% On-going present
%%
%% Beginning of file 'sample.tex'
%%
%% Modified 2005 December 5
%%
%% This is a sample manuscript marked up using the
%% AASTeX v5.x LaTeX 2e macros.

%% The first piece of markup in an AASTeX v5.x document
%% is the \documentclass command. LaTeX will ignore
%% any data that comes before this command.

%% The command below calls the preprint style
%% which will produce a one-column, single-spaced document.
%% Examples of commands for other substyles follow. Use
%% whichever is most appropriate for your purposes.
%%
%%\documentclass[12pt,preprint]{aastex}

%% manuscript produces a one-column, double-spaced document:

%%\documentclass[manuscript]{aastex}

%% preprint2 produces a double-column, single-spaced document:

 %\documentclass[preprint2]{aastex}
%\documentclass[preprint2]{aastex}
%\documentclass[manuscript]{aastex}
\documentclass[iop]{emulateapj}
\renewcommand{\baselinestretch}{0.95}
%% Sometimes a paper's abstract is too long to fit on the
%% title page in preprint2 mode. When that is the case,
%% use the longabstract style option.

%% \documentclass[preprint2,longabstract]{aastex}

%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
%% If you are submitting to a journal that translates manuscripts
%% into SGML, you need to follow certain guidelines when preparing
%% your macros. See the AASTeX v5.x Author Guide
%% for information.

\usepackage{enumitem}

\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm
        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$~}\fi}} 
\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}
\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\ba{\begin{eqnarray}}
\def\ea{\end{eqnarray}}

%% You can insert a short comment on the title page using the command below.

%\slugcomment{Not to appear in Nonlearned J., 45.}

%% If you wish, you may supply running head information, although
%% this information may be modified by the editorial offices.
%% The left head contains a list of authors,
%% usually a maximum of three (otherwise use et al.).  The right
%% head is a modified title of up to roughly 44 characters.
%% Running heads will not print in the manuscript style.

%\title[]
%{}

\shorttitle{Reshift Dependent Alcock-Paczynski effect from SDSS-III DR12}
\shortauthors{X.-D. Li, C. Park, C.G. Sabiu, H. Park, D.H. Weinberg, J. Kim, S.E. Hong}

%% This is the end of the preamble.  Indicate the beginning of the
%% paper itself with \begin{document}.

\begin{document}

%% LaTeX will automatically break titles if they run longer than
%% one line. However, you may use \\ to force a line break if
%% you desire.

\title{Cosmological constraints from the redshift dependence of the Alcock-Paczynski effect: application to the SDSS-III BOSS DR12 galaxies}

%\author{Xiao-Dong~Li\altaffilmark{1}, Changbom~Park\altaffilmark{1}, J.~E.~Forero-Romero\altaffilmark{2} and Juhan Kim%\altaffilmark{3}}
%\affil{\altaffilmark{1}School of Physics, Korea Institute for Advanced Study, Heogiro 85, Seoul 130-722, Korea }
%\affil{\altaffilmark{2}Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, %Colombia}
%\affil{\altaffilmark{3}Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-%gu, Seoul 130-722, Korea }
%\affil{\it (xiaodongli@kias.re.kr, cbp@kias.re.kr, je.forero@uniandes.edu.co, kjhan@kias.re.kr)}

%\author[Xiao-Dong~Li, Changbom~Park, Cristiano G. Sabiu, Juhan Kim and Sungwook E. Hong]
%{ Xiao-Dong Li$^{1,\dagger}$, Changbom Park$^{1}$, Cristiano G. Sabiu$^{2}$, Juhan Kim$^{3,1,\star}$, Sungwook E. Hong$^{1}$\\
%$^1$School of Physics, Korea Institute for Advanced Study, 85 Heogi-ro, Dongdaemun-gu, Seoul 130-722, Korea\\
%$^2$Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 305-348, Korea\\
%$^3$Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 130-722, Korea\\
%$^{\dagger}$xiaodongli@kias.re.kr\\
%$\star$Corresponding Author: ***@kasi.re.kr}

\author{Xiao-Dong Li, Changbom Park,}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 02455, Korea}
\author{Cristiano G. Sabiu, Hyunbae Park,}
\affil{Korea Astronomy and Space Science Institute, Daejeon 305-348, Korea}
\author{David H. Weinberg,}
\affil{Department of Astronomy and CCAPP, The Ohio State University, 140 West 18th Avenue, Columbus, OH 43210, USA}
\author{Donald P. Schneider,}
\affil{Department of Astronomy and Astrophysics, The Pennsylvania State University, 
University Park, PA 16802 }
\affil{Institute for Gravitation and the Cosmos, The Pennsylvania State University, 
University Park, PA 16802 }
\author{Juhan Kim\altaffilmark{1},}
\affil{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 02455, Korea}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 02455, Korea}
\and
\author{Sungwook E. Hong}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 02455, Korea}

%\altaffiltext{1}{xiaodongli@kias.re.kr}
%\altaffiltext{2}{cbp@kias.re.kr}
%\altaffiltext{3}{csabiu@kasi.re.kr}
%\altaffiltext{4}{\bf Hyunbae: your email}
\altaffiltext{1}{Corresponding Author: kjhan@kias.re.kr}

% \email{xiaodongli@kias.re.kr}
% \email{cbp@kias.re.kr}
% \email{je.forero@uniandes.edu.co}

% \author{S. Djorgovski\altaffilmark{1,2,3} and Ivan R. King\altaffilmark{1}}
% \affil{Astronomy Department, University of California,
%     Berkeley, CA 94720}
%
% \author{C. D. Biemesderfer\altaffilmark{4,5}}
% \affil{National Optical Astronomy Observatories, Tucson, AZ 85719}
% \email{aastex-help@aas.org}
%
% \and
%
% \author{R. J. Hanisch\altaffilmark{5}}
% \affil{Space Telescope Science Institute, Baltimore, MD 21218}
%
% %% Notice that each of these authors has alternate affiliations, which
% %% are identified by the \altaffilmark after each name.  Specify alternate
% %% affiliation information with \altaffiltext, with one command per each
% %% affiliation.
%
% \altaffiltext{1}{Visiting Astronomer, Cerro Tololo Inter-American Observatory.
% CTIO is operated by AURA, Inc.\ under contract to the National Science
% Foundation.}
% \altaffiltext{2}{Society of Fellows, Harvard University.}
% \altaffiltext{3}{present address: Center for Astrophysics,
%     60 Garden Street, Cambridge, MA 02138}
% \altaffiltext{4}{Visiting Programmer, Space Telescope Science Institute}
% \altaffiltext{5}{Patron, Alonso's Bar and Grill}

%% Mark off your abstract in the ``abstract'' environment. In the manuscript
%% style, abstract will output a Received/Accepted line after the
%% title and affiliation information. No date will appear since the author
%% does not have this information. The dates will be filled in by the
%% editorial office after submission.

\begin{abstract}
We apply the methodology developed in \cite{Li2014,Li2015} to BOSS DR12 galaxies and 
derive cosmological constraints from the redshift dependence of the Alcock-Paczynski (AP) effect.
The apparent anisotropy in the distribution of observed galaxies arise from two main sources,
the redshift-space distortion (RSD) effect due to the galaxy peculiar velocities,
and the geometric distortion when incorrect cosmological models are assumed for 
%the coordinate transformation from redshift space to comoving space, 
transforming redshift to comoving distance,
known as the AP effect.
%We focus on the redshift dependence of the anisotropic clustering of galaxies to constrain cosmological parameters.
Anisotropies produced by the RSD effect are, although large,
maintaining a nearly uniform magnitude over a large range of redshift,
while the degree of anisotropies from the AP effect varies with redshift by much larger magnitude. 
%We found that the redshift dependence of the anisotropy introduced by RSD is much less significant compared with the anisotropy caused by AP.
%We focus on the redshift dependence of the anisotropic clustering of galaxies to constrain cosmological parameters 
%which is less sensitive to RSD contamination.
We split the DR12 galaxies into six redshift bins, measure the 2-point correlation function in each bin,
and assess the redshift evolution of anisotropies.
%Assuming a flat Universe consisting of a pressure-less dark matter component 
%with current ratio $\Omega_m$, and a dark energy component with constant equation of state $w$,
We obtain constraints of 
$\Omega_m=0.290 \pm 0.053,\ \ w = -1.07 \pm 0.15$,
which are comparable with the current constraints from other cosmological probes
such as type Ia supernovae, cosmic microwave background, and baryon acoustic oscillation (BAO).
Combining these cosmological probes with our method yield tight constraints of 
$ \Omega_m = 0.301 \pm 0.006,\ w=-1.054 \pm 0.025$.
Our method is complementary to the other large scale structure probes like BAO and topology.
%We discuss the caveats and possibilities for improving upon our methodology.
We expect this technique will play an important role in deriving cosmological constraints from
large scale structure surveys.
\end{abstract}

%% Keywords should appear after the \end{abstract} command. The uncommented
%% example has been keyed in ApJ style. See the instructions to authors
%% for the journal to which you are submitting your paper to determine
%% what keyword punctuation is appropriate.

\keywords{large-scale structure of Universe --- dark energy --- cosmological parameters}

%% From the front matter, we move on to the body of the paper.
%% In the first two sections, notice the use of the natbib \citep
%% and \citet commands to identify citations.  The citations are
%% tied to the reference list via symbolic KEYs. The KEY corresponds
%% to the KEY in the \bibitem in the reference list below. We have
%% chosen the first three characters of the first author's name plus
%% the last two numeral of the year of publication as our KEY for
%% each reference.

%% Authors who wish to have the most important objects in their paper
%% linked in the electronic edition to a data center may do so by tagging
%% their objects with \objectname{} or \object{}.  Each macro takes the
%% object name as its required argument. The optional, square-bracket
%% argument should be used in cases where the data center identification
%% differs from what is to be printed in the paper.  The text appearing
%% in curly braces is what will appear in print in the published paper.
%% If the object name is recognized by the data centers, it will be linked
%% in the electronic edition to the object data available at the data centers
%%
%% Note that for sources with brackets in their names, e.g. [WEG2004] 14h-090,
%% the brackets must be escaped with backslashes when used in the first
%% square-bracket argument, for instance, \object[\[WEG2004\] 14h-090]{90}).
%%  Otherwise, LaTeX will issue an error.

\section{Introduction}

The current standard model of cosmology has been highly successful at reproducing the Universe on large scales. %large scale observations of the Universe. 
From the temperature fluctuations in the cosmic microwave background (CMB), 
to the late time clustering of galaxies, 
the vacuum energy dominated cold dark matter model ($\Lambda$CDM) fits the data surprisingly well \citep{Planck2015,Anderson2013}. 
This result is all the more impressive considering both the underlying assumptions, 
such as homogeneity, isotropy, scale invariance of the primordial fluctuations, 
and the minimal set of cosmological parameters that are required.

Nonetheless, these models produce the unsatisfactory prospect that we must include within our ontology both a vacuum energy 
that is much smaller than that predicted from  quantum mechanics, 
or alternatively a new scalar field (dark energy) that has negative pressure
\citep{SW1989,Riess1998,Perl1999,PR2003,Li2011}, 
and a new matter component, which is not contained within the standard $SU(3)\times SU(2) \times U(1)$ formulation of particle physics.

With an over-abundance of models for both dark energy-like accelerated expansion and dark matter, 
it is crucial to obtain precise and model-independent measurements of the cosmic evolution, usually referred to as background observables. 
Two such observables are the angular diameter distance, $D_A$, and the Hubble factor, $H$.  
If these quantities can be measured at various redshifts and to a high degree of accuracy then our ability to differentiate between various competing models will be greatly increased.

In the last few years there has been increasing interest in using the Alcock-Paczynski (AP) effect \citep{AP1979} 
in the large-scale clustering of galaxies to obtain constraints on $D_A$ and $H$ \citep{Guzzo2008,topology}. 
Assuming an incorrect cosmological model for the coordinate transformation from redshift space to comoving space produces residual geometric distortions. 
These distortions are induced by the fact that measured distances along and perpendicular to the line of sight are fundamentally different. 
Measuring the ratio of galaxy clustering in the radial and transverse directions provides a probe of this AP effect.

There have been several methods proposed for applying the AP test to the large scale structure (LSS).
The most widely adopted one uses anisotropic clustering \citep{Ballinger1996,Matsubara1996},
which has been used for the 2 degree Field Quasar Survey \citep{Outram2004},
the WiggleZ dark energy survey \citep{Blake2011}, 
the Sloan Digital Sky Survey-I/II (SDSS-I/II) Luminous Red Galaxy (LRG) survey \citep{Eisenstein et al. 2011,ChuangWang2012},
and the SDSS-III Baryon Oscillation Spectroscopic Survey (BOSS) 
%\citep{Reid2012,Beutler2013,Linder2013,2014arXiv1407.2257S, 2014ApJ...781...96L}.
\citep{Reid2012,Beutler2013,Linder2013,2014arXiv1407.2257S, 2014ApJ...781...96L,
Alam2016, Beutler2016, Sanchez2016}
The main caveat of this method is that,
because the radial distances of galaxies are inferred from redshifts,
AP tests are inevitably limited by redshift-space distortions (RSD) \citep{Ballinger1996},
which leads to apparent anisotropy even if the adopted cosmology is correct.
The RSDs must be accurately modeled for the 2-point statistics of galaxy clustering.

\cite{Marinoni2010} proposed using the symmetry properties of galaxy pairs.
Unfortunately this method is also seriously limited by RSD.
The peculiar velocity distorts the redshift and changes the apparent tilt angles of galaxy pairs.
The effect depends on both redshift and underlying cosmology, and is rather difficult to model accurately \citep{Jennings2011}.
\cite{Ryden1995} and \cite{LavausWandelt1995} proposed another method using the apparent stretching of voids.
This approach has the advantage that the void regions are easier to model compared with dense regions,
but has limitations in that it utilizes only low density regions of the LSS
and requires large samples.

\cite{Li2014} proposed another method utilizing the redshift dependence of AP effect to overcome the RSD problem.
The anisotropies produced by RSD effect are, although very large,
close to uniform in magnitude over a large range of redshift.
Conversely, if cosmological parameters are incorrectly chosen, the LSS
appear anisotropic and the degree of anisotropy varies with redshift. 
%We found that the redshift dependence of the anisotropy introduced by RSD is much less significant compared with the anisotropy caused by AP.
%Thus we can focus on the redshift dependence of the galaxy density gradient field, 
%which is less affected by RSD, but still sensitive to cosmological parameters.
We used the {\it galaxy density gradient field} 
to characterize the anisotropies in LSS and tested the idea on Horizon Run 3 (HR3) N-body simulations \citep{horizonrun},
demonstrating that the method leads to unbiased estimation of the density parameter $\Omega_m$ and the dark energy equation of state (EoS) $w$.

The same topic was revisited in \cite{Li2015}, but using the {\it galaxy two-point correlation function} (2pCF) as the statistical tool.
The 2pCF as a function of angle, $\xi(\mu)$, is measured at different redshifts.
Similar to \cite{Li2014}, we found that the RSD effect, although significantly distorting $\xi(\mu)$, 
exhibits much less redshift evolution compared to the amount of change in $\xi(\mu)$ due to incorrectly adopted cosmologies.
When incorrect cosmological parameters are adopted, 
the shape of $\xi(\mu)$ appears anisotropic due to the AP effect, 
and the amplitude is shifted by the change in comoving volume;
both effects have significant redshift dependence.
%By focusing on the redshift dependence of $\xi(\mu)$, we can correctly recover the cosmological parameters despite the contamination of RSD.
We test the method using the 2pCF on mock surveys drawn from HR3
%we measuring the redshift evolution of 2pCF also leads to unbiased estimation of cosmological parameters 
and find the constraints obtained are tighter than those from the methodology of \cite{Li2014}.

The change of the comoving volume size is another consequence of an incorrectly adopted cosmology, 
and has motivated investigations constraining cosmological parameters from number counting of 
galaxy clusters \citep{PS1974,VL1996}. 
An obstacle in using the comoving volume for cosmological tests is the evolution of the number of target objects.
The essential need for reducing the evolution effects in applying the test led \cite{topology} to propose a new method
using the topology of LSS. 
Since the topology is a measure of intrinsic connectivity of structures,
it is expected to be insensitive to non-linear gravitational evolution, type of density tracers,
and RSD on large scales.
This method has been applied to the WiggleZ Dark Energy Survey data by \cite{WiggleZtopoloy},
and to simulated BOSS samples \citep{Speare2015}.

In this paper we apply our methodology to SDSS-III BOSS Data Release 12 (DR12) galaxies \citep{Reidetal:2016}.
%We split the DR12 samples of CMASS and LOWZ into six redshift bins (three in each) and measure the redshift evolution of 
%anisotropy therein to determine the correct cosmological parameters leading to least redshift evolution of anisotropy.
We take the 2pCF as statistical tool characterizing the anisotropic clustering and follow the procedure of \cite{Li2015} to conduct the analysis.
We assume a flat Universe and constrain parameters of $\Omega_m$ and $w$.
2pCF is a mature statistic in cosmology and its optimal estimation and statistical properties are well understood.
Compared with the density gradient field statistic, it leads to tighter constraints and is less affected by survey geometry.

The outline of this paper is as follows. 
In Sec. 2 we describe the observational data used in this paper.
In Sec. 3 we discuss the N-body simulations and mock galaxy catalogues that are used in this analysis.
In Sec. 4 we briefly review the nature and consequences of the AP effect when performing coordinate transforms in a cosmological context. 
In Sec. 5 and Sec. 6, we describe our analysis method and present the cosmological constraints obtained from BOSS DR12 galaxies. 
We conclude in Sec. 7.

\section{The Observational Data}\label{sec:data}

The Sloan Digital Sky Survey (SDSS; York et al. 2000) %DANGEROUS
imaged approximately 7\,606 $\rm deg^2$
of the Northern Galactic Hemisphere and 
3\,172 $\rm deg^2$ of the Southern Galactic Hemisphere in the {\it ugriz} bands \citep{Fukugita1996,Gunn1998}.
The survey was performed using the 
2.5m Sloan telescope \citep{Gunn et al. 2006}
at the Apache Point Observatory in New Mexico.
%BOSS, as part of the SDSS-III survey \citep{Eisenstein et al. 2011},
%has obtained additional imaging,
%increasing the region of the south to 3\,172 $\rm deg^2$.
BOSS \citep{Dawson et al. 2012,Smee2013}, as a part of the SDSS-III survey \citep{Eisenstein et al. 2011},
has obtained spectra and redshifts 
of 1.37 million galaxies selected from the SDSS imaging,
covering a region of 9\,376 $\rm deg^2$.
The galaxy redshifts were measured by an automated pipeline \citep{Bolton2012}.

\begin{figure*}
   \centering{
   %\includegraphics[width=7cm]{Tpcf--contour.eps}
   %\includegraphics[width=16cm]{Tpcf--contour-others.eps}
   %\includegraphics[width=7.5cm,natwidth=8.3,natheight=9]{maskdr12v1lowres.png}
   %\includegraphics[width=7.5cm,natwidth=8.3,natheight=9]{maskdr12v1lowzlowres.png}
   %\includegraphics[width=8.5cm,natwidth=8.3,natheight=5]{Tpcf--gal_LN.jpg}
   %\includegraphics[width=8.5cm,natwidth=8.3,natheight=5]{Tpcf--gal_LS.jpg}
   %\includegraphics[width=8.5cm,natwidth=8.3,natheight=5]{Tpcf--gal_CN.jpg}
   %\includegraphics[width=8.5cm,natwidth=8.3,natheight=5]{Tpcf--gal_CS.jpg}
   %\includegraphics[width=8.5cm,natwidth=8.3,natheight=5]{Tpcf_LN.png}
   %\includegraphics[width=8.5cm,natwidth=8.3,natheight=5]{Tpcf_LS.png}
   %\includegraphics[width=8.5cm,natwidth=8.3,natheight=5]{Tpcf_CN.png}
   %\includegraphics[width=8.5cm,natwidth=8.3,natheight=5]{Tpcf_CS.png}
   \includegraphics[width=8.5cm]{Tpcf_LN.eps}
   \includegraphics[width=8.5cm]{Tpcf_LS.eps}
   \includegraphics[width=8.5cm]{Tpcf_CN.eps}
   \includegraphics[width=8.5cm]{Tpcf_CS.eps}
   %\includegraphics[width=8.5cm]{fig1_0.eps}
   %\includegraphics[width=8.5cm]{fig1_1.eps}
   %\includegraphics[width=8.5cm]{fig1_2.eps}
   %\includegraphics[width=8.5cm]{fig1_3.eps}
   }
   \caption{\label{fig_radec}
   The sky coverage of the LOWZ and CMASS samples in the north and south Galactic caps. 
   The individual points mark position of galaxies in the survey coordinate frame.
   The solid lines mark the right ascension and declination.
   The mean completeness is 97.2\% for the LOWZ sample, shown in the upper panels,
   and 98.8\% for the CMASS sample in the lower panels.
   The effective sky coverage is 8,337 $\rm deg^2$ for LOWZ and 9,376 $\rm deg^2$ for CMASS.
   %Each patch corresponds to a plate,
   %with the color determined by the completeness of that plate.
   See \cite{Reidetal:2016} for more details.
   }
\end{figure*}

The spectroscopic sample of BOSS has two primary catalogues.
%the LOWZ at $z\leq0.4$, and CMASS covering $0.4\leq z \leq 0.7$. %of galaxies.
The LOWZ sample is designed to extend the SDSS-I/II LRG sample to $z\approx 0.4$ and fainter luminosities,
in order to increase the number density of the sample by a factor of 3.
The CMASS sample covers a higher redshift ($0.4\lesssim z \lesssim 0.7$).
It was targeted to be an approximately stellar mass limited sample of massive, luminous galaxies.
The final data release (DR12) samples are described in \cite{Reidetal:2016},
where the details of targeting algorithms and the catalogues are provided.
%The full targeting algorithms used and the method for calculating the galaxy and random catalogues are presented in \citet{Reidetal:2016}, 
%Full details of targeting algorithms and the catalogues are provided in \citep{}, 
%and we do not replicate this here.

%The galaxy survey used two primary target algorithms, 
%selecting samples called LOWZ, with 361\,759 galaxies in the final data release DR12 \citep{dr12} between $0.15<z <0.43$ and CMASS, 
%with 771\,567 galaxies in DR12 between $0.43< z < 0.70$. 
%The full targeting algorithms used and the method for calculating the galaxy and random catalogues are presented in \citet{Reidetal:2016}, 
%which also shows that the samples jointly cover a large cosmic volume $V_{\rm eff}=7.4\,{\rm Gpc}^3$.
%with a number density of galaxies as a function of observed redshift, 
%that ensures that the shot noise does not dominate at BAO (baryon acoustic oscillation) scales. 
%The full targeting algorithms used and the method for calculating the galaxy and random catalogues are presented in \citet{Reidetal:2016}, 
%Full details of the catalogues are provided in \citet{Reidetal:2016}, 
%and we do not replicate this here.

%BOSS is designed to obtain 
%spectra and redshifts of $\sim$1.35 million galaxies 
%(together with 160\,000 quasars and approximately 100\,000 ancillary targets)
%selected from the SDSS imaging.
%The SDSS-I/II data \citep{York et al. 2000}

%CMASS and LOWZ\,

%We use data from the Sloan Digital Sky Survey \citep[SDSS; ][]{2000AJ....120.1579Y}. 
%SDSS has mapped over one quarter of the sky in five photometric bands down to a limiting magnitude of $r\sim 22.5$. 
%The photometric data is reduced and from it are selected targets for followup spectroscopy. 
%The spectroscopic survey, known as the Baryon Oscillation Spectroscopic Survey (BOSS), 
%is charged with obtaining spectra for 1.35 million galaxies over a 10,000 square degree footprint.

\begin{figure*}
   \centering{
   \includegraphics[width=19cm]{fig2.eps}
   }
   \caption{\label{fig_nbar}
      The redshift density distribution of the BOSS DR12 galaxy samples, assuming a $\Lambda$CDM cosmology with $\Omega_m=0.31$.
      The blue and green solid histograms show the distribution of LOWZ and CMASS galaxies respectively. 
      The vertical dashed lines define the six redshift bins that are used to cut the samples.
      Their redshift ranges are listed.
      The number of LOWZ (CMASS) galaxies in the three low (high) redshift bins are presented in the brackets.
      }
\end{figure*}

Figure \ref{fig_radec} presents the sky coverage of the BOSS DR12 samples used in this analysis. 
%The light grey shaded region shows the expected total footprint of the BOSS survey. 
%Colors indicate the spectroscopic completeness.
The mean completeness is 97.2\% for the LOWZ sample, in the upper panels, and 98.8\% for the CMASS sample shown in the lower panels.
   %Each patch of different color corresponds to a plate,
   %with the color determined by the completeness of that plate..
Figure \ref{fig_nbar} shows the galaxy number density of the two samples.
In this analysis we use 361\,759 LOWZ galaxies at $0.15<z <0.43$ and 
771\,567 CMASS galaxies at $0.43< z < 0.693$.
%in total galaxies.
We split the galaxies into six redshift bins: 
three bins in LOWZ ($0.150<z_1<0.274<z_2<0.351<z_3<0.430$), 
and three in CMASS ($0.430<z_4<0.511<z_5<0.572<z_6<0.693$), 
as illustrated in Figure \ref{fig_nbar}.

\begin{figure*}
   \centering{
   \includegraphics[width=19cm]{fig3.eps}
   }
   \caption{\label{fig_mock}
      Creation of galaxy samples for BOSS, from the HR3 or HR4 simulations.
      From an all-sky mock survey,
       we are able to produce four sets of NGC samples or eight sets of SGC samples with non-overlapping sky coverage.
      The individual points are the right ascension and declination of 1\% galaxies drawn from the CMASS samples.
      }
\end{figure*}

Each spectroscopically observed galaxy is assigned several weights to account for observational effects. 
The galaxy weights are constructed from three distinct effects.
%redshift failure, $w_{fail}$, minimum variance, $w_{FKP}$, and angular variation, $w_{sys}$. 
%These weights are described in more detail in \cite{2012MNRAS.427.3435A} and \cite{2012MNRAS.424..564R}. 
Firstly, galaxies lacking a redshift due to fiber collisions 
\footnote{Fiber collisions occur when two objects are close enough together such that two fibers cannot be placed.
In BOSS, the collision radius is 62 $''$.}
or inadequate spectral information are accounted for by reweighting
the nearest galaxy by a weight $w_{\rm fail}=(1+n)$, 
where $n$ is the number of close neighbors without a measured redshift. 
Secondly, all galaxies are assigned `FKP' weights \citep{1994ApJ...426...23F}
%as a function of redshift depending on the number density.
as a function of number density,
to optimize the clustering measurements in the face of shot-noise and cosmic variance.
%according to,
%\begin{equation}
%w^i_{FKP}=\frac{1}{1+n_i(z)P_0},
%\end{equation}
%where $n_i(z)$ is the comoving space density at redshift $z$ and $P_0 \sim P(k=0.1~{\rm $h^{-1}$Mpc}) \sim 2\times 10^{4}h^{-3}{\rm Mpc^3}$, 
%as in \cite{2012MNRAS.427.3435A}. 
The third weight corrects for angular variations of survey completeness and the systematics 
related to the angular variations in stellar density that make detection of
galaxies difficult in over-crowded regions of the sky. %\citep{2012MNRAS.424..564R}. 
The total weight for each galaxy is the product of these three weights, $w_{\rm total}=w_{\rm fail}w_{\rm FKP}w_{\rm sys}$.

For the statistical analyses, 
random catalogues having the same angular and redshift selection functions as the data 
are provided along with the data \citep{Reidetal:2016}.
%Each random point is assigned with a redshift of measured galaxy randomly drawed from galaxies.
%and a weight given by the $w_{\rm tot}$ of the measured galaxy.
The random points are also weighted but they only include the minimum variance `FKP' weight. 
%50 times as many random points as we have galaxies

\section{The Mock Galaxy Data}
\label{sec:mocks}
%We use HR3 and HR4...
%We use HR4 J08 ...

%Shape of $\\xi$ measured in HR4 very similar to data...
%Shape of

For LSS studies mock survey samples created from simulations are crucial
for the correction of systematics and covariance estimation.
The Horizon Run simulations are a suite of large volume N-body simulations that 
have resolutions and volumes capable of accurately reproducing the observational statistics of the current major redshift surveys like 
SDSS-III BOSS \citep{park 2005,2009ApJ...701.1547K,horizonrun}.
The HR3 \citep{horizonrun} and HR4 \citep{hr4} simulations, and the MultiDark-Patchy mock catalogues \citep{MDPATCHY} are used in our analysis.

From the HR3 and HR4 simulations we have generated all-sky light cone mock galaxy catalogues.
The all-sky spherical mocks are then incorporated with the same fiber collision effect, 
angular masks, and radial selection function with the real observational data,
creating mock surveys of BOSS DR12.

We impose a minimum mass limit varying along with redshift to match the radial density of BOSS samples.
The galaxies of the BOSS DR12 samples do not cleanly distribute above some particular mass boundary;
they always have a fuzzy, blur boundary extending to relatively small values (as an example, see Figure 3 of 
Parihar et al. 2014). %DANGEROUS
%rather than shaprly lying above a certain mass cut, 
Galaxies in the mock samples are systematically more massive than those from observations;
We will discuss the effect of this discrepancy in Sec. \ref{sec:caveats}.

\subsection{Horizon Run 4}

The HR4 simulation  \citep{hr4} used a box size $L={3150}$ $h^{-1}$Mpc, 
and $N=6300^3$ particles.  
The simulation used the second order Lagrangian perturbation theory (2LPT) initial conditions at $z_{i}=100$ and a WMAP5 cosmology
$(\Omega_{b},\Omega_{m},\Omega_\Lambda,h,\sigma_8,n_s)$  = (0.044, 0.26, 0.74, 0.72, 0.79, 0.96) \citep[]{komatsu 2011}, 
yielding a particle mass of $m_{p} \simeq 9.02 \times 10^9 \hMsun$.
This starting redshift, combined  with 2LPT initial conditions, ensures an accurate mass function and power spectrum \citep{2014NewA...30...79L}.

Mock galaxy samples are produced from the HR4 simulation by using a modified version of the one-to-one correspondence scheme \citep{hong2016}. 
The most bound member particles (MBPs) of simulated halos are adopted as the tracer of galaxies rather than the subhalos,
and the merger timescale is taken into account in the lifetime of merged halos.
We built the merger trees of simulated halos by tracking their MBPs from $z = 12$ to 0.
When a merger event occurs, we calculate the merger timescale described in \cite{jiang2008} (hereafter J08)
to determine when a satellite galaxy is completely disrupted.
%We modeled the position and the velocity of a galaxy from the position and velocity of its corresponding MBP.
By using the abundance matching, 
we modeled the luminosity of a central/isolated galaxies from their current mass
and of satellite galaxies 
from their mass at the time of infall.

\cite{hong2016} compared the 2pCF of our mock galaxy sample at $z = 0$ to the SDSS DR7 volume-limited galaxy sample \citep{zehavi2011}.
%When a typical subhalo-galaxy correspondence scheme is applied, 
%the 2pCF from our simulation is smaller than the observation and does not show a proper Finger-of-God (FOG) feature in our simulation resolution. 
%We found that %the %2pCF of our galaxy sample agrees well with the observation.
The simulated 2pCF shows a similar finger of god (FOG) feature \citep{FOG} as the observation in the contour map, 
and the projected 2pCF agrees with the observation within 1$\sigma$ deviation on scales greater than 1 ${h^{-1}}$Mpc.

%As will be introduced in the next section, 
The HR4 simulation yield one all-sky light cone mock galaxy catalogue reaching $r=3\,150$ ${h^{-1}}$Mpc.
As shown in Figure \ref{fig_mock},
from one all-sky survey, 
we are able to create four sets of non-overlapping north Galactic cap (NGC) samples for CMASS and LOWZ, 
or eight sets of non-overlapping south Galactic cap (SGC) samples.
In this paper we use these simulated galaxies for the estimation of the systematics in the 2pCF of the observed galaxies.
%We create four north

\begin{figure*}
   \centering{
   \includegraphics[height=8cm]{fig4_0.eps}
   \includegraphics[height=8cm]{fig4_1.eps}
   %\includegraphics[height=7cm]{FVol.eps}
   %\includegraphics[height=8cm]{xy.eps}
   %\includegraphics[height=8cm]{smu.eps}
   }
   \caption{\label{fig_xy}
   %Apparent distortion of objects in four wrongly assumed cosmologies, assuming a true cosmology of .
   The redshift dependence of the AP effect in four incorrect cosmologies,
   assuming that the true cosmology is $\Omega_m=0.31$, $w=-1$.
   The left panel shows the apparent distortion of four perfect squares,
   measured by an observer located at the origin.
   The apparently distorted shapes are plotted in red solid lines.
   The underlying true shapes are indicated in blue dashed lines.
   The right panel displays the degree of the shape distortion, as described by Equations (\ref{eq:stretch}).
   The BOSS DR12 galaxies used in our analysis have a redshift coverage of $0.15 < z < 0.693$ (marked 
   by the gray vertical lines). Clearly, the magnitude of the shape distortion due to AP changes with redshift.
   %measured by an observer located at the origin.
   %For reference, blue dashed squares show their shapes and positions in the true cosmology.
   }
\end{figure*}

\subsection{Horizon Run 3}
%In our analysis we also mock surveys constructed from one of the Horizon Run simulations, HR3.

As in HR4, HR3 also adopts a flat-space $\Lambda$CDM cosmology with the WMAP 5 year parameters.
The simulation was made within a cube of volume $(10.815\  h^{-1}{\rm{Gpc}})^3$
using $7120^3$ particles with particle mass of $1.25\times 10^{11}$\hMsun.
The simulations were integrated from $z=27$ and reached $z=0$ after making $N_{\rm step}=600$ global timesteps.
The collapsed high-density regions were identified using the Friend-of-Friend algorithm with the linking length of 0.2 times the mean particle separation.
The physically self-bound (PSB) subhalos that are gravitationally self-bound and tidally stable \citep{kim and park 2006} 
are identified and used as galaxy proxies.
The PSB halo finder is a group-finding algorithm that can efficiently identify halos located even in crowded regions. 
This method combines two physical criteria such as the tidal radius of a halo and the total energy of each particle to find member particles.
The group velocity of member particles is adopted as the peculiar velocity of each PSB subhalo.

%This provides a substantial increase in the similarity between simulation and observational data,
%as these dark matter subhalos are sites for galaxy formation.
%LRG (Xiao: is it OK to change all the ``LRG'' to ``galaxy''?) formation.

%.

%To simulate the SDSS survey,
%HR3 places 27 observers evenly within its cubical volume and allows
%each observer to survey out to a redshift of 0.7
We generate multiple BOSS-like surveys by placing 27 evenly spaced
observers within the HR3 cubical volume and allowing each to 
survey out to a redshift of 0.7
\footnote{In the analysis we choose the maximal redshift as 0.693 rather than 0.7. 
%The lightcone data created from HR3 simulations have cosmological redshift limit of $z<0.7$. 
The outer boundary of the mock survey becomes fuzzy due to the peculiar velocity effect 
on the galaxy redshifts (Eq. (\ref{eq:zvpeu})).
A population of galaxies, that are expected to enter the $z<0.7$ region from the outside, is missing.
%(these $z>0.7$ galaxies have a peculiar velocity toward us and 
%their observed redshfits become lower than 0.7).
To avoid this problem we set the maximal redshift at 0.693, 
23.3 $h^{-1}{\rm Mpc}$ away from $z=0.7$.}.
%creating 27 samples of independent, non-overlapping spherical regions.
%From the 27 spherical light cone `galaxy' catalogues, 
%we created 72 non-overlapping survey samples 
Each of these 27 independent and non-overlapping spherical 
regions are further cut up into the required SDSS survey geometry,
resulting in 72 non-overlapping light-cone galaxy catalogues 
\footnote{Using the 27 spherical light cones, we create 72 sets of NGC samples from 18 light cones, 
and 72 sets of SGC samples from the other 9 light cones.}
simulating BOSS DR12 within the redshift range of $0.15< z< 0.693$.
%As will be described in the next section, 
These mock surveys are used to estimate the covariance of the 2pCF in our analysis.

\subsection{MultiDark-Patchy Mocks}

In additional to the HR3 mock surveys, 
we also use 2\,000 MultiDark-Patchy mock catalogues \citep{Kitaura2014,MDPATCHY} to estimate the covariance matrix.

The MultiDark-Pathy mocks were produced using approximate gravity solvers 
and analytical-statistical biasing models.
They have been calibrated to a BigMultiDark N-body simulation \citep{K2014}, which 
%was performed using {\texttt {GADGET-2}} \citep{Springel2005} with 
uses $3\,840^3$ particles in a volume of $(2.5h^{-1}\rm Gpc)^3$
assuming a $\Lambda$CDM cosmology with
 $\Omega_m = 0.307115$, $\Omega_b = 0.048206$, $\sigma_8 = 0.8288$, $n_s = 0.9611$, and $H_0 = 67.77 {\rm km}\ s^{-1} {\rm Mpc}^{-1}$.
Halo abundance matching is used to reproduce the two and three-point 
clustering measurements of BOSS \citep{RT2015}.
The redshift evolution of the biased tracers 
is matched to observations by applying the 
aforementioned technique in a number of redshift bins,
with the resulting mock catalogues being combined together 
to form a contiguous lightcone.
%To simulate the redshift evolution in the observational data,
%the technique is applied at different redshift bins, 
%and then combined into light cones.
%The selection effects and survey mask of the BOSS survey are applied.

The resulting MultiDark-Patchy mock surveys reproduce the number density, 
selection function, survey geometry of the BOSS DR12 catalogues.
The 2pCF of the observational data is reproduced down to a few Mpc scales, in general within $1\sigma$ \citep{MDPATCHY}.
The MultiDark-Patchy mocks have been adopted for 
statistical analysis of BOSS data
in a series of works (see \cite{Alam2016} and references therein).
This large set of mock catalogues enabled us to perform 
a robust error estimation of the 2pCFs measured from the BOSS DR12 galaxies.

\section{AP Effect in Incorrect Cosmologies}
\label{sec:APeffect}

%Considering we are Let us consider an object in the Universe with certain size and shape.
%Its observed redshift span $\Delta z$ and angular size $\Delta \theta$ are related with the comoving sizes by
This section illustrates the AP effect when an incorrect cosmological model is used to calculate the distances of galaxies. Similar illustrations have been provided in \cite{Li2014,Li2015}.

Suppose that we probe the shape and volume of an object in the Universe,
which spans $\Delta z$ in redshift and $\Delta \theta$ in angle.
Its comoving sizes in the radial and transverse directions are given by
\begin{eqnarray}\label{eq:distance}
& &\Delta r_{\parallel} = \frac{c}{H(z)}\Delta z,\nonumber\\
& &\Delta r_{\bot}=(1+z)D_A(z)\Delta \theta,
\end{eqnarray}
where $H$ is the Hubble parameter and $D_A$ the proper angular diameter distance.
In the particular case of a flat Universe with constant dark energy EoS, they take the forms of
\begin{eqnarray}\label{eq:HDA}
& &H(z) = H_0\sqrt{\Omega_ma^{-3}+(1-\Omega_m)a^{-3(1+w)}},\nonumber\\
& &D_A(z) = \frac{c}{1+z}r(z)=\frac{c}{1+z}\int_0^z \frac{dz^\prime}{H(z^\prime)},
\end{eqnarray}
where $a=1/(1+z)$ is the cosmic scale factor,
$H_0$ is the present value of Hubble parameter and $r(z)$ is the comoving distance.

In case we adopted an incorrect set of cosmological parameters in Equation (\ref{eq:HDA}),
the inferred $\Delta r_{\parallel}$ and $\Delta r_{\bot}$ are also incorrect,
resulting in distorted shape (AP effect) and wrongly estimated volume (volume effect).
The degree of variations in shape and volume are
\begin{equation}\label{eq:stretch}
 %{\rm Degree\ of\ LOS\ stretch\equiv}
 %{\rm rat}_{\rm LOS\ stretch}\equiv
 \frac{[\Delta r_{\parallel}/\Delta r_{\perp}]_{\rm wrong}}{[\Delta r_{\parallel}/\Delta r_{\perp}]_{\rm true}} =
  \frac{[D_A(z)H(z)]_{\rm true}}{[D_A(z)H(z)]_{\rm wrong}} 
\end{equation}
\begin{equation}\label{eq:volume}
 %{\rm Degree\ of\ volume\ magnification \equiv}
 %{\rm rat}_{\rm volume\ mag}\equiv
 \frac{{\rm Volume}_{\rm wrong}}{{\rm Volume}_{\rm true}}
 = \frac{[\Delta r_{\parallel}(\Delta r_{\perp})^{2}]_{\rm wrong}}{[\Delta r_{\parallel}(\Delta r_{\perp})^{2}]_{\rm true}}
 = \frac{[D_A(z)^2/H(z)]_{\rm wrong}}{[D_A(z)^2 / H(z)]_{\rm true}},
\end{equation}
where ``true'' and ``wrong'' denote the values of quantities in the true cosmology and incorrectly assumed cosmology.
From the AP and volume effects, we can constrain  $D_A(z)H(z)$ and $D_A(z)^2 / H(z)$, respectively.

The apparent distortion of objects due to incorrect cosmological parameters is illustrated in the left panel of Figure \ref{fig_xy}.
Suppose that the true cosmology is a flat $\Lambda$CDM model with the present density parameter $\Omega_m=0.31$
and standard dark energy EoS $w=-1$ \citep[the best $\Lambda$CDM model determined by Planck 2015 results][]{Planck2015}.
%(the best $\Lambda$CDM model determined by Planck 2015 results \citep{Planck2015}).
If we distributed three square objects at various distances from 500 to 2,000 $h^{-1}$Mpc,
and had an observer located at the origin measure their redshifts and compute their positions and shapes 
using redshift-distance relations of four incorrect cosmologies:
\begin{enumerate}[label=(\roman*)]
\item $\Omega_m=0.4$, $w=-1$,
\item $\Omega_m=0.1$, $w=-1$,
\item $\Omega_m=0.31$, $w=-0.3$,
\item $\Omega_m=0.31$, $w=-2.5$,
\end{enumerate}
the mismatch between the true and assumed cosmology will cause the shapes of the squares appear distorted.
In the cosmological models (ii) and (iv) the squares are stretched in the line of sight (LOS) direction (hereafter ``LOS shape stretch''),
%and magnification of the volume (hereafter ``volume magnification''), 
while in the models (i) and (iii) we see opposite effects of LOS shape compression.

The right panel of Figure \ref{fig_xy} presents the degree of shape distortion as a function of redshift. 
In cosmology (i) and (iii), $\frac{[D_A(z)H(z)]_{\rm true}}{[D_A(z)H(z)]_{\rm wrong}}$ have values less than 1, 
indicating LOS shape compression,
while in cosmology (ii) the curve lies above 1, 
corresponding to an LOS shape stretch.
The effect in cosmology (iv) is more subtle. 
There is a transition from LOS shape stretch to compression at $z \approx 0.65$.

More importantly, Figure \ref{fig_xy} highlights the redshift dependence of the AP effect. 
If the conversion of redshift to the comoving distance was correctly made,
there would be no shape distortion at any redshift.
Conversely, the four cases with incorrectly chosen cosmological parameters illustrated 
in Figure \ref{fig_xy} 
show characteristic dependence of the shape distortion on redshift.
We measure the 2pCF of BOSS DR12 galaxies in various redshift bins
and constrain cosmological parameters using the redshift evolution
of the anisotropic clustering signal.
%Our method utilizes this redshift dependence to constrain cosmological parameters
%governing the expansion history of the Universe.
%For example, in cosmology (i), %with $\Omega_m=0.4$, 
%the LOS shape stretch become more significant with increasing redshift.
%In cosmology (iv), not only the magnitude of the effect evolves with redshift,
%but there is also a turnover from LOS shape stretch to compression.
%The magnitude of anisotropies produced by AP evolves with redshift.
%We can search for such pattern in the LSS statistic to see whether there exists distortions produced by AP effect,
%thus determine the correctness of the cosmological model.% adopted for the computation of $r(z)$.

\section{Methodology}\label{sec:methodology}

We measure the 2pCF in redshift bins of BOSS DR12 galaxies and 
determine cosmological parameters by examining the redshift evolution of clustering anisotropy.
Mock survey samples are used to correct the results for the systematics and to estimate the covariance.
%Our procedure is as follows.

\subsection{Grid of cosmology parameters}

The observed coordinates ({\it RA, Dec, z}) of galaxies
need to be converted to comoving coordinates ({\it x, y, z}) for the 2pCF analysis.
The dependence of clustering anisotropy on cosmology enters through the conversion from redshift to comoving distance,
i.e. the distance-redshift relation $r(z)$.
We consider the case of a flat Universe dominated by matter and dark energy,
so our $r(z)$ is governed by two parameters, $\Omega_m$ and $w$, as presented in Equation (\ref{eq:HDA})	.

In constraining these two parameters we examine the parameter space of 
$0.06\leq \Omega_m\leq 0.41$ and $-1.5 \leq w \leq -0.4$ with intervals of 
$\delta \Omega_m = 0.005$ and $\delta w = 0.025$,
forming a 71$\times$45 grid.
%This coverage and step size shall be enough for us to determine the 95\% confidence level (CL) region with satisfactory precision.
For each set of ($\Omega_m$, $w$), 
the comoving coordinates of all galaxies are computed, 
%the 2pCF of these galaxies in six redshift bins are measured,
%and a $\chi^2$ value is then obtained by requiring least redshift evolution of anisotropy.
%This enables us to infer the values and underlying distributions of $\Omega_m$ and $w$ through Bayesian analysis.
and the 2pCF is ready to be calculated.

\begin{figure*}
   \centering{
   \includegraphics[width=14cm]{fig5.eps}
   %\includegraphics[width=14cm]{Tpcf--contour.eps}
   }
   \caption{
    \label{fig_2pcfcon} 
    2D contour map of measured $\xi$ as a function of $\mu$ and $s$, from the six redshift bins of LOWZ and CMASS samples 
      in the cosmology of $\Omega_m=0.31$ $\Lambda$CDM model.
    The black dashed lines mark the scales 6\ $h^{-1}$Mpc $\leq s\leq$ 40\ $h^{-1}$Mpc.
    %The correlation functions have rather large values on small sales such as $s=5$ $h^{-1}$Mpc,
    %  and monotonically decreases to smaller values on larger scales due to weaker clustering.
    The contour lines are not horizontal due to the effects of peculiar velocity.
    The FOG and Kaiser effects clearly manifest themselves through the tilting of contour 
     lines where $1-\mu \rightarrow 0$ and $1-\mu \gtrsim0.1$, respectively.
    The six contour maps have rather similar appearance, implying small redshift evolution of $\xi$.
   }
      %The redshift density distribution of the BOSS DR12 galaxy samples, assuming a $\Lambda$CDM cosmology with $\Omega_m=0.31$.
      %The blue and green solid histograms show the distribution of LOWZ and CMASS galaxies respectively. 
      %The vertical dashed lines define the 6 redshift bins that are used to cut the samples.   }
\end{figure*}

\subsection{Measuring the correlation function}

%We probe the Alcock-Paczynski effects using the 2pCF. 
%The 2pCF is a mature statistic in cosmology and its optimal estimation considers minimal variance 
%while dealing with complicated masks and selection functions. 
%The most commonly adopted formulation is that of the 
We adopt the Landy-Szalay estimator~\citep{1993ApJ...412...64L} to calculate the 2pCF,
\begin{equation}
\xi(s,\mu)=\frac{DD-2DR+RR}{RR}\ ,
\end{equation}
where $DD$ is the number of galaxy--galaxy pairs, 
$DR$ the number of galaxy-random pairs, 
and $RR$ is the number of random--random pairs, 
all separated by a distance defined by $s\pm\Delta s$ and $\mu\pm\Delta\mu$, 
where $s$ is the distance between the pair and $\mu=\cos(\theta)$, 
with $\theta$ being the angle between the line joining the pair of galaxies and the LOS direction to the target galaxy. 
This statistic captures the anisotropy of the clustering signal.

The random catalogue consists of unclustered points whose number density in redshift space mimics the radial selection function of the observational data. 
In an effort to reduce the statistical variance of the estimator we use 50 times as many random points as we have galaxies.
The galaxies and random points are weighted as described in Sec. \ref{sec:data}.

Figure \ref{fig_2pcfcon} shows the 2D contour of measured $\xi$ as a function of $\mu$ and $s$,
from the six redshift bins of LOWZ and CMASS samples 
in the cosmology of $\Omega_m=0.31$ $\Lambda$CDM model.
%The correlation functions have rather large values on small sales such as $s=5$ $h^{-1}$Mpc,
%and monotonically decrease to smaller values on larger scales due to weaker clustering.
Due to the peculiar velocity effect, the contour lines are not horizontal.
The FOG \citep{FOG} and Kaiser \citep{Kaiser1987} effects 
clearly manifest themselves through the tilting of contour lines in regions of $\mu \rightarrow 1$ and $1-\mu \gtrsim0.1$, respectively.
A visual inspection of the contour maps from the six redshift bins 
reveals that they all have a similar appearance,
implying small redshift evolution of $\xi$.

\subsection{Probing the anisotropy through 2pCF}

The 2pCF is measured as a function of the separation $s$ and the angular direction $\mu$.
To probe the anisotropy we are more interested in the dependence of the 2pCF on $\mu$.
We follow the procedure of \cite{Li2015} and integrate the $\xi$ over the interval $s_{\rm max} \leq s \leq s_{\rm min}$.
We evaluate
\begin{equation}\label{eq:xideltas}
\xi_{\Delta s} (\mu) \equiv \int_{s_{\rm min}}^{s_{\rm max}} \xi (s,\mu)\ ds.%,\ \ \ {\rm at\ particular\ binned\ direction\ }\mu_i
\end{equation}
The integration is limited at both small and large scales.
At small scales the value of $\xi$ is seriously affected by the FOG effect \citep{FOG}
which depends on the galaxies bias.
This may introduce a redshift evolution in $\xi_{\Delta s}(\mu)$ that is relatively difficult to model.
At large scales the measurement is dominated by noise due to poor statistics.
\cite{Li2015} found that $s_{\rm min}=6-10$ $h^{-1}$Mpc and $s_{\rm max}=40-70$ $h^{-1}$Mpc are reasonable choices 
which provide consistent, tight and unbiased constraints on cosmological parameters.
In this analysis we choose $s_{\rm min}=6$ $h^{-1}$Mpc and $s_{\rm max}=40$ $h^{-1}$Mpc.

The redshift evolution of the bias of observed galaxies leads to redshift evolution of the strength of clustering,
which is difficult to accurately model.
We mitigate this systematic uncertainty by relying on the shape of $\xi_{\Delta s}(\mu)$, rather than its amplitude,
\begin{equation}\label{eq:norm}
 \hat\xi_{\Delta s}(\mu) \equiv \frac{\xi_{\Delta s}(\mu)}{\int_{0}^{\mu_{\rm max}}\xi_{\Delta s}(\mu)\ d\mu}.
\end{equation}
We impose a cut $\mu<\mu_{\rm max}$ to reduce the fiber collision and FOG effects which are stronger toward the LOS ($\mu\rightarrow1$) direction.

\begin{figure*}
   \centering{
   \includegraphics[width=16cm]{fig6.eps}
   }
   \caption{\label{fig_datamock}
   %Apparent distortion of objects in four wrongly assumed cosmologies, assuming a true cosmology of .
   $\hat\xi_{\Delta s}(\mu)$ measured from BOSS DR12 CMASS NGC sample 
    (consists of $\approx 565\,000$ galaxies at $0.15 < z < 0.693$)
    and one realization from the HR4 N-body simulation, in the WMAP5 cosmology.
   The lower panel shows the difference between the results of observational data and mock galaxies.
   $\hat\xi_{\Delta s}(\mu)$ are obtained by integrating $\xi (s,\mu)$ within the range {\rm 6\ $h^{-1}$Mpc}$\leq s\leq${\rm 40\ $h^{-1}$Mpc} 
      and normalizing the amplitude, 
    i.e., Eq. (\ref{eq:xideltas}) and Eq. (\ref{eq:norm}).
   To produce a clear view of the FOG effect, we split the angular range of $0.01\leq \mu \leq 1$ into as many as 40 bins.
   Using the HR4 mock galaxies, the enhancement near $\theta=0^\circ$ caused by the FOG effect
    and the tilt of the shape in $20^\circ\lesssim\theta\lesssim90^\circ$ 
    as a result of the large-scale flow,
    are all very well reproduced.
%    Thw lo
   This verifies the ability of our galaxies assignment method \citep{hong2016} 
    to reproduce the properties of galaxy distributions from large scale surveys.
   %Conversely, the HR3 PSB halo mock can not 
   %reproduce the shape of $\hat\xi_{\Delta s}(\mu)$.
   We use the HR4 mock galaxies to correct the systematics effects produced by the RSD.
   %The 72 sets of PSB mocks from HR3 are used to compute covariance.
   %measured by an observer located at the origin.
   %For reference, blue dashed squares show their shapes and positions in the true cosmology.
   }
\end{figure*}

The clustering properties may be affected by various properties of the galaxy sample, 
such as, the mass, morphology, color, concentration. 
In our simulation, using the merger tree, 
we identify ``galaxies'', therefore we only use the galaxy mass building history to simulate BOSS galaxies. 
Therefore, it is necessary for us to test if our mock galaxies can accurately 
reproduce the $\hat\xi_{\Delta s}(\mu)$ of observed galaxies.

%The clustering properties may be affected by the redshift evolution of properties of the galaxy sample, 
%such as the mass, morphology, color, concentration, and so on. 
%In our simulation, using the merger tree, we identify 'galaxies' so that we only use the galaxy mass to simulate BOSS galaxies. Therefore, it was necessary for us to test if our mock galaxies can accurately reproduce the shape of $\xi_{\Delta s}(\mu)$ of observed galaxies.

%As shown by Figure 6, the mock galaxies from our HR4 simulation can well reproduce the 
%$\hat\xi_{\Delta s}(\mu)$ of the observed galaxies.
Figure \ref{fig_datamock}  compares the shape of $\hat\xi_{\Delta s}(\mu)$ measured from observational data and mock survey samples.
It is clear that $\hat \xi_{\Delta s}(\mu)$ from mock galaxies identified in the HR4 simulation (green dotted line) agrees well with the observation.
%The HR4 galaxy mock can well reproduce the result from observational measurement.
The enhancement near $\theta=0^\circ$ is caused by the FOG effect,
and the characteristic shape in $20^\circ\lesssim\theta\lesssim90^\circ$ 
produced from the large-scale flow
are all very well reproduced.
This result verifies the ability of our mock galaxies to reproduce the clustering properties of the observed galaxies.
The small overestimate (underestimate) of $\hat\xi_{\Delta s}$ at large (small) $\mu$ could be due to 
that our mocks galaxies are more massive than those in the observations.
%methodology. (AMTB: need some good expression; need consult SW)
%Conversely, the HR3 PSB halo galaxies do not accurately reproduce the observations.
We use the HR4 galaxy mocks to correct the systematics.
%The HR3 PSB mock galaxies are used to estimate the covariance of 2pCF since 72 mock survey samples are available.

\begin{figure*}
   \centering{
   \includegraphics[width=16cm]{fig7.eps}
   %\includegraphics[height=9cm]{Tpcf-sys.eps}
   }
   \caption{\label{fig_sys}
   %Apparent distortion of objects in four wrongly assumed cosmologies, assuming a true cosmology of .
   Systematics in $\delta \hat \xi_{\Delta s}$, measured from the HR4 mock galaxy samples.
   The redshift evolution of RSD effect and properties of samples can lead to non-zero values of $\delta \hat\xi_{\Delta s}(z_i,z_1)$.
   For the 1st to 5th redshift bins, $\delta\hat\xi_{\Delta s, \rm sys}(z_i,z_1)\lesssim0.02$,
    indicating a small redshift evolution of the RSD effect and properties of galaxies.
   For the 6th redshift bin, the values of $\delta\hat\xi_{\Delta s, \rm sys}(z_6,z_1)$ are relatively large,
   because galaxies in that highest redshift bin are significantly more massive than those at lower redshifts.
   % so the measured $\hat\xi_{\Delta s}(\mu)$ has larger (smaller) values at $\mu\rightarrow1$ ($\mu\rightarrow0$) 
   % compared with the others.
   See Sec. \ref{sec:syscor} for details.
   %The values are estimated from the HR4 mock galaxies. % and subtract its contribution.
   }
\end{figure*}

%It is impossible to probe $\hat\xi_{\Delta s}(\mu)$ as a continuous function with infinite degrees of freedom. 
We divide the full angular range $0\leq\mu\leq\mu_{\rm max}$ into $n_{\mu}$ bins and measure its value in each bin.
Since we are free to choose $\mu_{\rm max}$ and $n_{\mu}$,
they are varied to optimize the S/N of our results.
This topic will be discussed in Sec. \ref{sec:binningscheme}.

\subsection{Characterizing the redshift evolution}

As shown in Figure \ref{fig_nbar}, we split the BOSS DR12 galaxies into six redshift bins, three in LOWZ and three in CMASS.
To study the redshift evolution of the clustering anisotropy 
we use the {\it first redshift bin} as the reference and compare the measurements in other bins with that in the first.
We define
\begin{equation} \label{eq:deltahatxi}
\delta \hat\xi_{\Delta s}(z_i,z_1,\mu_j)\ \equiv\ \hat\xi_{\Delta s}(z_i,\mu_j) - \hat\xi_{\Delta s}(z_1,\mu_j)
\end{equation}
where $\hat\xi_{\Delta s}(z_i,\mu_j)$ is $\hat\xi_{\Delta s}$ measured in the $i$th redshift bin and $j$th $\mu$ bin,
where $1\leq i \leq 6$ and $1\leq j \leq n_{\mu}$.
To characterize the shape of the curve well $n_\mu \gtrsim5$ is required.

\subsection{Correction for systematics}\label{sec:syscor}

Other than the AP effect, there are additional effects 
which may produce redshift-dependent anisotropy and affect the results.

The observational artifacts, such as fiber collisions, redshift failures, 
and the non-cosmological density fluctuations induced by stellar density and seeing,
are accounted for in the galaxy weights \citep{Reidetal:2016}.
Fiber collisions and redshift failures may affect the value of $\hat\xi(\mu)$ in the region close to LOS;
%We correct them by reweighting galaxies, include fiber collisions in the construction of mock surveys,
we abandon the angular region of $1-\mu<0.01$, 
to avoid possible systematics (see Appendix \ref{sec:RBtest} for more discussion).

%The SGC catalogues have higher target density than NGC and 
%thus a higher galaxy number density, known as the north/south asymmetry.
The non-contiguous NGC and SGC are less well cross-calibrated with respect to each other 
than they are internally calibrated \citep{Schlafly2010,SF2011,Parejko2013}.
We construct the NGC and SGC mock surveys separately to avoid possible systematics.
The 2pCF analysis is also carried out for the NGC and SGC independently.
%Also, in this analysis we only look at the radial evolution of clustering properties. 
The result should be robust as long as each catalogue is well calibrated internally.

%The variation in the density of catalogues is not expected to have large effect on our analysis.

%The redshift evolution of AP effect, RSD effect and properties of samples all may lead to non-zero values of $\delta \hat\xi_{\Delta s}$.
%To measure the signal from the redshift evolution of the AP effect,
%we estimate the value of $\delta \hat\xi_{\Delta s}$ from the other effects and subtract their contribution
%(hereafter $\delta\hat\xi_{\Delta s, \rm sys}$) from the total variation.

The apparent anisotropy introduced by RSD is, 
although greatly reduced by focusing on the redshift evolution, 
still the most significant systematic effect.

We estimate the value of $\delta \hat\xi_{\Delta s}$ from the systematic effects and subtract their contribution
(hereafter $\delta\hat\xi_{\Delta s, \rm sys}$) from the total variation.
The quantity $\delta\hat\xi_{\Delta s, \rm sys}$ is estimated from the HR4 mock galaxies.
The mock survey sample imitates the SDSS BOSS sample by mimicking
the survey as close as possible and includes past light cone effects.
The observational systematics such as the RSD, survey geometry, and shot noise
are included in the exactly same way as the observation.
The peculiar velocity perturbs the observed redshift through the relation
\begin{equation}\label{eq:zvpeu}
\Delta z = (1+z) \frac{v_{{\rm LOS}}}{c},
\end{equation}
where $v_{\rm LOS}$ is the LOS component of the peculiar velocity of galaxies.
The redshift evolution of galaxy peculiar velocities, 
resulting from growth of structure,
causes the anisotropy produced by RSD to have a small redshift evolution; 
this is the main source of systematic uncertainty in our results.

We take the HR4 mock galaxy samples and compute $r(z)$ of galaxies in the cosmology under which the simulation is based.
In this case there is no AP effect. 
Thus, the measured $\delta \hat\xi_{\Delta s}$ are the redshift evolution purely created by systematics effects.
They are adopted as the estimation of $\delta\hat\xi_{\Delta s, \rm sys}$,
and the results are illustrated in Figure \ref{fig_sys}. %shows $\delta\hat\xi_{\Delta s, \rm sys}(z_i,z_1)$ measured from the HR4 mock galaxy samples.
%Measurements of $\hat\xi_{\Delta s}$ in the 2th to 6th redshift bins are compared with that in the first bin.

For the 1st to 5th redshift bins, $\delta\hat\xi_{\Delta s, \rm sys}(z_i,z_1)\lesssim0.02$,
indicating a small redshift evolution of the RSD effect and properties of galaxies.
The only exception is the 6th redshift bin where the values of $\delta\hat\xi_{\Delta s, \rm sys}(z_6,z_1)$ are relatively large.
The reason for the large values is that the galaxies in that highest redshift bin are significantly more massive than those at lower redshifts,
so the measured high redshift $\hat\xi_{\Delta s}(\mu)$ has larger (smaller) values at $\mu\rightarrow1$ ($\mu\rightarrow0$) 
compared with the others
(an investigation of the dependence of $\hat\xi_{\Delta s}(\mu)$ on galaxy mass is provided in Sec. \ref{sec:caveats}).

%This should be the reason why .

\subsection{The caveats}\label{sec:caveats}

%The biggest systematic of our method, like all other applications of AP, is still the RSD problem.
\cite{Li2014,Li2015} found the RSD effect exhibits a small redshift dependence of $\hat \xi_{\Delta s}(\mu)$, 
mainly due to the structure growth and the selection effect
(different galaxy bias at different redshifts).
In this analysis we use the mock galaxy sample from HR4 to correct this systematics.
The galaxy assignment scheme of \cite{hong2016} applied to HR4 is very successful in modeling both the 
large scale Kaiser effect and the small scale FOG effect in nonlinear regions.
%After correcting the systematic effect of RSD, we obtain reasonable cosmological constraint consistent with all other cosmological probes.

There are two possible caveats in our procedure of the modeling of the RSD effect.

1) The RSD effect is estimated from mock survey samples created in a particular cosmology, 
i.e., the $\Omega_m=0.26$ $\Lambda$CDM model. %model from WMAP5 observations with .
If this adopted cosmology is different from the truth, then there could be a systematic bias in the estimation. %of RSD
We believe that this will not seriously affect our cosmological constraints.
\cite{Li2014} shows that the redshift dependence of RSD is not sensitive to cosmological parameters.
Also, the cosmologies adopted in simulations are consistent with our best-fit cosmological parameters within 1$\sigma$,
therefore our inferred cosmological constraints should be fairly accurate.
In a future analysis,
we will estimate the redshift evolution of the RSD effect from a set of cosmological simulations 
covering the relevant part of the parameter space.
This approach will remove the remaining uncertainty associated with the RSD effect, 
which is already a minor effect in our analysis.
%the statistical uncertainty of this method could be much smaller,
%and modeling the RSD effect in a cosmological dependent manner would be necessary.

\begin{figure*}
   \centering{
   \includegraphics[width=14cm]{fig8.eps}
   %\includegraphics[width=14cm]{Tpcf--contour.eps}
   }
   \caption{
    \label{fig_2pcf_masscut} 
    $\hat \xi_{\Delta s}(\mu)$ measured from a small HR4 mock galaxy sample with different minimal mass cuts.
    The mock galaxies are taken from the $z=0$ snapshot data within the radius $r<600$ $h^{-1}$Mpc.
    Only small variations of $\hat\xi_{\Delta s}(\mu)$ are produced when changing the minimal mass cuts.
    Higher mass cuts result in larger (smaller) $\hat\xi_{\Delta s}(\mu)$ at $\mu\rightarrow1$ ($\mu\rightarrow0$).
    %Considering the large variation of mass cuts, the variation of $\hat\xi_{\Delta s}(\mu)$ is not significant.
   }
      %The redshift density distribution of the BOSS DR12 galaxy samples, assuming a $\Lambda$CDM cosmology with $\Omega_m=0.31$.
      %The blue and green solid histograms show the distribution of LOWZ and CMASS galaxies respectively. 
      %The vertical dashed lines define the 6 redshift bins that are used to cut the samples.   }
\end{figure*}

2) The selection effect, i.e., the evolution of galaxy bias with redshifts, 
can introduce redshift evolution in the clustering properties of the observed galaxies.
%If that is not accurately modeled, people may worry about systematics. %may suffer from systematic errors.
%Again, we believe this is not a serious problem for our analysis.
In our analysis the amplitude of the 2pCF is normalized and only its angular information, 
the function $\hat \xi_{\Delta s}(\mu)$, is used.
This function is rather insensitive to the galaxy bias,
which mainly affects the strength of clustering.

As a test, Figure \ref{fig_2pcf_masscut} shows $\hat \xi_{\Delta s}(\mu)$ measured from a small HR4 galaxy sample with different minimal mass cuts.
The mock galaxies are taken from the $z=0$ snapshot data within the radius $r<600$ $h^{-1}$Mpc.
Applying the minimal mass cuts of $1,2,4\times 10^{13} h^{-1} M_{\odot}$, 
we created three sets of subsamples with number density of 
$\bar n=4.56,\ 2.10,\ 0.91 \times 10^{-4} ( h^{-1} \rm Mpc)^{-3}$, 
which roughly covers the scatter of the number density of BOSS DR12 galaxies at $0.15<z<0.7$
\footnote{The BOSS LOWZ and CMASS galaxies reside in massive haloes 
with a mean halo mass of $5.2 \times 10^{13} h^{-1} M_{\odot}$ and $2.6 \times 10^{13} h^{-1} M_{\odot}$ \citep{Parejko2013,White2011,Reidetal:2016},
respectively.
For CMASS galaxies, when the redshift changes from $z=0.43$ to $0.7$,
the mean stellar mass varies from $10^{11.6} {M_{\odot}}$ to $10^{11.9} {M_{\odot}}$ \citep{CMASSLSS2014}.}.

For subsamples with higher mass cuts the $\hat\xi_{\Delta s}(\mu)$
has larger (smaller) values at $\mu\rightarrow1$ ($\mu\rightarrow0$).
More massive samples result in less tilted $\hat\xi_{\Delta s}(\mu)$ in the region of $1-\mu\gtrsim0.1$
\footnote{This phenomenon is understandable.
The tilt of $\hat\xi_{\Delta s}(\mu)$ is related to the RSD effect, 
and also the overall amplitude of the 2pCF (the denominator of Eq. (\ref{eq:norm})).
The slope should be roughly proportional to $(v/b_g)^2$, 
where the peculiar velocity term $v^2$ denotes the effect of RSD, 
and the galaxy bias term $b_g^2$ represents the amplitude of the 2pCF. 
For the more massive sample, $b_g$ is much larger while $v$ is still close to the peculiar velocity of dark matter field,
%So their curves are less tilted.
therefore the slope is smaller.
}.
This explains the relative large value of $\hat \xi_{\Delta s,\rm sys}(z_6, z_1)$.
In particular, comparing the subsamples with mass cuts $4\times 10^{13}h^{-1} M_{\odot}$ and $1\times 10^{13}h^{-1} M_{\odot}$, 
we find the red dotted curve is higher (lower) than the blue solid line at $\mu\rightarrow1$ ($\mu\rightarrow0$),
with a difference of $\approx$0.1 (0.05),
consistent with the value of $\hat \xi_{\Delta s,\rm sys}(z_6, z_1)$ shown in Figure \ref{fig_sys}.

In addition, this result also explains the small discrepancy between the $\hat\xi_{\Delta s}(\mu)$ measured from the 
observational data and the HR4 simulations (Figure \ref{fig_datamock}).
The mock galaxies could be systematically more massive than the observed ones.
These systematics could be most significant in the 6th redshift bin
where mock galaxies are most massive, 
leading to possible overestimation of $\delta\hat\xi_{\Delta s,{\rm sys}}$.
We discuss the impact of this effect in Sec. 6.1.

$\hat\xi$ is much less affected by the galaxy bias compared with the amplitude of $\xi$,
which is enhanced by 40\% and 100\% when increasing the mass cut from $1\times 10^{13}h^{-1} M_{\odot}$ to $2,4\times 10^{13}h^{-1} M_{\odot}$ .

%compared with the result of ,

%the change of $\hat\xi_{\Delta s}(\mu)$ is not significant,
%so we conclude that $\hat\xi_{\Delta s}(\mu)$ is relatively insensitive to the galaxy bias.

%In addition, Figure 5 of \cite{Li2015} also shows that the peculiar velocities of the halos (PSB halos from HR3) are very insensitive to their masses. 
%This means the RSD effect coming from galaxies with different biases are similar.
%So the modeling of RSD effect does not require accurate modeling of the biases of the observed galaxies.

\subsection{$\chi^2$ function}\label{sec:likelihood}

We define a $\chi^2$ function to quantify the redshift evolution of clustering anisotropy
\begin{equation}\label{eq:chisq1}
\chi^2\equiv \sum_{i=2}^{6} \sum_{j_1=1}^{n_{\mu}} \sum_{j_2=1}^{n_{\mu}} {\bf p}(z_i,\mu_{j_1}) ({\bf Cov}_{i}^{-1})_{j_1,j_2}  {\bf p}(z_i,\mu_{j_2}),
\end{equation}
where ${\bf p}(z_i,\mu_{j})$ is the redshift evolution of clustering, 
$\hat \xi_{\Delta s}$, with systematic effects subtracted
\begin{eqnarray}\label{eq:bfp}
 {\bf p}(z_i,\mu_{j}) \equiv&\ \delta \hat\xi_{\Delta s}(z_i,z_1,\mu_j) - \delta \hat\xi_{\Delta s, \rm sys}(z_i,z_1,\mu_j)
\end{eqnarray}
${\bf Cov}_i$ is the covariance matrix estimated from the mock surveys. %72 sets of PSB mock galaxies identified from HR3 N-body simulation.

The covariance matrix inferred from a finite number of 
Monte Carlo realizations 
is always a biased estimate of the true matrix \citep{Hartlap}.
This bias can be corrected by rescaling the inverse covariance matrix as 
\begin{equation}
 {\bf Cov}^{-1}_{ij,\rm Hartlap} = \frac{N_s - n_{\mu}-2}{N_s-1} {\bf Cov}^{-1}_{ij},
\end{equation}
where $N_s$ is the number of mocks used in covariance estimation.
In the case when using the 2\,000 MultiDark-Patchy mocks, 
the rescaling is only 1.008, 1.013, 1.018 if adopting $n_{\mu}=20,\ 30, \ 40$.

Also, the error of covariance matrix propagates to the 
error on the estimated parameters, 
leading to scattering in the inferred constraints \citep{Percival2014}.
Fortunately, this too can be easily corrected by multiplying the likelihood by a factor of
\begin{equation}
m_1 = \frac{1+B(n_\mu - n_{p})}{1+A+B(n_p +1)},
\end{equation}
where $n_p$ is the number of parameters , and $A,B$ take the forms of
\begin{eqnarray}
A = \frac{2}{(N_s-n_\mu-1)(N_s-n_\mu-4)},\\
B = \frac{N_s-n_\mu-2}{(N_s-n_\mu-1)(N_s-n_\mu-4)}.
\end{eqnarray}
We find $m_1=$1.011, 1.016, 1.021 for $n_{\mu}=$20, 30, 40, if using the 2\,000 MultiDark-Patchy mocks.

\subsection{Averaging a set of replicate measurements to increase the S/N}\label{sec:binningscheme}

The angular cut, $\mu_{\rm max}$, and number of bins, $n_\mu$, is chosen freely.
%The cut $\mu_{\rm max}$ and the number of bins $n_\mu$ can be chosen freely in our analysis.
Different choices for these parameters yield slightly different results and different statistical uncertainties.
To suppress the statistical noise we adopt a large number of binning schemes and average their $\chi^2$s.

A value $\mu_{\rm max} = 0.99$ is sufficient to remove the fiber collision effect.
We have checked that our results are statistically robust against the choice of $\mu_{\rm max}$.

A larger $n_\mu$ tightens the constraint 
in the cost of more noise, 
while $n_\mu$ should be smaller than the number of mock samples used for covariance estimation.
We find $n_\mu \gtrsim 5$ gives relative tight constraints, 
and $n_\mu = 40$ is the limit we can reach given the size of the sample and the number of mock samples.

We run through the range $\mu_{\rm max} = 0.85, 0.86, ... 0.99$ at steps of 0.01 and $n_\mu =  6, ... 40$, in total 525 binning schemes.
%\footnote{In fact we only use 381 schemes.
%In some cases the estimation of covariance is not very successful, leading to singular matrix or very noisy $\chi^2$;
%We reject these cases.}.
We compute $\chi^2$ according to Equation (\ref{eq:chisq1}) for these choices and take an average of $\chi^2$s from a number of schemes.
This approach suppresses the statistical noise quite effectively. %in the contour map of $\chi^2(\Omega_m,w)$.

%We find noise in the $\chi^2$ probably due to the low statistic caused by the limited size of the sample and the covmat due to small size of mocks ...
%So we compute many values of $\chi^2$ using different $n_\mu$ and $\mu_{\rm max}$...
%The noise in $\chi^2$ shall be statistically random and by taking an average it is suppressed while the physical signal is preserved...
%We tested the dependence of the result on $\mu_{\rm max}$ and find the result is rather stable within the range $\mu_{\rm max}=0.85 - 0.99$...
%So we use $\mu_{\rm max} = 0.85, 0.86, ... 0.99$...
%Increasing $n_\mu$ tighens the constraintm, but in cost of larger noise in the result...
%Also $n_\mu$ shall be smaller than the number of mocks to compute covmat...
%So we use $n_\mu = 5, 6, ... 40$...
%So we define...
%\begin{equation}\label{eq:chisq2}
%\bar\chi^2\equiv \frac{ \sum \chi^2(n_\mu,\ \mu_{\rm max}) } {\rm Number\ of\ \chi^2} ... (find a proper way to illustrate this equation)
%\end{equation}

%{\bf AMTB: We need to give some results on the systematic effects. }

\begin{figure*}
   \centering{
   \includegraphics[width=18cm]{fig9_0.eps}
   \includegraphics[width=18cm]{fig9_1.eps}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}
   }
   \caption{\label{fig_TpCF}
   Upper panels: $\hat \xi_{\Delta s}(\mu)$ measured for the BOSS DR12 galaxies,
   which are divided into six redshift bins.
   Measurements from the three bins in LOWZ are indicated in solid lines, 
   while those from CMASS are the dashed lines.
   We present the measurements in three cosmologies,
   the $\Omega_m=0.31$ $\Lambda$CDM (left), the $\Omega_m=0.1$ $\Lambda$CDM (middle),
   and a cosmology with $\Omega_m=0.31$, $w=-2.5$ (right).   
   %We adopt $s_{\rm min}=6$ $h^{-1}$Mpc and $s_{\rm max}=40$ $h^{-1}$Mpc for the integral over the scale of 2pCF.
   The angular dependence of 2pCF is measured in 10 bins within the range $0.01\leq1-\mu\leq1$.
   In the middle and right panels, the redshift dependence of AP distortions leads to clear redshift evolution of $\hat \xi_{\Delta s}(\mu)$.
   Lower panels: The redshift evolution of the $\hat\xi_{\Delta s}$ after systematics correction,  
   $\delta\hat \xi_{\Delta s}(z_i,z_1)-\delta\hat \xi_{\Delta s,\rm sys}(z_i,z_1)$
   (for details of their definitions, see Eq. (\ref{eq:deltahatxi}) and Sec. \ref{sec:syscor}).
   For clarity we combine the curves of $z_2$ and $z_3$, which fluctuate
   due to the relatively small sample sizes.
   The statistical significance is indicated by the 1$\sigma$ error bars of $\delta\hat \xi_{\Delta s}(z_6,z_1)-\delta\hat \xi_{\Delta s,\rm sys}(z_6,z_1)$.
   The curves are statistically consistent with 0 in the $\Omega_m=0.31$ $\Lambda$CDM cosmology,
    while they deviate from 0 at significant confidence levels in the $\Omega_m=0.1$ cosmology and the $w=-2.5$ cosmology.
   %showing the redshift dependence of AP effect.
   Applying the likelihood analysis described in Sec. \ref{sec:likelihood},
    the two latter models disfavored at 5.3$\sigma$ and 7.5$\sigma$ CL compared to the $\Omega_m=0.31$ $\Lambda$CDM cosmology.
   }
\end{figure*}

\section{Result}

We apply our method to the BOSS DR12 CMASS and LOWZ galaxies.
We present the results in this section.

\subsection{Redshift evolution in wrong cosmologies}\label{sec:redevolvxi}

%{\bf Figure: $\xi$ curves, in different cosmologies, without and with RSD}

The upper panels of Figure \ref{fig_TpCF} present the $\hat \xi_{\Delta s}$ measured for BOSS galaxies in three different cosmologies.
In the left panel we adopt the Planck cosmology, i.e., $\Lambda$CDM with $\Omega_m=0.31$;
%which should be {\it close to the truth}.
In the other two panels, we choose two sets of parameters ---
the $\Omega_m=0.1$ $\Lambda$CDM cosmology (middle) and the cosmology with $\Omega_m=0.31$ and $w=-2.5$ (right).
We split the BOSS DR12 galaxies into six redshift bins,
construct their 3D distribution in these three cosmologies
and then measure $\hat \xi_{\Delta s}(\mu)$ according to the procedure of the last section.

For a sample of galaxies with homogeneous, isotropic spatial distribution, 
the measured $\hat \xi_{\Delta s}(\mu)$ is statistically uniform.
The distortion in $\hat \xi_{\Delta s}(\mu)$ introduced by RSD is large.
There are two distinct features in this distortion.
At $0\lesssim 1-\mu \lesssim 0.1$, $\hat \xi_{\Delta s}(\mu)$ turns up as $\mu\rightarrow1$
due to the large FOG effect.
In other directions, the anisotropic clustering produced by the large scale flow creates a monotonic angle dependence of $\hat\xi_{\Delta s}(\mu)$. %a slope in the curve.
These patterns are evident in all cosmologies.

%\subsubsection{AP effect}

The additional angular dependence of $\hat \xi_{\Delta s}(\mu)$ introduced by AP is not as strong as RSD;
However, it is still visible. 
In the middle and right panels, % of Figure \ref{fig_TpCF},
%where there is clear redshift evolution of $\hat \xi_{\Delta s}$.
the choice of two incorrect cosmologies results in an enhancement of  $\hat \xi_{\Delta s}(\mu)$ due to the 
apparent stretch of non-linear structures in the LOS direction
%As a result, near LOS the value of $\hat \xi_{\Delta s}$ is enhanced 
\footnote{{\it Stretch of structure enhances the value of $\xi_{\Delta s}$}.
On relatively small scales, the strong clustering produces large values of $\xi$.
The apparent stretch of structure means the strong clustering on small scales are, apparently, shifted to larger scales:
at some fixed scale, we measured larger $\xi$ if there is apparent stretch.
The value of $\xi_{\Delta s}$, which is the integral of $\xi$ within fixed range of $s$, is also enhanced.}.
This effect is evident when we compare  $\hat \xi_{\Delta s}(\mu)$ in these two panels to that in the left panel.

More importantly, in incorrect cosmologies the redshift dependence of the AP effect results in a redshift evolution of $\hat \xi_{\Delta s}$.
This unique feature makes the AP effect detectable even with the existence of the large RSD effect. %distinguishable from the RDS distortion.
When $\Omega_m=0.1$ and $w=-1$ are adopted, 
the LOS stretch of structure becomes stronger at higher redshift (see Figure \ref{fig_xy});
as a result, the enhancement of $\hat \xi_{\Delta s}$ along the LOS 
becomes more significant at higher redshifts.
The opposite behavior is seen for the choice of $\Omega_m=0.31$ and $w=-2.5$.
%We see very evident redshift evolution of $\hat \xi_{\Delta s}$.
%I.e., the redshift dependence of AP effect results in redshift evolution of $\hat \xi_{\Delta s}$.
However, we do not see such obvious redshift evolution in the Planck cosmology, % is not so obvious.
 indicating that the cosmological parameters of the Planck cosmology are close to the correct ones.
%The Planck cosmology is widely accepted as to be close to the true cosmology parameters of our Universe and 
%There the AP effect is not strong enough to produce an evident redshift evolution.

The lower panels of Figure \ref{fig_TpCF} show the redshift evolution of $\hat\xi_{\Delta s}$ after systematics correction, 
i.e., the quantity $\delta\hat \xi_{\Delta s}-\delta\hat \xi_{\Delta s,\rm sys}$.
The result is statistically consistent to 0 in Planck cosmology -- 
In the four curves, almost all points are consistent with 0 at $\lesssim1\sigma$ confidence level (CL).
The only exception is the leftmost point of $\delta\hat \xi_{\Delta s}(z_6,z_1)-\delta\hat \xi_{\Delta s,\rm sys}(z_6,z_1)$,
 which is negative at $\sim$2 $\sigma$ CL.
This result could be due to the overestimation of $\delta\hat\xi_{\Delta s, \rm sys}(z_6,z_1)$ as discussed in Sec. \ref{sec:syscor}.
This behavior will not affect our derived cosmological constraints:
Dropping this measurement by imposing a cut $\mu<0.9$
  does not shift the constrained on $\Omega_m$-$w$ (the pink contour of Figure \ref{fig_contours}).

In the $\Omega_m=0.1$ cosmology and the $w=-2.5$ cosmologies, however,
the measured $\delta\hat \xi_{\Delta s}-\delta\hat \xi_{\Delta s,\rm sys}$ deviates 
from zero at significant confidence levels.
Applying the likelihood analysis described in Sec. \ref{sec:likelihood},
 they are disfavored at 5.3$\sigma$ and 7.5$\sigma$ CL compared to the Planck cosmology.
Since these two cosmologies deviates from the $\Omega_m=0.31$ $\Lambda$CDM cosmology with $\Delta \Omega_m = 0.21$ and $\Delta w = 1.5$,
roughly speaking, we expect our method able to constrain $\Omega_m$ and $w$ with 1$\sigma$ uncertainties of 0.04 and 0.2, respectively.

%Overall, the effect of RSD on the 2pCF is large but its redshift dependence is small.
%The correct cosmology corresponds to the case with the lowest change of $\hat \xi_{\Delta s}$ with $z$.
%Even with RSD, we can still correctly determine the true cosmology by using the relative change of $\hat \xi_{\Delta s}$ with redshift.

\subsection{Cosmological constraint}\label{sec:constraint}

We constrain $\Omega_m$ and $w$ through Bayesian analysis \citep{Bayesian},
which derives the probability distribution function (PDF) of some parameters $\bf \theta$ (=($\Omega_m,w$) in this paper)
given observational data $\bf D$, 
according to Bayes' theorem:
\begin{equation}
 P({\bf \theta}|{\bf D}) = \frac{P({\bf \theta})P({\bf D}|{\bf \theta})}{m({\bf D})}.
\end{equation}
Here $P(\bf \theta)$, the prior distribution of the parameters,
contains all the information about the parameters known from substantive knowledge 
and expert opinion {\it before} observing the data.
The marginal PDF of $\bf D$, 
$m({\bf D})=\int P({\bf D|\theta})P({\bf \theta})d{\bf \theta}$, 
is a normalization constant independent of $\theta$.
All the information about the parameter $\bf \theta$ that stems from the experiment
is contained in the function $P({\bf D}|{\bf \theta})$, 
the conditional PDF of the observation $\bf D$ given the value of parameter.

\begin{figure*}
   \centering{
   %\includegraphics[width=7cm]{Tpcf--contour.eps}
   %\includegraphics[width=16cm]{Tpcf--contour-others.eps}
   \includegraphics[width=16cm]{fig10.eps}
   %\includegraphics[width=16cm,natwidth=52,natheight=40]{fig10.png}
   }
   \caption{\label{fig_contours}
   Likelihood contours (68.3\%, 95.4\%) in the $\Omega_m-w$ plane from our method and other cosmological probes.
   %obtained from the BOSS DR12 CMASS and LOWZ samples.
   Using the BOSS DR12 galaxies within the redshift range $0.15< z< 0.693$, our method achieves tight cosmological constraints on $\Omega_m$ and $w$.
   The 2,000 MultiDark-Patchy mocks are adopted to estimate the covariance matrix in our method.
   %The area of the 1$\sigma$ contour of our method is smaller than all other probes.
   Constraints from various probes are consistent with each other.
   See Sec. \ref{sec:constraint} for details.
   %in very good consistent with the other methods.
   }
\end{figure*}

In this analysis we simply assume flat priors for $\Omega_m$ and $w$,
and approximate $P({\bf D}|{\bf \theta})$ by a likelihood function $\mathcal{L}$
satisfying  $-2 \ln \mathcal{L}=\chi^2$;
the PDF of $\theta$ derived from our AP method takes the form
%The PDF cu is approximated by the {\it likelihood} function of $\mathcal{L}\propto \exp\left(-\frac{\chi^2}{2}\right)$.
%It is approximated by the {\it likelihood} function.
%So we have
\begin{equation}
 P({\bf \theta}|{\bf D}) \propto \mathcal{L} \propto \exp\left[-\frac{\chi^2}{2}\right].
\end{equation}
We use the {\texttt {COSMOMC}} software \citep{LB2002}
to obtain the Markov Chain Monte Carlo (MCMC) samples of $\theta$ following the PDF of $P({\bf \theta}|{\bf D})$.
Constraints on $\Omega_m$ and $w$ are derived from these samples.

We utilize the 2\,000 MultiDark-Patchy mocks to compute the covariance matrix, 
and take the averaged value of the $\chi^2$ map from
%the 55 binning schemes with $20\leq n_\mu \leq 30$
the 80 binning schemes with $20\leq n_\mu \leq 35$ 
and $\mu_{\rm max}\leq 0.95, ..., 0.99$
\footnote{The result is not sensitive to the choice of the binning scheme.}. 
The 68\% and 95\% likelihood contours of $\Omega_m$ and $w$ 
obtained from this analysis are shown in Figure \ref{fig_contours} (pink areas).
%For comparison, results from some other cosmological probes are also plotted.
Our AP method yields tight constraints on $\Omega_m$ and $w$ .
The mean values and standard deviations are
\begin{equation}
 %\Omega_m=0.314 \pm 0.038,\ \ w = -1.09 \pm 0.14.
 %\Omega_m=0.296 ^{+0.027}_{-0.021},\ \ w = -1.08 \pm 0.13. %% 20-30; no sefact
 %\Omega_m=0.296 \pm 0.048,\           \ w = -1.08 \pm 0.13. %% 20-30; no sefact
 %\Omega_m=0.290 ^{+0.029}_{-0.020},\ \ w = -1.07 \pm 0.15. %% 20-35; sefact
 \Omega_m=0.290 \pm 0.053,\          \ w = -1.07 \pm 0.15. %% 20-35; sefact
\end{equation}
This result is consistent with the Planck $\Lambda$CDM cosmology within 1$\sigma$ \citep{Planck2015}.

We find the expected negative degeneracy between $\Omega_m$ and $w$.
At low redshift, increasing $\Omega_m$ and increasing $w$ have a similar effect on the cosmic expansion.
When one parameter is increased the other parameter can be decreased to counteract the AP effect
\footnote{At high redshift the direction of degeneracy completely changes. 
There the effect of $w$ is less important and the cosmic expansion is mainly governed by $\Omega_m$.
This behavior is why \cite{Li2015} obtained a positive degeneracy between $\Omega_m$ and $w$ from mock surveys 
spanning a wide range of $0< z < 1.5$.
The degeneracy direction between $\Omega_m$ and $w$ depends on the redshift range of the sample used in the analysis.}.

For comparison, additional likelihood contours from other cosmological probes are displayed in Figure \ref{fig_contours}:
the JLA SNIa sample (green area, \cite{JLA}),
the BAO measurement from BOSS DR11 galaxies (bright yellow, \cite{Anderson2013}),
%\footnote{The CMASS and LOWZ samples from BOSS DR11 have a sky coverage of 8\,377 $\rm deg^2$ and a completeness of 97\%.
%They are very close to the DR12 samples.},
a combination of the BOSS DR11 BAO and the Hubble Space Telescope measurement of $H_0=70.6\pm3.3$ (dark yellow, \cite{Riess2011,E14H0}),
and the full-mission Planck observations of temperature and polarization anisotropies, released in 2015 (blue, \cite{Planck2015}).

%
The SNIa contours occupy a region similar to ours, but provide much weaker constraints. %has similar degeneracy to our method.% to us while the contour size is larger.
The direction of degeneracy is also similar.
%This is expectable.
By measuring the apparent magnitudes of type Ia supernovae distributed at different redshifts, 
 cosmologists can infer the luminosity distance $d_L$ as a function of redshift.
The JLA sample has similar redshift coverage to the BOSS DR12 galaxies,
which could be the reason for the similarity between the contours of the SNIa and our AP method.
%This is to some extent similar to our method, 
%which probes the redshift evolution of geometric distortion.
%which maybe the reason of the similarity 
%So the shapes and the positions of the contours from these two methods are a kind of close to each other.
%Comparing these two methods, we find our method has better constraining power.
%For SNIa probe, the degeneracy between $\Omega_m$ and $w$ is more serious and the contour extends to $\Omega_m=0$.

%The BOSS DR11 galaxies BAO measurements yields $D_V(z=0.32) = (1264 \pm 25 {\rm Mpc})(r_d /r_{d,\rm fid})$,
%$D_A(z=0.57) = (1421 \pm 20 {\rm Mpc})(r_d /r_{d,\rm fid})$, 
%and $H(z=0.57) = (96.8 \pm 3.4 {\rm km/s/Mpc})(r_{d,\rm fid} /r_d )$.
%Here $r_d$ is the drag epoch,
%$D_V(z)$ is the spherically averaged 2-point measurement of the BAO position, defined as $\left[cz(1+z)^2D_A(z)^2H^{-1}(z)\right]^{1/3}$, 
%and all measurements are presented as the ratio of the distance priors to their values in the fiducial cosmology \citep{Anderson2013}.
%At $z=0.57$, separating the clustering along and transverse to the LOS enables measurement of the sizes of the BAO ring in these two directions.

BAO itself can not effectively constrain $\Omega_m$ and $w$, 
since these parameters are highly degenerate with $H_0$ in determining the length scale.
Combining BAO with the $H_0$ measurements to break the degeneracy yields better constraint on the parameter space.
%The contour size is a bit larger than ours.
The direction of degeneracy of the combined constraint is roughly orthogonal to ours.
%This means we can combine these two LSS probes to break the degeneracy and significantly strengthen the constraining power.

CMB measurements provide a powerful probe of the geometry of the Universe,
but can not effectively constrain $\Omega_m$ and $w$ due to the strong degeneracy of the parameters.
%But combining CMB with the other probes can significantly shrink the volume of parameter space and tightens the constraint.
The CMB contour is almost orthogonal to the AP contour. 
%Contours from the two probes nicely overlapped with each other.
%In particular, our contour is well consistent with the Planck 2015 $\Lambad$CDM with $\Omega_m=0.308$.

Among all the individual cosmological probes, our method yields the most stringent 
constraint on $\Omega_m$ and $w$.
Our result is consistent with those of all other probes.
%Also, the degeneracy of our contour is different from most the other probes.
%We can take the advantage of this fact and tighten the constraint by combing them together.

Assuming that the five different cosmological probes of CMB, BAO, SNIa, $H_0$ and our method are 
statistically independent,
we combine the results by simply multiplying their likelihoods,
resulting in the total likelihood function
\begin{equation}\label{eq:likelihood}
\mathcal{L}_{\rm total} = \mathcal{L}_{\rm CMB} \times \mathcal{L}_{\rm BAO} \times \mathcal{L}_{\rm SNIa}\times \mathcal{L}_{\rm H_0}
 \times \mathcal{L}_{\rm Our\ AP}.
\end{equation}
The Planck team has released the {\texttt {COSMOMC}} outputs of MCMC samples
using CMB+BAO+JLA+$H_0$
\footnote{http://pla.esac.esa.int/pla/\#cosmology; 
Their BAO datasets include three sets of measurements from SDSS DR11 \citep{Anderson2013}, 6dFGS \citep{6dFGS} and SDSS MGS \citep{MGS}}.
We modify their MCMC samples (by changing the values of sample weight and likelihood)
 to include the likelihood of our method,
creating samples following the PDF of Eq. (\ref{eq:likelihood}).
The joint constraint from all five cosmological probes is
\begin{equation}
 %\Omega_m = 0.304 \pm 0.007,\ w=-1.04 \pm 0.03.
 %\Omega_m = 0.301 \pm 0.006,\ w=-1.054 \pm 0.024. %% 20-30, no se fact
 \Omega_m = 0.301 \pm 0.006,\ w=-1.054 \pm 0.025. %% 20-35, se fact
\end{equation}
Interestingly, we find that the constraint is in tension with $w=-1$ at 2.1$\sigma$ CL,
However, the statistical evidence is not strong enough to claim deviation from the cosmological constant.

%{\bf which are the strongest constraints on these parameters obtained so far}
%{\bf AMTB: 
Our AP method plays an important role in strengthening the constraints on $\Omega_m$ and $w$.
As a comparison, 
%combining CMB and our method yields 
%%$\Omega_m = 0.302 \pm 0.011,\ w=-1.05 \pm 0.04$,
%%$\Omega_m = 0.297 \pm 0.011,\ w=-1.07 \pm 0.04$, %% 20-30, nose
%%$\Omega_m = 0.295 \pm 0.014,\ w=-1.08 \pm 0.05$, % 20-35, se
%$\Omega_m = 0.295 \pm 0.014,\ w=-1.081 \pm 0.055$, % 20-35, se
a combination of CMB and BAO yields 
$\Omega_m = 0.306 \pm 0.013,\ w=-1.03 \pm 0.06$;
in the absence of our method, a combination of SNIa, CMB, BAO and $H_0$
yields $\Omega_m = 0.306 \pm 0.009,\ w=-1.03 \pm 0.04$ \citep{Planck2015}.
% }

%\bibitem[Blake et al. (2011)]{WiggleZB}
%Blake, C., Kazin, E.A., Beutler, F., et al.
%2011, MNRAS, 418, 1707
%\bibitem[Kazin et al. (2014)]{WiggleZK}
%Kazin, E.A., Koda, J., Blake, C., et al.
%2014, MNRAS, 441, 352

\section{Concluding Remarks}

We apply the methodology developed in \cite{Li2014,Li2015} to BOSS DR12 galaxies.
In LSS surveys, the observed galaxy distribution appears anisotropic due to two reasons:
the contamination of galaxy redshifts due to the galaxy peculiar velocities, known as the RSD effect, 
and the error in the distance due to inaccurate cosmological parameters. %incorrectly assumed cosmological model for the coordinate transformation from redshift space to comoving space, known as the AP effect.
\cite{Li2014} reported that anisotropies produced by RSD effect are, although large,
close to uniform in magnitude over a large range of redshift,
while the degree of anisotropies introduced by AP varies with redshift. 
%We found that the redshift dependence of the anisotropy introduced by RSD is much less significant compared with the anisotropy caused by AP.
Thus we can use the redshift dependence of the anisotropic clustering of galaxies to constrain cosmological parameters without 
being much affected by RSD.

%The methodology developed in \cite{Li2015} was applied.
As in \cite{Li2015}, we investigate the redshift-dependence of clustering anisotropy by examining the 2pCF.
The 2pCF measured along different angular directions was characterized by the function $\hat \xi_{\Delta s}(\mu)$.
%In incorrectly adopted cosmological models, 
When the cosmological parameters governing the expansion history of the universe are incorrectly chosen,
the shape of this function evolves with redshift.
We split the DR12 galaxies into six redshift bins, measure the 2pCF in each redshift bin,
and search for the underlying true values of $\Omega_m$ and $w$ of our Universe % (assuming flat Universe)
by requiring minimal redshift evolution of $\hat \xi_{\Delta s}(\mu)$ across the six redshift bins.
We obtain tight constraints of 
 %$\Omega_m=0.296 ^{+0.027}_{-0.021},\ \ w = -1.08 \pm 0.13$, %% 20-30; no sefact
 %$\Omega_m=0.296 \pm 0.048,\           \ w = -1.08 \pm 0.13$ %% 20-30; no sefact
 %$\Omega_m=0.290 ^{+0.029}_{-0.020},\ \ w = -1.07 \pm 0.15$ %% 20-35; sefact
 $\Omega_m=0.290 \pm 0.053,\          \ w = -1.07 \pm 0.15$ %% 20-35; sefact
from our method alone.

The constraints on $\Omega_m$ and $w$ from our AP method are comparable with or tighter % in constraining the parameter space of $\Omega_m$ and $w$ 
than the other cosmological probes of SNIa, CMB, BAO, and $H_0$.
For the direction of degeneracy, %between $\Omega_m$ and $w$ in the constrained parameter space,
our method is similar to SNIa and orthogonal to CMB and BAO+$H_0$.
Combining the results of our method with those of other cosmological probes, 
we obtain tight constraints 
%$\Omega_m = 0.301 \pm 0.006,\ w=-1.054 \pm 0.024$.
$\Omega_m = 0.301 \pm 0.006,\ w=-1.054 \pm 0.025$.

\subsection{Comparison with other LSS probes}

Our method uses the anisotropic galaxy on scales from 6 to 40 $h^{-1}$Mpc.
%a novel analysis method extracting physical information encoded in LSS. % compared with the others.
%We look at the geometric distortion of LSS due to AP effect 
%clustering created by AP exhibits redshift evolution.
%Here the clustering scales we choose to look at in this analysis is 
Constrains on cosmological parameters are obtained from the redshift dependence of $D_A(z) H(z)$.

As a comparison, the BAO method uses the BAO feature in the 
clustering of galaxies on scales of 100-150 $h^{-1}$Mpc 
created by the oscillation of the baryon-photon plasma in the early Universe.
Measuring the BAO feature in 1D or 2D yields measurements of $D_V$ or $D_A$ and $H$ at some representative redshifts.
%So the principles and the physical information probed in these two methods are fundamentally different.

The AP methods proposed to date, such as those using 
galaxy pairs and voids, measure the rate of geometric distortion and are sensitive to $D_A(z) H(z)$,
while our method uses its the redshift dependence.
These methods can be combined together to fully utilize the physics of AP test.
Also, reducing the RSD effect 
through the redshift dependence could be 
applicable to these methods.

The topology method proposed by \cite{topology} 
uses the redshift evolution of the volume effect and is sensitive to the quantity $D_A(z)^2 / H(z)$.
Combing this method with ours can yield separate constraints on $D_A$ and $H$ 
for the same observational sample.
Constraints from the other statistical measures,
such as the distribution function of size or richness of LSS,
can be also combined \citep{Park2012,Park2015}.
%Analyzing the distortion of apparent galaxies clustering due to RSD,
%people can constrain the growth rate, the clustering strength and the galaxy bias.

Recently, \cite{MS2016} developed a novel method 
constraining cosmological parameters based on the high-level similarity of the emission measure in the cluster outskirts.
In incorrect cosmologies, the emission measure from clusters exhibits redshift dependence.
%This leads to tight constraints on the redshift evolution of the cosmic length scale.
Utilizing a sample of 320 galaxy clusters ($0.056<z<1.24$) observed with Chandra,
they achieve tight cosmological constraints comparable to ours.
The idea of this novel technique is to some extent similar to our method 
(seeking for the conservation of geometric quantity with redshift),
and could have promising future.
%and can be combined with our method to

The above geometric methods can be combined with probes of RSD 
\citep{Guzzo2008,Blake2011a,Beutler2012,Reid2012b,Samushia2012,GM2016b,Li2016} 
to have a more complete study of LSS galaxy clustering.
See \cite{DHW2013} for a review of more LSS probes of dark energy.

%The above LSS analysis methods, based on different concepts, 
%and probing different types of physical information, 
%are mutually complementary.
%It is worthy combining them together to comprehensively utilize the physical information encoded in the LSS 
%and derive tight constraints on parameters of cosmology. % and galaxy science.
%which is also fundamentally different from our method which is

\subsection{Room for improvements}

This paper is the first application of this redshift dependent AP test to observed LSS data.
There remains considerable opportunity for improving the analysis methodology,
e.g., the optimized schemes of redshift binning and 
optimized choices of the scales of clustering (the values $s_{\rm min}$ and $s_{\rm max}$).
In this paper, the 2pCF is characterized by $\hat \xi_{\Delta s}(\mu)$.
It should be more advantageous to use 
the redshift evolution of 2pCF in two dimensions, i.e., $\hat \xi(s,\mu)$, 
to capture the full information.
It is also necessary to combine the 
information in the higher-order
statistic beyond the two point functions.
As pointed out in Sec. \ref{sec:caveats},
more theoretical and numerical studies on the 
redshift evolution of the RSD effect 
will remove the remaining small 
uncertainties in our results.

To avoid the difficulty of modeling galaxy bias we dropped the information of strength of clustering
through normalizing the amplitude of $\xi$.
In the case that we have good knowledge of galaxy bias, one can utilize the amplitude of $\xi$ to probe the redshift dependence of volume effect 
and obtain much tighter constraints.
\cite{Li2015} showed that
the area of constraining regions in $\Omega_m$ and $w$ space from the redshift dependence of the volume effect is 3.5 times smaller 
than that from the redshift dependence of the AP effect alone.

In this analysis, by reducing the RSD effect, 
%through looking at the redshift evolution,
we are able to use the galaxy clustering down to 6 $h^{-1}$Mpc.
This is a major advance in extracting the cosmological information 
on small scales where galaxy clustering is strong
and there are a lot of independent structures.

To make sure that the derived cosmological constraint is robust, 
in the procedure of systematics correction, 
one should construct many mock surveys in which the RSD and other systematic effects are reliably modeled.
%It could be crucial to adopt a good galaxy assignment scheme, 
%such as the MBP-galaxy correspondence model developed in \citep{hong2016}.
%adopted in this analysis, could be crucial.
%So we can obtain an accurate estimation of systematic effect.

It would also be helpful to investigate the effect of galaxy properties.
For example, in case of a dense survey containing galaxies with various properties, 
one can split the galaxy sample into subsamples with different galaxy properties, 
derive cosmological constraints from these subsamples, 
and check the consistency of the results.

%Our method is to some extent very similar with the methods using the overall shape of 
%the power spectrum or correlation function Park \& Kim (2010) Shoji et al. 2009 {\bf AMTB: Read them and check }.
%But we have one addition that uses the shape in a set of redshift slices to reduce the RSD effect.

%This is one of the reasons why our method is powerful.
%for the strong power of our method -- the small scale galaxy clustering contains abundant information.
%In future the development of simulation technique may enable us to accurately modeling galaxy clusterings on even smaller scales 
%and makes our method more powerful.

\subsection{Synergies with future observations}

The constraining power of our method is proportional not only to the size, 
but also to the redshift coverage of the galaxy sample.
In this analysis we utilize 1\,133\,326 BOSS DR12 galaxies covering $0.15< z < 0.693$.
Future redshift surveys such as eBOSS \citep{eBOSS}, EUCLID \citep{EUCLID}, and DESI \citep{DESI}
will have larger sample sizes and wider redshift coverage.
Our method is expected to yield much tighter cosmological constraints
and can be applied to constrain wider classes of 
cosmological models when these data are available.
%In the future we will have LSS surveys of 
% having much wider redshift coverage and much larger number of observed galaxies.
%{\bf Introducing the redshift range and galaxy numbers of future surveys?: eBOSS, DESI, LSST, ...?}
%Being able to utilizing small scale clustering information a denser survey will be also helpful to improve the power of our method.
%Even for the regions already probed by the current SDSS-III survey, 
%there is still large potential to improve the power of constraint by conducting a deeper survey to increase the S/N.

In this analysis we assume a flat Universe to constrain $\Omega_m$ and $w$.
Our method should be sensitive to all other cosmological parameters governing the cosmic expansion history,
e.g., the curvature of the Universe, 
and the other dark energy parameters.

Overall, the future of our method is extremely promising. 
With the progressive development of LSS experiments, 
we expect it to play an important role in deriving cosmological constraints from LSS surveys.
%and yielding fruitful out-comings.

\section*{Acknowledgments}

We thank the Korea Institute for Advanced Study for providing computing resources (KIAS Center for Advanced Computation Linux Cluster System).
%We thank Seokcheon Lee and Graziano Rossi for many helpful discussions.
We would like to thank Ho Seong Hwang, Francisco-Shu Kitaura, Benjamin L'Huillier, Donghui Jeong, Teppei Okumura, Will Percival, Hyunmi Song 
and Yi Zheng for kind helps and helpful discussions.
This work was partially supported by the
Supercomputing Center/Korea Institute of Science and
Technology Information with supercomputing resources
including technical support (KSC-2013-G2-003).

Based on observations obtained with Planck (http://www.esa.int/Planck), 
an ESA science mission with instruments and contributions directly funded by 
ESA Member States, NASA, and Canada.

Funding for SDSS-III has been provided by the Alfred P. Sloan Foundation, the Participating Institutions, the
National Science Foundation, and the U.S. Department of Energy Office of Science. 
The SDSS-III web site is http://www.sdss3.org/. 
SDSS-III is managed by the Astrophysical Research Consortium for the Participating Institutions
of the SDSS-III Collaboration including the University of Arizona, the Brazilian Participation Group, Brookhaven
National Laboratory, Carnegie Mellon University, University of Florida, the French Participation Group, 
the German Participation Group, Harvard University, the Instituto de Astrofisica de Canarias, the Michigan State/Notre
Dame/JINA Participation Group, Johns Hopkins University, Lawrence Berkeley National Laboratory, Max Planck
Institute for Astrophysics, Max Planck Institute for Extraterrestrial Physics, New Mexico State University, New
York University, Ohio State University, Pennsylvania State
University, University of Portsmouth, Princeton University,
the Spanish Participation Group, University of Tokyo, University of Utah, Vanderbilt University, University of Virginia, 
University of Washington, and Yale University.

\appendix

\section{A. Robustness Tests}\label{sec:RBtest}

We conduct a series of tests to check the robustness of our results.

The cosmological constraints presented in Sec. \ref{sec:constraint} (hereafter the ``main results'') are derived using 
the following options (hereafter the ``default options''):
\begin{itemize}
 \item We adopt $s_{\rm min}=6 h^{-1} {\rm Mpc},\ s_{\rm max}=40 h^{-1} {\rm Mpc}$ in the integrated 2pCF
 ($\xi_{\Delta s} (\mu) \equiv \int_{s_{\rm min}}^{s_{\rm max}} \xi (s,\mu)\ ds$).
 \item The effects of systematics are estimated from the HR4 mock galaxies. 
 When constructing the mocks, to determine when a satellite galaxy is disrupted,
 we adopt the J08 model to calculate the satellite galaxy merger timescale.
 \item In total 2\,000 sets of MultiDark-Patchy mock surveys are used to construct the covariance matrix.
 %\item In total 72 sets of HR3 PSB mock surveys are used to construct the covariance matrix.
 \item We drop the angular region $1 - \mu < 0.01$, to mitigate the effects of fiber collisions and redshift failures.
\end{itemize}

\begin{figure*}
   \centering{
   %\includegraphics[width=7cm]{Tpcf--contour.eps}
   %\includegraphics[width=16cm]{Tpcf--contour-others.eps}
   \includegraphics[width=16cm]{fig11.eps}
   %\includegraphics[width=16cm,natwidth=52,natheight=40]{fig11.png}
   }
   \caption{\label{fig_contours_HR3}
   Likelihood contours (68.3\%, 95.4\%) in the $\Omega_m-w$ plane from our method and other cosmological probes.
   The 72 HR3 mock surveys are utilized to estimate the covariance matrix;
    the corrections of \cite{Hartlap} and \cite{Percival2014} are not applied.
   %obtained from the BOSS DR12 CMASS and LOWZ samples.
   %Using the BOSS DR12 galaxies within the redshift range $0.15< z< 0.693$, our method achieves tight cosmological constraints on $\Omega_m$ and $w$.
   %The 2,000 MultiDark-Patchy mocks are utilized to estimate the covariance matrix.
   %The area of the 1$\sigma$ contour of our method is smaller than all other probes.
   %Constraints from various probes are consistent with each other.
   %See Sec. \ref{sec:constraint} for details.
   %in very good consistent with the other methods.
   }
\end{figure*}

\begin{figure*}
   \centering{
   \includegraphics[width=14cm]{fig12.eps}}
   %\includegraphics[width=5.9cm]{Tpcf--contour-nummock-36.eps}}
   \caption{ \label{fig_contour_RB}  
   Likelihood contours (68\%, 95.4\%) in the $\Omega_m$-$w$ plane, derived by applying our AP method to the BOSS DR12 galaxies.
    Different options are adopted to test the robustness (see Appendix \ref{sec:RBtest} for details). 
   %The 2,000 MultiDark-Patchy mocks are utilized to estimate the covariance matrix.
   %The upper-left panel displays the main results derived using the default options.
   %i.e. using $s_{\rm min}=6h^{-1}{\rm Mpc}$, $s_{\rm max}=40h^{-1}{\rm Mpc}$, $1 - \mu \ge 0.01$,
   %72 sets of HR3 PSB mocks for covariance estimation,
   %and J08 model to compute the merger timescale model in the construction of mock surveys.
   %The other panels show the contours when the options are altered one by one.
   %We find good consistency among these contours. 
   }
\end{figure*}

We check whether the results are sensitive to these options.
We modify the above options one by one, 
derive the corresponding cosmological constraints, 
and check how much they deviate from the main results.
%and are compared with the constraints derived using the default option set.
We present this information in Figure \ref{fig_contour_RB}. %displays the many sets of cosmological constraints derived with various sets of modified options.
%The upper-left panel shows the result using the default options, 
%while the other many panels display the result after changing one of these options.

We use the 72 sets of HR3 PSB mock surveys to construct the covariance matrix,
and adopt a coarser grid with $\delta \Omega_m=0.025,\ \delta w=0.05$ when covering the parameter space.
%Although the obtained contours look a little coarse, 
This resolution is high enough for the purpose of testing our methodology.
We adopt the averaged $\chi^2$ from the 525 binning schemes
with $6\leq n_\mu \leq 40$ and $\mu_{\rm max} \geq 0.85, ..., 0.99$.

When using the HR3 mock surveys, we do not apply the correction factors of \cite{Hartlap} and \cite{Percival2014}
as they are not accurate when $n_\mu$ is not much smaller than $N_s$.
The inferred constraints could suffer from statistical scatter caused by the error and bias in the estimated covariance matrix.
The results presented in this section are therefore only for illustrative purposes.

\subsection{$Covariance\ Estimation$}

In this analysis we use a set of 2\,000 MultiDark-Patchy mock surveys to compute the covariance matrix.
We check whether the result could change if adopting the HR3 N-body mock surveys.
%We check whether the relative small number of mock surveys could produce significant bias in the derived cosmological constraint.

The cosmological constraints in case of adopting the covariance matrix estimated from HR3 mock surveys
and the {\it high resolution grid} is displayed in Figure \ref{fig_contours_HR3}.
The results are consistent with the main results derived using the 2\,000 MultiDark-Patchy mocks.
The constrained area shrunk, particularly towards small $\Omega_m$ and large $w$ values;
%has a small shrinkage in the upper-left corner, 
that does not much affect the combined cosmological constraints.

In case of using HR3 mocks, the constraint from our method alone is
\begin{equation}
 \Omega_m=0.314 \pm 0.038,\ \ w = -1.09 \pm 0.14,
 %\Omega_m=0.296 ^{+0.027}_{-0.021},\ \ w = -1.08 \pm 0.13. %% 20-30; no sefact
 %\Omega_m=0.296 \pm 0.048,\           \ w = -1.08 \pm 0.13. %% 20-30; no sefact
 %\Omega_m=0.290 ^{+0.029}_{-0.020},\ \ w = -1.07 \pm 0.15. %% 20-35; sefact
 %\Omega_m=0.290 \pm 0.053,\          \ w = -1.07 \pm 0.15. %% 20-35; sefact
\end{equation}
and the joint constraint from all five cosmological probes is
\begin{equation}
 \Omega_m = 0.304 \pm 0.007,\ w=-1.04 \pm 0.03.
 %\Omega_m = 0.301 \pm 0.006,\ w=-1.054 \pm 0.024. %% 20-30, no se fact
 %\Omega_m = 0.301 \pm 0.006,\ w=-1.054 \pm 0.025. %% 20-35, se fact
\end{equation}
The difference between the above constraints and the results using the 2\,000 MultiDark-Patchy mocks is $\lesssim0.5\sigma$.

The first and second panels of the first row of of Figure \ref{fig_contour_RB} show  %the main results, 
the cosmological constraints from the {\it coarse grid}, 
using the covariance matrix estimated from 72 and 36 HR3 mock surveys, respectively.
They are consistent with the results displayed in Figure \ref{fig_contours_HR3}.

%We further take half of the HR3 mock surveys to compute the covariance matrix;
%the result is  presented in the row first and column second panel of Figure \ref{fig_contour_RB}.
%The result from 72 mocks gives slightly tighter constraint and less noisy contours than the result from 36 mocks.
%The locations of contour center are similar, and statistically are quite close to each other.

%Using 36 mocks we must adopt $n_\mu\lesssim20$ for the binning of $\xi_{\Delta s}(\mu)$,
%so it is expected that the results are slightly weaker than the results of using 72 mocks (where we take $n_{\mu}\leq40$).

%We further take the 2,000 sets of MultiDark-Patchy mock catalogues \citep{MDPATCHY} to compute the covaraince matrix.
%%This set of mock surveys have been adopted for the error estimations of the 2pCF and power spectrum measurement of the BOSS galaxies \citep{Alam2016}.
%Following \cite{Hartlap} and \cite{Percival2014}, we correct the covariance matrix
%for the statistical bias and scattering.

\subsection{$Mock\ galaxies\ for\ systematic\ correction$}

In the construction of HR4 mock galaxies \citep{hong2016}, 
the J08 model \citep{jiang2008}, a model derived from cosmological simulations, 
was adopted as the default option to calculate the merger timescale and to determine when a satellite galaxy is completely disrupted.

\cite{hong2016} also considered four alternative models for the calculation of merger timescale:
1) the LC93 model \citep{LC93} based on analytic calculation, 
2) the B08 \citep{B08} and 3) the V13 \citep{V13} models based on isolated simulations,
and 4) the M12 model \citep{M12} based on cosmological simulation.
%Among the five merger timescale models, 
%J08 was found to result in mock galaxies with properties and 2pCF best matching the observational data.
Among the five merger timescale models, 
J08 model produces mock galaxies having properties and 2pCF best agree with the observational data \citep{hong2016};
%So it was adopted in our main analysis.with
the LC93 model, having the shortest merger timescale among the five models,
produces galaxies with properties and 2pCF most deviated from the observations.

\begin{figure*}
   \centering{
   \includegraphics[width=16cm]{fig13.eps}
   %\includegraphics[height=9cm]{Tpcf-sys.eps}
   }
   \caption{\label{fig_sys_LC93}
   %Apparent distortion of objects in four wrongly assumed cosmologies, assuming a true cosmology of .
   Systematics in $\delta \hat \xi_{\Delta s}$, measured from the HR4 mock galaxies
   with the LC93 model adopted as the merger timescale model.
   Compared with the main result using the merger timescale model J08 (Figure \ref{fig_sys}), 
   there is a $\sim 25\%$ change in the amplitude of $\delta \hat \xi_{\Delta s}$.
   % so the measured $\hat\xi_{\Delta s}(\mu)$ has larger (smaller) values at $\mu\rightarrow1$ ($\mu\rightarrow0$) 
   % compared with the others.
   %See Sec. \ref{sec:syscor} for details.
   %The values are estimated from the HR4 mock galaxies. % and subtract its contribution.
   }
\end{figure*}

%To check whether our result is sensitive to these merger timescale models,
We adopt mock surveys created using the four alternative models to
measure the systematic correction $\delta \hat\xi_{\Delta s, {\rm sys}}$
and derive the cosmological constraints.
The difference between the $\delta \hat\xi_{\Delta s, {\rm sys}}$ estimated from the J08 model and the other models is $5\%-25\%$.
As an example, Figure \ref{fig_sys_LC93} presents the systematics correction estimated using LC93,
which has a $\sim25\%$ difference from the J08 estimation.

Nevertheless, Figure \ref{fig_contour_RB} shows that, 
when the alternative models adopted, 
the cosmological constraints are consistent with our main results;
the discrepancy is $\lesssim0.3\sigma$.

%In case of using the $z=0$ snapshot data rather than the lightcone galaxies to construct mock surveys,
%we find the contour slightly shifted to the upper-left direction.
%Statistically,

%Also, the shifts of contours mainly happens along the upper-left to lower-right diagonal.
%This means the joint constraint result, the constraint when combined with the other cosmological probes such as CMB, will not be very affected,
%since the CMB contour basically lies in the lower-left to upper-right diagonal.

\subsection{$Different\ s_{\rm max}$}

The results for $s_{\rm max}=30,\ 50 h^{-1}{\rm Mpc}$ are displayed in the first and second panels of the third row of Figure \ref{fig_contour_RB}.
%While the default choice of $s_{\rm max}=$ 40 $h^{-1}$Mpc gives the tightest constraint, 
Both of them are similar to the main results.

%The constraints while using 36 mocks for covariance matrix appears a little weaker.
%The reason is that, the smaller number of mocks, the smaller number of binning allowed in the analysis. 
%As discussed in Sec. \ref{sec:binningscheme}, in our main analysis we are able to use as much as 40 bins in the region $0.01\leq\mu\leq1$.
%When using 36 mocks we limit the largest bin number to 20, which leads to slightly weaker constraint.

\subsection{$Cut\ on\ \mu$}

%We checked whether the result is sensitive to the range of angular bins.
In our default options, we take $1 - \mu\ge0.01$.
For comparison, Figure \ref{fig_contour_RB} presents the cosmological constraints using the limits 
0.02, 0.05, and 0.1.
%0.02, 0.05 and 0.07. 
A larger limit means we abandon more angular regions near the LOS.
%That will make the result less affected by the factors such as fiber collision.
We find that changing the cut has little effect on the cosmological constraints.
%Even for the case of $1 - \mu\ge0.1$,
%where 10\% of the angular region is dropped,
%the constraints are still fully consistent with the main results.
%This suggests that our main result is less affected by the fiber collision.

This test suggests that our result is not affected by the fiber collisions and redshift failures.
%In the observational data, these effects are taken into consideration by reweighting the nearest neighbor of the galaxy.
%Also, we add the fiber collision effect when constructing mock surveys.
If fiber collisions and redshift failures have any sizable effect,
since they mainly affect the angular region close to LOS,
one expects a systematic variation of the cosmological constraints when varying the limit on $1-\mu$.
%Such a variation was not detected in this test.
%so the fiber collision and redshift failure effects are certainly removed

\subsection{$Excluding\ the\ 6th\ redshift\ bin$}

The highest redshift data requires the largest systematic correction, 
so it would be interesting to know how much of an effect there is when it is removed from the analysis.

The results when excluding the 6th redshift bin from the analysis is shown in the last panel of Figure \ref{fig_contour_RB}.
The constraint becomes weaker.
The 1$\sigma$ contour is shifted towards large values of $\Omega_m$ and $w$ by $\lesssim0.4\sigma$,
which should not significantly affect the combined constraint.

%This test suggests that our result is not affected by the fiber collisions and redshift failures.
%In the observational data, these effects are taken into consideration by reweighting the nearest neighbor of the galaxy.
%Also, we add the fiber collision effect when constructing mock surveys.
%If fiber collisions and redshift failures have any sizable effect,
%since they mainly affect the angular region close to LOS,
%one expects a systematic variation of the cosmological constraints when varying the limit on $1-\mu$.

\subsection{$Different\ s_{\rm min}$}

%\subsection{A2. Different $s_{\rm min}$}

Among the different options, %affecting our cosmological constraint, 
the one most likely to affect our results is $s_{\rm min}$.
%the smallest scale that are taken into account in the analysis.
%This is expectable. 
The 2pCF has relatively large values on smaller scales
%On small scales, the value of 2pCF is relatively large
(e.g. for the CMASS galaxies $\xi\approx10,5,1,0.25,0.05$ at $s=2,4,10,20,40 h^{-1}{\rm Mpc}$).
Varying $s_{\rm min}$ can dramatically change the value of $\xi_{\Delta s}(\mu)$,
and thus is likely to have a large effect on the result.

A series of input-output tests are conducted to check whether the derived constraints depend on $s_{\rm min}$.
The linear regression of the $\delta\hat\xi_{\Delta s}$ (of the observational sample) 
measured in the WMAP5 cosmology ($\Omega_m=0.26$ $\Lambda$CDM) 
is adopted as $\delta\xi_{\Delta s, \rm sys}$. 
We then follow the procedures of Sec. \ref{sec:methodology} to derive cosmological constraint.
%In that case we expect the WMAP5 cosmology being the best-fit.

\begin{figure*}
   \centering{
   %\includegraphics[width=12cm]{Tpcf--contour-diffsmin-dashcontours.eps}}
   \includegraphics[width=5.7cm]{fig14_0.eps}
   \includegraphics[width=10cm]{fig14_1.eps}}
   %\includegraphics[width=5.9cm]{Tpcf--contour-nummock-36.eps}}
   \caption{ \label{fig_contour_diffsmin} 
   Left panel: The input-output test in case of using our default options.
   The derived cosmological constraints are fully consistent with the input WMAP5 cosmology (marked by green plus).
   Right panels: Likelihood contours (68\%, 95.4\%) in the $\Omega_m$-$w$ plane for using $s_{\rm min}=2,4,6,8\ h^{-1} {\rm Mpc}$.
   Gray filled contours are cosmological constraints derived using our AP analysis.
%    From the input-output test we find $s_{\rm min}$
   %For $s_{\rm min}=2,4,8\ h^{-1}{\rm Mpc}$, some correction of the likelihood map was made based on the result of their input-output tests.
   %After the correction they are close to the result using the default option $s_{\rm min}=6h^{-1}\rm Mpc$.
   For $s_{\rm min}=2,4h^{-1}{\rm Mpc}$, the contours are shifted to the upper-left corner, 
   but the deviation from the $s_{\rm min}=6h^{-1}{\rm Mpc}$ is $\lesssim1\sigma$.
   The black solid contour lines show the constraint when combined with CMB+BAO+JLA+$H_0$.
   %The dashed contour lines show the combined constraints in case of no correction made for $s_{\rm min}=2,4,8\ h^{-1}{\rm Mpc}$. 
   The combined result is rather insensitive to choices of $s_{\rm min}$.}
\end{figure*}

When adopting $s_{\rm min}=6\ h^{-1}{\rm Mpc}$, the best-fit cosmology is exactly what we expect: the WMAP5 cosmology, 
i.e. the input cosmology is successfully recovered (left panel of Figure \ref{fig_contour_diffsmin}).
So $s_{\rm min}=6\ h^{-1}{\rm Mpc}$ is adopted as the default option in our analysis.
%When adopting different a $s_{\rm min}$ of $2,4,8\ h^{-1}{\rm Mpc}$, 
Other values of $s_{\rm min}$ do not recover the input cosmology as well as $s_{\rm min}=6h^{-1}{\rm Mpc}$.
%the derived best-fit cosmology can deviate with the input cosmology at $1-2\sigma$.
%This means that there exists a systematics bias in the cosmological constraints derived using these $s_{\rm min}$.
%Therefore, when using $s_{\rm min}=$2,4,8 $h^{-1}{\rm Mpc}$, 
%Similar phenomenon happens when we adopt several different cosmologies ranging from $\Omega_m=0.2-0.4$, 
%\footnote{The reason that why these $s_{\rm min}$ some cosmologies achieve a larger likelihood value than the input cosmology is not very clear. 
%It could be just due to statistical fluctuation, or some inaccuracy in our simple likelihood estimation.
%We believe that the issue can be resolved in case of using the redshift evolution of the 2D likelihood map.
%e.g. the covariance .
%In our likelihood analysis the covariance matrix is estimated in the WMAP5 cosmology and applied to the whole parameter space.
%That is not very precise since the covariance matrix certainly depends on the values of $(\Omega_m,w)$.
%Possibly for some sets of parameters the covariance is relatively smaller, 
%so there the likelihood is {\it overestimated} if still adopting the covariance of WMAP5 cosmology,
%making them appears more preferred in the sense of our likelihood analysis.
 %for $s_{\rm min}=2,4,8\ h^{-1}{\rm Mpc}$.

%So it is not plausible to use these $s_{\rm min}$ values in the analysis,
%if the underlying systematics not properly corrected.

The cosmological constraints obtained using $s_{\rm min}=2,4,6,8\ h^{-1} {\rm Mpc}$ 
are presented in the right panel of Figure \ref{fig_contour_diffsmin}.
In the case of $s_{\rm min}\neq6h^{-1} {\rm Mpc}$, we apply a simple correction to the derived likelihood map, 
based on the discrepancy between the best-fit cosmology and the input cosmology found in the input-output test.

%Here the gray filled contours are constraints from our AP analysis.
These contours are consistent with each other within 1$\sigma$.
The $s_{\rm min}=8\ h^{-1}{\rm Mpc}$ result is very close to the main result.
The $s_{\rm min}=2$ or $4\ h^{-1}{\rm Mpc}$ contours show a systematical shift to the upper-left corner,
but the deviation is $\lesssim1\sigma$.
%we find the systematics mainly shifts the position contour along the 
%upper-left to lower-right diagonal.
The difference choices of $s_{\rm min}$ produce little effect on 
the joint constraint when combined with other cosmological probes (CMB+BAO+JLA+$H_0$). 
%To check that, we plot the joint constraints when our method combined with .
The difference from the main results is $\lesssim0.3\sigma$.
%Actually, even without applying the correction, 
%the combined constraints of $s_{\rm min}=2,4,8\ h^{-1} {\rm Mpc}$ are still very close to the $s_{\rm min}=6h^{-1}{\rm Mpc}$ result,
%with a difference $\lesssim0.6\sigma$ (dashed contour lines).

%When integrating the 2pCF over $s$, 
The small scales contribute more in the integration of $\xi$ over $s$,
so the result is more affected by $s_{\rm min}$ compared with $s_{\rm max}$. 
We are going  to investigate the redshift evolution of 2d 2pCF in a future study, 
which hopefully can resolve this issue.

%In our main analysis we adopt $s_{\rm min}=6 h^{-1}{\rm Mpc}$, which is found to have almost no systematic deviation in the input-output tests.
%The dependence on $s_{\rm min}$ is understandable since the small scale $\xi$ is the dominate contributor in the integration.
%This issue could be resolved if using the 2D $\xi$ to conduce the analysis.

\subsection{$Summary$}

%We conduct a series of tests to check whether the derived cosmological constraints are sensitive to the options adopted in the likelihood analysis.
%For the default options used to derive our main result, 
%we adopt $s_{\rm min}=6h^{-1}{\rm Mpc}$, $s_{\rm max}=40h^{-1}{\rm Mpc}$, $1 - \mu \ge 0.01$,
%the 72 sets of HR3 PSB mocks for covariance estimation,
%and J08 merger timescale model (used in the construction of HR4 mock galaxies).

We conduct a series of tests and find that the derived cosmological constraints are insensitive to the options adopted in the analysis.
Cosmological constraints are derived using different options of $s_{\rm min}$, $s_{\rm max}$, limits on $1-\mu$, mocks for covariance estimation,
and satellite galaxy merger time scale.
We do not detect a significant change of our results.

%We modify the above options, 
%derive the corresponding cosmological constraints, 
%and check how much it deviates from the result using default options
%In all tests conducted, we do not detect a change in cosmological constraint which is statistically significant.
%In most cases, the shift of the contour is $\lesssim0.2\sigma$.
%Also, we find the shift only happens along the upper-left to lower-right diagonal of the $\Omega_m$-$w$ plane,
%making the joint constraint (the result when combined with the other cosmological probes) rather stable.

%Among these options, $s_{\rm min}$ is the only one found to have a relative large effect on the result.
%We performed a series of input-output tests, 
%and found using $s_{\rm min}=6h^{-1}{\rm Mpc}$ can lead to unbiased cosmological constraint.
%In case of using $s_{\rm min}=2,4,8\ h^{-1}{\rm Mpc}$, 
%a correction should be made to account for the bias in the derived likelihood map.
%In our main analysis, we adopt $s_{\rm min}=6h^{-1}{\rm Mpc}$, and no such correction is needed.

Yet there are still unchecked options. 
One example is the redshift binning scheme.
In this analysis, the galaxies are split into six redshift bins of
$0.150<z_1<0.274<z_2<0.351<z_3<0.430<z_4<0.511<z_5<0.572<z_6<0.693$.
%and investigate the redshift evolution of the 2pCFs measured in these redshift bins.
We have not checked whether the results depend on choices such as the redshift limits and the number of redshift bins,
because each redshift binning scheme requires to repeat the whole analysis that involves the calculation of the correlation function 
at each point of the parameter space.
This issue is worthy of investigation in future studies, 
to design a optimized scheme having the maximal ability to constrain cosmological parameters.
%We did not check whether our result different redshift limits

In summary, the tests show that, the cosmological constraints reported in this paper are robust.

%In all, %the options adopted in our main analysis are all based on cautious considerations and careful tests.
%After a series of robustness tests, we find our result relatively insensitive to their values.
%Furthermore, through the input-output test we find the default options adopted in the main analysis is able to derive unbiased cosmological constraint.
%We conclude that, the cosmological constraint reported in this paper is fairly robust.

\

\

\

\begin{thebibliography}{}

\bibitem[Ade et al.(2015)]{Planck2015}
Ade, P.A.R., Aghanim, N., \& Arnaud, M., et al. arXiv:1502.01589

\bibitem[Alam et al.(2016)]{Alam2016}
Alam, S., Ata, M., \& Bailey, S., et al. 2016,
submitted to MNRAS (arXiv:1607.03155)

\bibitem[{{Alam} {et~al}\mbox{.}(2015{\natexlab{a}}){Alam}, {Albareti},
  {Allende Prieto}, {Anders}, {Anderson}, {Anderton}, {Andrews}, {Armengaud},
  {Aubourg}, {Bailey}, \& et~al.}]{dr12}
{Alam} S., Albareti, F.D.,\& Allende Prieto, C., {et~al.}, 2015,  ApJS, 219, 12

\bibitem[Alcock \& Paczynski(1979)]{AP1979}
Alcock, C., \& Paczynski, B. 1979, Nature, 281, 358

%\bibitem[Anderson et al.(2012)]{2012MNRAS.427.3435A} 
%Anderson, L., Aubourg, E., Bailey, S., et al.\ 2012, MNRAS, 427, 3435

\bibitem[Anderson et al.(2013)]{Anderson2013}
Anderson, L., Aubourg, \'E., \& Bailey, S. et al. 2014, MNRAS, 441, 24

%\bibitem[Bassett et al.(2002)]{Bassett2002}
%Bassett, B.A., Kunz, M., Silk, J., \& Ungarelli, C. 2002, MNRAS, 336, 1217

\bibitem[Ballinger, Peacock \& Heavens 1996]{Ballinger1996}
Ballinger, W.E., Peacock, J.A., \& Heavens, A.F. 1996, MNRAS, 282, 877

\bibitem[Betoule et al.(2014)]{JLA}
Betoule, M., Kessler, R., \& Guy, J., et al. 2014, A\&A, 568, 32

%#################################################################

\bibitem[Beutler et al.(2011)]{6dFGS}
Beutler, F., Blake, C., \& Colless, M., et al. 2011, MNRAS, 416, 3017

\bibitem[Beutler et al.(2012)]{Beutler2012}
Beutler, F., Blake, C., \& Colless, M., et al. 
2012, MNRAS, 423, 3430

\bibitem[Beutler et al.(2013)]{Beutler2013}
Beutler, F., Saito, S., \& Seo, H.-J., et al. 2013, MNRAS, 443, 1065

\bibitem[Beutler et al.(2016)]{Beutler2016}
Beutler, F., Seo, H.-J., \& Saito, S., et al. 2016,
arXiv:1607.03150

\bibitem[Blake et al.(2011)]{Blake2011a}
Blake, C., Brough, S., Colless, M., et al.
2011, MNRAS, 415, 2876

\bibitem[Blake et al.(2011)]{Blake2011}
Blake, C., Glazebrook, K., \& Davis, T. M., 2011, MNRAS, 418, 1725

\bibitem[Blake et al.(2013)]{WiggleZtopoloy}
Blake, C., James, J.B., \& Poole, G.B. 2013, MNRAS, 437, 2488

\bibitem[Bolton et al.(2012)]{Bolton2012}
Bolton, A.S., Schlegel, \& D.J., Aubourg E., et al. 2012, AJ, 144, 144

\bibitem[Boylan-Kolchin et al.(2008)]{B08}
Boylan-Kolchin, M., Ma, C.-P., \& Quataert, E. 2008, MNRAS, 383, 93

%\bibitem[Bueno Belloso et al. (2012)]{BB2012}
%Bueno Belloso, A., Pettinari, G.W., Meures, N., \& Percival, W.J. 2012, Phys. Rev. D, 86, 023530

%\bibitem[Chevallier \& Polarski(2001)]{CP2001}
%Chevallier, M., Polarski, D. 2001, Int. J. Mod. Phys. D, 10, 213

%\bibitem[Choi et al.(2010)]{choi 2010}
%Choi, Y.-Y., Park, C., Kim, J., Gott, J.R., 
%Weinberg, D.H., Vogeley, M.S., \& Kim, S.S. 2010, ApJS, 190, 181

\bibitem[Christensen et al.(2001)]{Bayesian}
Christensen, N., Meyer, R., Knox, L., \& Luey, B. 2001, Class. Quant. Grav., 18, 2677

%\bibitem[Chuang et al.(2013)]{Chuang2013}
%Chuang, C.-H., Prada, F., Beutler, F., et al. 2013, arXiv:1312.4889

\bibitem[Chuang \& Wang(2012)]{ChuangWang2012}
Chuang, C.-H., \& Wang, Y. 2012, MNRAS, 426, 226

%\bibitem[Corasaniti \& Copeland(2003)]{Corasaniti2003}
%Corasaniti, P.S., Copeland, E.J. 2003, Phys. Rev. D, 67, 063521

%eBOSS: 
%http://arxiv.org/abs/1508.04473
\bibitem[Dawson et al.(2015)]{eBOSS}
Dawson, K.S., Kneib, J.P., \& Percival, W.J., et al. 2015, accepted AJ

\bibitem[Dawson et al.(2012)]{Dawson et al. 2012}
Dawson, K.S., Schlegel, D.J., \& Ahn, C.P., et al. 2012, AJ, 145, 10

\bibitem[Efstathiou (2014)]{E14H0}
Efstathiou, G. 2014, MNRAS, 440, 1138

\bibitem[Eisenstein et al.(2011)]{Eisenstein et al. 2011}
Eisenstein, D.J.,  Weinberg, D.H., \& Agolet, E., et al. 2011, AJ, 142, 72

\bibitem[Feldman, Kaiser \& Peacock (1994)]{1994ApJ...426...23F} 
Feldman, H.A., Kaiser, N., \& Peacock, J.A.\ 1994, ApJ, 426, 23

\bibitem[Fukugita et al.(1996)]{Fukugita1996}
Fukugita, M., Ichikawa, T., \& Gunn, J.E., et al. 1996, AJ, 111, 1748
%Publication:	
%Astronomical Journal v.111, p.1748

%\bibitem[Gingold \& Monaghan(1977)]{GM1977}
%Gingold, R.A., \& Monaghan, J.J. 1977, MNRAS, 181, 375

%\bibitem[Gott et al.(2009)]{gott 2009}
%Gott, J.R., Choi, Y.-Y., Park, C., \& Kim, J. 2009, ApJ, 695, L45

%\bibitem[Gott et al.(2008)]{gott 2008}
%Gott, J.R., Hambrick, D.C., Vogeley, M.S., Kim, J., Park, C., Choi, Y.-Y.,
%Cen, R., Ostriker, J.P., \& Nagamine, K. 2008, ApJ, 675, 16

\bibitem[Gil-Mar\'{i}n et al.(2016)]{GM2016b}
Gil-Mar\'{i}n, H., Percival, W.J., Verde, L., et al. 2016, submitted to MNRAS

\bibitem[Gunn et al.(1998)]{Gunn1998}	
Gunn, J.E., Carr, M., \& Rockosi, C. et al. 1998, AJ, 116, 3040

\bibitem[Gunn et al.(2006)]{Gunn et al. 2006}
Gunn, J.E., Siegmund, W.A., \& Mannery, E.J., et al. 2006, AJ, 131, 2332

\bibitem[Guzzo et al.(2008)]{Guzzo2008}
Guzzo, L., Pierleoni, M., \& Meneux, B., et al. 2008, Nature, 451, 541

\bibitem[Hartlap et al.(2006)]{Hartlap}
Hartlap J., Simon P. \& Schneider P. [astro-ph/0608064].

\bibitem[Hong et al.(2016)]{hong2016}
Hong, S.E., Park, C.,\&  Kim, J. 2016, ApJ, 823, 103

\bibitem[Jackson (1972)]{FOG}
Jackson, J., 1972, MNRAS, 156, 1

\bibitem[Jennings et al.(2011)]{Jennings2011}
Jennings, E., Baugh, C.M., \& Pascoli, S. 2011, MNRAS, 420, 1079

%\bibitem[Jeong et al.(2014)]{Jeong2014}
%Jeong, D., Dai, L., Kamionkowski, M., \& Szalay, A.S. 2014, arXiv:1408.4648

\bibitem[Jiang et al.(2008)]{jiang2008}
Jiang, C.Y., Jing, Y. P., \& Faltenbacher, A., et al. 2008, ApJ, 675, 1095

\bibitem[Kaiser (1987)]{Kaiser1987}
Kaiser, N. 1987, MNRAS, 227, 1

\bibitem[Kim \& Park(2006)]{kim and park 2006}
Kim, J., \& Park, C. 2006, ApJ, 639, 600

\bibitem[Kim et al.(2009)]{2009ApJ...701.1547K} 
Kim, J., Park, C., Gott, J.R., III, \& Dubinski, J.\ 2009, ApJ, 701, 1547

\bibitem[Kim et al.(2015)]{hr4}
Kim, J., Park, C., L'Huillier, B., \& Hong, S. E. 2015, JKAS, 48, 213

\bibitem[Kim et al.(2011)]{horizonrun}
Kim, J., Park, C., Rossi, G., Lee, S.M., \& Gott, J.R. 2011, JKAS, 44, 217

\bibitem[Kitaura et al.(2014)]{Kitaura2014}
Kitaura, F.S., Yepes, G., \& Prada, F. 2014, MNRAS, 439, 21

\bibitem[Kitaura et al.(2015)]{MDPATCHY}
Kitaura, F.S., Rodrı\'{i}guez-Torres, S.A., Chuang, C.-H., et al. arXiv:1509.06400

\bibitem[Klypin et al.(2016)]{K2014}
Klypin, A., Yepes, G., Gottlober, S., Prada, F., \& Hess, S. 2016,
MNRAS, 457, 4340%
%Mon.Not.Roy.Astron.Soc. 457 (2016) no.4, 4340

\bibitem[Komatsu et al.(2011)]{komatsu 2011}
Komatsu, E., Smith, K. M., \& Dunkley, J., et al. 2011, ApJS, 192, 18

\bibitem[Lacey \& Cole(1993)]{LC93}
Lacey, C., \& Cole, S. 1993, MNRAS, 262, 627

\bibitem[Landy \& Szalay(1993)]{1993ApJ...412...64L} 
Landy, S.D., \& Szalay, A.S.\ 1993, ApJ, 412, 64

%EUCLID:
%http://arxiv.org/abs/1110.3193
\bibitem[Laureijs et al.(2011)]{EUCLID}
Laureijs, R., Amiaux, J., \& Arduini, S., et al. 2011, arXiv:1110.3193

\bibitem[Lavaux \& Wandelt(2012)]{LavausWandelt1995}
Lavaux, G., \& Wandelt, B.D. 2012, ApJ, 754, 109

%\bibitem[Levi et al.(2013)]{2013arXiv1308.0847L} 
%Levi, M., Bebek, C., Beers, T., et al.\ 2013, arXiv:1308.0847

\bibitem[Lewis \& Bridle (2002)]{LB2002}
Lewis, A., \& Bridle, S. 2002, Phys. Rev. D, 66, 103511

\bibitem[L'Huillier et al.(2014)]{2014NewA...30...79L} 
L'Huillier, B., Park, C., \& Kim, J.\ 2014, New Astronomy, 30, 79

\bibitem[Li et al.(2011)]{Li2011}
Li, M., Li, X.-D., Wang, S., \& Wang, Y. 2011, Commun. Theor. Phys., 56, 525

\bibitem[Li et al.(2014)]{Li2014}
Li, X.-D., Park, C., Forero-Romero, J., \& Kim, J. 2014, ApJ, 796, 137

\bibitem[Li et al.(2015)]{Li2015}
Li, X.-D., Park, C., Sabiu, C.G., \& Kim, J. 2015, MNRAS, 450, 807

\bibitem[Li et al.(2016)]{Li2016}
Li, Z., Jing, Y.P., Zhang, P., \& Cheng, D. 2016, submitted to ApJ

%\bibitem[Linder(2003)]{Linder2003}
%Linder, E.V. 2003, Phys. Rev. Lett., 90, 091301

\bibitem[Linder et al.(2014)]{Linder2013}
Linder, E.V., Minji, O., Okumura, T., Sabiu, C.G., \& Song, Y.-S. 2014, Phys. Rev. D, 89, 063525

\bibitem[L{\'o}pez-Corredoira(2014)]{2014ApJ...781...96L} 
L{\'o}pez-Corredoira, M.\ 2014, ApJ, 781, 96

\bibitem[Marinoni \& Buzzi(2010)]{Marinoni2010}
Marinoni, C., \& Buzzi, A. 2010, Nature, 468, 539

\bibitem[Matsubara \& Suto(1996)]{Matsubara1996}
Matsubara T., \& Suto, Y. 1996, ApJ, 470, L1

\bibitem[McCavana et al.(2012)]{M12}
McCavana, T., Micic, M., Lewis, G. F., et al. 2012, MNRAS, 424, 361

\bibitem[Morandi \& Sun (2016)]{MS2016}
Morandi, A., \& Sun, M. arXiv:1601.03741

\bibitem[Outram et al.(2004)]{Outram2004}
Outram, P.J., Shanks, T., Boyle, B.J., Croom, S.M., Hoyle, F., Loaring, N.S., 
Miller, L., \& Smith, R.J. 2004, MNRAS, 348, 745

%\bibitem[Parejko et al.(2013)]{Parejko2013}
%Parejko, J. K., Sunayama, T., Padmanabhan, N., et al. 2013, MNRAS, 429, 98

\bibitem[Parejko et al.(2013)]{Parejko2013}
Parejko J.K., et al., 2013, MNRAS, 429, 98

\bibitem[Parihar et al.(2014)]{CMASSLSS2014}
Parihar, P., Vogeley, M.S., \& Gott, J.R., et al. 2014, ApJ, 796, 86

\bibitem[Park et al.(2005)]{park 2005}
Park, C., Kim, J., \& Gott, J.R. 2005, ApJ, 633, 1

\bibitem[Park \& Kim(2010)]{topology}
Park, C., \& Kim, Y.-R. 2010, ApJL, 715, L185

\bibitem[Park et al.(2012)]{Park2012}
Park, C., Choi, Y.-Y., Kim, J., Gott, J.R., Kim, S.S., \&
Kim, K.-S. 2012, ApJ, 759, 7

\bibitem[Park et al.(2015)]{Park2015}
Park, C., Song, H., Einasto, M., Lietzen, H., \&
Heinamaki, P. 2015, JKAS, 48, 75

\bibitem[Peebles \& Ratra(2003)]{PR2003}
Peebles, P.J.E., \& Ratra, B. 2003, Reviews of Modern Physics, 75, 559

\bibitem[Percival et al.(2014)]{Percival2014}
Percival, W.J., Ross, A.J., \& S\'{a}nchez, A.G., et al. 2014, MNRAS, 439, 2531

\bibitem[Perlmutter et al.(1999)]{Perl1999}
Perlmutter, S., Aldering, G., \& Goldhaber, G., et al. 1999, ApJ, 517, 565

\bibitem[Press \& Shechter(1974)]{PS1974}
Press, W.H., \& Schechter, P.L. 1974, ApJ, 187, 425

\bibitem[Reid et al.(2012)]{Reid2012}
Reid, B., Samushia, L., \& White, M., et al. 2012, MNRAS, 426, 2719

\bibitem[Reid et al.(2012)]{Reid2012b}
Reid, B., Samushia, L., \& White, M., et al. 2012, MNRAS, 404, 69

\bibitem[Reid et al.(2016)]{Reidetal:2016}
Reid, B., Ho, S., \& Padmanabhan, N., et al.  2016, MNRAS, 455, 1553

\bibitem[Riess et al.(1998)]{Riess1998}
Riess, A.G., Filippenko, A.V., \& Challis, P., et al. 1998, AJ, 116, 1009

\bibitem[Riess et al.(2011)]{Riess2011}
Riess, A.G., Macri, L., \& Casertano, S., et al. 2011, ApJ, 730, 119
%A 3\% Solution: Determination of the Hubble Constant with the Hubble Space Telescope and Wide Field Camera

\bibitem[Rodriguez-Torres et al.(2016)]{RT2015}
Rodr\'{i}guez-Torres, S.A., Chuang, C.-H., \&  Prada, F., et al. 
2016, MNRAS, 460, 1173

\bibitem[Ross et al.(2012)]{2012MNRAS.424..564R} 
Ross, A.J., Percival, W.J., \& S{\'a}nchez, A.G. et al.\ 2012, MNRAS, 424, 564

\bibitem[Ross et al.(2015)]{MGS}
Ross, A.J., Samushia, L., \& Howlett, C., et al. 2015, MNRAS, 449, 835

\bibitem[Ryden(1995)]{Ryden1995}
Ryden, B.S. 1995, ApJ, 452, 25

%\bibitem[Samushia et al.(2014)]{Samushia2014}
%Samushia, L., Reid, B. A., White, M., et al. 2014, MNRAS, 439, 3504

%\bibitem[Sanchez et al.(2013)]{Sanchez2013}
%Sanchez, A. G., Kazin, E. A., Beutler, F., et al. 2013, MNRAS, 433, 1202

%\bibitem[Sutter et al.(2014)]{Sutter2014}
%Sutter, P.M., Pisani, A., Wandelt, B.D., \& Weinberg, D.H. 2014, MNRAS, 443, 2983
\bibitem[Samushia et al.(2012)]{Samushia2012}
Samushia, L., Percival, W.J., \& Raccanelli, A. 2012,
MNRAS, 420, 2102.

\bibitem[Sanchez et al.(2016)]{Sanchez2016}
Sanchez, A. G., Scoccimarro, R., \& Crocce, M., et al.
arXiv:1607.03147

\bibitem[Schlafly et al.(2010)]{Schlafly2010}
Schlafly E.F., Finkbeiner D.P., Schlegel D.J., et al. 2010, ApJ, 725, 1175

\bibitem[Schlafly \& Finkbeiner(2011)]{SF2011}
Schlafly E.F., \& Finkbeiner D.P. 2011, ApJ, 737, 103

%DESI:
%http://arxiv.org/abs/1106.1706
\bibitem[Schlegel et al.(2011)]{DESI}
Schlegel, D., Abdalla, F., \& Abraham, T., et al. 2011, arXiv:1106.1706

\bibitem[Smee et al.(2013)]{Smee2013}
Smee, S.A., Gunn, J.E., \& Uomoto, A., et al. 2013, AJ, 146, 32

\bibitem[Song et al.(2014)]{2014arXiv1407.2257S} 
Song, Y.S., Sabiu, C.G., 
Okumura, T., Oh, M., \& Linder, E.V.\ 2014, JCAP, 12, 005

\bibitem[Speare et al.(2015)]{Speare2015}
Speare, R., Gott, J.R., Kim, J., \& Park, C.
2015, ApJ, 799, 176

%\bibitem[Springel et al.(2005)]{Springel2005}
%Springel, V., White, S.D.M., Jenkinset, A., et al. 2005, Nature, 435, 629

%\bibitem[Tojeiro \& Percival(2011)]{Tojeiro2011}
%Tojeiro R., \& Percivial W.J. 2011, MNRAS, 417, 1114

%\bibitem[Tojeiro et al.(2012)]{Tojeiro2012}
%Tojeiro, R., Percival, W. J., Wake, D. A., et al. 2012, MNRAS, 424, 136

\bibitem[Viana \& Liddle(1996)]{VL1996}
Viana, P.T.P., \& Liddle, A.R. 1996, MNRAS, 281, 323

\bibitem[Villalobos et al.(2013)]{V13}
Villalobos, \'{A}., ́De Lucia, G., Weinmann, S.M., Borgani, S., \& Murante, G. 2013, MNRAS, 433, L49

\bibitem[Weinberg et al.(2013)]{DHW2013}
Weinberg, D.H, Mortonson, M.J., Eisenstein, D.J., et al. 2013, Physics Reports, 530, 87

\bibitem[Weinberg (1989)]{SW1989}
Weinberg, S. 1989, Reviews of Modern Physics, 61, 1

\bibitem[White (2011)]{White2011}
White M., et al. 2011, ApJ, 728, 126

\bibitem[York et al.(2000)]{York et al. 2000}
York, D.G., Adelman, J., \& Anderson, J.E., et al. 2000, AJ, 120, 1579

\bibitem[Zehavi et al.(2011)]{zehavi2011}
Zehavi, I., Zheng, Z., \& Weinberg, D.H., et al. 2011, ApJ, 736, 59

\end{thebibliography}

\end{document}

### 2017-06-10 src/AP_grid.f90

@@ -25,13 +25,16 @@ implicit none
   ommin=0.1;  ommax=0.4; 
   w0min=-1.4; w0max=-0.3; 
   wamin=-2.5; wamax=0.9;
-  numom=120; numw0=120; numwa=120  
+  numom=100; numw0=100; numwa=100  
 
 !  nowmodel = model_wcdm;   wamin=0.0;wamax=0.0;numwa=1
-  nowmodel = model_cpl; ommin=0.31; ommax=0.31; numom=1
+  nowmodel = model_cpl; !ommin=0.31; ommax=0.31; numom=1
 !  nowmodel = model_olcdm
 
-  suffixstr = 'base1omws_om0.2600_w-1.0000_fixom0.31'
+ 
+  !ommin=0.1; ommax=0.2; numom=34; suffixstr = 'base1omws_om0.2600_w-1.0000_1'!_fixom0.31'
+  !ommin=0.20303030303d0; ommax=0.3; numom=33; suffixstr = 'base1omws_om0.2600_w-1.0000_2'!_fixom0.31'
+  !ommin=0.30303030303d0; ommax=0.4; numom=33; suffixstr = 'base1omws_om0.2600_w-1.0000_3'!_fixom0.31'
 !  suffixstr = 'base1omws_om0.2600_w-1.0000_ExcludeLastThreeBins_B'
 !  suffixstr = 'base1omws_om0.2600_w-1.0000_nbins35to40'
 !  suffixstr = 'base1omws_om0.2600_w-1.0000_smax40'

### 2017-06-22 Draft/Draft0.2.tex
minor changes

--- 2017-06-10 Draft/Draft0.1.tex
@@
-\documentclass[useAMS,usenatbib]{mnras}
+%\documentclass[preprint,prd,aps,amsmath,amssymb,nofootinbib]{revtex4}
+%\documentclass[prd,aps,amsmath,amssymb,nofootinbib]{revtex4}
+%\documentclass[aps,twocolumn,showpacs,floatfix,superscriptaddress]{revtex4}
+\documentclass[prl,twocolumn,superscriptaddress,aps,amsmath,amssymb,nofootinbib,altaffilletter]{revtex4}
+%\documentclass[prl,superscriptaddress,twocolumn,nopreprintnumbers,floatfix,preprintnumbers,altaffilletter]{revtex4}
+
+\usepackage{graphicx}
+\usepackage{subfigure}
+\usepackage{bm}
+\usepackage{amsmath}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{float}
 \usepackage{color}
-\usepackage{graphicx}
-\usepackage{dcolumn}
-\usepackage{bm}
-\usepackage{amssymb}
-\usepackage{latexsym}
-\usepackage[T1]{fontenc}
-\usepackage{aecompl}
-
-\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm
-        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$~}\fi}} 
-\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\graphicspath{{figs/}}
 
@@
 
-\title[Constraining CPL via clustering shells of BOSS]{Cosmological constraints via clustering shells: 
-constraining the Chevallier-Polarski-Linder parametrization using the SDSS-III BOSS data}
+\title{Dynamical dark energy constraints via clustering shells of SDSS-III BOSS galaxies}
 
-\author[X-D. Li, C.G. Sabiu,  C. Park, Y. Wang,  G. Zhao, H. Park, A. Shafieloo, J. Kim, S.E. Hong]
-{ Xiao-Dong Li,$^{1,\dagger}$
+\author{ Xiao-Dong Li,$^{1,\dagger}$
 Cristiano G. Sabiu,$^{2}$
@@
 Juhan Kim,$^{4,1}$
-and Sungwook E. Hong$^{2}$
-\\
-$^1$School of Physics, Korea Institute for Advanced Study, 85 Heogi-ro, Dongdaemun-gu, Seoul 130-722, Korea\\
-$^2$Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 305-348, Korea\\
-$^3$NAOC\\
-$^4$Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 130-722, Korea\\
-$^{\dagger}$xiaodongli@kias.re.kr\\
-$\star$Corresponding Author: ***}
+and Sungwook E. Hong$^{2}$}
 
-%\date{Accepted 1988 December 15. Received 1988 December 14; in original form 1988 October 11}
-
-% \begin{keywords}
-% methods: data analysis -- methods: statistical -- Galaxies:
-% kinematics and dynamics -- Cosmology: observations -- large-scale
-% structure of universe
-% \end{keywords}
-
-\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2002}
-
-\maketitle
-
-\label{firstpage}
+  \affiliation{School of Physics, Korea Institute for Advanced Study, 85 Heogi-ro, Dongdaemun-gu, Seoul 130-722, Korea}
+  \affiliation{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 305-348, Korea}
+  \affiliation{NAOC}
+  \affiliation{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 130-722, Korea}
 
 \begin{abstract}
-We use the anisotropic clustering of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
+We use the anisotropic {\it clustering shells} of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
 12 spanning the redshift range $0.15<z<0.69$ to place constraints on the expansion history of the Universe. 
 Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy $w=w_0+w_a\frac{z}{1+z}$,
-while improving upon earlier works (Li et al. 2016), 
+while improving upon earlier works \citep{Li2016}, 
 we present a novel use of the Alcock-Paczynski (AP) test via the small scales clustering difference between redshift bins. 
@@
 
-% \begin{keywords}
-% circumstellar matter -- infrared: stars.
-% \end{keywords}
+\pacs{95.36.+x, 98.80.–k}
+\maketitle
 
-\section{Introduction}
+%\section{Introduction}
+{\it Introduction.}---
 The  origin  of  the  accelerating  expansion  of  the  universe  is  one of  the  most  salient  questions  in  contemporary cosmology. 
@@
 
-\cite{Li2016} applied the AP method to galaxies from the 3rd incarnation of the Sloan Digital Sky Survey (SDSS-III).
+\citep{Li2016} applied the AP method to galaxies from the 3rd incarnation of the Sloan Digital Sky Survey (SDSS-III).
 Combining the method with measurements of Cosmic Microwave Background (CMB), type Ia supernovae (SNIa), 
@@
 
-The paper is organised as follows; 
-in \S\ref{sec:method} we will briefly review the {\em clustering shells} method as proposed by \citet{Li2016} 
-and then discuss some improvements that allow us to extend and generalise the analysis for any dark energy model. 
-%In \S\ref{wcdm_constraint} we perform a consistency check with our pervious work using the same SDSS DR12 galaxies 
-%and focusing on a constant dark energy e.o.s parameter, $w$. 
-The results are presented in \S\ref{sec:results}, showing the constraints on the expansion history in terms of CPL parameters, $w_0, w_a$. 
-In \S\ref{sec:test} we perform test on the robustness of our results. 
-We then conclude in \S\ref{sec:conclusion}.
+%The paper is organised as follows; 
+%in \S\ref{sec:method} we will briefly review the {\em clustering shells} method as proposed by \citet{Li2016} 
+%and then discuss some improvements that allow us to extend and generalise the analysis for any dark energy model. 
+%%In \S\ref{wcdm_constraint} we perform a consistency check with our pervious work using the same SDSS DR12 galaxies 
+%%and focusing on a constant dark energy e.o.s parameter, $w$. 
+%The results are presented in \S\ref{sec:results}, showing the constraints on the expansion history in terms of CPL parameters, $w_0, w_a$. 
+%In \S\ref{sec:test} we perform test on the robustness of our results. 
+%We then conclude in \S\ref{sec:conclusion}.
 
-\section{Methodology}\label{sec:method}
+%\section{Methodology}\label{sec:method}
+{\it Methodology.}---
 
@@
 $0.150<z_1<0.274<z_2<0.351<z_3<0.430<z_4<0.511<z_5<0.572<z_6<0.693$.
-The number density of galaxies and the redshift binning scheme is plotted in the left panel of Fig.\ref{fig_TPCF}.
+The number density of galaxies and the redshift binning scheme is plotted in the left panel of Fig.\ref{fig_TpCF}.
 
@@
 
-The right panel of Fig.\ref{fig_TPCF} shows the contour map of $\xi(s,\mu)$ measured in the six redshift bins.
+The right panel of Fig.\ref{fig_TpCF} shows the contour map of $\xi(s,\mu)$ measured in the six redshift bins.
 The contour lines are not horizontal due to the effects of peculiar velocity,
@@
 with systematic effects subtracted:
-$ {\bf p}(z_i,\mu_{j}) \equiv\  \left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right] - \left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right]_{\rm sys}$.
+\begin{eqnarray}
+ {\bf p}(z_i,\mu_{j}) \equiv\ & \left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right] \\ \nonumber
+ &- \left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right]_{\rm sys}.
+\end{eqnarray}
 We use a number of $n_{\mu}$=20, 21, ... 25 bins for the value of $\hat\xi_{\Delta s}(\mu)$ at $0<\mu<\mu_{\rm max}$.
@@
 
-\section{Results}\label{sec:results}
+%\section{Results}\label{sec:results}
+{\it Results.}---
 
@@
 %%% To be written!!!
-\section{Robustness Test}\label{sec:test}
+%\section{Robustness Test}\label{sec:test}
+{\it Robustness Test.}---
 
@@
 
-\section{Conclusion}\label{sec:conclusion}
+%\section{Conclusion}\label{sec:conclusion}
+{\it Conclusion.}---
 
@@
 
-\section*{Acknowledgments}
-
+\begin{acknowledgments}
 We thank the Korea Institute for Advanced Study for providing computing resources (KIAS Center for Advanced Computation Linux Cluster System). 
@@
 We thank Stephen Appleby, Seokcheon Lee, van putten Maurice, Graziano Rossi and Yi Wang for helpful discussions.
+\end{acknowledgments}
+
+%% After the acknowledgments section, use the following syntax and the
+%% \facility{} macro to list the keywords of facilities used in the research
+%% for the paper.  Each keyword will be checked against the master list during
+%% copy editing.  Individual instruments or configurations can be provided
+%% in parentheses, after the keyword, but they will not be verified.
+
+%{\it Facilities:} \facility{Nickel}, \facility{HST (STIS)}, \facility{CXO (ASIS)}.
+
+%% Appendix material should be preceded with a single \appendix command.
+%% There should be a \section command for each appendix. Mark appendix
+%% subsections with the same markup you use in the main body of the paper.
+
+%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
+%% The equation counter will reset when it encounters the \appendix
+%% command and will number appendix equations (A1), (A2), etc.
+
+%% The reference list follows the main body and any appendices.
+%% Use LaTeX's thebibliography environment to mark up your reference list.
+%% Note \begin{thebibliography} is followed by an empty set of
+%% curly braces.  If you forget this, LaTeX will generate the error
+%% "Perhaps a missing \item?".
+%%
+%% thebibliography produces citations in the text using \bibitem-\cite
+%% cross-referencing. Each reference is preceded by a
+%% \bibitem command that defines in curly braces the KEY that corresponds
+%% to the KEY in the \cite commands (see the first section above).
+%% Make sure that you provide a unique KEY for every \bibitem or else the
+%% paper will not LaTeX. The square brackets should contain
+%% the citation text that LaTeX will insert in
+%% place of the \cite commands.
+
+%% We have used macros to produce journal name abbreviations.
+%% AASTeX provides a number of these for the more frequently-cited journals.
+%% See the Author Guide for a list of them.
+
+%% Note that the style of the \bibitem labels (in []) is slightly
+%% different from previous examples.  The natbib system solves a host
+%% of citation expression problems, but it is necessary to clearly
+%% delimit the year from the author name used in the citation.
+%% See the natbib documentation for more details and options.
+
+%\bibitem[Canizares et al.(1978)]{can78} Canizares, C. R.,
+%    Grindlay, J. E., Hiltner, W. A., Liller, W., \&
+%    McClintock, J. E.  1978, \apj, 224, 39
+
+%Wang Q H, Lindon O, Hardle W. 
+%Semiparametric regression analysis with missing response at random. 
+%J Am Stat Assoc, 2004, 99: 334－345
 
 \begin{thebibliography}{}
+%\citep{Riess:1998}
+%[astro-ph/0205436].
 
@@
 
-\bsp
-
-\label{lastpage}
-
 \end{document}

### 2017-06-22 Make_Neat_Github.sh

@@ -1,0 +1,29 @@
+
+mkdir -p ../APCPL/covmats
+cp -r src/*.f90 ../APCPL/src/
+cp -r src/Makefile ../APCPL/src/
+
+#exit
+
+for mubin in 20 21 22 23 24 25
+do
+ cp covmats/${mubin}mubins.mumax0.97.iz6.CovMock_2000.s6.0to40.0.covmat ../APCPL/covmats
+done
+
+mkdir -p ../APCPL/2pCFs/
+
+
+
+for catname in DR12v4-CMASS DR12v4-LOWZ
+do
+mkdir -p ../APCPL/2pCFs/$catname/xyzw.binsplitted
+for ibin in 1 2 3
+do
+cp /home/xiaodongli/SparseFilaments/data/input/boss2pcf/data/$catname/xyzw.binsplitted/data.xyzw.${ibin}of3.cosmo-converted.om0.2600_w-1.0000.rmax150.750rbins.600mubins.2pcf ../APCPL/2pCFs/$catname/xyzw.binsplitted
+for imock in 0 1 2 3 
+do
+filename=J08.RSD.00$imock.xyzw.${ibin}of3.rmax150.150rbins.120mubins.2pcf
+cp /home/xiaodongli/SparseFilaments/data/input/boss2pcf/data/$catname/xyzw.binsplitted/$filename ../APCPL/2pCFs/$catname/xyzw.binsplitted
+done
+done
+done

### 2017-06-22 src/AP_MCMC.f90

@@ -1,0 +1,281 @@
+
+module vol_avg_DAH
+implicit none
+
+contains
+
+end module
+
+!!!
+program main
+use LSS_ximu_tests
+USE de_model_init
+!USE de_chisqs_JLA
+implicit none
+  
+  integer :: i,j,k,i1,i2,iz,num_MCMCchain,numomwstds,nlines
+  
+  
+  integer :: iomcol=1,iw0col=1,iwacol=1,iomkcol=1,iH0col=1,maxcol, ifile,iline
+  
+  real(rt) :: omegam, omstds(1000), wstds(1000), DAs(nz), Hs(nz), & 
+    chisqs_nosyscor(n1,n2,nz-1), chisqs_syscor(n1,n2,nz-1), chisqs_nosyscor_all(nz-1), chisqs_syscor_all(nz-1), &
+    tmpX(1000),nowlnlike,nowAPlnlike,nowweight,nowom,noww0,nowH0,nowwa,nowomk,APlnlikemin,&
+    t0,t1,t2,dt
+  real(rt), allocatable :: APlnlikes(:), smutabstds(:,:,:,:,:)
+  character(charlen) :: inputMCMCfile, outputMCMCfile, mcmcdir, nowchisqstr, fileindexstr, MCMCfilestr, suffixstr=''
+  type(omwpar) :: nowpar
+  integer,parameter :: model_wcdm=3, model_cpl=4, model_owcdm=5, model_ocpl=6, model_lcdm=7, model_olcdm=8
+  integer :: nowmodel
+  logical :: smutabstds_inited, debug=.false., avg_counts = .false., print_allinfo=.false.
+
+
+!  nowmodel = model_wcdm
+  nowmodel = model_cpl
+!  nowmodel = model_olcdm
+  suffixstr = 'base1omws_om0.2600_w-1.0000_nbins26to27'
+!  suffixstr = 'base1omws_om0.2600_w-1.0000_ExcludeLastThreeBins_B'
+!  suffixstr = 'base1omws_om0.2600_w-1.0000_nbins35to40'
+!  suffixstr = 'base1omws_om0.2600_w-1.0000_smax40'
+!  suffixstr = 'base1omws_om0.3100_w-1.0000_smax40'
+!  suffixstr = 'base1omws_om0.1100_w-2.0000'
+!  print_allinfo = .true.
+  
+!---------------------------------------------------------
+  !--------------------------------
+  ! Settings of the model
+  
[…]

### 2017-06-22 Draft/Draft0.3.tex
minor changes

--- 2017-06-22 Draft/Draft0.2.tex
@@
   \affiliation{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 305-348, Korea}
-  \affiliation{NAOC}
+  \affiliation{National Astronomy Observatories, Chinese Academy of Science, Beijing, 100012, P.R.China}
   \affiliation{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 130-722, Korea}
@@
 we present a novel use of the Alcock-Paczynski (AP) test via the small scales clustering difference between redshift bins. 
-This differential measure appears to be a robust statistical tool which mitigates many systematic effect, 
+This differential measure appears to be a robust statistical tool which mitigates many systematic effects, 
 allowing for competitive and unbiased constrains. 
@@
 Adding the AP method reduces the $w_0-w_a$ contour area by 50\%.
-The method can be combined with the BAO method, 
+The method can be combined with the standard BAO method, 
 increasing the science output of ongoing and future galaxy surveys by a factor of 2.
@@
 modifications to gravity,  and a  non-zero  vacuum energy \cite[see][for a comprehensive review]{2012IJMPD..2130002Y}. 
-It is, therefore, crucial to obtain precise and unbiased measurements of the expansion history of the Universe allowing us to 
+Considering the wealth of theoretical explanations, it is crucial to obtain precise and unbiased measurements of the expansion history of the Universe allowing us to 
 differentiate between competing dark energy models.
@@
 has allowed tight constraints to be placed on the background averaged distance scales, $D_A(z)$ and $H^{-1}(z)$.  
-Assuming an incorrect cosmological model for the coordinate transformation from redshift space to comoving space produces residual geometric distortions. 
+Assuming an incorrect cosmological model for the coordinate transformation between redshift space and comoving space, produces residual geometric distortions in the resultant galaxy distribution. 
 These distortions are induced by the fact that measured distances along 
@@
 
-The main caveat of AP test is that,
-because the radial distances of galaxies are inferred from observed redshifts,
-AP tests are inevitably limited by peculiar motions of galaxies,
-which leads to apparent anisotropy even if the adopted cosmology is correct.
+The main caveat of the AP test is due to the fact that 
+the radial distances of galaxies are inferred from observed redshifts.
+Thus AP tests are inevitably affected by peculiar motions of galaxies,
+which leads to apparent anisotropy in the clustering signal, even if the adopted cosmology is correct.
 The effect, known as redshift-space distortions (RSD),
-is very difficult to be accurately modeled in the 2-point statistics of galaxy clustering \citep{Ballinger1996}.
+is notoriously difficult to model accurately in the 2-point statistics of galaxy clustering \citep{Ballinger1996}.
 
 As alternative methods, \cite{Marinoni2010} proposed using the symmetry properties of galaxy pairs;
-%Unfortunately this method is also seriously limited by RSD.
 however, since the peculiar velocity distorts the redshifts and changes the apparent tilt angles of galaxy pairs,
@@
 This approach has the advantage that the void regions are easier to model compared with dense regions,
-but has limitations in that it utilizes only low density regions of the LSS and requires large samples to achieve good statistics \citep{Qingqing2016}.
+but has limitations in that it utilizes only low density regions of the LSS and requires large samples to achieve competitive constraints \citep{Qingqing2016}.
 
@@
 In an effort to mitigate the RSD effect, \cite{Li2014} proposed utilizing the {\it redshift dependence} of the AP effect. 
-The anisotropies produced by the RSD effect are, although large, close to uniform in magnitude over a wide range in redshift. 
+The clustering anisotropies produced by are, although large, close to uniform in magnitude over a wide range in redshift. 
 However, if cosmological parameters are incorrectly chosen resulting in an AP effect, 
 the anisotropy in the clustering signal has a clear redshift dependence. 
-In a later work, \cite{Li2015} developed the AP methodology 
-which investigates the redshift dependence of galaxy 2-point correlation function (2pCF), 
+In a later work, \cite{Li2015} developed an AP methodology 
+that utilises the redshift dependence of the galaxy 2-point correlation function (2pCF), 
 measured as a function of angle between the galaxy pair and line-of-sight (LoS).
+As an illustration, Fig.\ref{fig_xy} shows how the shape distortion of objects (anisotropy of clustering signal) varies with distance (or redshift) when incorrect values of  $w_0$ or $w_a$ are used to infer distances.
 
@@
    \caption{\label{fig_xy}
-   The distance dependence of shape distortion in four wrongly assumed cosmologies,
+   The distance dependence of the shape distortion in four wrongly assumed cosmologies,
    assuming a true cosmology of $\Omega_m=0.31$, $w=-1$.
    There are four perfect squares with their true shapes plotted in blue dashed lines.
-   They are measured by an observer located at the origin, and the distances are computed in the two wrong cosmologies.
+   They are measured by an observer located at the origin, and the distances are reprojected in the four wrong cosmologies.
    The apparently distorted shapes are plotted in red solid lines.
@@
 
-\citep{Li2016} applied the AP method to galaxies from the 3rd incarnation of the Sloan Digital Sky Survey (SDSS-III).
-Combining the method with measurements of Cosmic Microwave Background (CMB), type Ia supernovae (SNIa), 
-baryon acoustic oscialltions (BAO), and $H_0$,
+\citep{Li2016} applied their AP method to galaxies from the 3rd incarnation of the Sloan Digital Sky Survey (SDSS-III).
+Combining their method with measurements of the Cosmic Microwave Background (CMB), type Ia supernovae (SNIa), 
+baryon acoustic oscillations (BAO), and $H_0$,
 they obtained very tight constraints of $ \Omega_m = 0.301 \pm 0.006,\ w=-1.054 \pm 0.025$.
-By reducing the RSD effect, 
-they are able to use the galaxy clustering down to 6 $h^{-1}$Mpc,
-which is a major advance in extracting the cosmological information 
-on small scales where galaxy clustering is strong and there are a lot of independent structures.
+In reducing the RSD effect, 
+they were able to use galaxy clustering on scales down to 6 $h^{-1}$Mpc,
+which is a major advance in extracting cosmological information 
+on small scales where galaxy clustering is strong and there are many independent structures.
 
-In this work as a continuation of the serious work we move forward to infer the constraints on dynamical dark energy.
+In this paper, we continue to develop our previous methodology and proceed to infer the constraints on dynamical dark energy.
 We will present a slightly improved methodology to that of \citep{Li2016},
-allowing for faster likelihood estimation and thus the exploration of larger parameter spaces. 
+allowing for faster likelihood estimation and thus the exploration of larger, higher dimensional parameter spaces. 
 The methodology we will present here, can be applied to any model of dynamical dark energy, 
-or indeed any appropriately chosen non-parametric approach could also be considered. 
+or indeed any appropriately chosen parametric or non-parametric decomposition of the cosmic expansion history. 
 However, as a first step, in this paper we will focus on the widely used Chevallier-Polarski-Linder (CPL) parametrization
 $w(z) = w_0 + w_a \frac{z}{1+z}$.
-As an illustration, Fig.\ref{fig_xy} shows how the shape distortion of objects varies with distance
-in case of wrongly adopted $w_0$ or $w_a$.
 
@@
 
-The spectroscopic sample of SDSS-III BOSS (Baryon Oscillation Spectroscopic Survey) has two primary catalogues:
+The spectroscopic galaxy sample of SDSS-III BOSS (Baryon Oscillation Spectroscopic Survey) has two primary catalogues:
 %the LOWZ at $z\leq0.4$, and CMASS covering $0.4\leq z \leq 0.7$. %of galaxies.
@@
 Following our previous methodology \citep{Li2016}, the information of small-scale anisotropic clustering is computed
-\footnote{These correlations were computed using the public, kd-tree + MPI code called KSTAT \citep{kstat}.} 
+\footnote{These correlations were computed using the public code \texttt{KSTAT} \citep{kstat}.} 
 as $\xi_{\Delta s} (\mu) \equiv \int_{s_{\rm min}}^{s_{\rm max}} \xi (s,\mu)\ ds$, 
@@
 and the RSD effect clearly manifest itself through the tilting of contour lines.
-But the shape of the tilted lines remain similar at different redshifts, which enables us avoiding RSD by looking at the redshift dependence.
+However, the shape of the tilted lines remain similar at different redshifts, a fact that enables us  to mitigate the RSD effect by focusing on the redshift dependence of the anisotropic clustering signal.
 The ``correct'' cosmological model is selected by minimising the amount of redshift evolution of $\hat\xi_{\Delta s}$,
@@
 \end{equation}
-where ${\bf p}(z_i,\mu_{j})$ is the redshift evolution of clustering with respective to the lowest redshift bin,
-with systematic effects subtracted:
+where ${\bf p}(z_i,\mu_{j})$ is the redshift evolution of clustering with respect to the lowest redshift bin,
+while subtracting systematic effects:
 \begin{eqnarray}
@@
 -- which is taken as the $\Omega_m=0.26$ $\Lambda$CDM --
-and ``translated'' to the measurements in a ``target'' cosmology using the realtion of 
+and ``translated'' to the measurements in a ``target'' cosmology using the relations, 
 \begin{eqnarray}
@@
 %in the fiducial cosmology and group the bins in the target cosmology.
-The ``edge effects'' in case of one small pixel belonging to more than one large pixel
-are treated by computing the fraction of the area.
-We found that using the approximated method the computed 
-$\hat\xi_{\Delta s}(\mu)$ in non-fiducial cosmologies suffer from
+In the case when one small pixel belongs to more than one larger pixel (``edge effect'' ),
+a correction is applied by computing the fraction of the overlapping area.
+We found when using the approximate method the computed 
+$\hat\xi_{\Delta s}(\mu)$ in a non-fiducial cosmology suffers from
 an error of $\approx0.5\%$, which is 10 times smaller than 
@@
 
-The Planck team has released the {\texttt {COSMOMC}} \citep{LB2002} outputs of four ``chains'' in the CPL model, 
-using a combination of four techniques:
+The Planck team has released the {\texttt {COSMOMC}} \citep{LB2002} outputs of four MCMC ``chains'' in the CPL model, 
+using a combination of four datasets:
 the full-mission Planck observations of CMB temperature and polarization anisotropies \cite{Planck2015},
@@
 \footnote{http://pla.esac.esa.int/pla/\#cosmology}.
-These chains contain the CMB+BAO+SNIa+$H_0$ likelihood computed at $\sim$37 thounsands sets of cosmological parameters,
+These MCMC chains contain the CMB+BAO+SNIa+$H_0$ likelihood computed for $\sim$37,000 sets of cosmological parameters,
 yielding constraints of 
@@
 %To include the AP method into the constraints,
-We then compute the likelihood of AP method at these parameters, 
-multiplying the sample likelihoods with ours and also correspondingly changing the sample weights,
-and derive the CMB+BAO+SNIa+$H_0$+AP constraints on CPL parameters
+We then compute the likelihood of the LOWZ+CMASS AP measurements for each of the parameter combinations provided in the Planck chain.
+After multiplying the sample likelihoods with ours, while also changing the sample weights {\bf (HOW CHANGE?)}, we derive the CMB+BAO+SNIa+$H_0$+AP constraints on CPL parameters,
 \begin{equation}
@@
     %4 -0.3808376E-01  0.2716607E+00 -0.3105235E+00  0.2321461E+00 -0.6033103E+00  0.4782076E+00   w_a    
-\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29,    
+\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29.
 %    1  0.3014353E+00  0.7759923E-02  0.2974325E+00  0.3048882E+00  0.2889838E+00  0.3152269E+00   \Omega_m
@@
 %$$.
-While the central values of parameters do not shift significantly,
-the erro bars of $w_0$ and $w_a$ are reduced by 38.4\% and 29.7\%, respectively.% $$-40\%$ by adding our method into the analysis.
+While the central values of parameters do not shift appreciably,
+the error bars of $w_0$ and $w_a$ are reduced by 38.4\% and 29.7\%, respectively.% $$-40\%$ by adding our method into the analysis.
 
-The marginalised constraints on $w_0-w_a$ are shown in the left panel of Fig.\ref{fig_con}, 
+The marginalised constraints on $w_0-w_a$ are shown in the left panel of Fig.\ref{fig_con}.
 Adding our new AP constraints significantly reduces the allowable parameter space. 
-We can also visualise this as allowable bands in $w(z)$ as can be seen in the right panel of Fig.\ref{fig_con}.
+This can also be visualise as allowable bands in $w(z)$ as can be seen in the right panel of Fig.\ref{fig_con}.
 
 The derived cosmological constraints are fully consistent with a cosmological constant dark energy component having no evolution.
-Adding the AP method reduces the statistical errors by $\sim$30-40\%,
-reduces the 95.4\% CL $w_0-w_a$ contour by 50\%.
-This reveals the power of the our method in constraining the redshift evolution of dark energy.
+Adding the new AP method to the CMB+BAO+SNIa+$H_0$ constraints reduces the statistical errors by $\sim$30-40\%,
+and reduces the 95.4\% CL $w_0-w_a$ contour by 50\%.
+This reveals the constraining power of the small scale AP effect for probing the redshift evolution of dark energy.
 
@@
 the result does not change if 
-we adopt $\mu_{\rm max}=0.99\ (0.85)$ to include more (less) near-LOS regions in the analysis,
-decrease the number of bins to $n_{\mu}=15-20$,
+we adopt $\mu_{\rm max}=0.99\ (0.85)$ to include more (less) regions near the LOS,
+decrease the number of angular bins to $n_{\mu}=15-20$,
 change the range of clustering to $8-30 \rm Mpc/h$,
@@
 This enables a robust Alcock-Paczynski test on relatively small scales.
-In this paper we improved the methodology and obtained tight constraints on the CPL parametrization of dark energy. 
+In this paper we improved the methodology and obtained tight constraints on the CPL parametrization of dark energy using 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
+12 spanning the redshift range $0.15<z<0.69$ . 
 Adding our constraints to the CMB+SNIa+BAO+$H_0$ combination, the $w_0-w_a$ contour was reduced by $\sim50$\%.
 
-The AP method presented in this work has many advantages over the 'traditional' galaxy clustering method.
+The AP method presented in this work has many advantages over the `traditional' galaxy clustering method.
 Since it works with the redshift evolution of the anisotropic clustering signal it significantly reduces the effect of systematics. 
@@
 CGS acknowledges support from the National Research Foundation (NRF,  \#2017R1D1A1B03034900). 
-We thank Stephen Appleby, Seokcheon Lee, van putten Maurice, Graziano Rossi and Yi Wang for helpful discussions.
+We thank Stephen Appleby, Seokcheon Lee, Maurice van Putten, Graziano Rossi and Yi Wang for helpful discussions.
 \end{acknowledgments}

### 2017-06-22 Draft/Draft0.4.bib2.tex
minor changes

--- 2017-06-22 Draft/Draft0.3.tex
@@
-%\documentclass[preprint,prd,aps,amsmath,amssymb,nofootinbib]{revtex4}
-%\documentclass[prd,aps,amsmath,amssymb,nofootinbib]{revtex4}
-%\documentclass[aps,twocolumn,showpacs,floatfix,superscriptaddress]{revtex4}
-\documentclass[prl,twocolumn,superscriptaddress,aps,amsmath,amssymb,nofootinbib,altaffilletter]{revtex4}
-%\documentclass[prl,superscriptaddress,twocolumn,nopreprintnumbers,floatfix,preprintnumbers,altaffilletter]{revtex4}
-
+\documentclass{natureprintstyle}
+%\documentclass[12pt]{nature}
+
+\spacing{1}
+\spacing{2}
+\spacing{1}
+
+%\usepackage{epsfig,caption}
+\usepackage{amsmath,amssymb}
+\usepackage[applemac]{inputenc}
 \usepackage{graphicx}
-\usepackage{subfigure}
+\usepackage{color}
 \usepackage{bm}
-\usepackage{amsmath}
-\usepackage{array}
-\usepackage{multirow}
-\usepackage{float}
-\usepackage{color}
-\graphicspath{{figs/}}
-
-\begin{document}
-
-\title{Dynamical dark energy constraints via clustering shells of SDSS-III BOSS galaxies}
-
-\author{ Xiao-Dong Li,$^{1,\dagger}$
+\usepackage{longtable}
+\usepackage{amssymb}
+\usepackage{rotating}
+\usepackage{hyperref}
+%\captionsetup[figure]{labelformat=empty}
+%\captionsetup[table]{labelformat=empty}
+
+\newcommand{\gt}{$>$}
+\newcommand{\diamonds}{\textsc{D\large{iamonds}}}
+\usepackage{hyperref}
+
+\let\citep\cite
+\let\citet\cite
+
+\bibliographystyle{naturemag}
+
+\title{\sffamily Dynamical dark energy constraints via clustering shells of SDSS-III BOSS galaxies}
+
+\author{\sffamily 
+Xiao-Dong Li,$^{1,\dagger}$
 Cristiano G. Sabiu,$^{2}$
@@
 and Sungwook E. Hong$^{2}$}
-
-  \affiliation{School of Physics, Korea Institute for Advanced Study, 85 Heogi-ro, Dongdaemun-gu, Seoul 130-722, Korea}
-  \affiliation{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 305-348, Korea}
-  \affiliation{National Astronomy Observatories, Chinese Academy of Science, Beijing, 100012, P.R.China}
-  \affiliation{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 130-722, Korea}
-
+%Enrico Corsaro$^{1,2,3,4}$, Yueh-Ning Lee$^1$, Rafael A.
+Garc\'{i}a$^{1}$, Patrick Hennebelle$^1$, Savita Mathur$^{5}$, Paul G.
+Beck$^1$, Stephane Mathis$^1$, Dennis Stello$^{6,7}$ \& J\'er\^{o}me Bouvier$^8$}
+
+\begin{document}
+\maketitle
+\let\thefootnote\relax\footnote{
+
+\begin{affiliations}
+  \item School of Physics, Korea Institute for Advanced Study, 85 Heogi-ro, Dongdaemun-gu, Seoul 130-722, Korea
+  \item Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 305-348, Korea
+  \item National Astronomy Observatories, Chinese Academy of Science, Beijing, 100012, P.R.China
+  \item Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 130-722, Korea
+\end{affiliations}
+}
+
+\vspace{-3.5mm}
 \begin{abstract}
+\sffamily
 We use the anisotropic {\it clustering shells} of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
@@
 
-\pacs{95.36.+x, 98.80.–k}
-\maketitle
-
-%\section{Introduction}
+\sffamily
 {\it Introduction.}---
@@
 
-\begin{figure*}
-   \centering{
-   \includegraphics[height=5cm]{fig_xy.eps}
-   %\includegraphics[height=8cm]{fig4_1.eps}
-   %\includegraphics[height=7cm]{FVol.eps}
-   %\includegraphics[height=8cm]{xy.eps}
-   %\includegraphics[height=8cm]{smu.eps}
-   }
-   \caption{\label{fig_xy}
-   The distance dependence of the shape distortion in four wrongly assumed cosmologies,
-   assuming a true cosmology of $\Omega_m=0.31$, $w=-1$.
-   There are four perfect squares with their true shapes plotted in blue dashed lines.
-   They are measured by an observer located at the origin, and the distances are reprojected in the four wrong cosmologies.
-   The apparently distorted shapes are plotted in red solid lines.
-   }
-\end{figure*}
-
-%$\xi_{\Delta s}(\mu)\equiv \int_{s_{\rm min}}^{s_{\rm max}} xi(s,\mu) ds$
-%($s$ is the clustering scale).
-%The RSD effect significantly distorts the shape of $\xi_{\Delta s}(mu)$ but exhibits much less redshift evolution 
-%compared to the amount of change in due to incorrectly adopted cosmologies .
-
-%When incorrect cosmological parameters are adopted, the shape of $\xi(\mu)$
-%appears anisotropic due to the AP effect, and the amplitude
-%is shifted by the change in comoving volume; both effects
-%have significant redshift dependence. We test the method
-%using the 2pCF on mock surveys drawn from HR3 and
-%find the constraints obtained are tighter than those from
-%the methodology of Li et al. (2014).
-
 \citep{Li2016} applied their AP method to galaxies from the 3rd incarnation of the Sloan Digital Sky Survey (SDSS-III).
@@
 
-%The paper is organised as follows; 
-%in \S\ref{sec:method} we will briefly review the {\em clustering shells} method as proposed by \citet{Li2016} 
-%and then discuss some improvements that allow us to extend and generalise the analysis for any dark energy model. 
-%%In \S\ref{wcdm_constraint} we perform a consistency check with our pervious work using the same SDSS DR12 galaxies 
-%%and focusing on a constant dark energy e.o.s parameter, $w$. 
-%The results are presented in \S\ref{sec:results}, showing the constraints on the expansion history in terms of CPL parameters, $w_0, w_a$. 
-%In \S\ref{sec:test} we perform test on the robustness of our results. 
-%We then conclude in \S\ref{sec:conclusion}.
-
-%\section{Methodology}\label{sec:method}
-{\it Methodology.}---
-
+The Planck team has released the {\texttt {COSMOMC}} \citep{LB2002} outputs of four MCMC ``chains'' in the CPL model, 
+using a combination of four datasets:
+the full-mission Planck observations of CMB temperature and polarization anisotropies \cite{Planck2015},
+the BAO distance priors measured from SDSS DR11 \citep{Anderson2013}, 6dFGS \citep{6dFGS} and SDSS MGS \citep{MGS},
+the ``JLA'' SNIa sample \citep{JLA},
+and the Hubble Space Telescope measurement of $H_0=70.6\pm3.3$ \cite{Riess2011,E14H0}.
+These MCMC chains contain the CMB+BAO+SNIa+$H_0$ likelihood computed for $\sim$37,000 sets of cosmological parameters,
+yielding constraints of 
+\begin{equation}
+ \Omega_m = 0.309 \pm 0.010, w_0 = -0.938 \pm 0.109, w_a = -0.38 \pm 0.41.
+\end{equation}
+%To include the AP method into the constraints,
+We then compute the likelihood of the LOWZ+CMASS AP measurements for each of the parameter combinations provided in the Planck chain. 
+To do this, we splited the 1,133,326 galaxies from the SDSS DR12 into six redshift bins,
+measured the 2pCF in these redshift bins, 
+and use a $\chi^2$ function to assess the redshift dependence.
+Systematic effects are estimated via mocks made from Horizon Run 4 simulations \citep{HR4}, and subtracted when computing the $\chi^2$.
+After adding the sample log-likelihoods with ours, 
+while also multiply the sample weights by our likelihoods, 
+we derive the CMB+BAO+SNIa+$H_0$+AP constraints on CPL parameters,
+\begin{equation}
+%\Omega_m = 0.300 \pm 0.008, w_0 = -1.056 \pm 0.061, w_a = -0.04 \pm 0.27,
+    %1  0.2999656E+00  0.7616334E-02  0.2958745E+00  0.3035033E+00  0.2878169E+00  0.3132870E+00   \Omega_m
+    %2  0.6904801E+00  0.8675444E-02  0.6808558E+00  0.6993898E+00  0.6722945E+00  0.7052207E+00   h
+    %3 -0.1056468E+01  0.6096323E-01 -0.1116874E+01 -0.9965903E+00 -0.1175041E+01 -0.9287388E+00   w
+    %4 -0.3808376E-01  0.2716607E+00 -0.3105235E+00  0.2321461E+00 -0.6033103E+00  0.4782076E+00   w_a    
+\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29.
+%    1  0.3014353E+00  0.7759923E-02  0.2974325E+00  0.3048882E+00  0.2889838E+00  0.3152269E+00   \Omega_m
+%    2  0.6887652E+00  0.8760036E-02  0.6797134E+00  0.6978279E+00  0.6703971E+00  0.7044224E+00   h
+%    3 -0.1041626E+01  0.6732817E-01 -0.1107730E+01 -0.9768319E+00 -0.1172149E+01 -0.8979017E+00   w
+%    4 -0.7173374E-01  0.2860547E+00 -0.3572176E+00  0.2107347E+00 -0.6775045E+00  0.4558817E+00   w_a    
+\end{equation}
+%$$.
+While the central values of parameters do not shift appreciably,
+the error bars of $w_0$ and $w_a$ are reduced by 38.4\% and 29.7\%, respectively.% $$-40\%$ by adding our method into the analysis.
+
+The marginalised constraints on $w_0-w_a$ are shown in the left panel of Fig.\ref{fig_con}.
+Adding our new AP constraints significantly reduces the allowable parameter space. 
+This can also be visualise as allowable bands in $w(z)$ as can be seen in the right panel of Fig.\ref{fig_con}.
+
+The derived cosmological constraints are fully consistent with a cosmological constant dark energy component having no evolution.
+Adding the new AP method to the CMB+BAO+SNIa+$H_0$ constraints reduces the statistical errors by $\sim$30-40\%,
+and reduces the 95.4\% CL $w_0-w_a$ contour by 50\%.
+This reveals the constraining power of the small scale AP effect for probing the redshift evolution of dark energy.
+
+We performed a thorough test of all the possible variables in our methodology.
+Figure \ref{fig_contest} shows that,
+the result does not change if change them.
+%we adopt $\mu_{\rm max}=0.99\ (0.85)$ to include more (less) regions near the LOS,
+%decrease the number of angular bins to $n_{\mu}=15-20$,
+%change the range of clustering to $8-30 \rm Mpc/h$,
+%change the fiducial cosmology to $\Omega_m=0.26,\ w=-0.6$,
+%exclude 1 or 2 high redshift bins,
+%or reduce the number of mocks to 1000.
+The most striking point to note in our testing is that the 
+shift in contour position is very small even when we do not include the systematic correction.
+This is reassuring, since we may have worried that {\it cosmological dependence} 
+on the systematic correction could influence on our final results.
+
+In sum, \cite{Li2016} proposed to constrain cosmological parameters via 
+the redshift dependence of galaxy anisotropic clustering.
+This enables a robust AP test on relatively small scales.
+In this paper we improved the methodology and obtained tight constraints on the CPL parametrization of dark energy.
+%using 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
+%12 spanning the redshift range $0.15<z<0.69$ . 
+%Adding our constraints to the CMB+SNIa+BAO+$H_0$ combination, the $w_0-w_a$ contour was reduced by $\sim50$\%.
+The AP method presented in this work has many advantages over the `traditional' galaxy clustering method.
+Since it works with the redshift evolution of the anisotropic clustering signal it significantly reduces the effect of systematics. 
+It avoids the great difficulty in accurate modelling of the RSD, non-linear clustering and galaxy bias.
+It is applicable on much smaller scales, allowing for the inclusion of more $k$-modes and hence more information.
+
+The presented method of clustering shells can be applied to many spectroscopic galaxy surveys. 
+The method is complimentary to the BAO method and the two methods can be combined together, 
+increasing (by roughly twice) the science output of ongoing and future surveys, with little to no additional cost.
+We expect it play an important role in helping us unveiling the mystery of dark energy.
+
+\begin{thebibliography}{10}
+\expandafter\ifx\csname url\endcsname\relax
+  \def\url#1{\texttt{#1}}\fi
+\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
+\providecommand{\bibinfo}[2]{#2}
+\providecommand{\eprint}[2][]{\url{#2}}
+
+\bibitem[Ade et al. (2015)]{Planck2015}
+Ade, P.A.R., Aghanim, N., \& Arnaud, M., et al. arXiv:1502.01589
+
+\bibitem[Alam et al.(2016)]{Alam2016}
+Alam, S., Ata, M., \& Bailey, S., et al. 2016,
+submitted to MNRAS (arXiv:1607.03155)
+
+%\bibitem[{{Alam} {et~al}\mbox{.}(2015{\natexlab{a}}){Alam}, {Albareti},
+%  {Allende Prieto}, {Anders}, {Anderson}, {Anderton}, {Andrews}, {Armengaud},
+%  {Aubourg}, {Bailey}, \& et~al.}]{dr12}
+%{Alam} S., Albareti, F.D.,\& Allende Prieto, C., {et~al.}, 2015,  ApJS, 219, 12
+
+\bibitem[Alcock \& Paczynski(1979)]{AP1979}
+Alcock, C., \& Paczynski, B. 1979, Nature, 281, 358
+
+%\bibitem[Anderson et al.(2012)]{2012MNRAS.427.3435A} 
+%Anderson, L., Aubourg, E., Bailey, S., et al.\ 2012, MNRAS, 427, 3435
+
+\bibitem[Anderson et al.(2013)]{Anderson2013}
+Anderson, L., Aubourg, \'E., \& Bailey, S. et al. 2014, MNRAS, 441, 24
+
+%\bibitem[Bassett et al.(2002)]{Bassett2002}
+%Bassett, B.A., Kunz, M., Silk, J., \& Ungarelli, C. 2002, MNRAS, 336, 1217
+
+\bibitem[Ballinger, Peacock \& Heavens 1996]{Ballinger1996}
+Ballinger, W.E., Peacock, J.A., \& Heavens, A.F. 1996, MNRAS, 282, 877
+
+\bibitem[Betoule et al.(2014)]{JLA}
+Betoule, M., Kessler, R., \& Guy, J., et al. 2014, A\&A, 568, 32
+
+\bibitem[Beutler et al.(2011)]{6dFGS}
+Beutler, F., Blake, C., \& Colless, M., et al. 2011, MNRAS, 416, 3017
+
+\bibitem[Beutler et al.(2013)]{Beutler2013}
+Beutler, F., Saito, S., \& Seo, H.-J., et al. 2013, MNRAS, 443, 1065
+
+\bibitem[Beutler et al.(2016)]{Beutler2016}
+Beutler, F., Seo, H.-J., \& Saito, S., et al. 2016,
+arXiv:1607.03150
+
+\bibitem[Blake et al.(2011)]{Blake2011}
+Blake, C., Glazebrook, K., \& Davis, T. M., 2011, MNRAS, 418, 1725
+
+\bibitem[Blake et al.(2013)]{WiggleZtopoloy}
+Blake, C., James, J.B., \& Poole, G.B. 2013, MNRAS, 437, 2488
+
+\bibitem[Bolton et al.(2012)]{Bolton2012}
+Bolton, A.S., Schlegel, \& D.J., Aubourg E., et al. 2012, AJ, 144, 144
+
+\bibitem[Boylan-Kolchin et al.(2008)]{B08}
+Boylan-Kolchin, M., Ma, C.-P., \& Quataert, E. 2008, MNRAS, 383, 93
+
+%\bibitem[Bueno Belloso et al. (2012)]{BB2012}
+%Bueno Belloso, A., Pettinari, G.W., Meures, N., \& Percival, W.J. 2012, Phys. Rev. D, 86, 023530
+
+%\bibitem[Chevallier \& Polarski(2001)]{CP2001}
+%Chevallier, M., Polarski, D. 2001, Int. J. Mod. Phys. D, 10, 213
+
+%\bibitem[Choi et al.(2010)]{choi 2010}
+%Choi, Y.-Y., Park, C., Kim, J., Gott, J.R., 
+%Weinberg, D.H., Vogeley, M.S., \& Kim, S.S. 2010, ApJS, 190, 181
+
+\bibitem[Christensen et al.(2001)]{Bayesian}
+Christensen, N., Meyer, R., Knox, L., \& Luey, B. 2001, Class. Quant. Grav., 18, 2677
+
+%\bibitem[Chuang et al.(2013)]{Chuang2013}
+%Chuang, C.-H., Prada, F., Beutler, F., et al. 2013, arXiv:1312.4889
+
+\bibitem[Chuang \& Wang(2012)]{ChuangWang2012}
+Chuang, C.-H., \& Wang, Y. 2012, MNRAS, 426, 226
+
+%\bibitem[Corasaniti \& Copeland(2003)]{Corasaniti2003}
+%Corasaniti, P.S., Copeland, E.J. 2003, Phys. Rev. D, 67, 063521
+
+%eBOSS: 
+%http://arxiv.org/abs/1508.04473
+\bibitem[Dawson et al.(2015)]{eBOSS}
+Dawson, K.S., Kneib, J.P., \& Percival, W.J., et al. 2015, accepted AJ
+
+\bibitem[Dawson et al.(2012)]{Dawson et al. 2012}
+Dawson, K.S., Schlegel, D.J., \& Ahn, C.P., et al. 2012, AJ, 145, 10
+
+\bibitem[Efstathiou (2014)]{E14H0}
+Efstathiou, G. 2014, MNRAS, 440, 1138
+
+\bibitem[Eisenstein et al.(2011)]{Eisenstein et al. 2011}
+Eisenstein, D.J.,  Weinberg, D.H., \& Agolet, E., et al. 2011, AJ, 142, 72
+
+\bibitem[Feldman, Kaiser \& Peacock (1994)]{1994ApJ...426...23F} 
+Feldman, H.A., Kaiser, N., \& Peacock, J.A.\ 1994, ApJ, 426, 23
+
+\bibitem[Fukugita et al. (1996)]{Fukugita1996}
+Fukugita, M., Ichikawa, T., \& Gunn, J.E., et al. 1996, AJ, 111, 1748
+%Publication:	
+%Astronomical Journal v.111, p.1748
+
+%\bibitem[Gingold \& Monaghan(1977)]{GM1977}
+%Gingold, R.A., \& Monaghan, J.J. 1977, MNRAS, 181, 375
+
+%\bibitem[Gott et al.(2009)]{gott 2009}
+%Gott, J.R., Choi, Y.-Y., Park, C., \& Kim, J. 2009, ApJ, 695, L45
+
+%\bibitem[Gott et al.(2008)]{gott 2008}
+%Gott, J.R., Hambrick, D.C., Vogeley, M.S., Kim, J., Park, C., Choi, Y.-Y.,
+%Cen, R., Ostriker, J.P., \& Nagamine, K. 2008, ApJ, 675, 16
+
+\bibitem[Gunn et al. (1998)]{Gunn1998}	
+Gunn, J.E., Carr, M., \& Rockosi, C. et al. 1998, AJ, 116, 3040
+
+\bibitem[Gunn et al.(2006)]{Gunn et al. 2006}
+Gunn, J.E., Siegmund, W.A., \& Mannery, E.J., et al. 2006, AJ, 131, 2332
+
+\bibitem[Guzzo et al.(2008)]{Guzzo2008}
+Guzzo, L., Pierleoni, M., \& Meneux, B., et al. 2008, Nature, 451, 541
+
+\bibitem[Hartlap et al.(2006)]{Hartlap}
+Hartlap J., Simon P. \& Schneider P. [astro-ph/0608064].
+
+\bibitem[Hong et al.(2016)]{hong2016}
+Hong, S.E., Park, C.,\&  Kim, J. 2016, ApJ, 823, 103
+
+\bibitem[Jackson (1972)]{FOG}
+Jackson, J., 1972, MNRAS, 156, 1
+
+\bibitem[Jennings et al.(2011)]{Jennings2011}
+Jennings, E., Baugh, C.M., \& Pascoli, S. 2011, MNRAS, 420, 1079
+
+%\bibitem[Jeong et al.(2014)]{Jeong2014}
+%Jeong, D., Dai, L., Kamionkowski, M., \& Szalay, A.S. 2014, arXiv:1408.4648
+
+\bibitem[Jiang et al.(2008)]{jiang2008}
+Jiang, C.Y., Jing, Y. P., \& Faltenbacher, A., et al. 2008, ApJ, 675, 1095
+
+\bibitem[Kaiser (1987)]{Kaiser1987}
+Kaiser, N. 1987, MNRAS, 227, 1
+
+\bibitem[Kim \& Park(2006)]{kim and park 2006}
+Kim, J., \& Park, C. 2006, ApJ, 639, 600
+
+\bibitem[Kim et al.(2009)]{2009ApJ...701.1547K} 
+Kim, J., Park, C., Gott, J.R., III, \& Dubinski, J.\ 2009, ApJ, 701, 1547
+
+\bibitem[Kim et al.(2015)]{hr4}
+Kim, J., Park, C., L'Huillier, B., \& Hong, S. E. 2015, JKAS, 48, 213
+
+\bibitem[Kim et al.(2011)]{horizonrun}
+Kim, J., Park, C., Rossi, G., Lee, S.M., \& Gott, J.R. 2011, JKAS, 44, 217
+
+\bibitem[Kitaura et al.(2015)]{MDPATCHY}
+Kitaura, F.S., Rodriguez-Torres, S., Chuang, C.-H., et al. arXiv:1509.06400
+
+\bibitem[Komatsu et al.(2011)]{komatsu 2011}
+Komatsu, E., Smith, K. M., \& Dunkley, J., et al. 2011, ApJS, 192, 18
+
+\bibitem[Lacey \& Cole(1993)]{LC93}
+Lacey, C., \& Cole, S. 1993, MNRAS, 262, 627
+
+\bibitem[Landy \& Szalay(1993)]{1993ApJ...412...64L} 
+Landy, S.D., \& Szalay, A.S.\ 1993, ApJ, 412, 64
+
+%EUCLID:
+%http://arxiv.org/abs/1110.3193
+\bibitem[Laureijs et al.(2011)]{EUCLID}
+Laureijs, R., Amiaux, J., \& Arduini, S., et al. 2011, arXiv:1110.3193
+
+\bibitem[Lavaux \& Wandelt(2012)]{LavausWandelt1995}
+Lavaux, G., \& Wandelt, B.D. 2012, ApJ, 754, 109
+
+%\bibitem[Levi et al.(2013)]{2013arXiv1308.0847L} 
+%Levi, M., Bebek, C., Beers, T., et al.\ 2013, arXiv:1308.0847
+
+\bibitem[Lewis \& Bridle (2002)]{LB2002}
+Lewis, A., \& Bridle, S. 2002, Phys. Rev. D, 66, 103511
+
+\bibitem[L'Huillier et al.(2014)]{2014NewA...30...79L} 
+L'Huillier, B., Park, C., \& Kim, J.\ 2014, New Astronomy, 30, 79
+
+\bibitem[Li et al.(2011)]{Li2011}
+Li, M., Li, X.-D., Wang, S., \& Wang, Y. 2011, Commun. Theor. Phys., 56, 525
+
+\bibitem[Li et al.(2014)]{Li2014}
+Li, X.-D., Park, C., Forero-Romero, J., \& Kim, J. 2014, ApJ, 796, 137
+
+\bibitem[Li et al.(2015)]{Li2015}
+Li, X.-D., Park, C., Sabiu, C.G., \& Kim, J. 2015, MNRAS, 450, 807
+
+\bibitem[Li et al.(2016)]{Li2016}
+Li, X.-D., Park, C., \& Sabiu, C.G., et al. 2016, ApJ, 832, 103
+
+%\bibitem[Linder(2003)]{Linder2003}
+%Linder, E.V. 2003, Phys. Rev. Lett., 90, 091301
+
+\bibitem[Linder et al.(2014)]{Linder2013}
+Linder, E.V., Minji, O., Okumura, T., Sabiu, C.G., \& Song, Y.-S. 2014, Phys. Rev. D, 89, 063525
+
+\bibitem[L{\'o}pez-Corredoira(2014)]{2014ApJ...781...96L} 
+L{\'o}pez-Corredoira, M.\ 2014, ApJ, 781, 96
+
+\bibitem[Mao et al. (2016)]{Qingqing2016}
+Mao, Q., Berlind, A.A., Scherrer, R.J., et al. 2016, submitted to ApJ
+
+\bibitem[Marinoni \& Buzzi(2010)]{Marinoni2010}
+Marinoni, C., \& Buzzi, A. 2010, Nature, 468, 539
+
+\bibitem[Matsubara \& Suto(1996)]{Matsubara1996}
+Matsubara T., \& Suto, Y. 1996, ApJ, 470, L1
+
+\bibitem[McCavana et al.(2012)]{M12}
+McCavana, T., Micic, M., Lewis, G. F., et al. 2012, MNRAS, 424, 361
+
+\bibitem[Morandi \& Sun (2016)]{MS2016}
+Morandi, A., \& Sun, M. arXiv:1601.03741
+
+\bibitem[Outram et al.(2004)]{Outram2004}
+Outram, P.J., Shanks, T., Boyle, B.J., Croom, S.M., Hoyle, F., Loaring, N.S., 
+Miller, L., \& Smith, R.J. 2004, MNRAS, 348, 745
+
+%\bibitem[Parejko et al.(2013)]{Parejko2013}
+%Parejko, J. K., Sunayama, T., Padmanabhan, N., et al. 2013, MNRAS, 429, 98
+
+\bibitem[Parejko et al.(2013)]{Parejko2013}
+Parejko J.K., et al., 2013, MNRAS, 429, 98
+
+\bibitem[Parihar et al. (2014)]{CMASSLSS2014}
+Parihar, P., Vogeley, M.S., \& Gott, J.R., et al. 2014, ApJ, 796, 86
+
+\bibitem[Park et al.(2005)]{park 2005}
+Park, C., Kim, J., \& Gott, J.R. 2005, ApJ, 633, 1
+
+\bibitem[Park \& Kim(2010)]{topology}
+Park, C., \& Kim, Y.-R. 2010, ApJL, 715, L185
+
+\bibitem[Park et al. (2012)]{Park2012}
+Park, C., Choi, Y.-Y., Kim, J., Gott, J.R., Kim, S.S., \&
+Kim, K.-S. 2012, ApJ, 759, 7
+
+\bibitem[Park et al. (2015)]{Park2015}
+Park, C., Song, H., Einasto, M., Lietzen, H., \&
+Heinamaki, P. 2015, JKAS, 48, 75
+
+\bibitem[Peebles \& Ratra(2003)]{PR2003}
+Peebles, P.J.E., \& Ratra, B. 2003, Reviews of Modern Physics, 75, 559
+
+\bibitem[Percival et al.(2014)]{Percival2014}
+Percival, W.J., Ross, A.J., \& S\'{a}nchez, A.G., et al. 2014, MNRAS, 439, 2531
+
+\bibitem[Perlmutter et al.(1999)]{Perl1999}
+Perlmutter, S., Aldering, G., \& Goldhaber, G., et al. 1999, ApJ, 517, 565
+
+\bibitem[Press \& Shechter(1974)]{PS1974}
+Press, W.H., \& Schechter, P.L. 1974, ApJ, 187, 425
+
+\bibitem[Reid et al.(2012)]{Reid2012}
+Reid, B., Samushia, L., \& White, M., et al. 2012, MNRAS, 426, 2719
+
+\bibitem[Reid et al.(2016)]{Reidetal:2016}
+Reid, B., Ho, S., \& Padmanabhan, N., et al.  2016, MNRAS, 455, 1553
+
+\bibitem[Riess et al.(1998)]{Riess1998}
+Riess, A.G., Filippenko, A.V., \& Challis, P., et al. 1998, AJ, 116, 1009
+
+\bibitem[Riess et al.(2011)]{Riess2011}
+Riess, A.G., Macri, L., \& Casertano, S., et al. 2011, ApJ, 730, 119
+%A 3\% Solution: Determination of the Hubble Constant with the Hubble Space Telescope and Wide Field Camera
+
+\bibitem[Ross et al.(2012)]{2012MNRAS.424..564R} 
+Ross, A.J., Percival, W.J., \& S{\'a}nchez, A.G. et al.\ 2012, MNRAS, 424, 564
+
+\bibitem[Ross et al.(2015)]{MGS}
+Ross, A.J., Samushia, L., \& Howlett, C., et al. 2015, MNRAS, 449, 835
+
+\bibitem[Ryden(1995)]{Ryden1995}
+Ryden, B.S. 1995, ApJ, 452, 25
+
+%\bibitem[Samushia et al.(2014)]{Samushia2014}
+%Samushia, L., Reid, B. A., White, M., et al. 2014, MNRAS, 439, 3504
+
+%\bibitem[Sanchez et al.(2013)]{Sanchez2013}
+%Sanchez, A. G., Kazin, E. A., Beutler, F., et al. 2013, MNRAS, 433, 1202
+
+%\bibitem[Sutter et al.(2014)]{Sutter2014}
+%Sutter, P.M., Pisani, A., Wandelt, B.D., \& Weinberg, D.H. 2014, MNRAS, 443, 2983
+
+\bibitem[Sanchez et al.(2016)]{Sanchez2016}
+Sanchez, A. G., Scoccimarro, R., \& Crocce, M., et al.
+arXiv:1607.03147
+
+\bibitem[Schlafly et al.(2010)]{Schlafly2010}
+Schlafly E.F., Finkbeiner D.P., Schlegel D.J., et al. 2010, ApJ, 725, 1175
+
+\bibitem[Schlafly \& Finkbeiner(2011)]{SF2011}
+Schlafly E.F., \& Finkbeiner D.P. 2011, ApJ, 737, 103
+
+%DESI:
+%http://arxiv.org/abs/1106.1706
+\bibitem[Schlegel et al.(2011)]{DESI}
+Schlegel, D., Abdalla, F., \& Abraham, T., et al. 2011, arXiv:1106.1706
+
+\bibitem[Smee et al.(2013)]{Smee2013}
+Smee, S.A., Gunn, J.E., \& Uomoto, A., et al. 2013, AJ, 146, 32
+
+\bibitem[Song et al.(2014)]{2014arXiv1407.2257S} 
+Song, Y.S., Sabiu, C.G., 
+Okumura, T., Oh, M., \& Linder, E.V.\ 2014, JCAP, 12, 005
+
+\bibitem[Speare et al. (2015)]{Speare2015}
+Speare, R., Gott, J.R., Kim, J., \& Park, C.
+2015, ApJ, 799, 176
+
+%\bibitem[Tojeiro \& Percival(2011)]{Tojeiro2011}
+%Tojeiro R., \& Percivial W.J. 2011, MNRAS, 417, 1114
+
+%\bibitem[Tojeiro et al.(2012)]{Tojeiro2012}
+%Tojeiro, R., Percival, W. J., Wake, D. A., et al. 2012, MNRAS, 424, 136
+
+\bibitem[Viana \& Liddle(1996)]{VL1996}
+Viana, P.T.P., \& Liddle, A.R. 1996, MNRAS, 281, 323
+
+\bibitem[Villalobos et al.(2013)]{V13}
+Villalobos, \'{A}., ́De Lucia, G., Weinmann, S.M., Borgani, S., \& Murante, G. 2013, MNRAS, 433, L49
+
+\bibitem[Weinberg (1989)]{SW1989}
+Weinberg, S. 1989, Reviews of Modern Physics, 61, 1
+
+\bibitem[White (2011)]{White2011}
+White M., et al. 2011, ApJ, 728, 126
+
+\bibitem[Yoo \& Watanabe(2012)]{2012IJMPD..2130002Y} Yoo, J., \& Watanabe, Y.\ 2012, International Journal of Modern Physics D, 21, 1230002
+
+\bibitem[York et al.(2000)]{York et al. 2000}
+York, D.G., Adelman, J., \& Anderson, J.E., et al. 2000, AJ, 120, 1579
+
+\bibitem[Zehavi et al.(2011)]{zehavi2011}
+Zehavi, I., Zheng, Z., \& Weinberg, D.H., et al. 2011, ApJ, 736, 59
+
+%\bibitem{Milliman14}
+%\bibinfo{author}{Milliman}, K.~E. {\it et~al.}
+%\newblock \bibinfo{title}{WIYN Open Cluster Study. LX. Spectroscopic Binary Orbits in NGC 6819.}
+%\newblock{\it Astron. \ J.}{\bf\, 148}, 38--57 (2014).
+
+\end{thebibliography}
+
+\begin{addendum}
+\item [Acknowledgements] 
+We thank the Korea Institute for Advanced Study for providing computing resources (KIAS Center for Advanced Computation Linux Cluster System).
+CGS acknowledges support from the National Research Foundation (NRF,  \#2017R1D1A1B03034900). 
+We thank Stephen Appleby, Seokcheon Lee, Maurice van Putten, Graziano Rossi and Yi Wang for helpful discussions.
+
+\item[Author contributions]
+
+X.L. computed the approximated 2pCFs in the many cosmologies, computed the likelihoods based on them, derived the final cosmological constraints, and did the robustness tests. 
+C.S. wrote the code computing the 2pCFs, and contributed in the likelihood analysis and the robustness tests. 
+C.P. proposed the concept of using redshift dependence to do AP tests, and have extensive discussions with X.L. about the likelihood analysis, 
+systematic correction, and robustness tests.
+Y.W. and G.Z. contributed in the computing the approximated 2pCFs in non-fiducial cosmologies, and the robustness tests.
+H.P. contributed in the cross-check of the 2pCF measurements, the likelihood analysis, and the systematic correction.
+A.S. contributed in the fast likelihood in non-fiducial cosmologies and the cosmological interpretation of the results.
+J.K. and S.H. performed the Horizon Run 4 simulations and built the mock galaxy samples.
+All authors commented on the manuscript.
+
+\item[Author information]
+%Supplementary information is available for this paper. 
+Reprints and permissions information is available at \href{www.nature.com/reprints}{www.nature.com/reprints}.
+Correspondence and requests for materials should be addressed to X.D. (e-mail: \href{mailto:xiaodongli@kias.re.kr}{xiaodongli@kias.re.kr}).
+
+\item[Competing interests]
+The authors declare no competing financial interests.
+
+\end{addendum}
+
+\newpage
+
+\begin{figure}[tb]
+   \centering{
+   \includegraphics[height=5cm]{fig_xy.eps}
+   }
+   \vspace{-2mm}
+   \caption{\label{fig_xy}
+   The distance dependence of the shape distortion in four wrongly assumed cosmologies,
+   assuming a true cosmology of $\Omega_m=0.31$, $w=-1$.
+   There are four perfect squares with their true shapes plotted in blue dashed lines.
+   They are measured by an observer located at the origin, and the distances are reprojected in the four wrong cosmologies.
+   The apparently distorted shapes are plotted in red solid lines.
+   }
+   \vspace{-4mm}
+\end{figure}
+
+\begin{figure}[tb]
+   \centering{
+   \includegraphics[height=5.3cm]{fig_nbar.eps}
+   \includegraphics[width=7cm,]{fig_2pcf.eps}
+   }
+   \caption{\label{fig_TpCF}
+   Left panel: We split the BOSS DR12 galaxies into six redshift bins to measure the evolution of shape distortion.
+   The blue and green solid histograms show the redshift density distribution of LOWZ and CMASS galaxies in the $\Omega_m=0.31$ $\Lambda$CDM. 
+   The vertical dashed lines define the six redshift bins that are used to cut the samples.                                       .
+   The number of LOWZ/CMASS galaxies in the three low/high redshift bins are listed.
+   Right panel: 2D contour map of measured $\xi$ as a function of $\mu$ and $s$, from the six redshift bins of LOWZ and CMASS samples, 
+      in the cosmology of $\Omega_m=0.31$ $\Lambda$CDM model.
+    The black dashed lines mark the clustering region 6-40\ Mpc/h studied in the AP method.
+    The six contour maps have rather similar appearance, implying small redshift evolution of $\xi$ from RSD.
+   }
+\end{figure}
+
+\begin{figure}[tb]
+   \centering{
+   \includegraphics[height=5cm,natwidth=6,natheight=4.5]{figCPL_b.pdf}
+   %\includegraphics[width=5.5cm,natwidth=4,natheight=4]{figCPL_b_BAOSNIaAP.pdf}
+   \includegraphics[height=5cm,natwidth=6,natheight=4.5]{figCPL_d.pdf}
+   }
+   \caption{\label{fig_con}
+   Left panel: 68.3\%, 95.4\% CL likelihood contours in the  $w_0-w_a$ plane.
+   %Results are consistent with $\Lambda$CDM.
+   The constrained area is significantly reduced after combined with the AP method.
+   %This shows the power of the AP method in constraining dynamical dark energy.
+   %Middle panel: $w_0-w_a$ likelihood contours using datasets of CMB+BAO, CMB+BAO+SNIa+$H_0$ and CMB+BAO+AP+$H_0$.
+   %When combined with CMB+BAO, AP method yields much tighter constraints than SNIa.
+   Right panel: Redshift evolution of $w(z)$, with/without adding the AP constraint.
+   Adding AP tightens the constraints and reduces the redshift evolution of $w$ (tilt of $w(z)$).
+   }
+\end{figure}
+
+\begin{figure}[tb]
+   \centering{
+   \includegraphics[width=16cm,natwidth=6,natheight=5]{fig_con_tests.pdf}
+   %\includegraphics[width=9cm,natwidth=4,natheight=4]{fig2b.pdf}
+   %\includegraphics[height=8cm]{fig2b.pdf}
+%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
+%    \includegraphics[height=8cm]{smu.eps}
+   }
+   \caption{\label{fig_contest}
+   Robustness test of the AP method. 
+   For the ``default'' constraints (pink contours) are derived using six redshift bins, 
+   $\mu_{\rm max}=0.97$, $n_{\mu}=15-20$, $s=6-40 \rm Mpc/h$,
+   a fiducial cosmology $\Omega_m=0.26,\ w=-1.0$ for the measurement of 2pCF,
+   systematic effects estimated from HR4 simulations, 
+   and covariance estimated using 2,000 PATCHY mocks.
+   When altering these options, the results remain robust (black contours).
+   }
+\end{figure}
+
+\clearpage
+\setcounter{page}{1}
+\setcounter{figure}{0}
+\setcounter{table}{0}
+
+\begin{center}
+{\textbf{ \Large \uppercase{Methods}} }
+\end{center}
+
+\noindent
+%{\textbf{Target selection and data preparation.}}  
 The spectroscopic galaxy sample of SDSS-III BOSS (Baryon Oscillation Spectroscopic Survey) has two primary catalogues:
@@
 
-Following our previous methodology \citep{Li2016}, the information of small-scale anisotropic clustering is computed
-\footnote{These correlations were computed using the public code \texttt{KSTAT} \citep{kstat}.} 
+Following our previous methodology \citep{Li2016}, the information of small-scale anisotropic clustering is computed.
+%\footnote{These correlations were computed using the public code \texttt{KSTAT} \citep{kstat}.} 
 as $\xi_{\Delta s} (\mu) \equiv \int_{s_{\rm min}}^{s_{\rm max}} \xi (s,\mu)\ ds$, 
@@
 
-%\section{Reproducing wCDM Constraints}\label{wcdm_constraint}
-%As a first trial, we firstly try to reproduce the constraints on $\Omega_m$ and $w$ in \citep{Li2016}:
-%As a first trial of reproduce the $\Omega_m-w$ constraints presented in \citep{Li2016},
-%we obtains
-%\begin{equation}
-%\Omega_m = 0.301 \pm 0.008,\ w=-1.053\pm 0.034\ (w\rm CDM).
-%    1  0.3010870E+00  0.7818562E-02  0.2973018E+00  0.3045011E+00  0.2883318E+00  0.3150334E+00   \Omega_m
-%    2  0.6886453E+00  0.8507156E-02  0.6802557E+00  0.6975813E+00  0.6708444E+00  0.7047652E+00   h
-%    3 -0.1053343E+01  0.3395215E-01 -0.1087474E+01 -0.1020395E+01 -0.1121890E+01 -0.9819443E+00   w
-%\end{equation}
-%The results are rather insensitive to the choice of fiducial cosmology.
-%while taking a different fiducial cosmology yields
-%\begin{eqnarray}
-%\Omega_m = 0.300 \pm 0.008,\ w=-1.057\pm 0.034\ (\rm fid:\ \Omega_m=0.26, w=-0.6),\\    
-%\Omega_m = 0.301 \pm 0.009,\ w=-1.055\pm 0.039\ (\rm fid:\ \Omega_m=0.31, w=-1.0),\\
-%\Omega_m = 0.302 \pm 0.008,\ w=-1.050\pm 0.035\ (\rm fid:\ \Omega_m=0.31, w=-0.6),\\
-%\Omega_m = 0.301 \pm 0.009,\ w=-1.052\pm 0.038\ (\rm fid:\ \Omega_m=0.31, w=-1.4),\\
-%\Omega_m = 0.304 \pm 0.008,\ w=-1.037\pm 0.034\ (\rm fid:\ \Omega_m=0.11, w=-2.0).
-%\end{eqnarray}
-%so the derived constraints are rather insensitive to the fiducial cosmology.
-%Even when adopting an extremely unlikely fiducial cosmological model, such as $\Omega_m=0.11, w=-2.0$, 
-%yields correct estimation of parameters of $\Omega_m = 0.304 \pm 0.008,\ w=-1.037\pm 0.034$.
-%For consideration of safety, when using the approxmiated method we slightly reduced the number of binning in $\hat\xi_{\Delta s}(\mu)$,
-%so the error bars are slightly larger than \citep{Li2016} %due to the limitation of approximation method
-%\footnote{We use $n_{\mu}$=20-25, while \citep{Li2016} adopted $n_{\mu}$=25-35.
-%The approximate 2pCF contour begins to be noisy if using such a large number of $n_\mu$.}.
-%from the 
-%The approximate 2pCF may not be accurate enough }
-
-%Using other fiducial cosmologies we derive similar cosmological constraints...
-%We simply adopt the $\Omega_m=0.26, w=-1$ as the fiducial cosmology in the following analysis...
-
-%\section{Results}\label{sec:results}
-{\it Results.}---
-
-\begin{figure*}
-   \centering{
-   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
-   \includegraphics[height=5.3cm]{fig_nbar.eps}
-   \includegraphics[width=7cm,]{fig_2pcf.eps}
-   }
-   \caption{\label{fig_TpCF}
-   Left panel: We split the BOSS DR12 galaxies into six redshift bins to measure the evolution of shape distortion.
-   The blue and green solid histograms show the redshift density distribution of LOWZ and CMASS galaxies in the $\Omega_m=0.31$ $\Lambda$CDM. 
-   The vertical dashed lines define the six redshift bins that are used to cut the samples.
-%   Their redshift ranges are listed.                                       .
-   The number of LOWZ/CMASS galaxies in the three low/high redshift bins are listed.
-   Right panel: 2D contour map of measured $\xi$ as a function of $\mu$ and $s$, from the six redshift bins of LOWZ and CMASS samples, 
-      in the cosmology of $\Omega_m=0.31$ $\Lambda$CDM model.
-    The black dashed lines mark the clustering region 6-40\ Mpc/h studied in the AP method.
-    %The correlation functions have rather large values on small sales such as $s=5$ $h^{-1}$Mpc,
-    %  and monotonically decreases to smaller values on larger scales due to weaker clustering.
-    The six contour maps have rather similar appearance, implying small redshift evolution of $\xi$ from RSD.
-   }
-\end{figure*}
-
-The Planck team has released the {\texttt {COSMOMC}} \citep{LB2002} outputs of four MCMC ``chains'' in the CPL model, 
-using a combination of four datasets:
-the full-mission Planck observations of CMB temperature and polarization anisotropies \cite{Planck2015},
-the BAO distance priors measured from SDSS DR11 \citep{Anderson2013}, 6dFGS \citep{6dFGS} and SDSS MGS \citep{MGS},
-the ``JLA'' SNIa sample \citep{JLA},
-and the Hubble Space Telescope measurement of $H_0=70.6\pm3.3$ \cite{Riess2011,E14H0}.
-\footnote{http://pla.esac.esa.int/pla/\#cosmology}.
-These MCMC chains contain the CMB+BAO+SNIa+$H_0$ likelihood computed for $\sim$37,000 sets of cosmological parameters,
-yielding constraints of 
-\begin{equation}
- \Omega_m = 0.309 \pm 0.010, w_0 = -0.938 \pm 0.109, w_a = -0.38 \pm 0.41.
-\end{equation}
-%To include the AP method into the constraints,
-We then compute the likelihood of the LOWZ+CMASS AP measurements for each of the parameter combinations provided in the Planck chain.
-After multiplying the sample likelihoods with ours, while also changing the sample weights {\bf (HOW CHANGE?)}, we derive the CMB+BAO+SNIa+$H_0$+AP constraints on CPL parameters,
-\begin{equation}
-%\Omega_m = 0.300 \pm 0.008, w_0 = -1.056 \pm 0.061, w_a = -0.04 \pm 0.27,
-    %1  0.2999656E+00  0.7616334E-02  0.2958745E+00  0.3035033E+00  0.2878169E+00  0.3132870E+00   \Omega_m
-    %2  0.6904801E+00  0.8675444E-02  0.6808558E+00  0.6993898E+00  0.6722945E+00  0.7052207E+00   h
-    %3 -0.1056468E+01  0.6096323E-01 -0.1116874E+01 -0.9965903E+00 -0.1175041E+01 -0.9287388E+00   w
-    %4 -0.3808376E-01  0.2716607E+00 -0.3105235E+00  0.2321461E+00 -0.6033103E+00  0.4782076E+00   w_a    
-\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29.
-%    1  0.3014353E+00  0.7759923E-02  0.2974325E+00  0.3048882E+00  0.2889838E+00  0.3152269E+00   \Omega_m
-%    2  0.6887652E+00  0.8760036E-02  0.6797134E+00  0.6978279E+00  0.6703971E+00  0.7044224E+00   h
-%    3 -0.1041626E+01  0.6732817E-01 -0.1107730E+01 -0.9768319E+00 -0.1172149E+01 -0.8979017E+00   w
-%    4 -0.7173374E-01  0.2860547E+00 -0.3572176E+00  0.2107347E+00 -0.6775045E+00  0.4558817E+00   w_a    
-\end{equation}
-%$$.
-While the central values of parameters do not shift appreciably,
-the error bars of $w_0$ and $w_a$ are reduced by 38.4\% and 29.7\%, respectively.% $$-40\%$ by adding our method into the analysis.
-
-The marginalised constraints on $w_0-w_a$ are shown in the left panel of Fig.\ref{fig_con}.
-Adding our new AP constraints significantly reduces the allowable parameter space. 
-This can also be visualise as allowable bands in $w(z)$ as can be seen in the right panel of Fig.\ref{fig_con}.
-
-The derived cosmological constraints are fully consistent with a cosmological constant dark energy component having no evolution.
-Adding the new AP method to the CMB+BAO+SNIa+$H_0$ constraints reduces the statistical errors by $\sim$30-40\%,
-and reduces the 95.4\% CL $w_0-w_a$ contour by 50\%.
-This reveals the constraining power of the small scale AP effect for probing the redshift evolution of dark energy.
-
-%\cite{Li2016} shows that the AP method outperforms SNIa in constraining the parameter space of $\Omega_m-w$.
-%Similarly we find it outperforms in constraining $w_0-w_a$, as shown in the middle panel of Fig.\ref{fig_TpCF}.
-
-\begin{figure*}
-   \centering{
-   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
-   \includegraphics[height=5cm,natwidth=6,natheight=4.5]{figCPL_b.pdf}
-   %\includegraphics[width=5.5cm,natwidth=4,natheight=4]{figCPL_b_BAOSNIaAP.pdf}
-   \includegraphics[height=5cm,natwidth=6,natheight=4.5]{figCPL_d.pdf}
-   %\includegraphics[height=8cm]{fig2b.pdf}
-%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
-%    \includegraphics[height=8cm]{smu.eps}
-   }
-   \caption{\label{fig_con}
-   Left panel: 68.3\%, 95.4\% CL likelihood contours in the  $w_0-w_a$ plane.
-   %Results are consistent with $\Lambda$CDM.
-   The constrained area is significantly reduced after combined with the AP method.
-   %This shows the power of the AP method in constraining dynamical dark energy.
-   %Middle panel: $w_0-w_a$ likelihood contours using datasets of CMB+BAO, CMB+BAO+SNIa+$H_0$ and CMB+BAO+AP+$H_0$.
-   %When combined with CMB+BAO, AP method yields much tighter constraints than SNIa.
-   Right panel: Redshift evolution of $w(z)$, with/without adding the AP constraint.
-   Adding AP tightens the constraints and reduces the redshift evolution of $w$ (tilt of $w(z)$).
-   }
-\end{figure*}
-
-In this short paper we have chosen to focus on the popular CPL parameterisation of dark energy, 
-however our methodology could be used with any model of cosmic expansion history.
-
-%%% To be written!!!
-%\section{Robustness Test}\label{sec:test}
-{\it Robustness Test.}---
-
-Analysing the same DR12 BOSS data, \citet{Li2016} obtained constraints on $\Omega_m$ and $w$
-\begin{equation}\label{eq:wcdm_constrain_default}
-\Omega_m=0.301\pm 0.006, w=-1.054\pm 0.025.
-\end{equation}
-In our new ``approximate 2pCF'' approach, while taking a fiducial cosmological model of $\Omega_m=0.26, w=-1$, we obtain consistent results of,
-\begin{equation}
-\Omega_m = 0.301 \pm 0.008,\ w=-1.053\pm 0.034.
-%    1  0.3010870E+00  0.7818562E-02  0.2973018E+00  0.3045011E+00  0.2883318E+00  0.3150334E+00   \Omega_m
-%    2  0.6886453E+00  0.8507156E-02  0.6802557E+00  0.6975813E+00  0.6708444E+00  0.7047652E+00   h
-%    3 -0.1053343E+01  0.3395215E-01 -0.1087474E+01 -0.1020395E+01 -0.1121890E+01 -0.9819443E+00   w
-\end{equation}
-Since we use a smaller $n_{\mu}$ value than that adopted by \citep{Li2016}
-\footnote{\citep{Li2016} adopted $n_{\mu}=25-35$ to achieve tighter constraints.
-Since we are using an approximate 2pCF, for robustness considerations we use $n_{\mu}=20-25$.}, 
-resulting in a slightly enlarged error bar. 
-The central values of the parameters agree quite well, demonstrating the reliability of the approximate 2pCF method.
-
-%\begin{figure*}
-%   \centering{
-%   \includegraphics[width=6cm]{figIO.eps}
-%   %\includegraphics[width=9cm,natwidth=4,natheight=4]{fig2b.pdf}
-%   %\includegraphics[height=8cm]{fig2b.pdf}
-%   %   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
-%   %    \includegraphics[height=8cm]{smu.eps}
-%   }
-%   \caption{\label{fig_IO}
-%   Input-output test of the AP method. 
-%   The input cosmology (marker by green plus) is recovered at $\sim$0.5$\sigma$ 
-%   using 4 realizations.
-%   }
-%\end{figure*}
-
-We also performed an input-output test on four realizations of the HR4 mock catalogues \cite{hr4}.
-%In the framework of $w$CDM cosmology, %Figure \ref{fig_IO} shows 
-The input cosmology $\Omega_m=0.26$, $w=-1$ is recovered well, lying within the $\sim$0.5$\sigma$ CL region.
-
-Finally, we performed a thorough test of all the possible variables in our methodology.
-Figure \ref{fig_contest} shows that,
-the result does not change if 
-we adopt $\mu_{\rm max}=0.99\ (0.85)$ to include more (less) regions near the LOS,
-decrease the number of angular bins to $n_{\mu}=15-20$,
-change the range of clustering to $8-30 \rm Mpc/h$,
-change the fiducial cosmology to $\Omega_m=0.26,\ w=-0.6$,
-exclude 1 or 2 high redshift bins,
-or reduce the number of mocks to 1000.
-%Constraints get weaker if increase $s_{\rm min}$,
-%but are consistent with the original one.
-%Even if we choose an extremely unrealistic fiducial cosmology, i.e. 
-% $\Omega_m=0.11,\ w=-2.0$, the change in contour is still mild.
-The most striking point to note in our testing is that the 
-shift in contour position is very small even when we do not include the systematic correction.
-This is reassuring, since we may have worried that {\it cosmological dependence} on the systematic correction could influence on our final results.
-
-%We measure the evolution of $\hat\xi_{\Delta s}$ in six redshift bins.
-%on scales of $s_{\rm min}=6$, $s_{\rm max}=40$.
-%Systematics subtracted with the help of HR4 simulation.
-%Covariance matrix
-
-\begin{figure*}
-   \centering{
-   \includegraphics[width=16cm,natwidth=6,natheight=5]{fig_con_tests.pdf}
-   %\includegraphics[width=9cm,natwidth=4,natheight=4]{fig2b.pdf}
-   %\includegraphics[height=8cm]{fig2b.pdf}
-%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
-%    \includegraphics[height=8cm]{smu.eps}
-   }
-   \caption{\label{fig_contest}
-   Robustness test of the AP method. 
-   For the ``default'' constraints (pink contours) are derived using six redshift bins, 
-   $\mu_{\rm max}=0.97$, $n_{\mu}=15-20$, $s=6-40 \rm Mpc/h$,
-   a fiducial cosmology $\Omega_m=0.26,\ w=-1.0$ for the measurement of 2pCF,
-   systematic effects estimated from HR4 simulations, 
-   and covariance estimated using 2,000 PATCHY mocks.
-   When altering these options, the results remain robust (black contours).
-   }
-\end{figure*}
-
-%\section{Conclusion}\label{sec:conclusion}
-{\it Conclusion.}---
-
-In \cite{Li2016} we proposed to constrain cosmological parameters via 
-the redshift dependence of galaxy anisotropic clustering. 
-This enables a robust Alcock-Paczynski test on relatively small scales.
-In this paper we improved the methodology and obtained tight constraints on the CPL parametrization of dark energy using 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
-12 spanning the redshift range $0.15<z<0.69$ . 
-Adding our constraints to the CMB+SNIa+BAO+$H_0$ combination, the $w_0-w_a$ contour was reduced by $\sim50$\%.
-
-The AP method presented in this work has many advantages over the `traditional' galaxy clustering method.
-Since it works with the redshift evolution of the anisotropic clustering signal it significantly reduces the effect of systematics. 
-It avoids the great difficulty in accurate modelling of the RSD, non-linear clustering and galaxy bias.
-It is applicable on much smaller scales, allowing for the inclusion of more $k$-modes and hence more information.
-
-%By reducing the RSD effect the method enables using clustering information on scales of $s<6 \rm Mpc/h$.
-%This is a major advance in extracting cosmological information on relatively small scales clustering.
-
-%In sum, our AP method have many advantages:
-%\begin{itemize}
-%\item {\it It leads to very tight cosmological constraints (powerful)}. The 
-% \item {\it Focusing on the redshift evolution of anisotropy it successfully overcome the problem of RSD, 
-% which has long time been a limitation to the application of AP to LSS (successful).}
-% In traditional approaches it is very challenging to model the RSD and enable a robust AP test.
-% \item {\it It is robust against systematics (reliable)}. 
-% \cite{Li2016} shows that $\hat\xi_{\Delta s}$ is insensitive to RSD or galaxy bias.
-% Figure \ref{fig_con_tests} shows that the change in results is small even if we do not correct the systematics at all.
-% \item {\it It is a major advance in extracting cosmological information on relatively small scales clustering (unique).} 
-% Clustering of galaxies happen on all scales,
-%but the size and shape of BAO ring only captures information mostly on scales of $s=100-120 {\rm Mpc/h}$.
-%In the analysis of correlation function shape, people mostly use $s\gtrsim 40$ Mpc/h.
-%Our AP method enters much smaller scales.
-%
-% \item {\it It does not require complicate modeling of non-linear structure growth and RSD (simple).}
-% \item {\it It is complimentary to BAO (useful).}
-% The method explores much smaller clustering scales than BAO. 
-% \cite{Li2016} shows that, actually the directions of $\Omega_m-w$ contours of the two methods are orthogonal to each other.
-%\end{itemize}
-
-%While it is of essential importance to build larger experiments to 
-%explore more of our Universe,
-%the physical interpretation of the data is of equal importance.
-%Considering our method enables {\it twice as much as before} information about the cosmic expansion history extracted from LSS data.
-%This, in a way, significantly enhances the valuable data obtained from the very expensive experiments costing billions of dollars.
-
-The presented method of clustering shells can be applied to many spectroscopic galaxy surveys. 
-The method is complimentary to the BAO method and the two methods can be combined together, 
-increasing (by roughly twice) the science output of ongoing and future surveys, with little to no additional cost.
-We expect it play an important role in helping us unveiling the mystery of dark energy.
-
-\begin{acknowledgments}
-We thank the Korea Institute for Advanced Study for providing computing resources (KIAS Center for Advanced Computation Linux Cluster System).
-CGS acknowledges support from the National Research Foundation (NRF,  \#2017R1D1A1B03034900). 
-We thank Stephen Appleby, Seokcheon Lee, Maurice van Putten, Graziano Rossi and Yi Wang for helpful discussions.
-\end{acknowledgments}
-
-%% After the acknowledgments section, use the following syntax and the
-%% \facility{} macro to list the keywords of facilities used in the research
-%% for the paper.  Each keyword will be checked against the master list during
-%% copy editing.  Individual instruments or configurations can be provided
-%% in parentheses, after the keyword, but they will not be verified.
-
-%{\it Facilities:} \facility{Nickel}, \facility{HST (STIS)}, \facility{CXO (ASIS)}.
-
-%% Appendix material should be preceded with a single \appendix command.
-%% There should be a \section command for each appendix. Mark appendix
-%% subsections with the same markup you use in the main body of the paper.
-
-%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
-%% The equation counter will reset when it encounters the \appendix
-%% command and will number appendix equations (A1), (A2), etc.
-
-%% The reference list follows the main body and any appendices.
-%% Use LaTeX's thebibliography environment to mark up your reference list.
-%% Note \begin{thebibliography} is followed by an empty set of
-%% curly braces.  If you forget this, LaTeX will generate the error
-%% "Perhaps a missing \item?".
-%%
-%% thebibliography produces citations in the text using \bibitem-\cite
-%% cross-referencing. Each reference is preceded by a
-%% \bibitem command that defines in curly braces the KEY that corresponds
-%% to the KEY in the \cite commands (see the first section above).
-%% Make sure that you provide a unique KEY for every \bibitem or else the
-%% paper will not LaTeX. The square brackets should contain
-%% the citation text that LaTeX will insert in
-%% place of the \cite commands.
-
-%% We have used macros to produce journal name abbreviations.
-%% AASTeX provides a number of these for the more frequently-cited journals.
-%% See the Author Guide for a list of them.
-
-%% Note that the style of the \bibitem labels (in []) is slightly
-%% different from previous examples.  The natbib system solves a host
-%% of citation expression problems, but it is necessary to clearly
-%% delimit the year from the author name used in the citation.
-%% See the natbib documentation for more details and options.
-
-%\bibitem[Canizares et al.(1978)]{can78} Canizares, C. R.,
-%    Grindlay, J. E., Hiltner, W. A., Liller, W., \&
-%    McClintock, J. E.  1978, \apj, 224, 39
-
-%Wang Q H, Lindon O, Hardle W. 
-%Semiparametric regression analysis with missing response at random. 
-%J Am Stat Assoc, 2004, 99: 334－345
-
-\begin{thebibliography}{}
-%\citep{Riess:1998}
-%[astro-ph/0205436].
+\noindent
+{\textbf{Data availability.}} 
+The codes computing the likelihood of the AP tests are available on GitHub,
+\href{https://github.com/xiaodongli1986/APCPL.git}
+{https://github.com/xiaodongli1986/APCPL.git}.
+The codes computing the correlation functions are available via
+\href{https://bitbucket.org/csabiu/kstat}
+{https://bitbucket.org/csabiu/kstat}.
+The MCMC chains for CPL are publicly available via the Planck Legacy Archive
+\href{http://pla.esac.esa.int/pla/}
+{http://pla.esac.esa.int/pla/}.
+The COSMOMC software are publicly available and documented at
+\href{http://cosmologist.info/cosmomc/}
+{http://cosmologist.info/cosmomc/}.
+The SDSS DR12 galaxy samples are publicly available and documented at
+\href{https://data.sdss.org/sas/dr12/boss/lss/}
+{https://data.sdss.org/sas/dr12/boss/lss/}.
+The Horizun Run 4 simulation data is documented at
+\href{http://sdss.kias.re.kr/astro/Horizon-Runs/Horizon-Run4.php}
+{http://sdss.kias.re.kr/astro/Horizon-Runs/Horizon-Run4.php}.
+To use the simulation data, contact directly Juhan Kim \href{kjhan@kias.re.kr}{kjhan@kias.re.kr}.
+
+\begin{thebibliography}{10}
+\setcounter{enumiv}{29}
+
+\expandafter\ifx\csname url\endcsname\relax
+  \def\url#1{\texttt{#1}}\fi
+\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
+\providecommand{\bibinfo}[2]{#2}
+\providecommand{\eprint}[2][]{\url{#2}}
 
@@
 
-\bibitem[{{Alam} {et~al}\mbox{.}(2015{\natexlab{a}}){Alam}, {Albareti},
-  {Allende Prieto}, {Anders}, {Anderson}, {Anderton}, {Andrews}, {Armengaud},
-  {Aubourg}, {Bailey}, \& et~al.}]{dr12}
-{Alam} S., Albareti, F.D.,\& Allende Prieto, C., {et~al.}, 2015,  ApJS, 219, 12
+%\bibitem[{{Alam} {et~al}\mbox{.}(2015{\natexlab{a}}){Alam}, {Albareti},
+%  {Allende Prieto}, {Anders}, {Anderson}, {Anderton}, {Andrews}, {Armengaud},
+%  {Aubourg}, {Bailey}, \& et~al.}]{dr12}
+%{Alam} S., Albareti, F.D.,\& Allende Prieto, C., {et~al.}, 2015,  ApJS, 219, 12
 
@@
 \bibitem[Kitaura et al.(2015)]{MDPATCHY}
-Kitaura, F.S., Rodrı\'{i}guez-Torres, S., Chuang, C.-H., et al. arXiv:1509.06400
+Kitaura, F.S., Rodriguez-Torres, S., Chuang, C.-H., et al. arXiv:1509.06400
 
@@
 
-\bibitem[Sabiu (2013)]{kstat}
-C.G. Sabiu 2013
-https://bitbucket.org/csabiu/kstat
-http://ascl.net/code/v/1634
-
 \bibitem[Sanchez et al.(2016)]{Sanchez2016}
@@
 
+%\clearpage
+%\input{supplementaryinformation.tex}
+
 \end{document}

### 2017-06-22 Draft/Draft0.5.tex
minor changes

--- 2017-06-22 Draft/Draft0.4.bib2.tex
@@
 
-\title{\sffamily Dynamical dark energy constraints via clustering shells of SDSS-III BOSS galaxies}
+\title{%\sffamily 
+Dynamical dark energy constraints via clustering shells of SDSS-III BOSS galaxies}
+\title{%\sffamily 
+Constraints on the cosmic expansion history using the small scale clustering of SDSS-III BOSS galaxies}
 
-\author{\sffamily 
-Xiao-Dong Li,$^{1,\dagger}$
+\author{%\sffamily 
+Xiao-Dong Li,$^{1}$
 Cristiano G. Sabiu,$^{2}$
 Changbom Park,$^{1}$
-Yuting Wang,$^{3,\star}$
+Yuting Wang,$^{3}$
 Gong-bo Zhao,$^{3}$
@@
 and Sungwook E. Hong$^{2}$}
-%Enrico Corsaro$^{1,2,3,4}$, Yueh-Ning Lee$^1$, Rafael A.
-Garc\'{i}a$^{1}$, Patrick Hennebelle$^1$, Savita Mathur$^{5}$, Paul G.
-Beck$^1$, Stephane Mathis$^1$, Dennis Stello$^{6,7}$ \& J\'er\^{o}me Bouvier$^8$}
 
@@
 \begin{abstract}
-\sffamily
-We use the anisotropic {\it clustering shells} of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
-12 spanning the redshift range $0.15<z<0.69$ to place constraints on the expansion history of the Universe. 
-Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy $w=w_0+w_a\frac{z}{1+z}$,
+%\sffamily
+We use the small scale anisotropic clustering signal of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
+12, spanning the redshift range $0.15<z<0.69$ to place constraints on the expansion history of the Universe. 
+Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$,
 while improving upon earlier works \citep{Li2016}, 
 we present a novel use of the Alcock-Paczynski (AP) test via the small scales clustering difference between redshift bins. 
-This differential measure appears to be a robust statistical tool which mitigates many systematic effects, 
-allowing for competitive and unbiased constrains. 
-A combination of CMB+BAO+SNIa+$H_0$+AP yields
+This differential measure is shown to be a robust statistical tool that mitigates many systematic effects, 
+allowing for competitive and unbiased constrains to be placed on cosmological parameters.
+We find that our results, in combination with the CMB, BAO, SNIa and $H_0$ from Cepheid data yield, 
 $\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ w_a = -0.07 \pm 0.29$ (68.3\% CL). 
-Adding the AP method reduces the $w_0-w_a$ contour area by 50\%.
-The method can be combined with the standard BAO method, 
+Adding our new AP measurements to the aforementioned results reduced the $w_0-w_a$ 1-$\sigma$ contour area by 50\%.
+The AP method can be combined with the standard BAO method, 
 increasing the science output of ongoing and future galaxy surveys by a factor of 2.
@@
 
-\sffamily
-{\it Introduction.}---
-The  origin  of  the  accelerating  expansion  of  the  universe  is  one of  the  most  salient  questions  in  contemporary cosmology. 
-Proposed mechanisms include  evolving  scalar  fields  remnant  from  the  big  bang, 
-modifications to gravity,  and a  non-zero  vacuum energy \cite[see][for a comprehensive review]{2012IJMPD..2130002Y}. 
+%\sffamily
+%{\it Introduction.}---
+The  origin  of  the late-time accelerating  expansion  of  the  universe  is  one of  the  most  salient  questions  in  contemporary cosmology.
+Theoretical explanations for this phenomena are many and range from a non-zero  vacuum energy and evolving  scalar  fields  remnant  from  the  big  bang, to modifications of Einstein's General Relativity\cite{2012IJMPD..2130002Y}.
 Considering the wealth of theoretical explanations, it is crucial to obtain precise and unbiased measurements of the expansion history of the Universe allowing us to 
-differentiate between competing dark energy models.
+differentiate between competing models.
 
@@
 
-The main caveat of the AP test is due to the fact that 
+The main caveat in applying the AP test is due to the fact that 
 the radial distances of galaxies are inferred from observed redshifts.
-Thus AP tests are inevitably affected by peculiar motions of galaxies,
+Thus AP tests are inevitably affected by peculiar the motions of galaxies,
 which leads to apparent anisotropy in the clustering signal, even if the adopted cosmology is correct.
 The effect, known as redshift-space distortions (RSD),
-is notoriously difficult to model accurately in the 2-point statistics of galaxy clustering \citep{Ballinger1996}.
+is notoriously difficult to model accurately in the statistics of galaxy clustering \citep{Ballinger1996}.
 
-As alternative methods, \cite{Marinoni2010} proposed using the symmetry properties of galaxy pairs;
+The symmetry properties of galaxy pairs\cite{Marinoni2010}  could also be used to probe the AP effect;
 however, since the peculiar velocity distorts the redshifts and changes the apparent tilt angles of galaxy pairs,
 this method is also seriously limited by RSD \citep{Jennings2011}.
-\cite{Ryden1995} and \cite{LavausWandelt1995} proposed another method using the apparent stretching of voids.
-This approach has the advantage that the void regions are easier to model compared with dense regions,
-but has limitations in that it utilizes only low density regions of the LSS and requires large samples to achieve competitive constraints \citep{Qingqing2016}.
+
+In an effort to minimise RSD contamination, the shape of void regions\cite{Ryden1995,LavausWandelt1995}  has been 
+proposed as an AP probe.
+This approach has the advantage that the void regions are easier to model compared with dense regions, but has limitations in that it utilizes only low density regions of the LSS and requires large samples to achieve competitive constraints \citep{Qingqing2016}.
 
@@
 
-In an effort to mitigate the RSD effect, \cite{Li2014} proposed utilizing the {\it redshift dependence} of the AP effect. 
-The clustering anisotropies produced by are, although large, close to uniform in magnitude over a wide range in redshift. 
+Previously, we proposed to use the  {\it redshift dependence} of the AP distortion\cite{Li2014} as a way of mitigating the RSD effect.
+The clustering anisotropies produced by RSD are, although large, close to uniform in magnitude over a wide range in redshift.
 However, if cosmological parameters are incorrectly chosen resulting in an AP effect,
 the anisotropy in the clustering signal has a clear redshift dependence. 
-In a later work, \cite{Li2015} developed an AP methodology 
+In a later work\cite{Li2015}, we developed an AP methodology 
 that utilises the redshift dependence of the galaxy 2-point correlation function (2pCF), 
@@
 
-\citep{Li2016} applied their AP method to galaxies from the 3rd incarnation of the Sloan Digital Sky Survey (SDSS-III).
+In earlier work\citep{Li2016} we applied this AP method to galaxies from the 3rd incarnation of the Sloan Digital Sky Survey (SDSS-III).
 Combining their method with measurements of the Cosmic Microwave Background (CMB), type Ia supernovae (SNIa),
@@
 In this paper, we continue to develop our previous methodology and proceed to infer the constraints on dynamical dark energy. 
-We will present a slightly improved methodology to that of \citep{Li2016}, 
+We will present a slightly improved methodology to that of our previous work\citep{Li2016}, 
 allowing for faster likelihood estimation and thus the exploration of larger, higher dimensional parameter spaces. 
@@
 These MCMC chains contain the CMB+BAO+SNIa+$H_0$ likelihood computed for $\sim$37,000 sets of cosmological parameters,
-yielding constraints of 
-\begin{equation}
- \Omega_m = 0.309 \pm 0.010, w_0 = -0.938 \pm 0.109, w_a = -0.38 \pm 0.41.
-\end{equation}
-%To include the AP method into the constraints,
+yielding constraints of $ \Omega_m = 0.309 \pm 0.010, w_0 = -0.938 \pm 0.109, w_a = -0.38 \pm 0.41$.
+%\begin{equation}
+ %\Omega_m = 0.309 \pm 0.010, w_0 = -0.938 \pm 0.109, w_a = -0.38 \pm 0.41.
+%end{equation}
 We then compute the likelihood of the LOWZ+CMASS AP measurements for each of the parameter combinations provided in the Planck chain. 
@@
 measured the 2pCF in these redshift bins, 
-and use a $\chi^2$ function to assess the redshift dependence.
-Systematic effects are estimated via mocks made from Horizon Run 4 simulations \citep{HR4}, and subtracted when computing the $\chi^2$.
+subtract the systematic effects based on estimations from mocks made from Horizon Run 4 simulations \citep{HR4},
+and use a $\chi^2$ function to assess the redshift dependence
+(see Methods for further explanations).
 After adding the sample log-likelihoods with ours, 
 while also multiply the sample weights by our likelihoods, 
-we derive the CMB+BAO+SNIa+$H_0$+AP constraints on CPL parameters,
-\begin{equation}
-%\Omega_m = 0.300 \pm 0.008, w_0 = -1.056 \pm 0.061, w_a = -0.04 \pm 0.27,
-    %1  0.2999656E+00  0.7616334E-02  0.2958745E+00  0.3035033E+00  0.2878169E+00  0.3132870E+00   \Omega_m
-    %2  0.6904801E+00  0.8675444E-02  0.6808558E+00  0.6993898E+00  0.6722945E+00  0.7052207E+00   h
-    %3 -0.1056468E+01  0.6096323E-01 -0.1116874E+01 -0.9965903E+00 -0.1175041E+01 -0.9287388E+00   w
-    %4 -0.3808376E-01  0.2716607E+00 -0.3105235E+00  0.2321461E+00 -0.6033103E+00  0.4782076E+00   w_a    
-\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29.
-%    1  0.3014353E+00  0.7759923E-02  0.2974325E+00  0.3048882E+00  0.2889838E+00  0.3152269E+00   \Omega_m
-%    2  0.6887652E+00  0.8760036E-02  0.6797134E+00  0.6978279E+00  0.6703971E+00  0.7044224E+00   h
-%    3 -0.1041626E+01  0.6732817E-01 -0.1107730E+01 -0.9768319E+00 -0.1172149E+01 -0.8979017E+00   w
-%    4 -0.7173374E-01  0.2860547E+00 -0.3572176E+00  0.2107347E+00 -0.6775045E+00  0.4558817E+00   w_a    
-\end{equation}
-%$$.
+we derive the CMB+BAO+SNIa+$H_0$+AP constraints on CPL parameters, $\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29$.
+%\begin{equation}
+%\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29.
+%\end{equation}
 While the central values of parameters do not shift appreciably,
@@
 The derived cosmological constraints are fully consistent with a cosmological constant dark energy component having no evolution.
-Adding the new AP method to the CMB+BAO+SNIa+$H_0$ constraints reduces the statistical errors by $\sim$30-40\%,
-and reduces the 95.4\% CL $w_0-w_a$ contour by 50\%.
+Adding the new AP method to the CMB+BAO+SNIa+$H_0$ constraints reduces the statistical errors on many parameters by $\sim$30-40\% and reduces the $w_0-w_a$  (95.4\% CL) contour by 50\%.
 This reveals the constraining power of the small scale AP effect for probing the redshift evolution of dark energy.
@@
 We performed a thorough test of all the possible variables in our methodology.
-Figure \ref{fig_contest} shows that,
-the result does not change if change them.
+Figure \ref{fig_contest} shows that 
+the result is unaffected by the line-of-sight $\mu$-cut, the number of angular bins, the range of radial integration and the choice of fiducial cosmology. 
 %we adopt $\mu_{\rm max}=0.99\ (0.85)$ to include more (less) regions near the LOS,
@@
 This is reassuring, since we may have worried that {\it cosmological dependence} 
-on the systematic correction could influence on our final results.
+of the systematic correction could influence the final result.
 
-In sum, \cite{Li2016} proposed to constrain cosmological parameters via 
-the redshift dependence of galaxy anisotropic clustering.
-This enables a robust AP test on relatively small scales.
+In summary, we previously proposed to constrain cosmological parameters via 
+the redshift dependence of anisotropic galaxy clustering\cite{Li2016}.
+This approach enables a robust AP test on relatively small scales.
 In this paper we improved the methodology and obtained tight constraints on the CPL parametrization of dark energy.
@@
 increasing (by roughly twice) the science output of ongoing and future surveys, with little to no additional cost.
-We expect it play an important role in helping us unveiling the mystery of dark energy.
+We expect this approach will play an important role in helping us unveiling the mystery of dark energy.
 
@@
 
-\bibitem[Ade et al. (2015)]{Planck2015}
-Ade, P.A.R., Aghanim, N., \& Arnaud, M., et al. arXiv:1502.01589
+\bibitem{Li2016}%[Li et al.(2016)]
+Li, X.-D., Park, C., \& Sabiu, C.G., et al. 2016, ApJ, 832, 103
 
-\bibitem[Alam et al.(2016)]{Alam2016}
+\bibitem{2012IJMPD..2130002Y}%[Yoo \& Watanabe(2012)]
+Yoo, J., \& Watanabe, Y.\ 2012, International Journal of Modern Physics D, 21, 1230002
+
+\bibitem{AP1979}%[Alcock \& Paczynski(1979)]
+Alcock, C., \& Paczynski, B. 1979, Nature, 281, 358
+
+\bibitem{Outram2004}%[Outram et al.(2004)]
+Outram, P.J., Shanks, T., Boyle, B.J., Croom, S.M., Hoyle, F., Loaring, N.S., 
+Miller, L., \& Smith, R.J. 2004, MNRAS, 348, 745
+
+\bibitem{Blake2011}%[Blake et al.(2011)]
+Blake, C., Glazebrook, K., \& Davis, T. M., 2011, MNRAS, 418, 1725
+
+\bibitem{Alam2016}%[Alam et al.(2016)]
 Alam, S., Ata, M., \& Bailey, S., et al. 2016,
@@
 
-%\bibitem[{{Alam} {et~al}\mbox{.}(2015{\natexlab{a}}){Alam}, {Albareti},
-%  {Allende Prieto}, {Anders}, {Anderson}, {Anderton}, {Andrews}, {Armengaud},
-%  {Aubourg}, {Bailey}, \& et~al.}]{dr12}
-%{Alam} S., Albareti, F.D.,\& Allende Prieto, C., {et~al.}, 2015,  ApJS, 219, 12
+\bibitem{Ballinger1996}%[Ballinger, Peacock \& Heavens 1996]
+Ballinger, W.E., Peacock, J.A., \& Heavens, A.F. 1996, MNRAS, 282, 877
 
-\bibitem[Alcock \& Paczynski(1979)]{AP1979}
-Alcock, C., \& Paczynski, B. 1979, Nature, 281, 358
+\bibitem{Marinoni2010}%[Marinoni \& Buzzi(2010)]
+Marinoni, C., \& Buzzi, A. 2010, Nature, 468, 539
 
-%\bibitem[Anderson et al.(2012)]{2012MNRAS.427.3435A} 
-%Anderson, L., Aubourg, E., Bailey, S., et al.\ 2012, MNRAS, 427, 3435
+\bibitem{Jennings2011}%[Jennings et al.(2011)]
+Jennings, E., Baugh, C.M., \& Pascoli, S. 2011, MNRAS, 420, 1079
 
-\bibitem[Anderson et al.(2013)]{Anderson2013}
+\bibitem{Ryden1995}%[Ryden(1995)]
+Ryden, B.S. 1995, ApJ, 452, 25
+
+\bibitem{LavausWandelt1995}%[Lavaux \& Wandelt(2012)]
+Lavaux, G., \& Wandelt, B.D. 2012, ApJ, 754, 109
+
+\bibitem{Qingqing2016}%[Mao et al. (2016)]
+Mao, Q., Berlind, A.A., Scherrer, R.J., et al. 2016, submitted to ApJ
+
+\bibitem{Li2014}%[Li et al.(2014)]
+Li, X.-D., Park, C., Forero-Romero, J., \& Kim, J. 2014, ApJ, 796, 137
+
+\bibitem{Li2015}%[Li et al.(2015)]
+Li, X.-D., Park, C., Sabiu, C.G., \& Kim, J. 2015, MNRAS, 450, 807
+
+\bibitem{LB2002}%[Lewis \& Bridle (2002)]
+Lewis, A., \& Bridle, S. 2002, Phys. Rev. D, 66, 103511
+
+\bibitem{Planck2015}%[Ade et al. (2015)]
+Ade, P.A.R., Aghanim, N., \& Arnaud, M., et al. 2016, A\&A, 594, A13
+
+\bibitem{Anderson2013}%[Anderson et al.(2013)]
 Anderson, L., Aubourg, \'E., \& Bailey, S. et al. 2014, MNRAS, 441, 24
 
-%\bibitem[Bassett et al.(2002)]{Bassett2002}
-%Bassett, B.A., Kunz, M., Silk, J., \& Ungarelli, C. 2002, MNRAS, 336, 1217
+\bibitem{6dFGS}%[Beutler et al.(2011)]
+Beutler, F., Blake, C., \& Colless, M., et al. 2011, MNRAS, 416, 3017
 
-\bibitem[Ballinger, Peacock \& Heavens 1996]{Ballinger1996}
-Ballinger, W.E., Peacock, J.A., \& Heavens, A.F. 1996, MNRAS, 282, 877
+\bibitem{MGS}%[Ross et al.(2015)]
+Ross, A.J., Samushia, L., \& Howlett, C., et al. 2015, MNRAS, 449, 835
 
-\bibitem[Betoule et al.(2014)]{JLA}
+\bibitem{JLA}%[Betoule et al.(2014)]
 Betoule, M., Kessler, R., \& Guy, J., et al. 2014, A\&A, 568, 32
 
-\bibitem[Beutler et al.(2011)]{6dFGS}
-Beutler, F., Blake, C., \& Colless, M., et al. 2011, MNRAS, 416, 3017
+\bibitem{Riess2011}%[Riess et al.(2011)]
+Riess, A.G., Macri, L., \& Casertano, S., et al. 2011, ApJ, 730, 119
 
-\bibitem[Beutler et al.(2013)]{Beutler2013}
-Beutler, F., Saito, S., \& Seo, H.-J., et al. 2013, MNRAS, 443, 1065
-
-\bibitem[Beutler et al.(2016)]{Beutler2016}
-Beutler, F., Seo, H.-J., \& Saito, S., et al. 2016,
-arXiv:1607.03150
-
-\bibitem[Blake et al.(2011)]{Blake2011}
-Blake, C., Glazebrook, K., \& Davis, T. M., 2011, MNRAS, 418, 1725
-
-\bibitem[Blake et al.(2013)]{WiggleZtopoloy}
-Blake, C., James, J.B., \& Poole, G.B. 2013, MNRAS, 437, 2488
-
-\bibitem[Bolton et al.(2012)]{Bolton2012}
-Bolton, A.S., Schlegel, \& D.J., Aubourg E., et al. 2012, AJ, 144, 144
-
-\bibitem[Boylan-Kolchin et al.(2008)]{B08}
-Boylan-Kolchin, M., Ma, C.-P., \& Quataert, E. 2008, MNRAS, 383, 93
-
-%\bibitem[Bueno Belloso et al. (2012)]{BB2012}
-%Bueno Belloso, A., Pettinari, G.W., Meures, N., \& Percival, W.J. 2012, Phys. Rev. D, 86, 023530
-
-%\bibitem[Chevallier \& Polarski(2001)]{CP2001}
-%Chevallier, M., Polarski, D. 2001, Int. J. Mod. Phys. D, 10, 213
-
-%\bibitem[Choi et al.(2010)]{choi 2010}
-%Choi, Y.-Y., Park, C., Kim, J., Gott, J.R., 
-%Weinberg, D.H., Vogeley, M.S., \& Kim, S.S. 2010, ApJS, 190, 181
-
-\bibitem[Christensen et al.(2001)]{Bayesian}
-Christensen, N., Meyer, R., Knox, L., \& Luey, B. 2001, Class. Quant. Grav., 18, 2677
-
-%\bibitem[Chuang et al.(2013)]{Chuang2013}
-%Chuang, C.-H., Prada, F., Beutler, F., et al. 2013, arXiv:1312.4889
-
-\bibitem[Chuang \& Wang(2012)]{ChuangWang2012}
-Chuang, C.-H., \& Wang, Y. 2012, MNRAS, 426, 226
-
-%\bibitem[Corasaniti \& Copeland(2003)]{Corasaniti2003}
-%Corasaniti, P.S., Copeland, E.J. 2003, Phys. Rev. D, 67, 063521
-
-%eBOSS: 
-%http://arxiv.org/abs/1508.04473
-\bibitem[Dawson et al.(2015)]{eBOSS}
-Dawson, K.S., Kneib, J.P., \& Percival, W.J., et al. 2015, accepted AJ
-
-\bibitem[Dawson et al.(2012)]{Dawson et al. 2012}
-Dawson, K.S., Schlegel, D.J., \& Ahn, C.P., et al. 2012, AJ, 145, 10
-
-\bibitem[Efstathiou (2014)]{E14H0}
+\bibitem{E14H0}%[Efstathiou (2014)]
 Efstathiou, G. 2014, MNRAS, 440, 1138
 
-\bibitem[Eisenstein et al.(2011)]{Eisenstein et al. 2011}
-Eisenstein, D.J.,  Weinberg, D.H., \& Agolet, E., et al. 2011, AJ, 142, 72
+\bibitem{HR4}%[Kim et al.(2015)]
+Kim, J., Park, C., L'Huillier, B., \& Hong, S. E. 2015, JKAS, 48, 213
 
-\bibitem[Feldman, Kaiser \& Peacock (1994)]{1994ApJ...426...23F} 
-Feldman, H.A., Kaiser, N., \& Peacock, J.A.\ 1994, ApJ, 426, 23
+%\bibitem{Lee12}
+%\bibinfo{author}{Lee}, E.~J., {Murray}, N., {Rahman}, M. 
+%\newblock \bibinfo{title}{Milky Way Star-forming Complexes and the Turbulent Motion of the Galaxy's Molecular Gas.}
+%\newblock{\it Astrophys. \ J.}{\bf\, 752}, 146-159 (2012).
 
-\bibitem[Fukugita et al. (1996)]{Fukugita1996}
-Fukugita, M., Ichikawa, T., \& Gunn, J.E., et al. 1996, AJ, 111, 1748
-%Publication:	
-%Astronomical Journal v.111, p.1748
+%%%% For methods
+\bibitem{Reidetal:2016}%[Reid et al.(2016)]
+Reid, B., Ho, S., \& Padmanabhan, N., et al.  2016, MNRAS, 455, 1553
 
-%\bibitem[Gingold \& Monaghan(1977)]{GM1977}
-%Gingold, R.A., \& Monaghan, J.J. 1977, MNRAS, 181, 375
+\bibitem{komatsu2011}%[Komatsu et al.(2011)]
+Komatsu, E., Smith, K. M., \& Dunkley, J., et al. 2011, ApJS, 192, 18
 
-%\bibitem[Gott et al.(2009)]{gott 2009}
-%Gott, J.R., Choi, Y.-Y., Park, C., \& Kim, J. 2009, ApJ, 695, L45
+\bibitem{hong2016}%[Hong et al.(2016)]
+Hong, S.E., Park, C.,\&  Kim, J. 2016, ApJ, 823, 103
 
-%\bibitem[Gott et al.(2008)]{gott 2008}
-%Gott, J.R., Hambrick, D.C., Vogeley, M.S., Kim, J., Park, C., Choi, Y.-Y.,
-%Cen, R., Ostriker, J.P., \& Nagamine, K. 2008, ApJ, 675, 16
+\bibitem{MDPATCHY}%[Kitaura et al.(2015)]
+Kitaura, F.S., Rodriguez-Torres, S., Chuang, C.-H., et al.2016, MNRAS, 456, 4156
 
-\bibitem[Gunn et al. (1998)]{Gunn1998}	
-Gunn, J.E., Carr, M., \& Rockosi, C. et al. 1998, AJ, 116, 3040
-
-\bibitem[Gunn et al.(2006)]{Gunn et al. 2006}
-Gunn, J.E., Siegmund, W.A., \& Mannery, E.J., et al. 2006, AJ, 131, 2332
-
-\bibitem[Guzzo et al.(2008)]{Guzzo2008}
-Guzzo, L., Pierleoni, M., \& Meneux, B., et al. 2008, Nature, 451, 541
-
-\bibitem[Hartlap et al.(2006)]{Hartlap}
+\bibitem{Hartlap}%[Hartlap et al.(2006)]
 Hartlap J., Simon P. \& Schneider P. [astro-ph/0608064].
 
-\bibitem[Hong et al.(2016)]{hong2016}
-Hong, S.E., Park, C.,\&  Kim, J. 2016, ApJ, 823, 103
-
-\bibitem[Jackson (1972)]{FOG}
-Jackson, J., 1972, MNRAS, 156, 1
-
-\bibitem[Jennings et al.(2011)]{Jennings2011}
-Jennings, E., Baugh, C.M., \& Pascoli, S. 2011, MNRAS, 420, 1079
-
-%\bibitem[Jeong et al.(2014)]{Jeong2014}
-%Jeong, D., Dai, L., Kamionkowski, M., \& Szalay, A.S. 2014, arXiv:1408.4648
-
-\bibitem[Jiang et al.(2008)]{jiang2008}
-Jiang, C.Y., Jing, Y. P., \& Faltenbacher, A., et al. 2008, ApJ, 675, 1095
-
-\bibitem[Kaiser (1987)]{Kaiser1987}
-Kaiser, N. 1987, MNRAS, 227, 1
-
-\bibitem[Kim \& Park(2006)]{kim and park 2006}
-Kim, J., \& Park, C. 2006, ApJ, 639, 600
-
-\bibitem[Kim et al.(2009)]{2009ApJ...701.1547K} 
-Kim, J., Park, C., Gott, J.R., III, \& Dubinski, J.\ 2009, ApJ, 701, 1547
-
-\bibitem[Kim et al.(2015)]{hr4}
-Kim, J., Park, C., L'Huillier, B., \& Hong, S. E. 2015, JKAS, 48, 213
-
-\bibitem[Kim et al.(2011)]{horizonrun}
-Kim, J., Park, C., Rossi, G., Lee, S.M., \& Gott, J.R. 2011, JKAS, 44, 217
-
-\bibitem[Kitaura et al.(2015)]{MDPATCHY}
-Kitaura, F.S., Rodriguez-Torres, S., Chuang, C.-H., et al. arXiv:1509.06400
-
-\bibitem[Komatsu et al.(2011)]{komatsu 2011}
-Komatsu, E., Smith, K. M., \& Dunkley, J., et al. 2011, ApJS, 192, 18
-
-\bibitem[Lacey \& Cole(1993)]{LC93}
-Lacey, C., \& Cole, S. 1993, MNRAS, 262, 627
-
-\bibitem[Landy \& Szalay(1993)]{1993ApJ...412...64L} 
-Landy, S.D., \& Szalay, A.S.\ 1993, ApJ, 412, 64
-
-%EUCLID:
-%http://arxiv.org/abs/1110.3193
-\bibitem[Laureijs et al.(2011)]{EUCLID}
-Laureijs, R., Amiaux, J., \& Arduini, S., et al. 2011, arXiv:1110.3193
-
-\bibitem[Lavaux \& Wandelt(2012)]{LavausWandelt1995}
-Lavaux, G., \& Wandelt, B.D. 2012, ApJ, 754, 109
-
-%\bibitem[Levi et al.(2013)]{2013arXiv1308.0847L} 
-%Levi, M., Bebek, C., Beers, T., et al.\ 2013, arXiv:1308.0847
-
-\bibitem[Lewis \& Bridle (2002)]{LB2002}
-Lewis, A., \& Bridle, S. 2002, Phys. Rev. D, 66, 103511
-
-\bibitem[L'Huillier et al.(2014)]{2014NewA...30...79L} 
-L'Huillier, B., Park, C., \& Kim, J.\ 2014, New Astronomy, 30, 79
-
-\bibitem[Li et al.(2011)]{Li2011}
-Li, M., Li, X.-D., Wang, S., \& Wang, Y. 2011, Commun. Theor. Phys., 56, 525
-
-\bibitem[Li et al.(2014)]{Li2014}
-Li, X.-D., Park, C., Forero-Romero, J., \& Kim, J. 2014, ApJ, 796, 137
-
-\bibitem[Li et al.(2015)]{Li2015}
-Li, X.-D., Park, C., Sabiu, C.G., \& Kim, J. 2015, MNRAS, 450, 807
-
-\bibitem[Li et al.(2016)]{Li2016}
-Li, X.-D., Park, C., \& Sabiu, C.G., et al. 2016, ApJ, 832, 103
-
-%\bibitem[Linder(2003)]{Linder2003}
-%Linder, E.V. 2003, Phys. Rev. Lett., 90, 091301
-
-\bibitem[Linder et al.(2014)]{Linder2013}
-Linder, E.V., Minji, O., Okumura, T., Sabiu, C.G., \& Song, Y.-S. 2014, Phys. Rev. D, 89, 063525
-
-\bibitem[L{\'o}pez-Corredoira(2014)]{2014ApJ...781...96L} 
-L{\'o}pez-Corredoira, M.\ 2014, ApJ, 781, 96
-
-\bibitem[Mao et al. (2016)]{Qingqing2016}
-Mao, Q., Berlind, A.A., Scherrer, R.J., et al. 2016, submitted to ApJ
-
-\bibitem[Marinoni \& Buzzi(2010)]{Marinoni2010}
-Marinoni, C., \& Buzzi, A. 2010, Nature, 468, 539
-
-\bibitem[Matsubara \& Suto(1996)]{Matsubara1996}
-Matsubara T., \& Suto, Y. 1996, ApJ, 470, L1
-
-\bibitem[McCavana et al.(2012)]{M12}
-McCavana, T., Micic, M., Lewis, G. F., et al. 2012, MNRAS, 424, 361
-
-\bibitem[Morandi \& Sun (2016)]{MS2016}
-Morandi, A., \& Sun, M. arXiv:1601.03741
-
-\bibitem[Outram et al.(2004)]{Outram2004}
-Outram, P.J., Shanks, T., Boyle, B.J., Croom, S.M., Hoyle, F., Loaring, N.S., 
-Miller, L., \& Smith, R.J. 2004, MNRAS, 348, 745
-
-%\bibitem[Parejko et al.(2013)]{Parejko2013}
-%Parejko, J. K., Sunayama, T., Padmanabhan, N., et al. 2013, MNRAS, 429, 98
-
-\bibitem[Parejko et al.(2013)]{Parejko2013}
-Parejko J.K., et al., 2013, MNRAS, 429, 98
-
-\bibitem[Parihar et al. (2014)]{CMASSLSS2014}
-Parihar, P., Vogeley, M.S., \& Gott, J.R., et al. 2014, ApJ, 796, 86
-
-\bibitem[Park et al.(2005)]{park 2005}
-Park, C., Kim, J., \& Gott, J.R. 2005, ApJ, 633, 1
-
-\bibitem[Park \& Kim(2010)]{topology}
-Park, C., \& Kim, Y.-R. 2010, ApJL, 715, L185
-
-\bibitem[Park et al. (2012)]{Park2012}
-Park, C., Choi, Y.-Y., Kim, J., Gott, J.R., Kim, S.S., \&
-Kim, K.-S. 2012, ApJ, 759, 7
-
-\bibitem[Park et al. (2015)]{Park2015}
-Park, C., Song, H., Einasto, M., Lietzen, H., \&
-Heinamaki, P. 2015, JKAS, 48, 75
-
-\bibitem[Peebles \& Ratra(2003)]{PR2003}
-Peebles, P.J.E., \& Ratra, B. 2003, Reviews of Modern Physics, 75, 559
-
-\bibitem[Percival et al.(2014)]{Percival2014}
+\bibitem{Percival2014}%[Percival et al.(2014)]
 Percival, W.J., Ross, A.J., \& S\'{a}nchez, A.G., et al. 2014, MNRAS, 439, 2531
-
-\bibitem[Perlmutter et al.(1999)]{Perl1999}
-Perlmutter, S., Aldering, G., \& Goldhaber, G., et al. 1999, ApJ, 517, 565
-
-\bibitem[Press \& Shechter(1974)]{PS1974}
-Press, W.H., \& Schechter, P.L. 1974, ApJ, 187, 425
-
-\bibitem[Reid et al.(2012)]{Reid2012}
-Reid, B., Samushia, L., \& White, M., et al. 2012, MNRAS, 426, 2719
-
-\bibitem[Reid et al.(2016)]{Reidetal:2016}
-Reid, B., Ho, S., \& Padmanabhan, N., et al.  2016, MNRAS, 455, 1553
-
-\bibitem[Riess et al.(1998)]{Riess1998}
-Riess, A.G., Filippenko, A.V., \& Challis, P., et al. 1998, AJ, 116, 1009
-
-\bibitem[Riess et al.(2011)]{Riess2011}
-Riess, A.G., Macri, L., \& Casertano, S., et al. 2011, ApJ, 730, 119
-%A 3\% Solution: Determination of the Hubble Constant with the Hubble Space Telescope and Wide Field Camera
-
-\bibitem[Ross et al.(2012)]{2012MNRAS.424..564R} 
-Ross, A.J., Percival, W.J., \& S{\'a}nchez, A.G. et al.\ 2012, MNRAS, 424, 564
-
-\bibitem[Ross et al.(2015)]{MGS}
-Ross, A.J., Samushia, L., \& Howlett, C., et al. 2015, MNRAS, 449, 835
-
-\bibitem[Ryden(1995)]{Ryden1995}
-Ryden, B.S. 1995, ApJ, 452, 25
-
-%\bibitem[Samushia et al.(2014)]{Samushia2014}
-%Samushia, L., Reid, B. A., White, M., et al. 2014, MNRAS, 439, 3504
-
-%\bibitem[Sanchez et al.(2013)]{Sanchez2013}
-%Sanchez, A. G., Kazin, E. A., Beutler, F., et al. 2013, MNRAS, 433, 1202
-
-%\bibitem[Sutter et al.(2014)]{Sutter2014}
-%Sutter, P.M., Pisani, A., Wandelt, B.D., \& Weinberg, D.H. 2014, MNRAS, 443, 2983
-
-\bibitem[Sanchez et al.(2016)]{Sanchez2016}
-Sanchez, A. G., Scoccimarro, R., \& Crocce, M., et al.
-arXiv:1607.03147
-
-\bibitem[Schlafly et al.(2010)]{Schlafly2010}
-Schlafly E.F., Finkbeiner D.P., Schlegel D.J., et al. 2010, ApJ, 725, 1175
-
-\bibitem[Schlafly \& Finkbeiner(2011)]{SF2011}
-Schlafly E.F., \& Finkbeiner D.P. 2011, ApJ, 737, 103
-
-%DESI:
-%http://arxiv.org/abs/1106.1706
-\bibitem[Schlegel et al.(2011)]{DESI}
-Schlegel, D., Abdalla, F., \& Abraham, T., et al. 2011, arXiv:1106.1706
-
-\bibitem[Smee et al.(2013)]{Smee2013}
-Smee, S.A., Gunn, J.E., \& Uomoto, A., et al. 2013, AJ, 146, 32
-
-\bibitem[Song et al.(2014)]{2014arXiv1407.2257S} 
-Song, Y.S., Sabiu, C.G., 
-Okumura, T., Oh, M., \& Linder, E.V.\ 2014, JCAP, 12, 005
-
-\bibitem[Speare et al. (2015)]{Speare2015}
-Speare, R., Gott, J.R., Kim, J., \& Park, C.
-2015, ApJ, 799, 176
-
-%\bibitem[Tojeiro \& Percival(2011)]{Tojeiro2011}
-%Tojeiro R., \& Percivial W.J. 2011, MNRAS, 417, 1114
-
-%\bibitem[Tojeiro et al.(2012)]{Tojeiro2012}
-%Tojeiro, R., Percival, W. J., Wake, D. A., et al. 2012, MNRAS, 424, 136
-
-\bibitem[Viana \& Liddle(1996)]{VL1996}
-Viana, P.T.P., \& Liddle, A.R. 1996, MNRAS, 281, 323
-
-\bibitem[Villalobos et al.(2013)]{V13}
-Villalobos, \'{A}., ́De Lucia, G., Weinmann, S.M., Borgani, S., \& Murante, G. 2013, MNRAS, 433, L49
-
-\bibitem[Weinberg (1989)]{SW1989}
-Weinberg, S. 1989, Reviews of Modern Physics, 61, 1
-
-\bibitem[White (2011)]{White2011}
-White M., et al. 2011, ApJ, 728, 126
-
-\bibitem[Yoo \& Watanabe(2012)]{2012IJMPD..2130002Y} Yoo, J., \& Watanabe, Y.\ 2012, International Journal of Modern Physics D, 21, 1230002
-
-\bibitem[York et al.(2000)]{York et al. 2000}
-York, D.G., Adelman, J., \& Anderson, J.E., et al. 2000, AJ, 120, 1579
-
-\bibitem[Zehavi et al.(2011)]{zehavi2011}
-Zehavi, I., Zheng, Z., \& Weinberg, D.H., et al. 2011, ApJ, 736, 59
-
-%\bibitem{Milliman14}
-%\bibinfo{author}{Milliman}, K.~E. {\it et~al.}
-%\newblock \bibinfo{title}{WIYN Open Cluster Study. LX. Spectroscopic Binary Orbits in NGC 6819.}
-%\newblock{\it Astron. \ J.}{\bf\, 148}, 38--57 (2014).
 
@@
 
-X.L. computed the approximated 2pCFs in the many cosmologies, computed the likelihoods based on them, derived the final cosmological constraints, and did the robustness tests. 
-C.S. wrote the code computing the 2pCFs, and contributed in the likelihood analysis and the robustness tests. 
-C.P. proposed the concept of using redshift dependence to do AP tests, and have extensive discussions with X.L. about the likelihood analysis, 
-systematic correction, and robustness tests.
-Y.W. and G.Z. contributed in the computing the approximated 2pCFs in non-fiducial cosmologies, and the robustness tests.
-H.P. contributed in the cross-check of the 2pCF measurements, the likelihood analysis, and the systematic correction.
-A.S. contributed in the fast likelihood in non-fiducial cosmologies and the cosmological interpretation of the results.
-J.K. and S.H. performed the Horizon Run 4 simulations and built the mock galaxy samples.
+X.L. computed the approximated 2pCFs in the many cosmologies, did the statistical analysis and computed the likelihoods, 
+derived the final cosmological constraints, and conducted the robustness tests. 
+C.S. wrote the code for computing the 2pCFs, and contributed in the likelihood methodology and the robustness tests. 
+C.P. contributed in the concept of using the redshift dependence, the LSS statistical, the likelihood methodology,
+the horizon run simulations, the systematic corrections, and the robustness tests.
+Y.W. and G.Z. contributed in the computing of approximated 2pCFs in non-fiducial cosmologies and the robustness tests.
+H.P. contributed in the 2pCF measurements, the likelihood computation, and the systematic correction.
+A.S. contributed in the fast computation of likelihoods in non-fiducial cosmologies and the cosmological interpretation of the results.
+J.K. and S.H. performed the Horizon Run 4 simulations and created the mock galaxy samples.
 All authors commented on the manuscript.
@@
 Reprints and permissions information is available at \href{www.nature.com/reprints}{www.nature.com/reprints}.
-Correspondence and requests for materials should be addressed to X.D. (e-mail: \href{mailto:xiaodongli@kias.re.kr}{xiaodongli@kias.re.kr}).
+Correspondence and requests for materials should be addressed to X.L. (e-mail: \href{mailto:xiaodongli@kias.re.kr}{xiaodongli@kias.re.kr}).
 
@@
    \caption{\label{fig_xy}
-   The distance dependence of the shape distortion in four wrongly assumed cosmologies,
-   assuming a true cosmology of $\Omega_m=0.31$, $w=-1$.
+   {\bf The distance dependence of the shape distortion in four wrongly assumed cosmologies}.
+   Assuming a true cosmology of $\Omega_m=0.31$, $w=-1$.
    There are four perfect squares with their true shapes plotted in blue dashed lines.
@@
    \centering{
-   \includegraphics[height=5.3cm]{fig_nbar.eps}
-   \includegraphics[width=7cm,]{fig_2pcf.eps}
+   %\includegraphics[height=5.3cm]{fig_nbar.eps}
+   %\includegraphics[width=7cm,]{fig_2pcf.eps}
+   \includegraphics[width=14cm]{fig_nbar.eps}
+   \includegraphics[width=14cm,]{fig_2pcf.eps}
    }
    \caption{\label{fig_TpCF}
-   Left panel: We split the BOSS DR12 galaxies into six redshift bins to measure the evolution of shape distortion.
+   {\bf Spliting the SDSS galaxies into six redshiftbins, and measuring the correlation function.}
+   Upper panel: We split the BOSS DR12 galaxies into six redshift bins to measure the evolution of shape distortion.
    The blue and green solid histograms show the redshift density distribution of LOWZ and CMASS galaxies in the $\Omega_m=0.31$ $\Lambda$CDM. 
@@
    The number of LOWZ/CMASS galaxies in the three low/high redshift bins are listed.
-   Right panel: 2D contour map of measured $\xi$ as a function of $\mu$ and $s$, from the six redshift bins of LOWZ and CMASS samples, 
+   Lower panel: 2D contour map of measured $\xi$ as a function of $\mu$ and $s$, from the six redshift bins of LOWZ and CMASS samples, 
       in the cosmology of $\Omega_m=0.31$ $\Lambda$CDM model.
@@
    \centering{
-   \includegraphics[height=5cm,natwidth=6,natheight=4.5]{figCPL_b.pdf}
+   \includegraphics[height=7cm,natwidth=6,natheight=4.5]{figCPL_b.pdf}
    %\includegraphics[width=5.5cm,natwidth=4,natheight=4]{figCPL_b_BAOSNIaAP.pdf}
-   \includegraphics[height=5cm,natwidth=6,natheight=4.5]{figCPL_d.pdf}
+   \includegraphics[height=7cm,natwidth=6,natheight=4.5]{figCPL_d.pdf}
    }
    \caption{\label{fig_con}
-   Left panel: 68.3\%, 95.4\% CL likelihood contours in the  $w_0-w_a$ plane.
+   {\bf Cosmological constraints on the CPL dark energy parametrization $w=w_0+w_a\frac{z}{1+z}$.}
+   Upper panel: 68.3\%, 95.4\% CL likelihood contours in the  $w_0-w_a$ plane.
    %Results are consistent with $\Lambda$CDM.
@@
    %When combined with CMB+BAO, AP method yields much tighter constraints than SNIa.
-   Right panel: Redshift evolution of $w(z)$, with/without adding the AP constraint.
+   Lower panel: Redshift evolution of $w(z)$, with/without adding the AP constraint.
    Adding AP tightens the constraints and reduces the redshift evolution of $w$ (tilt of $w(z)$).
@@
    \caption{\label{fig_contest}
-   Robustness test of the AP method. 
+   {\bf Robustness test of the results.}
    For the ``default'' constraints (pink contours) are derived using six redshift bins, 
@@
 an N-body simulation with box size $L={3150}$ $h^{-1}$Mpc, number of particles $6300^3$,   
-initial redshift $z_{i}=100$, and WMAP5 cosmological parameters 
-$(\Omega_{b},\Omega_{m},\Omega_\Lambda,h,\sigma_8,n_s)$  = (0.044, 0.26, 0.74, 0.72, 0.79, 0.96) \citep[]{komatsu 2011}. 
+initial redshift $z_{i}=100$, and WMAP5\citep{komatsu2011} cosmological parameters 
+$(\Omega_{b},\Omega_{m},\Omega_\Lambda,h,\sigma_8,n_s)$  = (0.044, 0.26, 0.74, 0.72, 0.79, 0.96). 
 Mock galaxy samples are produced using a modified version of the one-to-one correspondence scheme \citep{hong2016}. 
-The covariance matrix ${\bf Cov}$ is computed from the 2,000 sets of MultiDark PATCHY mock catalogues \citep{MDPATCHY}.
+The covariance matrix, ${\bf Cov}$, is computed from the 2,000 sets of MultiDark PATCHY mock catalogues \citep{MDPATCHY}.
 The statistical bias and scattering in the likelihood function (due to the finite number of mocks in covariance estimation) 
-are corrected following \citet{Hartlap} and \citet{Percival2014}.
+are adequately corrected\citet{Hartlap,Percival2014}.
 
-In \cite{Li2016} the likelihood contour of $\Omega_m-w$ was constructed by
+In our earlier work\cite{Li2016}, the likelihood contour of $\Omega_m-w$ was constructed by
 measuring the 2PCF 3,375 times,
@@
 %with $0.06\leq \Omega_m\leq 0.41$, $-1.5 \leq w \leq -0.4$.
-This procedure took 1 month using 500 cores of the KIAS {\texttt baekdu} cluster.
-It would be too expensive to do such a computation on a 3D grid of $\Omega_m-w_0-w_a$,
-so here we take an approach  of ``approximate 2PCF'', described as follows.
+This procedure took 1 month using 500 cores of the KIAS {\texttt {baekdu}} cluster.
+It would be computationally intractable to attempt a full MCMC of all relevant cosmological parameters using this approach. 
+Thus we adopt an ``approximate 2PCF'' by transforming our measurements from one cosmology to another.
+%It would be too expensive to do such a computation on a 3D grid of $\Omega_m-w_0-w_a$,
+%so here we take an approach  of ``approximate 2PCF'', described as follows.
 
-The number of pairs are only counted in a fiducial cosmology
+In detail, the number of pairs are only counted in a fiducial cosmology
 -- which is taken as the $\Omega_m=0.26$ $\Lambda$CDM --
@@
 %in the fiducial cosmology and group the bins in the target cosmology.
-In the case when one small pixel belongs to more than one larger pixel (``edge effect'' ),
+In the case when one small pixel belongs to more than one larger pixel,
 a correction is applied by computing the fraction of the overlapping area.
@@
 {\textbf{Data availability.}} 
-The codes computing the likelihood of the AP tests are available on GitHub,
+The codes for computing the likelihood of the AP tests are available on GitHub,
 \href{https://github.com/xiaodongli1986/APCPL.git}
 {https://github.com/xiaodongli1986/APCPL.git}.
-The codes computing the correlation functions are available via
+The codes for computing the correlation functions are available via
 \href{https://bitbucket.org/csabiu/kstat}
-{https://bitbucket.org/csabiu/kstat}.
+{https://bitbucket.org/csabiu/kstat} and \href{http://ascl.net/code/v/1634}{http://ascl.net/code/v/1634}.
 The MCMC chains for CPL are publicly available via the Planck Legacy Archive
@@
 {http://sdss.kias.re.kr/astro/Horizon-Runs/Horizon-Run4.php}.
-To use the simulation data, contact directly Juhan Kim \href{kjhan@kias.re.kr}{kjhan@kias.re.kr}.
-
-\begin{thebibliography}{10}
-\setcounter{enumiv}{29}
-
-\expandafter\ifx\csname url\endcsname\relax
-  \def\url#1{\texttt{#1}}\fi
-\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
-\providecommand{\bibinfo}[2]{#2}
-\providecommand{\eprint}[2][]{\url{#2}}
-
-\bibitem[Ade et al. (2015)]{Planck2015}
-Ade, P.A.R., Aghanim, N., \& Arnaud, M., et al. arXiv:1502.01589
-
-\bibitem[Alam et al.(2016)]{Alam2016}
-Alam, S., Ata, M., \& Bailey, S., et al. 2016,
-submitted to MNRAS (arXiv:1607.03155)
-
-%\bibitem[{{Alam} {et~al}\mbox{.}(2015{\natexlab{a}}){Alam}, {Albareti},
-%  {Allende Prieto}, {Anders}, {Anderson}, {Anderton}, {Andrews}, {Armengaud},
-%  {Aubourg}, {Bailey}, \& et~al.}]{dr12}
-%{Alam} S., Albareti, F.D.,\& Allende Prieto, C., {et~al.}, 2015,  ApJS, 219, 12
-
-\bibitem[Alcock \& Paczynski(1979)]{AP1979}
-Alcock, C., \& Paczynski, B. 1979, Nature, 281, 358
-
-%\bibitem[Anderson et al.(2012)]{2012MNRAS.427.3435A} 
-%Anderson, L., Aubourg, E., Bailey, S., et al.\ 2012, MNRAS, 427, 3435
-
-\bibitem[Anderson et al.(2013)]{Anderson2013}
-Anderson, L., Aubourg, \'E., \& Bailey, S. et al. 2014, MNRAS, 441, 24
-
-%\bibitem[Bassett et al.(2002)]{Bassett2002}
-%Bassett, B.A., Kunz, M., Silk, J., \& Ungarelli, C. 2002, MNRAS, 336, 1217
-
-\bibitem[Ballinger, Peacock \& Heavens 1996]{Ballinger1996}
-Ballinger, W.E., Peacock, J.A., \& Heavens, A.F. 1996, MNRAS, 282, 877
-
-\bibitem[Betoule et al.(2014)]{JLA}
-Betoule, M., Kessler, R., \& Guy, J., et al. 2014, A\&A, 568, 32
-
-\bibitem[Beutler et al.(2011)]{6dFGS}
-Beutler, F., Blake, C., \& Colless, M., et al. 2011, MNRAS, 416, 3017
-
-\bibitem[Beutler et al.(2013)]{Beutler2013}
-Beutler, F., Saito, S., \& Seo, H.-J., et al. 2013, MNRAS, 443, 1065
-
-\bibitem[Beutler et al.(2016)]{Beutler2016}
-Beutler, F., Seo, H.-J., \& Saito, S., et al. 2016,
-arXiv:1607.03150
-
-\bibitem[Blake et al.(2011)]{Blake2011}
-Blake, C., Glazebrook, K., \& Davis, T. M., 2011, MNRAS, 418, 1725
-
-\bibitem[Blake et al.(2013)]{WiggleZtopoloy}
-Blake, C., James, J.B., \& Poole, G.B. 2013, MNRAS, 437, 2488
-
-\bibitem[Bolton et al.(2012)]{Bolton2012}
-Bolton, A.S., Schlegel, \& D.J., Aubourg E., et al. 2012, AJ, 144, 144
-
-\bibitem[Boylan-Kolchin et al.(2008)]{B08}
-Boylan-Kolchin, M., Ma, C.-P., \& Quataert, E. 2008, MNRAS, 383, 93
-
-%\bibitem[Bueno Belloso et al. (2012)]{BB2012}
-%Bueno Belloso, A., Pettinari, G.W., Meures, N., \& Percival, W.J. 2012, Phys. Rev. D, 86, 023530
-
-%\bibitem[Chevallier \& Polarski(2001)]{CP2001}
-%Chevallier, M., Polarski, D. 2001, Int. J. Mod. Phys. D, 10, 213
-
-%\bibitem[Choi et al.(2010)]{choi 2010}
-%Choi, Y.-Y., Park, C., Kim, J., Gott, J.R., 
-%Weinberg, D.H., Vogeley, M.S., \& Kim, S.S. 2010, ApJS, 190, 181
-
-\bibitem[Christensen et al.(2001)]{Bayesian}
-Christensen, N., Meyer, R., Knox, L., \& Luey, B. 2001, Class. Quant. Grav., 18, 2677
-
-%\bibitem[Chuang et al.(2013)]{Chuang2013}
-%Chuang, C.-H., Prada, F., Beutler, F., et al. 2013, arXiv:1312.4889
-
-\bibitem[Chuang \& Wang(2012)]{ChuangWang2012}
-Chuang, C.-H., \& Wang, Y. 2012, MNRAS, 426, 226
-
-%\bibitem[Corasaniti \& Copeland(2003)]{Corasaniti2003}
-%Corasaniti, P.S., Copeland, E.J. 2003, Phys. Rev. D, 67, 063521
-
-%eBOSS: 
-%http://arxiv.org/abs/1508.04473
-\bibitem[Dawson et al.(2015)]{eBOSS}
-Dawson, K.S., Kneib, J.P., \& Percival, W.J., et al. 2015, accepted AJ
-
-\bibitem[Dawson et al.(2012)]{Dawson et al. 2012}
-Dawson, K.S., Schlegel, D.J., \& Ahn, C.P., et al. 2012, AJ, 145, 10
-
-\bibitem[Efstathiou (2014)]{E14H0}
-Efstathiou, G. 2014, MNRAS, 440, 1138
-
-\bibitem[Eisenstein et al.(2011)]{Eisenstein et al. 2011}
-Eisenstein, D.J.,  Weinberg, D.H., \& Agolet, E., et al. 2011, AJ, 142, 72
-
-\bibitem[Feldman, Kaiser \& Peacock (1994)]{1994ApJ...426...23F} 
-Feldman, H.A., Kaiser, N., \& Peacock, J.A.\ 1994, ApJ, 426, 23
-
-\bibitem[Fukugita et al. (1996)]{Fukugita1996}
-Fukugita, M., Ichikawa, T., \& Gunn, J.E., et al. 1996, AJ, 111, 1748
-%Publication:	
-%Astronomical Journal v.111, p.1748
-
-%\bibitem[Gingold \& Monaghan(1977)]{GM1977}
-%Gingold, R.A., \& Monaghan, J.J. 1977, MNRAS, 181, 375
-
-%\bibitem[Gott et al.(2009)]{gott 2009}
-%Gott, J.R., Choi, Y.-Y., Park, C., \& Kim, J. 2009, ApJ, 695, L45
-
-%\bibitem[Gott et al.(2008)]{gott 2008}
-%Gott, J.R., Hambrick, D.C., Vogeley, M.S., Kim, J., Park, C., Choi, Y.-Y.,
-%Cen, R., Ostriker, J.P., \& Nagamine, K. 2008, ApJ, 675, 16
-
-\bibitem[Gunn et al. (1998)]{Gunn1998}	
-Gunn, J.E., Carr, M., \& Rockosi, C. et al. 1998, AJ, 116, 3040
-
-\bibitem[Gunn et al.(2006)]{Gunn et al. 2006}
-Gunn, J.E., Siegmund, W.A., \& Mannery, E.J., et al. 2006, AJ, 131, 2332
-
-\bibitem[Guzzo et al.(2008)]{Guzzo2008}
-Guzzo, L., Pierleoni, M., \& Meneux, B., et al. 2008, Nature, 451, 541
-
-\bibitem[Hartlap et al.(2006)]{Hartlap}
-Hartlap J., Simon P. \& Schneider P. [astro-ph/0608064].
-
-\bibitem[Hong et al.(2016)]{hong2016}
-Hong, S.E., Park, C.,\&  Kim, J. 2016, ApJ, 823, 103
-
-\bibitem[Jackson (1972)]{FOG}
-Jackson, J., 1972, MNRAS, 156, 1
-
-\bibitem[Jennings et al.(2011)]{Jennings2011}
-Jennings, E., Baugh, C.M., \& Pascoli, S. 2011, MNRAS, 420, 1079
-
-%\bibitem[Jeong et al.(2014)]{Jeong2014}
-%Jeong, D., Dai, L., Kamionkowski, M., \& Szalay, A.S. 2014, arXiv:1408.4648
-
-\bibitem[Jiang et al.(2008)]{jiang2008}
-Jiang, C.Y., Jing, Y. P., \& Faltenbacher, A., et al. 2008, ApJ, 675, 1095
-
-\bibitem[Kaiser (1987)]{Kaiser1987}
-Kaiser, N. 1987, MNRAS, 227, 1
-
-\bibitem[Kim \& Park(2006)]{kim and park 2006}
-Kim, J., \& Park, C. 2006, ApJ, 639, 600
-
-\bibitem[Kim et al.(2009)]{2009ApJ...701.1547K} 
-Kim, J., Park, C., Gott, J.R., III, \& Dubinski, J.\ 2009, ApJ, 701, 1547
-
-\bibitem[Kim et al.(2015)]{hr4}
-Kim, J., Park, C., L'Huillier, B., \& Hong, S. E. 2015, JKAS, 48, 213
-
-\bibitem[Kim et al.(2011)]{horizonrun}
-Kim, J., Park, C., Rossi, G., Lee, S.M., \& Gott, J.R. 2011, JKAS, 44, 217
-
-\bibitem[Kitaura et al.(2015)]{MDPATCHY}
-Kitaura, F.S., Rodriguez-Torres, S., Chuang, C.-H., et al. arXiv:1509.06400
-
-\bibitem[Komatsu et al.(2011)]{komatsu 2011}
-Komatsu, E., Smith, K. M., \& Dunkley, J., et al. 2011, ApJS, 192, 18
-
-\bibitem[Lacey \& Cole(1993)]{LC93}
-Lacey, C., \& Cole, S. 1993, MNRAS, 262, 627
-
-\bibitem[Landy \& Szalay(1993)]{1993ApJ...412...64L} 
-Landy, S.D., \& Szalay, A.S.\ 1993, ApJ, 412, 64
-
-%EUCLID:
-%http://arxiv.org/abs/1110.3193
-\bibitem[Laureijs et al.(2011)]{EUCLID}
-Laureijs, R., Amiaux, J., \& Arduini, S., et al. 2011, arXiv:1110.3193
-
-\bibitem[Lavaux \& Wandelt(2012)]{LavausWandelt1995}
-Lavaux, G., \& Wandelt, B.D. 2012, ApJ, 754, 109
-
-%\bibitem[Levi et al.(2013)]{2013arXiv1308.0847L} 
-%Levi, M., Bebek, C., Beers, T., et al.\ 2013, arXiv:1308.0847
-
-\bibitem[Lewis \& Bridle (2002)]{LB2002}
-Lewis, A., \& Bridle, S. 2002, Phys. Rev. D, 66, 103511
-
-\bibitem[L'Huillier et al.(2014)]{2014NewA...30...79L} 
-L'Huillier, B., Park, C., \& Kim, J.\ 2014, New Astronomy, 30, 79
-
-\bibitem[Li et al.(2011)]{Li2011}
-Li, M., Li, X.-D., Wang, S., \& Wang, Y. 2011, Commun. Theor. Phys., 56, 525
-
-\bibitem[Li et al.(2014)]{Li2014}
-Li, X.-D., Park, C., Forero-Romero, J., \& Kim, J. 2014, ApJ, 796, 137
-
-\bibitem[Li et al.(2015)]{Li2015}
-Li, X.-D., Park, C., Sabiu, C.G., \& Kim, J. 2015, MNRAS, 450, 807
-
-\bibitem[Li et al.(2016)]{Li2016}
-Li, X.-D., Park, C., \& Sabiu, C.G., et al. 2016, ApJ, 832, 103
-
-%\bibitem[Linder(2003)]{Linder2003}
-%Linder, E.V. 2003, Phys. Rev. Lett., 90, 091301
-
-\bibitem[Linder et al.(2014)]{Linder2013}
-Linder, E.V., Minji, O., Okumura, T., Sabiu, C.G., \& Song, Y.-S. 2014, Phys. Rev. D, 89, 063525
-
-\bibitem[L{\'o}pez-Corredoira(2014)]{2014ApJ...781...96L} 
-L{\'o}pez-Corredoira, M.\ 2014, ApJ, 781, 96
-
-\bibitem[Mao et al. (2016)]{Qingqing2016}
-Mao, Q., Berlind, A.A., Scherrer, R.J., et al. 2016, submitted to ApJ
-
-\bibitem[Marinoni \& Buzzi(2010)]{Marinoni2010}
-Marinoni, C., \& Buzzi, A. 2010, Nature, 468, 539
-
-\bibitem[Matsubara \& Suto(1996)]{Matsubara1996}
-Matsubara T., \& Suto, Y. 1996, ApJ, 470, L1
-
-\bibitem[McCavana et al.(2012)]{M12}
-McCavana, T., Micic, M., Lewis, G. F., et al. 2012, MNRAS, 424, 361
-
-\bibitem[Morandi \& Sun (2016)]{MS2016}
-Morandi, A., \& Sun, M. arXiv:1601.03741
-
-\bibitem[Outram et al.(2004)]{Outram2004}
-Outram, P.J., Shanks, T., Boyle, B.J., Croom, S.M., Hoyle, F., Loaring, N.S., 
-Miller, L., \& Smith, R.J. 2004, MNRAS, 348, 745
-
-%\bibitem[Parejko et al.(2013)]{Parejko2013}
-%Parejko, J. K., Sunayama, T., Padmanabhan, N., et al. 2013, MNRAS, 429, 98
-
-\bibitem[Parejko et al.(2013)]{Parejko2013}
-Parejko J.K., et al., 2013, MNRAS, 429, 98
-
-\bibitem[Parihar et al. (2014)]{CMASSLSS2014}
-Parihar, P., Vogeley, M.S., \& Gott, J.R., et al. 2014, ApJ, 796, 86
-
-\bibitem[Park et al.(2005)]{park 2005}
-Park, C., Kim, J., \& Gott, J.R. 2005, ApJ, 633, 1
-
-\bibitem[Park \& Kim(2010)]{topology}
-Park, C., \& Kim, Y.-R. 2010, ApJL, 715, L185
-
-\bibitem[Park et al. (2012)]{Park2012}
-Park, C., Choi, Y.-Y., Kim, J., Gott, J.R., Kim, S.S., \&
-Kim, K.-S. 2012, ApJ, 759, 7
-
-\bibitem[Park et al. (2015)]{Park2015}
-Park, C., Song, H., Einasto, M., Lietzen, H., \&
-Heinamaki, P. 2015, JKAS, 48, 75
-
-\bibitem[Peebles \& Ratra(2003)]{PR2003}
-Peebles, P.J.E., \& Ratra, B. 2003, Reviews of Modern Physics, 75, 559
-
-\bibitem[Percival et al.(2014)]{Percival2014}
-Percival, W.J., Ross, A.J., \& S\'{a}nchez, A.G., et al. 2014, MNRAS, 439, 2531
-
-\bibitem[Perlmutter et al.(1999)]{Perl1999}
-Perlmutter, S., Aldering, G., \& Goldhaber, G., et al. 1999, ApJ, 517, 565
-
-\bibitem[Press \& Shechter(1974)]{PS1974}
-Press, W.H., \& Schechter, P.L. 1974, ApJ, 187, 425
-
-\bibitem[Reid et al.(2012)]{Reid2012}
-Reid, B., Samushia, L., \& White, M., et al. 2012, MNRAS, 426, 2719
-
-\bibitem[Reid et al.(2016)]{Reidetal:2016}
-Reid, B., Ho, S., \& Padmanabhan, N., et al.  2016, MNRAS, 455, 1553
-
-\bibitem[Riess et al.(1998)]{Riess1998}
-Riess, A.G., Filippenko, A.V., \& Challis, P., et al. 1998, AJ, 116, 1009
-
-\bibitem[Riess et al.(2011)]{Riess2011}
-Riess, A.G., Macri, L., \& Casertano, S., et al. 2011, ApJ, 730, 119
-%A 3\% Solution: Determination of the Hubble Constant with the Hubble Space Telescope and Wide Field Camera
-
-\bibitem[Ross et al.(2012)]{2012MNRAS.424..564R} 
-Ross, A.J., Percival, W.J., \& S{\'a}nchez, A.G. et al.\ 2012, MNRAS, 424, 564
-
-\bibitem[Ross et al.(2015)]{MGS}
-Ross, A.J., Samushia, L., \& Howlett, C., et al. 2015, MNRAS, 449, 835
-
-\bibitem[Ryden(1995)]{Ryden1995}
-Ryden, B.S. 1995, ApJ, 452, 25
-
-%\bibitem[Samushia et al.(2014)]{Samushia2014}
-%Samushia, L., Reid, B. A., White, M., et al. 2014, MNRAS, 439, 3504
-
-%\bibitem[Sanchez et al.(2013)]{Sanchez2013}
-%Sanchez, A. G., Kazin, E. A., Beutler, F., et al. 2013, MNRAS, 433, 1202
-
-%\bibitem[Sutter et al.(2014)]{Sutter2014}
-%Sutter, P.M., Pisani, A., Wandelt, B.D., \& Weinberg, D.H. 2014, MNRAS, 443, 2983
-
-\bibitem[Sanchez et al.(2016)]{Sanchez2016}
-Sanchez, A. G., Scoccimarro, R., \& Crocce, M., et al.
-arXiv:1607.03147
-
-\bibitem[Schlafly et al.(2010)]{Schlafly2010}
-Schlafly E.F., Finkbeiner D.P., Schlegel D.J., et al. 2010, ApJ, 725, 1175
-
-\bibitem[Schlafly \& Finkbeiner(2011)]{SF2011}
-Schlafly E.F., \& Finkbeiner D.P. 2011, ApJ, 737, 103
-
-%DESI:
-%http://arxiv.org/abs/1106.1706
-\bibitem[Schlegel et al.(2011)]{DESI}
-Schlegel, D., Abdalla, F., \& Abraham, T., et al. 2011, arXiv:1106.1706
-
-\bibitem[Smee et al.(2013)]{Smee2013}
-Smee, S.A., Gunn, J.E., \& Uomoto, A., et al. 2013, AJ, 146, 32
-
-\bibitem[Song et al.(2014)]{2014arXiv1407.2257S} 
-Song, Y.S., Sabiu, C.G., 
-Okumura, T., Oh, M., \& Linder, E.V.\ 2014, JCAP, 12, 005
-
-\bibitem[Speare et al. (2015)]{Speare2015}
-Speare, R., Gott, J.R., Kim, J., \& Park, C.
-2015, ApJ, 799, 176
-
-%\bibitem[Tojeiro \& Percival(2011)]{Tojeiro2011}
-%Tojeiro R., \& Percivial W.J. 2011, MNRAS, 417, 1114
-
-%\bibitem[Tojeiro et al.(2012)]{Tojeiro2012}
-%Tojeiro, R., Percival, W. J., Wake, D. A., et al. 2012, MNRAS, 424, 136
-
-\bibitem[Viana \& Liddle(1996)]{VL1996}
-Viana, P.T.P., \& Liddle, A.R. 1996, MNRAS, 281, 323
-
-\bibitem[Villalobos et al.(2013)]{V13}
-Villalobos, \'{A}., ́De Lucia, G., Weinmann, S.M., Borgani, S., \& Murante, G. 2013, MNRAS, 433, L49
-
-\bibitem[Weinberg (1989)]{SW1989}
-Weinberg, S. 1989, Reviews of Modern Physics, 61, 1
-
-\bibitem[White (2011)]{White2011}
-White M., et al. 2011, ApJ, 728, 126
-
-\bibitem[Yoo \& Watanabe(2012)]{2012IJMPD..2130002Y} Yoo, J., \& Watanabe, Y.\ 2012, International Journal of Modern Physics D, 21, 1230002
-
-\bibitem[York et al.(2000)]{York et al. 2000}
-York, D.G., Adelman, J., \& Anderson, J.E., et al. 2000, AJ, 120, 1579
-
-\bibitem[Zehavi et al.(2011)]{zehavi2011}
-Zehavi, I., Zheng, Z., \& Weinberg, D.H., et al. 2011, ApJ, 736, 59
-
-\end{thebibliography}
+The simulation data can be obtained by contacting directly Juhan Kim - \href{kjhan@kias.re.kr}{kjhan@kias.re.kr}.
 

### 2017-06-22 src/AP_MCMC.f90

@@ -1,15 +1,83 @@
 
-module vol_avg_DAH
+module redbin_weights_bossdr12_6bins
+use types_constants
 implicit none
 
-contains
 
-end module
+  real(rt) :: dr12v4_cmass_N_numgal(3,1000),dr12v4_cmass_S_numgal(3,1000),&
+            dr12v4_lowz_N_numgal(3,1000),dr12v4_lowz_S_numgal(3,1000)
+  character(charlen) :: dr12v4_cmass_N_numgal_file = '../datfiles/nbar-cmass-dr12v4-N-Reid.dat',&
+                      dr12v4_cmass_S_numgal_file = '../datfiles/nbar-cmass-dr12v4-S-Reid.dat',&
+                      dr12v4_lowz_N_numgal_file = '../datfiles/nbar-lowz-dr12v4-N-Reid.dat',&
+                      dr12v4_lowz_S_numgal_file = '../datfiles/nbar-lowz-dr12v4-S-Reid.dat'
+  real(rt), parameter :: numgal_zmin=0.0, numgal_zmax=1.0
+  integer, parameter  :: numgal_nbin = 200
+  real(rt), parameter :: numgal_dz = (numgal_zmax-numgal_zmin) / dble(numgal_nbin)
+  real(rt) :: numgals(numgal_nbin), numgal_zcenters(numgal_nbin), redbin_weights(6,numgal_nbin)
+  logical :: numgal_inited = .false.
+  real(rt) :: redbin_edges(7) = (/ 0.15_rt,  0.2741_rt, 0.3510_rt, 0.43_rt, 0.51_rt,  0.5720_rt, 0.6929_rt  /)
 
-!!!
+  contains
+
+  subroutine numgal_init()
+    integer  :: i,j,iredbin,i1,i2
+    character:: tmpchar
+    real(rt) :: zcen,zlow,zhigh,nbar,wfkp,shell_vol,numgal
+    
+    numgals = 0.0_rt
+    do i = 1, 4
+      if(i.eq.1) open(82785,file=dr12v4_lowz_N_numgal_file,action='read')
+      if(i.eq.2) open(82785,file=dr12v4_lowz_S_numgal_file,action='read')
+      if(i.eq.3) open(82785,file=dr12v4_cmass_N_numgal_file,action='read')
+      if(i.eq.4) open(82785,file=dr12v4_cmass_S_numgal_file,action='read')
+      do j = 1, 2
+        read(82785,*) tmpchar
+      enddo
+      do j = 1, numgal_nbin
[…]

### 2017-06-23 src/AP_MCMC.f90
minor changes

@@ -1,80 +1,8 @@
 
-module redbin_weights_bossdr12_6bins
-use types_constants
-implicit none
-
-
-  real(rt) :: dr12v4_cmass_N_numgal(3,1000),dr12v4_cmass_S_numgal(3,1000),&
-            dr12v4_lowz_N_numgal(3,1000),dr12v4_lowz_S_numgal(3,1000)
-  character(charlen) :: dr12v4_cmass_N_numgal_file = '../datfiles/nbar-cmass-dr12v4-N-Reid.dat',&
-                      dr12v4_cmass_S_numgal_file = '../datfiles/nbar-cmass-dr12v4-S-Reid.dat',&
-                      dr12v4_lowz_N_numgal_file = '../datfiles/nbar-lowz-dr12v4-N-Reid.dat',&
-                      dr12v4_lowz_S_numgal_file = '../datfiles/nbar-lowz-dr12v4-S-Reid.dat'
-  real(rt), parameter :: numgal_zmin=0.0, numgal_zmax=1.0
-  integer, parameter  :: numgal_nbin = 200
-  real(rt), parameter :: numgal_dz = (numgal_zmax-numgal_zmin) / dble(numgal_nbin)
-  real(rt) :: numgals(numgal_nbin), numgal_zcenters(numgal_nbin), redbin_weights(6,numgal_nbin)
-  logical :: numgal_inited = .false.
-  real(rt) :: redbin_edges(7) = (/ 0.15_rt,  0.2741_rt, 0.3510_rt, 0.43_rt, 0.51_rt,  0.5720_rt, 0.6929_rt  /)
-
-  contains
-
-  subroutine numgal_init()
-    integer  :: i,j,iredbin,i1,i2
-    character:: tmpchar
-    real(rt) :: zcen,zlow,zhigh,nbar,wfkp,shell_vol,numgal
-    
-    numgals = 0.0_rt
-    do i = 1, 4
-      if(i.eq.1) open(82785,file=dr12v4_lowz_N_numgal_file,action='read')
-      if(i.eq.2) open(82785,file=dr12v4_lowz_S_numgal_file,action='read')
-      if(i.eq.3) open(82785,file=dr12v4_cmass_N_numgal_file,action='read')
-      if(i.eq.4) open(82785,file=dr12v4_cmass_S_numgal_file,action='read')
-      do j = 1, 2
-        read(82785,*) tmpchar
-      enddo
[…]

### 2017-06-23 src/AP_grid.f90

@@ -21,6 +21,7 @@ implicit none
   integer :: nowmodel
   logical :: smutabstds_inited, debug=.false., print_allinfo=.false.
 
+!!! Next step: write this for wbinned model!!!
 
   ommin=0.1;  ommax=0.4; 
   w0min=-1.4; w0max=-0.3; 

### 2017-07-13 src/AP_MCMC_wbinned.f90
minor changes

@@ -1,4 +1,7 @@
 
+!!! Processing binned-w chains.
+!!  File formats: omegabh2, omegach2, theta, tau, w1, w2, ..., w30, logA, ns...
+!   We can not obtain values of Omegam! Not possible to continue!...
 
 program main
 use LSS_ximu_tests
@@ -12,7 +15,7 @@ implicit none
   integer :: i,j,k,i1,i2,iz,num_MCMCchain,numomwstds,nlines
   
   
-  integer :: iomcol=1,iw0col=1,iwacol=1,iomkcol=1,iH0col=1,maxcol, ifile,iline
+  integer :: maxcol, ifile,iline
   
   real(rt) :: omegam, omstds(1000), wstds(1000), DAs(nz), Hs(nz), & 
     chisqs_nosyscor(n1,n2,nz-1), chisqs_syscor(n1,n2,nz-1), chisqs_nosyscor_all(nz-1), chisqs_syscor_all(nz-1), &
@@ -22,53 +25,28 @@ implicit none
   real(rt), allocatable :: APlnlikes(:), smutabstds(:,:,:,:,:)
   character(charlen) :: inputMCMCfile, outputMCMCfile, mcmcdir, nowchisqstr, fileindexstr, MCMCfilestr, suffixstr=''
   type(omwpar) :: nowpar
-  integer,parameter :: model_wcdm=3, model_cpl=4, model_owcdm=5, model_ocpl=6, model_lcdm=7, model_olcdm=8
+!  integer,parameter :: model_wcdm=3, model_cpl=4, model_owcdm=5, model_ocpl=6, model_lcdm=7, model_olcdm=8
   integer :: nowmodel
-  logical :: smutabstds_inited, debug=.false., avg_counts = .false., print_allinfo=.false., VolumeWeightedDAH=.false.
+  logical :: smutabstds_inited, debug=.false., avg_counts = .false., print_allinfo=.false., VolumeWeightedDAH=.true.
 
   if(.not. numgal_inited) call numgal_init()
-  !stop
 
-  nowmodel = model_wcdm
 !  nowmodel = model_cpl
-!  nowmodel = model_olcdm
-  suffixstr = 'base1omws_om0.2600_w-1.0000_HalfNorm'
+  suffixstr = 'base1omws_om0.2600_w-1.0000_VolumeWeightedDAH'
[…]

### 2017-07-13 src/AP_Rhct.f90

@@ -1,0 +1,260 @@
+
+
+program main
+use LSS_ximu_tests
+USE de_model_init
+!USE de_chisqs_JLA
+implicit none
+  
+  integer :: i,j,k,i1,i2,iz,num_MCMCchain,numomwstds,nlines
+  
+  
+  real(rt) :: omegam, omstds(1000), wstds(1000), DAs(nz), Hs(nz), & 
+    chisqs_nosyscor(n1,n2,nz-1), chisqs_syscor(n1,n2,nz-1), chisqs_nosyscor_all(nz-1), chisqs_syscor_all(nz-1), &
+    nowlnlike,nowweight,nowom,noww0,nowH0,nowwa,nowomk,APlnlikemin,&
+    t0,t1,t2,dt, ommin, ommax, w0min, w0max, wamin, wamax
+  integer :: iline, numom, numw0, numwa, iom, iw0, iwa
+  real(rt), allocatable :: APlnlikes(:), smutabstds(:,:,:,:,:)
+  character(charlen) :: outputMCMCfile, mcmcdir, nowchisqstr, fileindexstr, MCMCfilestr, suffixstr=''
+  type(omwpar) :: nowpar
+  integer,parameter :: model_wcdm=3, model_cpl=4, model_owcdm=5, model_ocpl=6, model_lcdm=7, model_olcdm=8
+  integer :: nowmodel
+  logical :: smutabstds_inited, debug=.false., print_allinfo=.false., do_lcdm_constraint=.false.
+
+!!! Next step: write this for wbinned model!!!
+
+  de_model_lab  = de_wcdm_lab
+  ommin=0.0;  ommax=1.0; 
+   numw0=1; numwa=1;
+!  print *, log(2.732); stop
+  nowmodel = model_wcdm;   wamin=0.0;wamax=0.0;numwa=1
+!  nowmodel = model_wcdm; !ommin=0.31; ommax=0.31; numom=1
+!  nowmodel = model_olcdm
+
+ 
+  !ommin=0.1; ommax=0.2; numom=34; suffixstr = 'base1omws_om0.2600_w-1.0000_1'!_fixom0.31'
+  !ommin=0.20303030303d0; ommax=0.3; numom=33; suffixstr = 'base1omws_om0.2600_w-1.0000_2'!_fixom0.31'
[…]

### 2017-07-13 src/AP_grid.f90
minor changes

@@ -22,17 +22,21 @@ implicit none
   logical :: smutabstds_inited, debug=.false., print_allinfo=.false.
 
 
-  ommin=0.1;  ommax=0.4; 
+!  ommin=0.1;  ommax=0.4; 
+!  w0min=-1.4; w0max=-0.3; 
+!  wamin=-2.5; wamax=0.9;
+!  numom=120; numw0=120; numwa= 120 
+  ommin=0.01;  ommax=0.99; 
   w0min=-1.4; w0max=-0.3; 
   wamin=-2.5; wamax=0.9;
-  numom=100; numw0=100; numwa=100  
+  numom=150; numw0=120; numwa= 120 
 
 !  nowmodel = model_wcdm;   wamin=0.0;wamax=0.0;numwa=1
   nowmodel = model_cpl; !ommin=0.31; ommax=0.31; numom=1
 !  nowmodel = model_olcdm
 
- 
-  !ommin=0.1; ommax=0.2; numom=34; suffixstr = 'base1omws_om0.2600_w-1.0000_1'!_fixom0.31'
+ suffixstr = 'base1omws_om0.2600_w-1.0000_with_syscor_ext'!_fixom0.31'
+  !ommin=0.1; ommax=0.2; numom=34; 
   !ommin=0.20303030303d0; ommax=0.3; numom=33; suffixstr = 'base1omws_om0.2600_w-1.0000_2'!_fixom0.31'
   !ommin=0.30303030303d0; ommax=0.4; numom=33; suffixstr = 'base1omws_om0.2600_w-1.0000_3'!_fixom0.31'
 !  suffixstr = 'base1omws_om0.2600_w-1.0000_ExcludeLastThreeBins_B'
@@ -48,7 +52,8 @@ implicit none
   !--------------------------------
   ! Settings of the model
 
-  mcmcdir = '/home/xiaodongli/software/cosmomcs/12Oct_generic/chains/wcdm/'
+  !mcmcdir = '/home/xiaodongli/software/cosmomcs/12Oct_generic/chains/wcdm/'
+  mcmcdir = './'
   if(nowmodel .eq. model_wcdm) then! .or. nowmodel .eq. model_owcdm) then
   	  de_model_lab = de_wCDM_lab
           MCMCfilestr = 'base_w_AP'	  
@@ -164,8 +169,8 @@ implicit none
[…]

### 2017-07-13 Draft/Draft0.4.tex

--- 2017-06-22 Draft/Draft0.4.bib2.tex
@@
 
-\title{\sffamily Dynamical dark energy constraints via clustering shells of SDSS-III BOSS galaxies}
+\title{%\sffamily 
+Dynamical dark energy constraints via clustering shells of SDSS-III BOSS galaxies}
 
-\author{\sffamily 
-Xiao-Dong Li,$^{1,\dagger}$
+\author{%\sffamily 
+Xiao-Dong Li,$^{1}$
 Cristiano G. Sabiu,$^{2}$
 Changbom Park,$^{1}$
-Yuting Wang,$^{3,\star}$
+Yuting Wang,$^{3}$
 Gong-bo Zhao,$^{3}$
@@
 \begin{abstract}
-\sffamily
-We use the anisotropic {\it clustering shells} of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
+%\sffamily
+We use the anisotropic {\itshape clustering shells} of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
 12 spanning the redshift range  $0.15<z<0.69$ to place constraints on the expansion history of the Universe. 
@@
 
-\sffamily
-{\it Introduction.}---
+%\sffamily
+%{\it Introduction.}---
 The  origin  of  the  accelerating  expansion  of  the  universe  is  one of  the  most  salient  questions  in  contemporary cosmology. 
 Proposed mechanisms include  evolving  scalar  fields  remnant  from  the  big  bang, 
-modifications to gravity,  and a  non-zero  vacuum energy \cite[see][for a comprehensive review]{2012IJMPD..2130002Y}. 
+modifications to gravity,  and a  non-zero  vacuum energy (see \cite{2012IJMPD..2130002Y} for a comprehensive review). 
 Considering the wealth of theoretical explanations, it is crucial to obtain precise and unbiased measurements of the expansion history of the Universe allowing us to 
@@
 measured the 2pCF in these redshift bins, 
-and use a $\chi^2$ function to assess the redshift dependence.
-Systematic effects are estimated via mocks made from Horizon Run 4 simulations \citep{HR4}, and subtracted when computing the $\chi^2$.
+subtract the systematic effects based on estimations from mocks made from Horizon Run 4 simulations \citep{HR4},
+and use a $\chi^2$ function to assess the redshift dependence
+(see Methods for further explanations).
 After adding the sample log-likelihoods with ours, 
@@
 
-%\bibitem[{{Alam} {et~al}\mbox{.}(2015{\natexlab{a}}){Alam}, {Albareti},
-%  {Allende Prieto}, {Anders}, {Anderson}, {Anderton}, {Andrews}, {Armengaud},
-%  {Aubourg}, {Bailey}, \& et~al.}]{dr12}
-%{Alam} S., Albareti, F.D.,\& Allende Prieto, C., {et~al.}, 2015,  ApJS, 219, 12
+\bibitem{Ballinger1996}%[Ballinger, Peacock \& Heavens 1996]
+Ballinger, W.E., Peacock, J.A., \& Heavens, A.F. 1996, MNRAS, 282, 877
 
-\bibitem[Alcock \& Paczynski(1979)]{AP1979}
-Alcock, C., \& Paczynski, B. 1979, Nature, 281, 358
+\bibitem{Marinoni2010}%[Marinoni \& Buzzi(2010)]
+Marinoni, C., \& Buzzi, A. 2010, Nature, 468, 539
 
-%\bibitem[Anderson et al.(2012)]{2012MNRAS.427.3435A} 
-%Anderson, L., Aubourg, E., Bailey, S., et al.\ 2012, MNRAS, 427, 3435
+\bibitem{Jennings2011}%[Jennings et al.(2011)]
+Jennings, E., Baugh, C.M., \& Pascoli, S. 2011, MNRAS, 420, 1079
 
-\bibitem[Anderson et al.(2013)]{Anderson2013}
+\bibitem{Ryden1995}%[Ryden(1995)]
+Ryden, B.S. 1995, ApJ, 452, 25
+
+\bibitem{LavausWandelt1995}%[Lavaux \& Wandelt(2012)]
+Lavaux, G., \& Wandelt, B.D. 2012, ApJ, 754, 109
+
+\bibitem{Qingqing2016}%[Mao et al. (2016)]
+Mao, Q., Berlind, A.A., Scherrer, R.J., et al. 2016, submitted to ApJ
+
+\bibitem{Li2014}%[Li et al.(2014)]
+Li, X.-D., Park, C., Forero-Romero, J., \& Kim, J. 2014, ApJ, 796, 137
+
+\bibitem{Li2015}%[Li et al.(2015)]
+Li, X.-D., Park, C., Sabiu, C.G., \& Kim, J. 2015, MNRAS, 450, 807
+
+\bibitem{LB2002}%[Lewis \& Bridle (2002)]
+Lewis, A., \& Bridle, S. 2002, Phys. Rev. D, 66, 103511
+
+\bibitem{Planck2015}%[Ade et al. (2015)]
+Ade, P.A.R., Aghanim, N., \& Arnaud, M., et al. 2016, A\&A, 594, A13
+
+\bibitem{Anderson2013}%[Anderson et al.(2013)]
 Anderson, L., Aubourg, \'E., \& Bailey, S. et al. 2014, MNRAS, 441, 24
 
-%\bibitem[Bassett et al.(2002)]{Bassett2002}
-%Bassett, B.A., Kunz, M., Silk, J., \& Ungarelli, C. 2002, MNRAS, 336, 1217
+\bibitem{6dFGS}%[Beutler et al.(2011)]
+Beutler, F., Blake, C., \& Colless, M., et al. 2011, MNRAS, 416, 3017
 
-\bibitem[Ballinger, Peacock \& Heavens 1996]{Ballinger1996}
-Ballinger, W.E., Peacock, J.A., \& Heavens, A.F. 1996, MNRAS, 282, 877
+\bibitem{MGS}%[Ross et al.(2015)]
+Ross, A.J., Samushia, L., \& Howlett, C., et al. 2015, MNRAS, 449, 835
 
-\bibitem[Betoule et al.(2014)]{JLA}
+\bibitem{JLA}%[Betoule et al.(2014)]
 Betoule, M., Kessler, R., \& Guy, J., et al. 2014, A\&A, 568, 32
 
-\bibitem[Beutler et al.(2011)]{6dFGS}
-Beutler, F., Blake, C., \& Colless, M., et al. 2011, MNRAS, 416, 3017
+\bibitem{Riess2011}%[Riess et al.(2011)]
+Riess, A.G., Macri, L., \& Casertano, S., et al. 2011, ApJ, 730, 119
 
-\bibitem[Beutler et al.(2013)]{Beutler2013}
-Beutler, F., Saito, S., \& Seo, H.-J., et al. 2013, MNRAS, 443, 1065
-
-\bibitem[Beutler et al.(2016)]{Beutler2016}
-Beutler, F., Seo, H.-J., \& Saito, S., et al. 2016,
-arXiv:1607.03150
-
-\bibitem[Blake et al.(2011)]{Blake2011}
-Blake, C., Glazebrook, K., \& Davis, T. M., 2011, MNRAS, 418, 1725
-
-\bibitem[Blake et al.(2013)]{WiggleZtopoloy}
-Blake, C., James, J.B., \& Poole, G.B. 2013, MNRAS, 437, 2488
-
-\bibitem[Bolton et al.(2012)]{Bolton2012}
-Bolton, A.S., Schlegel, \& D.J., Aubourg E., et al. 2012, AJ, 144, 144
-
-\bibitem[Boylan-Kolchin et al.(2008)]{B08}
-Boylan-Kolchin, M., Ma, C.-P., \& Quataert, E. 2008, MNRAS, 383, 93
-
-%\bibitem[Bueno Belloso et al. (2012)]{BB2012}
-%Bueno Belloso, A., Pettinari, G.W., Meures, N., \& Percival, W.J. 2012, Phys. Rev. D, 86, 023530
-
-%\bibitem[Chevallier \& Polarski(2001)]{CP2001}
-%Chevallier, M., Polarski, D. 2001, Int. J. Mod. Phys. D, 10, 213
-
-%\bibitem[Choi et al.(2010)]{choi 2010}
-%Choi, Y.-Y., Park, C., Kim, J., Gott, J.R., 
-%Weinberg, D.H., Vogeley, M.S., \& Kim, S.S. 2010, ApJS, 190, 181
-
-\bibitem[Christensen et al.(2001)]{Bayesian}
-Christensen, N., Meyer, R., Knox, L., \& Luey, B. 2001, Class. Quant. Grav., 18, 2677
-
-%\bibitem[Chuang et al.(2013)]{Chuang2013}
-%Chuang, C.-H., Prada, F., Beutler, F., et al. 2013, arXiv:1312.4889
-
-\bibitem[Chuang \& Wang(2012)]{ChuangWang2012}
-Chuang, C.-H., \& Wang, Y. 2012, MNRAS, 426, 226
-
-%\bibitem[Corasaniti \& Copeland(2003)]{Corasaniti2003}
-%Corasaniti, P.S., Copeland, E.J. 2003, Phys. Rev. D, 67, 063521
-
-%eBOSS: 
-%http://arxiv.org/abs/1508.04473
-\bibitem[Dawson et al.(2015)]{eBOSS}
-Dawson, K.S., Kneib, J.P., \& Percival, W.J., et al. 2015, accepted AJ
-
-\bibitem[Dawson et al.(2012)]{Dawson et al. 2012}
-Dawson, K.S., Schlegel, D.J., \& Ahn, C.P., et al. 2012, AJ, 145, 10
-
-\bibitem[Efstathiou (2014)]{E14H0}
+\bibitem{E14H0}%[Efstathiou (2014)]
 Efstathiou, G. 2014, MNRAS, 440, 1138
 
-\bibitem[Eisenstein et al.(2011)]{Eisenstein et al. 2011}
-Eisenstein, D.J.,  Weinberg, D.H., \& Agolet, E., et al. 2011, AJ, 142, 72
+\bibitem{HR4}%[Kim et al.(2015)]
+Kim, J., Park, C., L'Huillier, B., \& Hong, S. E. 2015, JKAS, 48, 213
 
-\bibitem[Feldman, Kaiser \& Peacock (1994)]{1994ApJ...426...23F} 
-Feldman, H.A., Kaiser, N., \& Peacock, J.A.\ 1994, ApJ, 426, 23
+%\bibitem{Lee12}
+%\bibinfo{author}{Lee}, E.~J., {Murray}, N., {Rahman}, M. 
+%\newblock \bibinfo{title}{Milky Way Star-forming Complexes and the Turbulent Motion of the Galaxy's Molecular Gas.}
+%\newblock{\it Astrophys. \ J.}{\bf\, 752}, 146-159 (2012).
 
-\bibitem[Fukugita et al. (1996)]{Fukugita1996}
-Fukugita, M., Ichikawa, T., \& Gunn, J.E., et al. 1996, AJ, 111, 1748
-%Publication:	
-%Astronomical Journal v.111, p.1748
+%%%% For methods
+\bibitem{Reidetal:2016}%[Reid et al.(2016)]
+Reid, B., Ho, S., \& Padmanabhan, N., et al.  2016, MNRAS, 455, 1553
 
-%\bibitem[Gingold \& Monaghan(1977)]{GM1977}
-%Gingold, R.A., \& Monaghan, J.J. 1977, MNRAS, 181, 375
+\bibitem{komatsu 2011}%[Komatsu et al.(2011)]
+Komatsu, E., Smith, K. M., \& Dunkley, J., et al. 2011, ApJS, 192, 18
 
-%\bibitem[Gott et al.(2009)]{gott 2009}
-%Gott, J.R., Choi, Y.-Y., Park, C., \& Kim, J. 2009, ApJ, 695, L45
+\bibitem{hong2016}%[Hong et al.(2016)]
+Hong, S.E., Park, C.,\&  Kim, J. 2016, ApJ, 823, 103
 
-%\bibitem[Gott et al.(2008)]{gott 2008}
-%Gott, J.R., Hambrick, D.C., Vogeley, M.S., Kim, J., Park, C., Choi, Y.-Y.,
-%Cen, R., Ostriker, J.P., \& Nagamine, K. 2008, ApJ, 675, 16
+\bibitem{MDPATCHY}%[Kitaura et al.(2015)]
+Kitaura, F.S., Rodriguez-Torres, S., Chuang, C.-H., et al.2016, MNRAS, 456, 4156
 
-\bibitem[Gunn et al. (1998)]{Gunn1998}	
-Gunn, J.E., Carr, M., \& Rockosi, C. et al. 1998, AJ, 116, 3040
-
-\bibitem[Gunn et al.(2006)]{Gunn et al. 2006}
-Gunn, J.E., Siegmund, W.A., \& Mannery, E.J., et al. 2006, AJ, 131, 2332
-
-\bibitem[Guzzo et al.(2008)]{Guzzo2008}
-Guzzo, L., Pierleoni, M., \& Meneux, B., et al. 2008, Nature, 451, 541
-
-\bibitem[Hartlap et al.(2006)]{Hartlap}
+\bibitem{Hartlap}%[Hartlap et al.(2006)]
 Hartlap J., Simon P. \& Schneider P. [astro-ph/0608064].
 
-\bibitem[Hong et al.(2016)]{hong2016}
-Hong, S.E., Park, C.,\&  Kim, J. 2016, ApJ, 823, 103
-
-\bibitem[Jackson (1972)]{FOG}
-Jackson, J., 1972, MNRAS, 156, 1
-
-\bibitem[Jennings et al.(2011)]{Jennings2011}
-Jennings, E., Baugh, C.M., \& Pascoli, S. 2011, MNRAS, 420, 1079
-
-%\bibitem[Jeong et al.(2014)]{Jeong2014}
-%Jeong, D., Dai, L., Kamionkowski, M., \& Szalay, A.S. 2014, arXiv:1408.4648
-
-\bibitem[Jiang et al.(2008)]{jiang2008}
-Jiang, C.Y., Jing, Y. P., \& Faltenbacher, A., et al. 2008, ApJ, 675, 1095
-
-\bibitem[Kaiser (1987)]{Kaiser1987}
-Kaiser, N. 1987, MNRAS, 227, 1
-
-\bibitem[Kim \& Park(2006)]{kim and park 2006}
-Kim, J., \& Park, C. 2006, ApJ, 639, 600
-
-\bibitem[Kim et al.(2009)]{2009ApJ...701.1547K} 
-Kim, J., Park, C., Gott, J.R., III, \& Dubinski, J.\ 2009, ApJ, 701, 1547
-
-\bibitem[Kim et al.(2015)]{hr4}
-Kim, J., Park, C., L'Huillier, B., \& Hong, S. E. 2015, JKAS, 48, 213
-
-\bibitem[Kim et al.(2011)]{horizonrun}
-Kim, J., Park, C., Rossi, G., Lee, S.M., \& Gott, J.R. 2011, JKAS, 44, 217
-
-\bibitem[Kitaura et al.(2015)]{MDPATCHY}
-Kitaura, F.S., Rodriguez-Torres, S., Chuang, C.-H., et al. arXiv:1509.06400
-
-\bibitem[Komatsu et al.(2011)]{komatsu 2011}
-Komatsu, E., Smith, K. M., \& Dunkley, J., et al. 2011, ApJS, 192, 18
-
-\bibitem[Lacey \& Cole(1993)]{LC93}
-Lacey, C., \& Cole, S. 1993, MNRAS, 262, 627
-
-\bibitem[Landy \& Szalay(1993)]{1993ApJ...412...64L} 
-Landy, S.D., \& Szalay, A.S.\ 1993, ApJ, 412, 64
-
-%EUCLID:
-%http://arxiv.org/abs/1110.3193
-\bibitem[Laureijs et al.(2011)]{EUCLID}
-Laureijs, R., Amiaux, J., \& Arduini, S., et al. 2011, arXiv:1110.3193
-
-\bibitem[Lavaux \& Wandelt(2012)]{LavausWandelt1995}
-Lavaux, G., \& Wandelt, B.D. 2012, ApJ, 754, 109
-
-%\bibitem[Levi et al.(2013)]{2013arXiv1308.0847L} 
-%Levi, M., Bebek, C., Beers, T., et al.\ 2013, arXiv:1308.0847
-
-\bibitem[Lewis \& Bridle (2002)]{LB2002}
-Lewis, A., \& Bridle, S. 2002, Phys. Rev. D, 66, 103511
-
-\bibitem[L'Huillier et al.(2014)]{2014NewA...30...79L} 
-L'Huillier, B., Park, C., \& Kim, J.\ 2014, New Astronomy, 30, 79
-
-\bibitem[Li et al.(2011)]{Li2011}
-Li, M., Li, X.-D., Wang, S., \& Wang, Y. 2011, Commun. Theor. Phys., 56, 525
-
-\bibitem[Li et al.(2014)]{Li2014}
-Li, X.-D., Park, C., Forero-Romero, J., \& Kim, J. 2014, ApJ, 796, 137
-
-\bibitem[Li et al.(2015)]{Li2015}
-Li, X.-D., Park, C., Sabiu, C.G., \& Kim, J. 2015, MNRAS, 450, 807
-
-\bibitem[Li et al.(2016)]{Li2016}
-Li, X.-D., Park, C., \& Sabiu, C.G., et al. 2016, ApJ, 832, 103
-
-%\bibitem[Linder(2003)]{Linder2003}
-%Linder, E.V. 2003, Phys. Rev. Lett., 90, 091301
-
-\bibitem[Linder et al.(2014)]{Linder2013}
-Linder, E.V., Minji, O., Okumura, T., Sabiu, C.G., \& Song, Y.-S. 2014, Phys. Rev. D, 89, 063525
-
-\bibitem[L{\'o}pez-Corredoira(2014)]{2014ApJ...781...96L} 
-L{\'o}pez-Corredoira, M.\ 2014, ApJ, 781, 96
-
-\bibitem[Mao et al. (2016)]{Qingqing2016}
-Mao, Q., Berlind, A.A., Scherrer, R.J., et al. 2016, submitted to ApJ
-
-\bibitem[Marinoni \& Buzzi(2010)]{Marinoni2010}
-Marinoni, C., \& Buzzi, A. 2010, Nature, 468, 539
-
-\bibitem[Matsubara \& Suto(1996)]{Matsubara1996}
-Matsubara T., \& Suto, Y. 1996, ApJ, 470, L1
-
-\bibitem[McCavana et al.(2012)]{M12}
-McCavana, T., Micic, M., Lewis, G. F., et al. 2012, MNRAS, 424, 361
-
-\bibitem[Morandi \& Sun (2016)]{MS2016}
-Morandi, A., \& Sun, M. arXiv:1601.03741
-
-\bibitem[Outram et al.(2004)]{Outram2004}
-Outram, P.J., Shanks, T., Boyle, B.J., Croom, S.M., Hoyle, F., Loaring, N.S., 
-Miller, L., \& Smith, R.J. 2004, MNRAS, 348, 745
-
-%\bibitem[Parejko et al.(2013)]{Parejko2013}
-%Parejko, J. K., Sunayama, T., Padmanabhan, N., et al. 2013, MNRAS, 429, 98
-
-\bibitem[Parejko et al.(2013)]{Parejko2013}
-Parejko J.K., et al., 2013, MNRAS, 429, 98
-
-\bibitem[Parihar et al. (2014)]{CMASSLSS2014}
-Parihar, P., Vogeley, M.S., \& Gott, J.R., et al. 2014, ApJ, 796, 86
-
-\bibitem[Park et al.(2005)]{park 2005}
-Park, C., Kim, J., \& Gott, J.R. 2005, ApJ, 633, 1
-
-\bibitem[Park \& Kim(2010)]{topology}
-Park, C., \& Kim, Y.-R. 2010, ApJL, 715, L185
-
-\bibitem[Park et al. (2012)]{Park2012}
-Park, C., Choi, Y.-Y., Kim, J., Gott, J.R., Kim, S.S., \&
-Kim, K.-S. 2012, ApJ, 759, 7
-
-\bibitem[Park et al. (2015)]{Park2015}
-Park, C., Song, H., Einasto, M., Lietzen, H., \&
-Heinamaki, P. 2015, JKAS, 48, 75
-
-\bibitem[Peebles \& Ratra(2003)]{PR2003}
-Peebles, P.J.E., \& Ratra, B. 2003, Reviews of Modern Physics, 75, 559
-
-\bibitem[Percival et al.(2014)]{Percival2014}
+\bibitem{Percival2014}%[Percival et al.(2014)]
 Percival, W.J., Ross, A.J., \& S\'{a}nchez, A.G., et al. 2014, MNRAS, 439, 2531
-
-\bibitem[Perlmutter et al.(1999)]{Perl1999}
-Perlmutter, S., Aldering, G., \& Goldhaber, G., et al. 1999, ApJ, 517, 565
-
-\bibitem[Press \& Shechter(1974)]{PS1974}
-Press, W.H., \& Schechter, P.L. 1974, ApJ, 187, 425
-
-\bibitem[Reid et al.(2012)]{Reid2012}
-Reid, B., Samushia, L., \& White, M., et al. 2012, MNRAS, 426, 2719
-
-\bibitem[Reid et al.(2016)]{Reidetal:2016}
-Reid, B., Ho, S., \& Padmanabhan, N., et al.  2016, MNRAS, 455, 1553
-
-\bibitem[Riess et al.(1998)]{Riess1998}
-Riess, A.G., Filippenko, A.V., \& Challis, P., et al. 1998, AJ, 116, 1009
-
-\bibitem[Riess et al.(2011)]{Riess2011}
-Riess, A.G., Macri, L., \& Casertano, S., et al. 2011, ApJ, 730, 119
-%A 3\% Solution: Determination of the Hubble Constant with the Hubble Space Telescope and Wide Field Camera
-
-\bibitem[Ross et al.(2012)]{2012MNRAS.424..564R} 
-Ross, A.J., Percival, W.J., \& S{\'a}nchez, A.G. et al.\ 2012, MNRAS, 424, 564
-
-\bibitem[Ross et al.(2015)]{MGS}
-Ross, A.J., Samushia, L., \& Howlett, C., et al. 2015, MNRAS, 449, 835
-
-\bibitem[Ryden(1995)]{Ryden1995}
-Ryden, B.S. 1995, ApJ, 452, 25
-
-%\bibitem[Samushia et al.(2014)]{Samushia2014}
-%Samushia, L., Reid, B. A., White, M., et al. 2014, MNRAS, 439, 3504
-
-%\bibitem[Sanchez et al.(2013)]{Sanchez2013}
-%Sanchez, A. G., Kazin, E. A., Beutler, F., et al. 2013, MNRAS, 433, 1202
-
-%\bibitem[Sutter et al.(2014)]{Sutter2014}
-%Sutter, P.M., Pisani, A., Wandelt, B.D., \& Weinberg, D.H. 2014, MNRAS, 443, 2983
-
-\bibitem[Sanchez et al.(2016)]{Sanchez2016}
-Sanchez, A. G., Scoccimarro, R., \& Crocce, M., et al.
-arXiv:1607.03147
-
-\bibitem[Schlafly et al.(2010)]{Schlafly2010}
-Schlafly E.F., Finkbeiner D.P., Schlegel D.J., et al. 2010, ApJ, 725, 1175
-
-\bibitem[Schlafly \& Finkbeiner(2011)]{SF2011}
-Schlafly E.F., \& Finkbeiner D.P. 2011, ApJ, 737, 103
-
-%DESI:
-%http://arxiv.org/abs/1106.1706
-\bibitem[Schlegel et al.(2011)]{DESI}
-Schlegel, D., Abdalla, F., \& Abraham, T., et al. 2011, arXiv:1106.1706
-
-\bibitem[Smee et al.(2013)]{Smee2013}
-Smee, S.A., Gunn, J.E., \& Uomoto, A., et al. 2013, AJ, 146, 32
-
-\bibitem[Song et al.(2014)]{2014arXiv1407.2257S} 
-Song, Y.S., Sabiu, C.G., 
-Okumura, T., Oh, M., \& Linder, E.V.\ 2014, JCAP, 12, 005
-
-\bibitem[Speare et al. (2015)]{Speare2015}
-Speare, R., Gott, J.R., Kim, J., \& Park, C.
-2015, ApJ, 799, 176
-
-%\bibitem[Tojeiro \& Percival(2011)]{Tojeiro2011}
-%Tojeiro R., \& Percivial W.J. 2011, MNRAS, 417, 1114
-
-%\bibitem[Tojeiro et al.(2012)]{Tojeiro2012}
-%Tojeiro, R., Percival, W. J., Wake, D. A., et al. 2012, MNRAS, 424, 136
-
-\bibitem[Viana \& Liddle(1996)]{VL1996}
-Viana, P.T.P., \& Liddle, A.R. 1996, MNRAS, 281, 323
-
-\bibitem[Villalobos et al.(2013)]{V13}
-Villalobos, \'{A}., ́De Lucia, G., Weinmann, S.M., Borgani, S., \& Murante, G. 2013, MNRAS, 433, L49
-
-\bibitem[Weinberg (1989)]{SW1989}
-Weinberg, S. 1989, Reviews of Modern Physics, 61, 1
-
-\bibitem[White (2011)]{White2011}
-White M., et al. 2011, ApJ, 728, 126
-
-\bibitem[Yoo \& Watanabe(2012)]{2012IJMPD..2130002Y} Yoo, J., \& Watanabe, Y.\ 2012, International Journal of Modern Physics D, 21, 1230002
-
-\bibitem[York et al.(2000)]{York et al. 2000}
-York, D.G., Adelman, J., \& Anderson, J.E., et al. 2000, AJ, 120, 1579
-
-\bibitem[Zehavi et al.(2011)]{zehavi2011}
-Zehavi, I., Zheng, Z., \& Weinberg, D.H., et al. 2011, ApJ, 736, 59
-
-%\bibitem{Milliman14}
-%\bibinfo{author}{Milliman}, K.~E. {\it et~al.}
-%\newblock \bibinfo{title}{WIYN Open Cluster Study. LX. Spectroscopic Binary Orbits in NGC 6819.}
-%\newblock{\it Astron. \ J.}{\bf\, 148}, 38--57 (2014).
 
@@
 
-X.L. computed the approximated 2pCFs in the many cosmologies, computed the likelihoods based on them, derived the final cosmological constraints, and did the robustness tests. 
-C.S. wrote the code computing the 2pCFs, and contributed in the likelihood analysis and the robustness tests. 
-C.P. proposed the concept of using redshift dependence to do AP tests, and have extensive discussions with X.L. about the likelihood analysis, 
-systematic correction, and robustness tests.
-Y.W. and G.Z. contributed in the computing the approximated 2pCFs in non-fiducial cosmologies, and the robustness tests.
-H.P. contributed in the cross-check of the 2pCF measurements, the likelihood analysis, and the systematic correction.
-A.S. contributed in the fast likelihood in non-fiducial cosmologies and the cosmological interpretation of the results.
-J.K. and S.H. performed the Horizon Run 4 simulations and built the mock galaxy samples.
+X.L. computed the approximated 2pCFs in the many cosmologies, did the statistical analysis and computed the likelihoods, 
+derived the final cosmological constraints, and conducted the robustness tests. 
+C.S. wrote the code computing the 2pCFs, and contributed in the likelihood methodology and the robustness tests. 
+C.P. contributed in the concept of using the redshift dependence, the LSS statistical, the likelihood methodology,
+the horizon run simulations, the systematic corrections, and the robustness tests.
+Y.W. and G.Z. contributed in the computing of approximated 2pCFs in non-fiducial cosmologies and the robustness tests.
+H.P. contributed in the 2pCF measurements, the likelihood computation, and the systematic correction.
+A.S. contributed in the fast computation of likelihoods in non-fiducial cosmologies and the cosmological interpretation of the results.
+J.K. and S.H. performed the Horizon Run 4 simulations and created the mock galaxy samples.
 All authors commented on the manuscript.
@@
 
-\begin{thebibliography}{10}
-\setcounter{enumiv}{29}
-
-\expandafter\ifx\csname url\endcsname\relax
-  \def\url#1{\texttt{#1}}\fi
-\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
-\providecommand{\bibinfo}[2]{#2}
-\providecommand{\eprint}[2][]{\url{#2}}
-
-\bibitem[Ade et al. (2015)]{Planck2015}
-Ade, P.A.R., Aghanim, N., \& Arnaud, M., et al. arXiv:1502.01589
-
-\bibitem[Alam et al.(2016)]{Alam2016}
-Alam, S., Ata, M., \& Bailey, S., et al. 2016,
-submitted to MNRAS (arXiv:1607.03155)
-
-%\bibitem[{{Alam} {et~al}\mbox{.}(2015{\natexlab{a}}){Alam}, {Albareti},
-%  {Allende Prieto}, {Anders}, {Anderson}, {Anderton}, {Andrews}, {Armengaud},
-%  {Aubourg}, {Bailey}, \& et~al.}]{dr12}
-%{Alam} S., Albareti, F.D.,\& Allende Prieto, C., {et~al.}, 2015,  ApJS, 219, 12
-
-\bibitem[Alcock \& Paczynski(1979)]{AP1979}
-Alcock, C., \& Paczynski, B. 1979, Nature, 281, 358
-
-%\bibitem[Anderson et al.(2012)]{2012MNRAS.427.3435A} 
-%Anderson, L., Aubourg, E., Bailey, S., et al.\ 2012, MNRAS, 427, 3435
-
-\bibitem[Anderson et al.(2013)]{Anderson2013}
-Anderson, L., Aubourg, \'E., \& Bailey, S. et al. 2014, MNRAS, 441, 24
-
-%\bibitem[Bassett et al.(2002)]{Bassett2002}
-%Bassett, B.A., Kunz, M., Silk, J., \& Ungarelli, C. 2002, MNRAS, 336, 1217
-
-\bibitem[Ballinger, Peacock \& Heavens 1996]{Ballinger1996}
-Ballinger, W.E., Peacock, J.A., \& Heavens, A.F. 1996, MNRAS, 282, 877
-
-\bibitem[Betoule et al.(2014)]{JLA}
-Betoule, M., Kessler, R., \& Guy, J., et al. 2014, A\&A, 568, 32
-
-\bibitem[Beutler et al.(2011)]{6dFGS}
-Beutler, F., Blake, C., \& Colless, M., et al. 2011, MNRAS, 416, 3017
-
-\bibitem[Beutler et al.(2013)]{Beutler2013}
-Beutler, F., Saito, S., \& Seo, H.-J., et al. 2013, MNRAS, 443, 1065
-
-\bibitem[Beutler et al.(2016)]{Beutler2016}
-Beutler, F., Seo, H.-J., \& Saito, S., et al. 2016,
-arXiv:1607.03150
-
-\bibitem[Blake et al.(2011)]{Blake2011}
-Blake, C., Glazebrook, K., \& Davis, T. M., 2011, MNRAS, 418, 1725
-
-\bibitem[Blake et al.(2013)]{WiggleZtopoloy}
-Blake, C., James, J.B., \& Poole, G.B. 2013, MNRAS, 437, 2488
-
-\bibitem[Bolton et al.(2012)]{Bolton2012}
-Bolton, A.S., Schlegel, \& D.J., Aubourg E., et al. 2012, AJ, 144, 144
-
-\bibitem[Boylan-Kolchin et al.(2008)]{B08}
-Boylan-Kolchin, M., Ma, C.-P., \& Quataert, E. 2008, MNRAS, 383, 93
-
-%\bibitem[Bueno Belloso et al. (2012)]{BB2012}
-%Bueno Belloso, A., Pettinari, G.W., Meures, N., \& Percival, W.J. 2012, Phys. Rev. D, 86, 023530
-
-%\bibitem[Chevallier \& Polarski(2001)]{CP2001}
-%Chevallier, M., Polarski, D. 2001, Int. J. Mod. Phys. D, 10, 213
-
-%\bibitem[Choi et al.(2010)]{choi 2010}
-%Choi, Y.-Y., Park, C., Kim, J., Gott, J.R., 
-%Weinberg, D.H., Vogeley, M.S., \& Kim, S.S. 2010, ApJS, 190, 181
-
-\bibitem[Christensen et al.(2001)]{Bayesian}
-Christensen, N., Meyer, R., Knox, L., \& Luey, B. 2001, Class. Quant. Grav., 18, 2677
-
-%\bibitem[Chuang et al.(2013)]{Chuang2013}
-%Chuang, C.-H., Prada, F., Beutler, F., et al. 2013, arXiv:1312.4889
-
-\bibitem[Chuang \& Wang(2012)]{ChuangWang2012}
-Chuang, C.-H., \& Wang, Y. 2012, MNRAS, 426, 226
-
-%\bibitem[Corasaniti \& Copeland(2003)]{Corasaniti2003}
-%Corasaniti, P.S., Copeland, E.J. 2003, Phys. Rev. D, 67, 063521
-
-%eBOSS: 
-%http://arxiv.org/abs/1508.04473
-\bibitem[Dawson et al.(2015)]{eBOSS}
-Dawson, K.S., Kneib, J.P., \& Percival, W.J., et al. 2015, accepted AJ
-
-\bibitem[Dawson et al.(2012)]{Dawson et al. 2012}
-Dawson, K.S., Schlegel, D.J., \& Ahn, C.P., et al. 2012, AJ, 145, 10
-
-\bibitem[Efstathiou (2014)]{E14H0}
-Efstathiou, G. 2014, MNRAS, 440, 1138
-
-\bibitem[Eisenstein et al.(2011)]{Eisenstein et al. 2011}
-Eisenstein, D.J.,  Weinberg, D.H., \& Agolet, E., et al. 2011, AJ, 142, 72
-
-\bibitem[Feldman, Kaiser \& Peacock (1994)]{1994ApJ...426...23F} 
-Feldman, H.A., Kaiser, N., \& Peacock, J.A.\ 1994, ApJ, 426, 23
-
-\bibitem[Fukugita et al. (1996)]{Fukugita1996}
-Fukugita, M., Ichikawa, T., \& Gunn, J.E., et al. 1996, AJ, 111, 1748
-%Publication:	
-%Astronomical Journal v.111, p.1748
-
-%\bibitem[Gingold \& Monaghan(1977)]{GM1977}
-%Gingold, R.A., \& Monaghan, J.J. 1977, MNRAS, 181, 375
-
-%\bibitem[Gott et al.(2009)]{gott 2009}
-%Gott, J.R., Choi, Y.-Y., Park, C., \& Kim, J. 2009, ApJ, 695, L45
-
-%\bibitem[Gott et al.(2008)]{gott 2008}
-%Gott, J.R., Hambrick, D.C., Vogeley, M.S., Kim, J., Park, C., Choi, Y.-Y.,
-%Cen, R., Ostriker, J.P., \& Nagamine, K. 2008, ApJ, 675, 16
-
-\bibitem[Gunn et al. (1998)]{Gunn1998}	
-Gunn, J.E., Carr, M., \& Rockosi, C. et al. 1998, AJ, 116, 3040
-
-\bibitem[Gunn et al.(2006)]{Gunn et al. 2006}
-Gunn, J.E., Siegmund, W.A., \& Mannery, E.J., et al. 2006, AJ, 131, 2332
-
-\bibitem[Guzzo et al.(2008)]{Guzzo2008}
-Guzzo, L., Pierleoni, M., \& Meneux, B., et al. 2008, Nature, 451, 541
-
-\bibitem[Hartlap et al.(2006)]{Hartlap}
-Hartlap J., Simon P. \& Schneider P. [astro-ph/0608064].
-
-\bibitem[Hong et al.(2016)]{hong2016}
-Hong, S.E., Park, C.,\&  Kim, J. 2016, ApJ, 823, 103
-
-\bibitem[Jackson (1972)]{FOG}
-Jackson, J., 1972, MNRAS, 156, 1
-
-\bibitem[Jennings et al.(2011)]{Jennings2011}
-Jennings, E., Baugh, C.M., \& Pascoli, S. 2011, MNRAS, 420, 1079
-
-%\bibitem[Jeong et al.(2014)]{Jeong2014}
-%Jeong, D., Dai, L., Kamionkowski, M., \& Szalay, A.S. 2014, arXiv:1408.4648
-
-\bibitem[Jiang et al.(2008)]{jiang2008}
-Jiang, C.Y., Jing, Y. P., \& Faltenbacher, A., et al. 2008, ApJ, 675, 1095
-
-\bibitem[Kaiser (1987)]{Kaiser1987}
-Kaiser, N. 1987, MNRAS, 227, 1
-
-\bibitem[Kim \& Park(2006)]{kim and park 2006}
-Kim, J., \& Park, C. 2006, ApJ, 639, 600
-
-\bibitem[Kim et al.(2009)]{2009ApJ...701.1547K} 
-Kim, J., Park, C., Gott, J.R., III, \& Dubinski, J.\ 2009, ApJ, 701, 1547
-
-\bibitem[Kim et al.(2015)]{hr4}
-Kim, J., Park, C., L'Huillier, B., \& Hong, S. E. 2015, JKAS, 48, 213
-
-\bibitem[Kim et al.(2011)]{horizonrun}
-Kim, J., Park, C., Rossi, G., Lee, S.M., \& Gott, J.R. 2011, JKAS, 44, 217
-
-\bibitem[Kitaura et al.(2015)]{MDPATCHY}
-Kitaura, F.S., Rodriguez-Torres, S., Chuang, C.-H., et al. arXiv:1509.06400
-
-\bibitem[Komatsu et al.(2011)]{komatsu 2011}
-Komatsu, E., Smith, K. M., \& Dunkley, J., et al. 2011, ApJS, 192, 18
-
-\bibitem[Lacey \& Cole(1993)]{LC93}
-Lacey, C., \& Cole, S. 1993, MNRAS, 262, 627
-
-\bibitem[Landy \& Szalay(1993)]{1993ApJ...412...64L} 
-Landy, S.D., \& Szalay, A.S.\ 1993, ApJ, 412, 64
-
-%EUCLID:
-%http://arxiv.org/abs/1110.3193
-\bibitem[Laureijs et al.(2011)]{EUCLID}
-Laureijs, R., Amiaux, J., \& Arduini, S., et al. 2011, arXiv:1110.3193
-
-\bibitem[Lavaux \& Wandelt(2012)]{LavausWandelt1995}
-Lavaux, G., \& Wandelt, B.D. 2012, ApJ, 754, 109
-
-%\bibitem[Levi et al.(2013)]{2013arXiv1308.0847L} 
-%Levi, M., Bebek, C., Beers, T., et al.\ 2013, arXiv:1308.0847
-
-\bibitem[Lewis \& Bridle (2002)]{LB2002}
-Lewis, A., \& Bridle, S. 2002, Phys. Rev. D, 66, 103511
-
-\bibitem[L'Huillier et al.(2014)]{2014NewA...30...79L} 
-L'Huillier, B., Park, C., \& Kim, J.\ 2014, New Astronomy, 30, 79
-
-\bibitem[Li et al.(2011)]{Li2011}
-Li, M., Li, X.-D., Wang, S., \& Wang, Y. 2011, Commun. Theor. Phys., 56, 525
-
-\bibitem[Li et al.(2014)]{Li2014}
-Li, X.-D., Park, C., Forero-Romero, J., \& Kim, J. 2014, ApJ, 796, 137
-
-\bibitem[Li et al.(2015)]{Li2015}
-Li, X.-D., Park, C., Sabiu, C.G., \& Kim, J. 2015, MNRAS, 450, 807
-
-\bibitem[Li et al.(2016)]{Li2016}
-Li, X.-D., Park, C., \& Sabiu, C.G., et al. 2016, ApJ, 832, 103
-
-%\bibitem[Linder(2003)]{Linder2003}
-%Linder, E.V. 2003, Phys. Rev. Lett., 90, 091301
-
-\bibitem[Linder et al.(2014)]{Linder2013}
-Linder, E.V., Minji, O., Okumura, T., Sabiu, C.G., \& Song, Y.-S. 2014, Phys. Rev. D, 89, 063525
-
-\bibitem[L{\'o}pez-Corredoira(2014)]{2014ApJ...781...96L} 
-L{\'o}pez-Corredoira, M.\ 2014, ApJ, 781, 96
-
-\bibitem[Mao et al. (2016)]{Qingqing2016}
-Mao, Q., Berlind, A.A., Scherrer, R.J., et al. 2016, submitted to ApJ
-
-\bibitem[Marinoni \& Buzzi(2010)]{Marinoni2010}
-Marinoni, C., \& Buzzi, A. 2010, Nature, 468, 539
-
-\bibitem[Matsubara \& Suto(1996)]{Matsubara1996}
-Matsubara T., \& Suto, Y. 1996, ApJ, 470, L1
-
-\bibitem[McCavana et al.(2012)]{M12}
-McCavana, T., Micic, M., Lewis, G. F., et al. 2012, MNRAS, 424, 361
-
-\bibitem[Morandi \& Sun (2016)]{MS2016}
-Morandi, A., \& Sun, M. arXiv:1601.03741
-
-\bibitem[Outram et al.(2004)]{Outram2004}
-Outram, P.J., Shanks, T., Boyle, B.J., Croom, S.M., Hoyle, F., Loaring, N.S., 
-Miller, L., \& Smith, R.J. 2004, MNRAS, 348, 745
-
-%\bibitem[Parejko et al.(2013)]{Parejko2013}
-%Parejko, J. K., Sunayama, T., Padmanabhan, N., et al. 2013, MNRAS, 429, 98
-
-\bibitem[Parejko et al.(2013)]{Parejko2013}
-Parejko J.K., et al., 2013, MNRAS, 429, 98
-
-\bibitem[Parihar et al. (2014)]{CMASSLSS2014}
-Parihar, P., Vogeley, M.S., \& Gott, J.R., et al. 2014, ApJ, 796, 86
-
-\bibitem[Park et al.(2005)]{park 2005}
-Park, C., Kim, J., \& Gott, J.R. 2005, ApJ, 633, 1
-
-\bibitem[Park \& Kim(2010)]{topology}
-Park, C., \& Kim, Y.-R. 2010, ApJL, 715, L185
-
-\bibitem[Park et al. (2012)]{Park2012}
-Park, C., Choi, Y.-Y., Kim, J., Gott, J.R., Kim, S.S., \&
-Kim, K.-S. 2012, ApJ, 759, 7
-
-\bibitem[Park et al. (2015)]{Park2015}
-Park, C., Song, H., Einasto, M., Lietzen, H., \&
-Heinamaki, P. 2015, JKAS, 48, 75
-
-\bibitem[Peebles \& Ratra(2003)]{PR2003}
-Peebles, P.J.E., \& Ratra, B. 2003, Reviews of Modern Physics, 75, 559
-
-\bibitem[Percival et al.(2014)]{Percival2014}
-Percival, W.J., Ross, A.J., \& S\'{a}nchez, A.G., et al. 2014, MNRAS, 439, 2531
-
-\bibitem[Perlmutter et al.(1999)]{Perl1999}
-Perlmutter, S., Aldering, G., \& Goldhaber, G., et al. 1999, ApJ, 517, 565
-
-\bibitem[Press \& Shechter(1974)]{PS1974}
-Press, W.H., \& Schechter, P.L. 1974, ApJ, 187, 425
-
-\bibitem[Reid et al.(2012)]{Reid2012}
-Reid, B., Samushia, L., \& White, M., et al. 2012, MNRAS, 426, 2719
-
-\bibitem[Reid et al.(2016)]{Reidetal:2016}
-Reid, B., Ho, S., \& Padmanabhan, N., et al.  2016, MNRAS, 455, 1553
-
-\bibitem[Riess et al.(1998)]{Riess1998}
-Riess, A.G., Filippenko, A.V., \& Challis, P., et al. 1998, AJ, 116, 1009
-
-\bibitem[Riess et al.(2011)]{Riess2011}
-Riess, A.G., Macri, L., \& Casertano, S., et al. 2011, ApJ, 730, 119
-%A 3\% Solution: Determination of the Hubble Constant with the Hubble Space Telescope and Wide Field Camera
-
-\bibitem[Ross et al.(2012)]{2012MNRAS.424..564R} 
-Ross, A.J., Percival, W.J., \& S{\'a}nchez, A.G. et al.\ 2012, MNRAS, 424, 564
-
-\bibitem[Ross et al.(2015)]{MGS}
-Ross, A.J., Samushia, L., \& Howlett, C., et al. 2015, MNRAS, 449, 835
-
-\bibitem[Ryden(1995)]{Ryden1995}
-Ryden, B.S. 1995, ApJ, 452, 25
-
-%\bibitem[Samushia et al.(2014)]{Samushia2014}
-%Samushia, L., Reid, B. A., White, M., et al. 2014, MNRAS, 439, 3504
-
-%\bibitem[Sanchez et al.(2013)]{Sanchez2013}
-%Sanchez, A. G., Kazin, E. A., Beutler, F., et al. 2013, MNRAS, 433, 1202
-
-%\bibitem[Sutter et al.(2014)]{Sutter2014}
-%Sutter, P.M., Pisani, A., Wandelt, B.D., \& Weinberg, D.H. 2014, MNRAS, 443, 2983
-
-\bibitem[Sanchez et al.(2016)]{Sanchez2016}
-Sanchez, A. G., Scoccimarro, R., \& Crocce, M., et al.
-arXiv:1607.03147
-
-\bibitem[Schlafly et al.(2010)]{Schlafly2010}
-Schlafly E.F., Finkbeiner D.P., Schlegel D.J., et al. 2010, ApJ, 725, 1175
-
-\bibitem[Schlafly \& Finkbeiner(2011)]{SF2011}
-Schlafly E.F., \& Finkbeiner D.P. 2011, ApJ, 737, 103
-
-%DESI:
-%http://arxiv.org/abs/1106.1706
-\bibitem[Schlegel et al.(2011)]{DESI}
-Schlegel, D., Abdalla, F., \& Abraham, T., et al. 2011, arXiv:1106.1706
-
-\bibitem[Smee et al.(2013)]{Smee2013}
-Smee, S.A., Gunn, J.E., \& Uomoto, A., et al. 2013, AJ, 146, 32
-
-\bibitem[Song et al.(2014)]{2014arXiv1407.2257S} 
-Song, Y.S., Sabiu, C.G., 
-Okumura, T., Oh, M., \& Linder, E.V.\ 2014, JCAP, 12, 005
-
-\bibitem[Speare et al. (2015)]{Speare2015}
-Speare, R., Gott, J.R., Kim, J., \& Park, C.
-2015, ApJ, 799, 176
-
-%\bibitem[Tojeiro \& Percival(2011)]{Tojeiro2011}
-%Tojeiro R., \& Percivial W.J. 2011, MNRAS, 417, 1114
-
-%\bibitem[Tojeiro et al.(2012)]{Tojeiro2012}
-%Tojeiro, R., Percival, W. J., Wake, D. A., et al. 2012, MNRAS, 424, 136
-
-\bibitem[Viana \& Liddle(1996)]{VL1996}
-Viana, P.T.P., \& Liddle, A.R. 1996, MNRAS, 281, 323
-
-\bibitem[Villalobos et al.(2013)]{V13}
-Villalobos, \'{A}., ́De Lucia, G., Weinmann, S.M., Borgani, S., \& Murante, G. 2013, MNRAS, 433, L49
-
-\bibitem[Weinberg (1989)]{SW1989}
-Weinberg, S. 1989, Reviews of Modern Physics, 61, 1
-
-\bibitem[White (2011)]{White2011}
-White M., et al. 2011, ApJ, 728, 126
-
-\bibitem[Yoo \& Watanabe(2012)]{2012IJMPD..2130002Y} Yoo, J., \& Watanabe, Y.\ 2012, International Journal of Modern Physics D, 21, 1230002
-
-\bibitem[York et al.(2000)]{York et al. 2000}
-York, D.G., Adelman, J., \& Anderson, J.E., et al. 2000, AJ, 120, 1579
-
-\bibitem[Zehavi et al.(2011)]{zehavi2011}
-Zehavi, I., Zheng, Z., \& Weinberg, D.H., et al. 2011, ApJ, 736, 59
-
-\end{thebibliography}
-
 %\clearpage

### 2017-07-13 Draft/Draft0.6.tex

--- 2017-06-22 Draft/Draft0.5.tex
@@
 $\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ w_a = -0.07 \pm 0.29$ (68.3\% CL). 
-Adding our new AP measurements to the aforementioned results reduced the $w_0-w_a$ 1-$\sigma$ contour area by 50\%.
+Adding our new AP measurements to the aforementioned results reduced the $w_0-w_a$ 2-$\sigma$ contour area by 50\%.
 The AP method can be combined with the standard BAO method, 
-increasing the science output of ongoing and future galaxy surveys by a factor of 2.
+greatly increasing the power of ongoing and future galaxy surveys in probing dark energy.
 \end{abstract}
@@
 However, if cosmological parameters are incorrectly chosen resulting in an AP effect,
-the anisotropy in the clustering signal has a clear redshift dependence. 
+the anisotropy in the clustering signal has a clear redshift dependence
+(as an illustration, Fig.\ref{fig_xy} shows how the shape distortion of objects varies with distance (i.e., redshift) 
+when incorrect cosmologies are used to infer distances).
 In a later work\cite{Li2015}, we developed an AP methodology 
@@
 measured as a function of angle between the galaxy pair and line-of-sight (LoS).
-As an illustration, Fig.\ref{fig_xy} shows how the shape distortion of objects (anisotropy of clustering signal) varies with distance (or redshift) when incorrect values of  $w_0$ or $w_a$ are used to infer distances.
 
-In earlier work\citep{Li2016} we applied this AP method to galaxies from the 3rd incarnation of the Sloan Digital Sky Survey (SDSS-III).
-Combining their method with measurements of the Cosmic Microwave Background (CMB), type Ia supernovae (SNIa),
+In an earlier work\citep{Li2016} we applied this AP method to galaxies from the 3rd incarnation of the Sloan Digital Sky Survey (SDSS-III). 
+Combining the method with measurements of the Cosmic Microwave Background (CMB), type Ia supernovae (SNIa), 
 baryon acoustic oscillations (BAO), and $H_0$,
-they obtained very tight constraints of $ \Omega_m = 0.301 \pm 0.006,\ w=-1.054 \pm 0.025$.
+we obtained very tight constraints of $ \Omega_m = 0.301 \pm 0.006,\ w=-1.054 \pm 0.025$.
 In reducing the RSD effect, 
-they were able to use galaxy clustering on scales down to 6 $h^{-1}$Mpc,
+we were able to use galaxy clustering on scales down to 6 $h^{-1}$Mpc,
 which is a major advance in extracting cosmological information 
@@
 We will present a slightly improved methodology to that of our previous work\citep{Li2016}, 
-allowing for faster likelihood estimation and thus the exploration of larger, higher dimensional parameter spaces. 
+allowing for faster likelihood estimation and thus the exploration of larger, higher dimensional parameter spaces
+(see Methods for details). 
 The methodology we will present here, can be applied to any model of dynamical dark energy, 
 or indeed any appropriately chosen parametric or non-parametric decomposition of the cosmic expansion history. 
-However, as a first step, in this paper we will focus on the widely used Chevallier-Polarski-Linder (CPL) parametrization
-$w(z) = w_0 + w_a \frac{z}{1+z}$.
+However, as a first step, in this paper we will focus on the widely used Chevallier-Polarski-Linder (CPL) parametrization\cite{CPL_CP,CPL_L},
+\begin{equation}
+w(z) = w_0 + w_a (1-a) = w_0 + w_a \frac{z}{1+z}.
+\end{equation}
+This parametrization characterizes dark energy equation-of-state (EoS) by two free parameters.
+$w_0$ determines the present-day value, while parameter $w_a$ characterizes the first-order derivative of $w$ with respect to $a$. 
+The CPL parametrization has many obvious advantages, for instance, a manageable parameter space, 
+the bounded behavior at high redshift, 
+and the ability to accurately reconstruct many dark energy theories\cite{CPL_L}. 
+So it was widely used in the literature to reconstruct dark energy from observations.
 
+%The CPL parametrization has been widely used to study the dynamical properties of dark energy in literature.
 The Planck team has released the {\texttt {COSMOMC}} \citep{LB2002} outputs of four MCMC ``chains'' in the CPL model, 
@@
 These MCMC chains contain the CMB+BAO+SNIa+$H_0$ likelihood computed for $\sim$37,000 sets of cosmological parameters,
-yielding constraints of $ \Omega_m = 0.309 \pm 0.010, w_0 = -0.938 \pm 0.109, w_a = -0.38 \pm 0.41$.
-%\begin{equation}
- %\Omega_m = 0.309 \pm 0.010, w_0 = -0.938 \pm 0.109, w_a = -0.38 \pm 0.41.
-%end{equation}
-We then compute the likelihood of the LOWZ+CMASS AP measurements for each of the parameter combinations provided in the Planck chain. 
+yielding constraints of %$ \Omega_m = 0.309 \pm 0.010, w_0 = -0.938 \pm 0.109, w_a = -0.38 \pm 0.41$.
+\begin{equation}
+ \Omega_m = 0.309 \pm 0.010, w_0 = -0.938 \pm 0.109, w_a = -0.38 \pm 0.41.
+\end{equation}
+
+To derive the constraints combined with our AP method,
+we then compute the likelihood of the SDSS LOWZ+CMASS AP measurements for each of the parameter combinations provided in the Planck chain. 
 To do this, we splited the 1,133,326 galaxies from the SDSS DR12 into six redshift bins,
-measured the 2pCF in these redshift bins, 
-subtract the systematic effects based on estimations from mocks made from Horizon Run 4 simulations \citep{HR4},
-and use a $\chi^2$ function to assess the redshift dependence
+measured the 2pCF (on scales of 6-40 $h^{-1}$Mpc) in these redshift bins (see Fig.\ref{fig_nbar}).
+This enables us investigating the redshift evolution of anisotropic clustering.
+We subtracted the systematic effects based on estimations from mocks made from Horizon Run 4 simulations \citep{HR4},
+and used a $\chi^2$ function to assess the redshift dependence.
 (see Methods for further explanations).
-After adding the sample log-likelihoods with ours, 
+
+After adding the log-likelihoods of the Planck team sample with ours, 
 while also multiply the sample weights by our likelihoods, 
-we derive the CMB+BAO+SNIa+$H_0$+AP constraints on CPL parameters, $\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29$.
-%\begin{equation}
-%\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29.
-%\end{equation}
+we derive the CMB+BAO+SNIa+$H_0$+AP constraints on CPL parameters, %$\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29$.
+\begin{equation}
+\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29.
+\end{equation}
 While the central values of parameters do not shift appreciably,
@@
 The derived cosmological constraints are fully consistent with a cosmological constant dark energy component having no evolution.
-Adding the new AP method to the CMB+BAO+SNIa+$H_0$ constraints reduces the statistical errors on many parameters by $\sim$30-40\% and reduces the $w_0-w_a$  (95.4\% CL) contour by 50\%.
+Adding the new AP method to the CMB+BAO+SNIa+$H_0$ constraints reduces the statistical errors on many parameters by $\sim$30-40\% 
+and reduces the $w_0-w_a$ (95.4\% CL) contour by 50\%.
 This reveals the constraining power of the small scale AP effect for probing the redshift evolution of dark energy.
@@
 Figure \ref{fig_contest} shows that 
-the result is unaffected by the line-of-sight $\mu$-cut, the number of angular bins, the range of radial integration and the choice of fiducial cosmology. 
+the result is unaffected by the line-of-sight $\mu$-cut, 
+the number of angular bins, 
+the range of radial integration and the choice of fiducial cosmology. 
 %we adopt $\mu_{\rm max}=0.99\ (0.85)$ to include more (less) regions near the LOS,
@@
 The method is complimentary to the BAO method and the two methods can be combined together, 
-increasing (by roughly twice) the science output of ongoing and future surveys, with little to no additional cost.
+increasing (by roughly twice) the power of ongoing and future surveys, with little to no additional cost.
 We expect this approach will play an important role in helping us unveiling the mystery of dark energy.
@@
 Li, X.-D., Park, C., Sabiu, C.G., \& Kim, J. 2015, MNRAS, 450, 807
+
+\bibitem{CPL_CP}
+Chevallier, M, \& Polarski, D. 2001, Int. J. Mod. Phys. D,  10, 213
+
+\bibitem{CPL_L}
+Linder, E. V. 2003, Phys. Rev. Lett, 90, 091301
 
@@
 C.S. wrote the code for computing the 2pCFs, and contributed in the likelihood methodology and the robustness tests. 
-C.P. contributed in the concept of using the redshift dependence, the LSS statistical, the likelihood methodology,
+C.P. contributed in the concept of using the redshift dependence to do AP test.
+He also contributed in the statistical methods of LSS, the likelihood methodology,
 the horizon run simulations, the systematic corrections, and the robustness tests.
@@
 H.P. contributed in the 2pCF measurements, the likelihood computation, and the systematic correction.
-A.S. contributed in the fast computation of likelihoods in non-fiducial cosmologies and the cosmological interpretation of the results.
+A.S. contributed in the fast computation of likelihoods in non-fiducial cosmologies, and the cosmological interpretation of the results.
 J.K. and S.H. performed the Horizon Run 4 simulations and created the mock galaxy samples.
@@
 a correction is applied by computing the fraction of the overlapping area.
+
 We found when using the approximate method the computed 
@@
 the statistical noise in the 2pCF.
+As a result, the approximate method reproduces the results presented in \cite{Li2016} quite well.
 

### 2017-07-13 Draft/Draft0.3.tex
minor changes

@@
 
-\author{ Xiao-Dong Li,$^{1,\dagger}$
+\author{ 
+Xiao-Dong Li,$^{1}$
 Cristiano G. Sabiu,$^{2}$
 Changbom Park,$^{1}$
-Yuting Wang,$^{3,\star}$
+Yuting Wang,$^{3}$
 Gong-bo Zhao,$^{3}$
@@
 \begin{abstract}
-We use the anisotropic {\it clustering shells} of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
-12 spanning the redshift range $0.15<z<0.69$ to place constraints on the expansion history of the Universe. 
-Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy $w=w_0+w_a\frac{z}{1+z}$,
+We use the small scale anisotropic clustering signal of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
+12, spanning the redshift range $0.15<z<0.69$ to place constraints on the expansion history of the Universe. 
+Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$,
 while improving upon earlier works \citep{Li2016}, 
 we present a novel use of the Alcock-Paczynski (AP) test via the small scales clustering difference between redshift bins. 
-This differential measure appears to be a robust statistical tool which mitigates many systematic effects, 
-allowing for competitive and unbiased constrains. 
-A combination of CMB+BAO+SNIa+$H_0$+AP yields
+This differential measure is shown to be a robust statistical tool that mitigates many systematic effects, 
+allowing for competitive and unbiased constrains to be placed on cosmological parameters.
+We find that our results, in combination with the CMB, BAO, SNIa and $H_0$ from Cepheid data yield, 
 $\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ w_a = -0.07 \pm 0.29$ (68.3\% CL). 
-Adding the AP method reduces the $w_0-w_a$ contour area by 50\%.
-The method can be combined with the standard BAO method, 
-increasing the science output of ongoing and future galaxy surveys by a factor of 2.
+Adding our new AP measurements to the aforementioned results reduced the $w_0-w_a$ 2-$\sigma$ contour area by 50\%.
+The AP method can be combined with the standard BAO method, 
+greatly increasing the power of ongoing and future galaxy surveys in probing dark energy.
 \end{abstract}
@@
 {\it Introduction.}---
-The  origin  of  the  accelerating  expansion  of  the  universe  is  one of  the  most  salient  questions  in  contemporary cosmology. 
-Proposed mechanisms include  evolving  scalar  fields  remnant  from  the  big  bang, 
-modifications to gravity,  and a  non-zero  vacuum energy \cite[see][for a comprehensive review]{2012IJMPD..2130002Y}. 
+The  origin  of  the late-time accelerating  expansion  of  the  universe  is  one of  the  most  salient  questions  in  contemporary cosmology.
+Theoretical explanations for this phenomena are many and range from a non-zero  vacuum energy and evolving  scalar  fields  remnant  from  the  big  bang, to modifications of Einstein's General Relativity\cite{2012IJMPD..2130002Y}.
 Considering the wealth of theoretical explanations, it is crucial to obtain precise and unbiased measurements of the expansion history of the Universe allowing us to 
-differentiate between competing dark energy models.
+differentiate between competing models.
 
@@
 
-In an effort to mitigate the RSD effect, \cite{Li2014} proposed utilizing the {\it redshift dependence} of the AP effect. 
-The clustering anisotropies produced by are, although large, close to uniform in magnitude over a wide range in redshift. 
+Previously, we proposed to use the  {\it redshift dependence} of the AP distortion\cite{Li2014} as a way of mitigating the RSD effect.
+The clustering anisotropies produced by RSD are, although large, close to uniform in magnitude over a wide range in redshift.
 However, if cosmological parameters are incorrectly chosen resulting in an AP effect,
-the anisotropy in the clustering signal has a clear redshift dependence. 
-In a later work, \cite{Li2015} developed an AP methodology 
+the anisotropy in the clustering signal has a clear redshift dependence
+(as an illustration, Fig.\ref{fig_xy} shows how the shape distortion of objects varies with distance (i.e., redshift) 
+when incorrect cosmologies are used to infer distances).
+In a later work\cite{Li2015}, we developed an AP methodology 
 that utilises the redshift dependence of the galaxy 2-point correlation function (2pCF), 
 measured as a function of angle between the galaxy pair and line-of-sight (LoS).
-As an illustration, Fig.\ref{fig_xy} shows how the shape distortion of objects (anisotropy of clustering signal) varies with distance (or redshift) when incorrect values of  $w_0$ or $w_a$ are used to infer distances.
+
+In an earlier work\citep{Li2016} we applied this AP method to galaxies from the 3rd incarnation of the Sloan Digital Sky Survey (SDSS-III). 
+Combining the method with measurements of the Cosmic Microwave Background (CMB), type Ia supernovae (SNIa), 
+baryon acoustic oscillations (BAO), and $H_0$,
+we obtained very tight constraints of $ \Omega_m = 0.301 \pm 0.006,\ w=-1.054 \pm 0.025$.
+In reducing the RSD effect, 
+we were able to use galaxy clustering on scales down to 6 $h^{-1}$Mpc,
+which is a major advance in extracting cosmological information 
+on small scales where galaxy clustering is strong and there are many independent structures.
 
@@
    \caption{\label{fig_xy}
-   The distance dependence of the shape distortion in four wrongly assumed cosmologies,
-   assuming a true cosmology of $\Omega_m=0.31$, $w=-1$.
+   The distance dependence of the shape distortion in four wrongly assumed cosmologies.
+   Assuming a true cosmology of $\Omega_m=0.31$, $w=-1$.
    There are four perfect squares with their true shapes plotted in blue dashed lines.
@@
 
-%$\xi_{\Delta s}(\mu)\equiv \int_{s_{\rm min}}^{s_{\rm max}} xi(s,\mu) ds$
-%($s$ is the clustering scale).
-%The RSD effect significantly distorts the shape of $\xi_{\Delta s}(mu)$ but exhibits much less redshift evolution 
-%compared to the amount of change in due to incorrectly adopted cosmologies .
-
-%When incorrect cosmological parameters are adopted, the shape of $\xi(\mu)$
-%appears anisotropic due to the AP effect, and the amplitude
-%is shifted by the change in comoving volume; both effects
-%have significant redshift dependence. We test the method
-%using the 2pCF on mock surveys drawn from HR3 and
-%find the constraints obtained are tighter than those from
-%the methodology of Li et al. (2014).
-
-\citep{Li2016} applied their AP method to galaxies from the 3rd incarnation of the Sloan Digital Sky Survey (SDSS-III).
-Combining their method with measurements of the Cosmic Microwave Background (CMB), type Ia supernovae (SNIa), 
-baryon acoustic oscillations (BAO), and $H_0$,
-they obtained very tight constraints of $ \Omega_m = 0.301 \pm 0.006,\ w=-1.054 \pm 0.025$.
-In reducing the RSD effect, 
-they were able to use galaxy clustering on scales down to 6 $h^{-1}$Mpc,
-which is a major advance in extracting cosmological information 
-on small scales where galaxy clustering is strong and there are many independent structures.
-
 In this paper, we continue to develop our previous methodology and proceed to infer the constraints on dynamical dark energy. 
-We will present a slightly improved methodology to that of \citep{Li2016},
+We will present a slightly improved methodology to that of our previous work\citep{Li2016}, 
 allowing for faster likelihood estimation and thus the exploration of larger, higher dimensional parameter spaces. 
@@
 or indeed any appropriately chosen parametric or non-parametric decomposition of the cosmic expansion history. 
-However, as a first step, in this paper we will focus on the widely used Chevallier-Polarski-Linder (CPL) parametrization
-$w(z) = w_0 + w_a \frac{z}{1+z}$.
+However, as a first step, in this paper we will focus on the widely used Chevallier-Polarski-Linder (CPL) parametrization\cite{CPL_CP,CPL_L},
+\begin{equation}
+w(z) = w_0 + w_a (1-a) = w_0 + w_a \frac{z}{1+z}.
+\end{equation}
 
@@
 %in the fiducial cosmology and group the bins in the target cosmology.
-In the case when one small pixel belongs to more than one larger pixel (``edge effect'' ),
+In the case when one small pixel belongs to more than one larger pixel,
 a correction is applied by computing the fraction of the overlapping area.
+
 We found when using the approximate method the computed 
@@
    \caption{\label{fig_TpCF}
+   Spliting the SDSS galaxies into six redshiftbins, and measuring the correlation function.
    Left panel: We split the BOSS DR12 galaxies into six redshift bins to measure the evolution of shape distortion.
    The blue and green solid histograms show the redshift density distribution of LOWZ and CMASS galaxies in the $\Omega_m=0.31$ $\Lambda$CDM. 
-   The vertical dashed lines define the six redshift bins that are used to cut the samples.
-%   Their redshift ranges are listed.                                       .
+   The vertical dashed lines define the six redshift bins that are used to cut the samples.                                       .
    The number of LOWZ/CMASS galaxies in the three low/high redshift bins are listed.
@@
     The black dashed lines mark the clustering region 6-40\ Mpc/h studied in the AP method.
-    %The correlation functions have rather large values on small sales such as $s=5$ $h^{-1}$Mpc,
-    %  and monotonically decreases to smaller values on larger scales due to weaker clustering.
     The six contour maps have rather similar appearance, implying small redshift evolution of $\xi$ from RSD.
@@
 
+The CPL parametrization characterizes dark energy equation-of-state (EoS) by two free parameters.
+$w_0$ determines the present-day value, while parameter $w_a$ characterizes the first-order derivative of $w$ with respect to $a$. 
+The CPL parametrization has many obvious advantages, for instance, a manageable parameter space, 
+the bounded behavior at high redshift, 
+and the ability to accurately reconstruct many dark energy theories\cite{CPL_L}. 
+So it was widely used in the literature to reconstruct dark energy from observations.
 The Planck team has released the {\texttt {COSMOMC}} \citep{LB2002} outputs of four MCMC ``chains'' in the CPL model, 
@@
 and the Hubble Space Telescope measurement of $H_0=70.6\pm3.3$ \cite{Riess2011,E14H0}.
-\footnote{http://pla.esac.esa.int/pla/\#cosmology}.
 These MCMC chains contain the CMB+BAO+SNIa+$H_0$ likelihood computed for $\sim$37,000 sets of cosmological parameters,
-yielding constraints of 
+yielding constraints of %$ \Omega_m = 0.309 \pm 0.010, w_0 = -0.938 \pm 0.109, w_a = -0.38 \pm 0.41$.
 \begin{equation}
@@
 \end{equation}
-%To include the AP method into the constraints,
-We then compute the likelihood of the LOWZ+CMASS AP measurements for each of the parameter combinations provided in the Planck chain.
-After multiplying the sample likelihoods with ours, while also changing the sample weights {\bf (HOW CHANGE?)}, we derive the CMB+BAO+SNIa+$H_0$+AP constraints on CPL parameters,
+%To derive the constraints combined with our AP method,
+%we then compute the likelihood of the SDSS LOWZ+CMASS AP measurements for each of the parameter combinations provided in the Planck chain. 
+%To do this, we splited the 1,133,326 galaxies from the SDSS DR12 into six redshift bins,
+%measured the 2pCF (on scales of 6-40 $h^{-1}$Mpc) in these redshift bins (see Fig.\ref{fig_nbar}).
+%This enables us investigating the redshift evolution of anisotropic clustering.
+%We subtracted the systematic effects based on estimations from mocks made from Horizon Run 4 simulations \citep{HR4},
+%and used a $\chi^2$ function to assess the redshift dependence.
+%(see Methods for further explanations).
+After adding the log-likelihoods of the Planck team sample with ours, 
+while also multiply the sample weights by our likelihoods, 
+we derive the CMB+BAO+SNIa+$H_0$+AP constraints on CPL parameters, %$\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29$.
 \begin{equation}
-%\Omega_m = 0.300 \pm 0.008, w_0 = -1.056 \pm 0.061, w_a = -0.04 \pm 0.27,
-    %1  0.2999656E+00  0.7616334E-02  0.2958745E+00  0.3035033E+00  0.2878169E+00  0.3132870E+00   \Omega_m
-    %2  0.6904801E+00  0.8675444E-02  0.6808558E+00  0.6993898E+00  0.6722945E+00  0.7052207E+00   h
-    %3 -0.1056468E+01  0.6096323E-01 -0.1116874E+01 -0.9965903E+00 -0.1175041E+01 -0.9287388E+00   w
-    %4 -0.3808376E-01  0.2716607E+00 -0.3105235E+00  0.2321461E+00 -0.6033103E+00  0.4782076E+00   w_a    
 \Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29.
-%    1  0.3014353E+00  0.7759923E-02  0.2974325E+00  0.3048882E+00  0.2889838E+00  0.3152269E+00   \Omega_m
-%    2  0.6887652E+00  0.8760036E-02  0.6797134E+00  0.6978279E+00  0.6703971E+00  0.7044224E+00   h
-%    3 -0.1041626E+01  0.6732817E-01 -0.1107730E+01 -0.9768319E+00 -0.1172149E+01 -0.8979017E+00   w
-%    4 -0.7173374E-01  0.2860547E+00 -0.3572176E+00  0.2107347E+00 -0.6775045E+00  0.4558817E+00   w_a    
 \end{equation}
-%$$.
 While the central values of parameters do not shift appreciably,
@@
 The derived cosmological constraints are fully consistent with a cosmological constant dark energy component having no evolution.
-Adding the new AP method to the CMB+BAO+SNIa+$H_0$ constraints reduces the statistical errors by $\sim$30-40\%,
-and reduces the 95.4\% CL $w_0-w_a$ contour by 50\%.
+Adding the new AP method to the CMB+BAO+SNIa+$H_0$ constraints reduces the statistical errors on many parameters by $\sim$30-40\% 
+and reduces the $w_0-w_a$ (95.4\% CL) contour by 50\%.
 This reveals the constraining power of the small scale AP effect for probing the redshift evolution of dark energy.
 
-%\cite{Li2016} shows that the AP method outperforms SNIa in constraining the parameter space of $\Omega_m-w$.
-%Similarly we find it outperforms in constraining $w_0-w_a$, as shown in the middle panel of Fig.\ref{fig_TpCF}.
+We performed a thorough test of all the possible variables in our methodology.
+Figure \ref{fig_contest} shows that 
+the result is unaffected by the line-of-sight $\mu$-cut, 
+the number of angular bins, 
+the range of radial integration and the choice of fiducial cosmology. 
+%we adopt $\mu_{\rm max}=0.99\ (0.85)$ to include more (less) regions near the LOS,
+%decrease the number of angular bins to $n_{\mu}=15-20$,
+%change the range of clustering to $8-30 \rm Mpc/h$,
+%change the fiducial cosmology to $\Omega_m=0.26,\ w=-0.6$,
+%exclude 1 or 2 high redshift bins,
+%or reduce the number of mocks to 1000.
+The most striking point to note in our testing is that the 
+shift in contour position is very small even when we do not include the systematic correction.
+This is reassuring, since we may have worried that {\it cosmological dependence} 
+of the systematic correction could influence the final result.
 
@@
    \caption{\label{fig_con}
+   Cosmological constraints on the CPL dark energy parametrization $w=w_0+w_a\frac{z}{1+z}$.
    Left panel: 68.3\%, 95.4\% CL likelihood contours in the  $w_0-w_a$ plane.
@@
 
-In this short paper we have chosen to focus on the popular CPL parameterisation of dark energy, 
-however our methodology could be used with any model of cosmic expansion history.
-
-%%% To be written!!!
-%\section{Robustness Test}\label{sec:test}
-{\it Robustness Test.}---
-
-Analysing the same DR12 BOSS data, \citet{Li2016} obtained constraints on $\Omega_m$ and $w$
-\begin{equation}\label{eq:wcdm_constrain_default}
-\Omega_m=0.301\pm 0.006, w=-1.054\pm 0.025.
-\end{equation}
-In our new ``approximate 2pCF'' approach, while taking a fiducial cosmological model of $\Omega_m=0.26, w=-1$, we obtain consistent results of,
-\begin{equation}
-\Omega_m = 0.301 \pm 0.008,\ w=-1.053\pm 0.034.
-%    1  0.3010870E+00  0.7818562E-02  0.2973018E+00  0.3045011E+00  0.2883318E+00  0.3150334E+00   \Omega_m
-%    2  0.6886453E+00  0.8507156E-02  0.6802557E+00  0.6975813E+00  0.6708444E+00  0.7047652E+00   h
-%    3 -0.1053343E+01  0.3395215E-01 -0.1087474E+01 -0.1020395E+01 -0.1121890E+01 -0.9819443E+00   w
-\end{equation}
-Since we use a smaller $n_{\mu}$ value than that adopted by \citep{Li2016}
-\footnote{\citep{Li2016} adopted $n_{\mu}=25-35$ to achieve tighter constraints.
-Since we are using an approximate 2pCF, for robustness considerations we use $n_{\mu}=20-25$.}, 
-resulting in a slightly enlarged error bar. 
-The central values of the parameters agree quite well, demonstrating the reliability of the approximate 2pCF method.
-
-%\begin{figure*}
-%   \centering{
-%   \includegraphics[width=6cm]{figIO.eps}
-%   %\includegraphics[width=9cm,natwidth=4,natheight=4]{fig2b.pdf}
-%   %\includegraphics[height=8cm]{fig2b.pdf}
-%   %   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
-%   %    \includegraphics[height=8cm]{smu.eps}
-%   }
-%   \caption{\label{fig_IO}
-%   Input-output test of the AP method. 
-%   The input cosmology (marker by green plus) is recovered at $\sim$0.5$\sigma$ 
-%   using 4 realizations.
-%   }
-%\end{figure*}
-
-We also performed an input-output test on four realizations of the HR4 mock catalogues \cite{hr4}.
-%In the framework of $w$CDM cosmology, %Figure \ref{fig_IO} shows 
-The input cosmology $\Omega_m=0.26$, $w=-1$ is recovered well, lying within the $\sim$0.5$\sigma$ CL region.
-
-Finally, we performed a thorough test of all the possible variables in our methodology.
-Figure \ref{fig_contest} shows that,
-the result does not change if 
-we adopt $\mu_{\rm max}=0.99\ (0.85)$ to include more (less) regions near the LOS,
-decrease the number of angular bins to $n_{\mu}=15-20$,
-change the range of clustering to $8-30 \rm Mpc/h$,
-change the fiducial cosmology to $\Omega_m=0.26,\ w=-0.6$,
-exclude 1 or 2 high redshift bins,
-or reduce the number of mocks to 1000.
-%Constraints get weaker if increase $s_{\rm min}$,
-%but are consistent with the original one.
-%Even if we choose an extremely unrealistic fiducial cosmology, i.e. 
-% $\Omega_m=0.11,\ w=-2.0$, the change in contour is still mild.
-The most striking point to note in our testing is that the 
-shift in contour position is very small even when we do not include the systematic correction.
-This is reassuring, since we may have worried that {\it cosmological dependence} on the systematic correction could influence on our final results.
-
-%We measure the evolution of $\hat\xi_{\Delta s}$ in six redshift bins.
-%on scales of $s_{\rm min}=6$, $s_{\rm max}=40$.
-%Systematics subtracted with the help of HR4 simulation.
 %Covariance matrix
@@
    \caption{\label{fig_contest}
-   Robustness test of the AP method. 
+   Robustness test of the results.
    For the ``default'' constraints (pink contours) are derived using six redshift bins, 
@@
 
-In \cite{Li2016} we proposed to constrain cosmological parameters via 
-the redshift dependence of galaxy anisotropic clustering. 
-This enables a robust Alcock-Paczynski test on relatively small scales.
-In this paper we improved the methodology and obtained tight constraints on the CPL parametrization of dark energy using 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
-12 spanning the redshift range $0.15<z<0.69$ . 
-Adding our constraints to the CMB+SNIa+BAO+$H_0$ combination, the $w_0-w_a$ contour was reduced by $\sim50$\%.
-
+In summary, we previously proposed to constrain cosmological parameters via 
+the redshift dependence of anisotropic galaxy clustering\cite{Li2016}.
+This approach enables a robust AP test on relatively small scales.
+In this paper we improved the methodology and obtained tight constraints on the CPL parametrization of dark energy.
+%using 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
+%12 spanning the redshift range $0.15<z<0.69$ . 
+%Adding our constraints to the CMB+SNIa+BAO+$H_0$ combination, the $w_0-w_a$ contour was reduced by $\sim50$\%.
 The AP method presented in this work has many advantages over the `traditional' galaxy clustering method.
@@
 
+The presented method of clustering shells can be applied to many spectroscopic galaxy surveys. 
+The method is complimentary to the BAO method and the two methods can be combined together, 
+increasing (by roughly twice) the power of ongoing and future surveys, with little to no additional cost.
+We expect this approach will play an important role in helping us unveiling the mystery of dark energy.
+
 %By reducing the RSD effect the method enables using clustering information on scales of $s<6 \rm Mpc/h$.
 %This is a major advance in extracting cosmological information on relatively small scales clustering.
-
-%In sum, our AP method have many advantages:
-%\begin{itemize}
-%\item {\it It leads to very tight cosmological constraints (powerful)}. The 
-% \item {\it Focusing on the redshift evolution of anisotropy it successfully overcome the problem of RSD, 
-% which has long time been a limitation to the application of AP to LSS (successful).}
-% In traditional approaches it is very challenging to model the RSD and enable a robust AP test.
-% \item {\it It is robust against systematics (reliable)}. 
-% \cite{Li2016} shows that $\hat\xi_{\Delta s}$ is insensitive to RSD or galaxy bias.
-% Figure \ref{fig_con_tests} shows that the change in results is small even if we do not correct the systematics at all.
-% \item {\it It is a major advance in extracting cosmological information on relatively small scales clustering (unique).} 
-% Clustering of galaxies happen on all scales,
-%but the size and shape of BAO ring only captures information mostly on scales of $s=100-120 {\rm Mpc/h}$.
-%In the analysis of correlation function shape, people mostly use $s\gtrsim 40$ Mpc/h.
-%Our AP method enters much smaller scales.
-%
-% \item {\it It does not require complicate modeling of non-linear structure growth and RSD (simple).}
-% \item {\it It is complimentary to BAO (useful).}
-% The method explores much smaller clustering scales than BAO. 
-% \cite{Li2016} shows that, actually the directions of $\Omega_m-w$ contours of the two methods are orthogonal to each other.
-%\end{itemize}
-
-%While it is of essential importance to build larger experiments to 
-%explore more of our Universe,
-%the physical interpretation of the data is of equal importance.
-%Considering our method enables {\it twice as much as before} information about the cosmic expansion history extracted from LSS data.
-%This, in a way, significantly enhances the valuable data obtained from the very expensive experiments costing billions of dollars.
-
-The presented method of clustering shells can be applied to many spectroscopic galaxy surveys. 
-The method is complimentary to the BAO method and the two methods can be combined together, 
-increasing (by roughly twice) the science output of ongoing and future surveys, with little to no additional cost.
-We expect it play an important role in helping us unveiling the mystery of dark energy.
 

### 2017-07-13 Draft/Draft0.7.tex
minor changes

--- 2017-07-13 Draft/Draft0.3.tex
@@
 
-\title{Dynamical dark energy constraints via clustering shells of SDSS-III BOSS galaxies}
+\title{Cosmological constraints from the redshift dependence of the Alcock-Paczynski effect: 
+constraining the linear evolution of dark energy}
 
@@
 $\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ w_a = -0.07 \pm 0.29$ (68.3\% CL). 
-Adding our new AP measurements to the aforementioned results reduced the $w_0-w_a$ 2-$\sigma$ contour area by 50\%.
+Addint our new AP measurements to the aforementioned results 
+reduces the error bars by 30-40\%,
+and reduces the area of $w_0-w_a$ contour by 50\%.
 The AP method can be combined with the standard BAO method,
@@
 \maketitle
+
+\begin{figure*}
+   \centering{
+   \includegraphics[height=5cm]{fig_xy.eps}
+   %\includegraphics[height=8cm]{fig4_1.eps}
+   %\includegraphics[height=7cm]{FVol.eps}
+   %\includegraphics[height=8cm]{xy.eps}
+   %\includegraphics[height=8cm]{smu.eps}
+   }
+   \caption{\label{fig_xy}
+   The distance dependence of the shape distortion in four wrongly assumed cosmologies.
+   Assuming a true cosmology of $\Omega_m=0.31$, $w=-1$.
+   There are four perfect squares with their true shapes plotted in blue dashed lines.
+   They are measured by an observer located at the origin, and the distances are reprojected in the four wrong cosmologies.
+   The apparently distorted shapes are plotted in red solid lines.
+   }
+\end{figure*}
 
@@
 
-\begin{figure*}
-   \centering{
-   \includegraphics[height=5cm]{fig_xy.eps}
-   %\includegraphics[height=8cm]{fig4_1.eps}
-   %\includegraphics[height=7cm]{FVol.eps}
-   %\includegraphics[height=8cm]{xy.eps}
-   %\includegraphics[height=8cm]{smu.eps}
-   }
-   \caption{\label{fig_xy}
-   The distance dependence of the shape distortion in four wrongly assumed cosmologies.
-   Assuming a true cosmology of $\Omega_m=0.31$, $w=-1$.
-   There are four perfect squares with their true shapes plotted in blue dashed lines.
-   They are measured by an observer located at the origin, and the distances are reprojected in the four wrong cosmologies.
-   The apparently distorted shapes are plotted in red solid lines.
-   }
-\end{figure*}
-
 In this paper, we continue to develop our previous methodology and proceed to infer the constraints on dynamical dark energy. 
@@
 \end{equation}
+This parametrization characterizes dark energy equation-of-state (EoS) by two free parameters.
+$w_0$ determines the present-day value, while parameter $w_a$ characterizes the first-order derivative of $w$ with respect to $a$.
 
-%The paper is organised as follows; 
-%in \S\ref{sec:method} we will briefly review the {\em clustering shells} method as proposed by \citet{Li2016} 
-%and then discuss some improvements that allow us to extend and generalise the analysis for any dark energy model. 
-%%In \S\ref{wcdm_constraint} we perform a consistency check with our pervious work using the same SDSS DR12 galaxies 
-%%and focusing on a constant dark energy e.o.s parameter, $w$. 
-%The results are presented in \S\ref{sec:results}, showing the constraints on the expansion history in terms of CPL parameters, $w_0, w_a$. 
-%In \S\ref{sec:test} we perform test on the robustness of our results. 
-%We then conclude in \S\ref{sec:conclusion}.
+The CPL parametrization has many obvious advantages, for instance, a manageable parameter space, 
+the bounded behavior at high redshift, 
+and the ability to accurately reconstruct many dark energy theories\cite{CPL_L}. 
+So it was widely used in the literature to reconstruct dark energy from observations.
+Fig.\ref{fig_xy} shows that redshift dependence of shape distortion is sensitive to both $w_0$ and $w_a$.
+So we expect these two parameters effectively constrained by our method.
 
@@
 The number density of galaxies and the redshift binning scheme is plotted in the left panel of Fig.\ref{fig_TpCF}.
+
+\begin{figure*}
+   \centering{
+   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
+   \includegraphics[height=6.5cm]{fig_nbar.eps}
+   \includegraphics[width=9.0cm,]{fig_2pcf.eps}
+   }
+   \caption{\label{fig_TpCF}
+   Spliting the SDSS galaxies into six redshiftbins, and measuring the correlation function.
+   Left panel: We split the BOSS DR12 galaxies into six redshift bins to measure the evolution of shape distortion.
+   The blue and green solid histograms show the redshift density distribution of LOWZ and CMASS galaxies in the $\Omega_m=0.31$ $\Lambda$CDM. 
+   The vertical dashed lines define the six redshift bins that are used to cut the samples.
+   The number of LOWZ/CMASS galaxies in the three low/high redshift bins are listed.
+   Right panel: 2D contour map of measured $\xi$ as a function of $\mu$ and $s$, from the six redshift bins of LOWZ and CMASS samples, 
+      in the cosmology of $\Omega_m=0.31$ $\Lambda$CDM model.
+    The black dashed lines mark the clustering region 6-40\ Mpc/h studied in the AP method.
+    The six contour maps have rather similar appearance, implying small redshift evolution of $\xi$ from RSD.
+   }
+\end{figure*}
 
@@
 The statistical bias and scattering in the likelihood function (due to the finite number of mocks in covariance estimation) 
-are adequately corrected\citet{Hartlap,Percival2014}.
+are adequately corrected \citep{Hartlap,Percival2014}.
 
@@
 $\hat\xi_{\Delta s}(\mu)$ in a non-fiducial cosmology suffers from
-an error of $\approx0.5\%$, which is 10 times smaller than 
-the statistical noise in the 2pCF.
-As a result, the approximate method reproduces the results presented in \cite{Li2016} quite well.
-
-%\section{Reproducing wCDM Constraints}\label{wcdm_constraint}
-%As a first trial, we firstly try to reproduce the constraints on $\Omega_m$ and $w$ in \citep{Li2016}:
-%As a first trial of reproduce the $\Omega_m-w$ constraints presented in \citep{Li2016},
-%we obtains
-%\begin{equation}
-%\Omega_m = 0.301 \pm 0.008,\ w=-1.053\pm 0.034\ (w\rm CDM).
-%    1  0.3010870E+00  0.7818562E-02  0.2973018E+00  0.3045011E+00  0.2883318E+00  0.3150334E+00   \Omega_m
-%    2  0.6886453E+00  0.8507156E-02  0.6802557E+00  0.6975813E+00  0.6708444E+00  0.7047652E+00   h
-%    3 -0.1053343E+01  0.3395215E-01 -0.1087474E+01 -0.1020395E+01 -0.1121890E+01 -0.9819443E+00   w
-%\end{equation}
-%The results are rather insensitive to the choice of fiducial cosmology.
-%while taking a different fiducial cosmology yields
-%\begin{eqnarray}
-%\Omega_m = 0.300 \pm 0.008,\ w=-1.057\pm 0.034\ (\rm fid:\ \Omega_m=0.26, w=-0.6),\\    
-%\Omega_m = 0.301 \pm 0.009,\ w=-1.055\pm 0.039\ (\rm fid:\ \Omega_m=0.31, w=-1.0),\\
-%\Omega_m = 0.302 \pm 0.008,\ w=-1.050\pm 0.035\ (\rm fid:\ \Omega_m=0.31, w=-0.6),\\
-%\Omega_m = 0.301 \pm 0.009,\ w=-1.052\pm 0.038\ (\rm fid:\ \Omega_m=0.31, w=-1.4),\\
-%\Omega_m = 0.304 \pm 0.008,\ w=-1.037\pm 0.034\ (\rm fid:\ \Omega_m=0.11, w=-2.0).
-%\end{eqnarray}
-%so the derived constraints are rather insensitive to the fiducial cosmology.
-%Even when adopting an extremely unlikely fiducial cosmological model, such as $\Omega_m=0.11, w=-2.0$, 
-%yields correct estimation of parameters of $\Omega_m = 0.304 \pm 0.008,\ w=-1.037\pm 0.034$.
-%For consideration of safety, when using the approxmiated method we slightly reduced the number of binning in $\hat\xi_{\Delta s}(\mu)$,
-%so the error bars are slightly larger than \citep{Li2016} %due to the limitation of approximation method
-%\footnote{We use $n_{\mu}$=20-25, while \citep{Li2016} adopted $n_{\mu}$=25-35.
-%The approximate 2pCF contour begins to be noisy if using such a large number of $n_\mu$.}.
-%from the 
-%The approximate 2pCF may not be accurate enough }
-
-%Using other fiducial cosmologies we derive similar cosmological constraints...
-%We simply adopt the $\Omega_m=0.26, w=-1$ as the fiducial cosmology in the following analysis...
+an error of $\lesssim0.5\%$, which is 10 times smaller than 
+the statistical noise.
+We checked that the approximate method can reproduce the results presented in \cite{Li2016} quite well.
 
@@
    %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
-   \includegraphics[height=5.3cm]{fig_nbar.eps}
-   \includegraphics[width=7cm,]{fig_2pcf.eps}
-   }
-   \caption{\label{fig_TpCF}
-   Spliting the SDSS galaxies into six redshiftbins, and measuring the correlation function.
-   Left panel: We split the BOSS DR12 galaxies into six redshift bins to measure the evolution of shape distortion.
-   The blue and green solid histograms show the redshift density distribution of LOWZ and CMASS galaxies in the $\Omega_m=0.31$ $\Lambda$CDM. 
-   The vertical dashed lines define the six redshift bins that are used to cut the samples.                                       .
-   The number of LOWZ/CMASS galaxies in the three low/high redshift bins are listed.
-   Right panel: 2D contour map of measured $\xi$ as a function of $\mu$ and $s$, from the six redshift bins of LOWZ and CMASS samples, 
-      in the cosmology of $\Omega_m=0.31$ $\Lambda$CDM model.
-    The black dashed lines mark the clustering region 6-40\ Mpc/h studied in the AP method.
-    The six contour maps have rather similar appearance, implying small redshift evolution of $\xi$ from RSD.
-   }
-\end{figure*}
-
-The CPL parametrization characterizes dark energy equation-of-state (EoS) by two free parameters.
-$w_0$ determines the present-day value, while parameter $w_a$ characterizes the first-order derivative of $w$ with respect to $a$. 
-The CPL parametrization has many obvious advantages, for instance, a manageable parameter space, 
-the bounded behavior at high redshift, 
-and the ability to accurately reconstruct many dark energy theories\cite{CPL_L}. 
-So it was widely used in the literature to reconstruct dark energy from observations.
-The Planck team has released the {\texttt {COSMOMC}} \citep{LB2002} outputs of four MCMC ``chains'' in the CPL model, 
-using a combination of four datasets:
-the full-mission Planck observations of CMB temperature and polarization anisotropies \cite{Planck2015},
-the BAO distance priors measured from SDSS DR11 \citep{Anderson2013}, 6dFGS \citep{6dFGS} and SDSS MGS \citep{MGS},
-the ``JLA'' SNIa sample \citep{JLA},
-and the Hubble Space Telescope measurement of $H_0=70.6\pm3.3$ \cite{Riess2011,E14H0}.
-These MCMC chains contain the CMB+BAO+SNIa+$H_0$ likelihood computed for $\sim$37,000 sets of cosmological parameters,
-yielding constraints of %$ \Omega_m = 0.309 \pm 0.010, w_0 = -0.938 \pm 0.109, w_a = -0.38 \pm 0.41$.
-\begin{equation}
- \Omega_m = 0.309 \pm 0.010, w_0 = -0.938 \pm 0.109, w_a = -0.38 \pm 0.41.
-\end{equation}
-%To derive the constraints combined with our AP method,
-%we then compute the likelihood of the SDSS LOWZ+CMASS AP measurements for each of the parameter combinations provided in the Planck chain. 
-%To do this, we splited the 1,133,326 galaxies from the SDSS DR12 into six redshift bins,
-%measured the 2pCF (on scales of 6-40 $h^{-1}$Mpc) in these redshift bins (see Fig.\ref{fig_nbar}).
-%This enables us investigating the redshift evolution of anisotropic clustering.
-%We subtracted the systematic effects based on estimations from mocks made from Horizon Run 4 simulations \citep{HR4},
-%and used a $\chi^2$ function to assess the redshift dependence.
-%(see Methods for further explanations).
-After adding the log-likelihoods of the Planck team sample with ours, 
-while also multiply the sample weights by our likelihoods, 
-we derive the CMB+BAO+SNIa+$H_0$+AP constraints on CPL parameters, %$\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29$.
-\begin{equation}
-\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29.
-\end{equation}
-While the central values of parameters do not shift appreciably,
-the error bars of $w_0$ and $w_a$ are reduced by 38.4\% and 29.7\%, respectively.% $$-40\%$ by adding our method into the analysis.
-
-The marginalised constraints on $w_0-w_a$ are shown in the left panel of Fig.\ref{fig_con}.
-Adding our new AP constraints significantly reduces the allowable parameter space. 
-This can also be visualise as allowable bands in $w(z)$ as can be seen in the right panel of Fig.\ref{fig_con}.
-
-The derived cosmological constraints are fully consistent with a cosmological constant dark energy component having no evolution.
-Adding the new AP method to the CMB+BAO+SNIa+$H_0$ constraints reduces the statistical errors on many parameters by $\sim$30-40\% 
-and reduces the $w_0-w_a$ (95.4\% CL) contour by 50\%.
-This reveals the constraining power of the small scale AP effect for probing the redshift evolution of dark energy.
-
-We performed a thorough test of all the possible variables in our methodology.
-Figure \ref{fig_contest} shows that 
-the result is unaffected by the line-of-sight $\mu$-cut, 
-the number of angular bins, 
-the range of radial integration and the choice of fiducial cosmology. 
-%we adopt $\mu_{\rm max}=0.99\ (0.85)$ to include more (less) regions near the LOS,
-%decrease the number of angular bins to $n_{\mu}=15-20$,
-%change the range of clustering to $8-30 \rm Mpc/h$,
-%change the fiducial cosmology to $\Omega_m=0.26,\ w=-0.6$,
-%exclude 1 or 2 high redshift bins,
-%or reduce the number of mocks to 1000.
-The most striking point to note in our testing is that the 
-shift in contour position is very small even when we do not include the systematic correction.
-This is reassuring, since we may have worried that {\it cosmological dependence} 
-of the systematic correction could influence the final result.
-
-\begin{figure*}
-   \centering{
-   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
-   \includegraphics[height=5cm,natwidth=6,natheight=4.5]{figCPL_b.pdf}
+   \includegraphics[height=6cm,natwidth=6,natheight=4.5]{figCPL_b.pdf}
    %\includegraphics[width=5.5cm,natwidth=4,natheight=4]{figCPL_b_BAOSNIaAP.pdf}
-   \includegraphics[height=5cm,natwidth=6,natheight=4.5]{figCPL_d.pdf}
+   \includegraphics[height=6cm,natwidth=6,natheight=4.5]{figCPL_d.pdf}
    %\includegraphics[height=8cm]{fig2b.pdf}
@@
 
+The Planck team has released the {\texttt {COSMOMC}} \citep{LB2002} outputs of four MCMC ``chains'' in the CPL model, 
+using a combination of four datasets:
+the full-mission Planck observations of CMB temperature and polarization anisotropies \cite{Planck2015},
+the BAO distance priors measured from SDSS DR11 \citep{Anderson2013}, 6dFGS \citep{6dFGS} and SDSS MGS \citep{MGS},
+the ``JLA'' SNIa sample \citep{JLA},
+and the Hubble Space Telescope measurement of $H_0=70.6\pm3.3$ \cite{Riess2011,E14H0}.
+These MCMC chains contain the CMB+BAO+SNIa+$H_0$ likelihood computed for $\sim$37,000 sets of cosmological parameters,
+yielding constraints of %$ \Omega_m = 0.309 \pm 0.010, w_0 = -0.938 \pm 0.109, w_a = -0.38 \pm 0.41$.
+\begin{eqnarray}
+ \Omega_m &=& 0.309 \pm 0.010,  \\ \nonumber
+ w_0 &=& -0.938 \pm 0.109,  \\ \nonumber
+ w_a &=& -0.38 \pm 0.41.
+\end{eqnarray}
+%To derive the constraints combined with our AP method,
+%we then compute the likelihood of the SDSS LOWZ+CMASS AP measurements for each of the parameter combinations provided in the Planck chain. 
+%To do this, we splited the 1,133,326 galaxies from the SDSS DR12 into six redshift bins,
+%measured the 2pCF (on scales of 6-40 $h^{-1}$Mpc) in these redshift bins (see Fig.\ref{fig_nbar}).
+%This enables us investigating the redshift evolution of anisotropic clustering.
+%We subtracted the systematic effects based on estimations from mocks made from Horizon Run 4 simulations \citep{HR4},
+%and used a $\chi^2$ function to assess the redshift dependence.
+%(see Methods for further explanations).
+After adding the log-likelihoods of the Planck team sample with ours, 
+while also multiply the sample weights by our likelihoods, 
+we derive the CMB+BAO+SNIa+$H_0$+AP constraints on CPL parameters, %$\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29$.
+\begin{eqnarray}
+\Omega_m &=& 0.301 \pm 0.008, \\ \nonumber
+w_0 &=& -1.042 \pm 0.067, \\ \nonumber
+w_a &=& -0.07 \pm 0.29.
+\end{eqnarray}
+While the central values of parameters do not shift appreciably,
+the error bars of $w_0$ and $w_a$ are reduced by 38.4\% and 29.7\%, respectively.% $$-40\%$ by adding our method into the analysis.
+
+The marginalised constraints on $w_0-w_a$ are shown in the left panel of Fig.\ref{fig_con}.
+Adding our new AP constraints significantly reduces the allowable parameter space. 
+This can also be visualise as allowable bands in $w(z)$ as can be seen in the right panel of Fig.\ref{fig_con}.
+
+The derived cosmological constraints are fully consistent with a cosmological constant dark energy component having no evolution.
+Adding the new AP method to the CMB+BAO+SNIa+$H_0$ constraints reduces the statistical errors on many parameters by $\sim$30-40\% 
+and reduces the $w_0-w_a$ (95.4\% CL) contour by 50\%.
+This reveals the constraining power of the small scale AP effect for probing the redshift evolution of dark energy.
+
+We performed a thorough test of all the possible variables in our methodology.
+Figure \ref{fig_contest} shows that 
+the result is unaffected by the line-of-sight $\mu$-cut, 
+the number of angular bins, 
+the range of radial integration and the choice of fiducial cosmology. 
+%we adopt $\mu_{\rm max}=0.99\ (0.85)$ to include more (less) regions near the LOS,
+%decrease the number of angular bins to $n_{\mu}=15-20$,
+%change the range of clustering to $8-30 \rm Mpc/h$,
+%change the fiducial cosmology to $\Omega_m=0.26,\ w=-0.6$,
+%exclude 1 or 2 high redshift bins,
+%or reduce the number of mocks to 1000.
+The most striking point to note in our testing is that the 
+shift in contour position is very small even when we do not include the systematic correction.
+This is reassuring, since we may have worried that {\it cosmological dependence} 
+of the systematic correction could influence the final result.
+
 %\section{Conclusion}\label{sec:conclusion}
@@
 %Adding our constraints to the CMB+SNIa+BAO+$H_0$ combination, the $w_0-w_a$ contour was reduced by $\sim50$\%.
+
 The AP method presented in this work has many advantages over the `traditional' galaxy clustering method.
@@
 We expect this approach will play an important role in helping us unveiling the mystery of dark energy.
-
-%By reducing the RSD effect the method enables using clustering information on scales of $s<6 \rm Mpc/h$.
-%This is a major advance in extracting cosmological information on relatively small scales clustering.
 
@@
 %[astro-ph/0205436].
+\bibitem{Li2016}%[Li et al.(2016)]
+Li, X.-D., Park, C., \& Sabiu, C.G., et al. 2016, ApJ, 832, 103
 
-\bibitem[Ade et al. (2015)]{Planck2015}
-Ade, P.A.R., Aghanim, N., \& Arnaud, M., et al. arXiv:1502.01589
+\bibitem{2012IJMPD..2130002Y}%[Yoo \& Watanabe(2012)]
+Yoo, J., \& Watanabe, Y.\ 2012, International Journal of Modern Physics D, 21, 1230002
 
-\bibitem[Alam et al.(2016)]{Alam2016}
+\bibitem{AP1979}%[Alcock \& Paczynski(1979)]
+Alcock, C., \& Paczynski, B. 1979, Nature, 281, 358
+
+\bibitem{Outram2004}%[Outram et al.(2004)]
+Outram, P.J., Shanks, T., Boyle, B.J., Croom, S.M., Hoyle, F., Loaring, N.S., 
+Miller, L., \& Smith, R.J. 2004, MNRAS, 348, 745
+
+\bibitem{Blake2011}%[Blake et al.(2011)]
+Blake, C., Glazebrook, K., \& Davis, T. M., 2011, MNRAS, 418, 1725
+
+\bibitem{Alam2016}%[Alam et al.(2016)]
 Alam, S., Ata, M., \& Bailey, S., et al. 2016,
@@
 
-\bibitem[{{Alam} {et~al}\mbox{.}(2015{\natexlab{a}}){Alam}, {Albareti},
-  {Allende Prieto}, {Anders}, {Anderson}, {Anderton}, {Andrews}, {Armengaud},
-  {Aubourg}, {Bailey}, \& et~al.}]{dr12}
-{Alam} S., Albareti, F.D.,\& Allende Prieto, C., {et~al.}, 2015,  ApJS, 219, 12
+\bibitem{Ballinger1996}%[Ballinger, Peacock \& Heavens 1996]
+Ballinger, W.E., Peacock, J.A., \& Heavens, A.F. 1996, MNRAS, 282, 877
 
-\bibitem[Alcock \& Paczynski(1979)]{AP1979}
-Alcock, C., \& Paczynski, B. 1979, Nature, 281, 358
+\bibitem{Marinoni2010}%[Marinoni \& Buzzi(2010)]
+Marinoni, C., \& Buzzi, A. 2010, Nature, 468, 539
 
-%\bibitem[Anderson et al.(2012)]{2012MNRAS.427.3435A} 
-%Anderson, L., Aubourg, E., Bailey, S., et al.\ 2012, MNRAS, 427, 3435
+\bibitem{Jennings2011}%[Jennings et al.(2011)]
+Jennings, E., Baugh, C.M., \& Pascoli, S. 2011, MNRAS, 420, 1079
 
-\bibitem[Anderson et al.(2013)]{Anderson2013}
+\bibitem{Ryden1995}%[Ryden(1995)]
+Ryden, B.S. 1995, ApJ, 452, 25
+
+\bibitem{LavausWandelt1995}%[Lavaux \& Wandelt(2012)]
+Lavaux, G., \& Wandelt, B.D. 2012, ApJ, 754, 109
+
+\bibitem{Qingqing2016}%[Mao et al. (2016)]
+Mao, Q., Berlind, A.A., Scherrer, R.J., et al. 2016, submitted to ApJ
+
+\bibitem{Li2014}%[Li et al.(2014)]
+Li, X.-D., Park, C., Forero-Romero, J., \& Kim, J. 2014, ApJ, 796, 137
+
+\bibitem{Li2015}%[Li et al.(2015)]
+Li, X.-D., Park, C., Sabiu, C.G., \& Kim, J. 2015, MNRAS, 450, 807
+
+\bibitem{CPL_CP}
+Chevallier, M, \& Polarski, D. 2001, Int. J. Mod. Phys. D,  10, 213
+
+\bibitem{CPL_L}
+Linder, E. V. 2003, Phys. Rev. Lett, 90, 091301
+
+\bibitem{Reidetal:2016}%[Reid et al.(2016)]
+Reid, B., Ho, S., \& Padmanabhan, N., et al.  2016, MNRAS, 455, 1553
+
+\bibitem{HR4}%[Kim et al.(2015)]
+Kim, J., Park, C., L'Huillier, B., \& Hong, S. E. 2015, JKAS, 48, 213
+
+\bibitem{hong2016}%[Hong et al.(2016)]
+Hong, S.E., Park, C.,\&  Kim, J. 2016, ApJ, 823, 103
+
+\bibitem{MDPATCHY}%[Kitaura et al.(2015)]
+Kitaura, F.S., Rodriguez-Torres, S., Chuang, C.-H., et al.2016, MNRAS, 456, 4156
+
+\bibitem{Hartlap}%[Hartlap et al.(2006)]
+Hartlap J., Simon P. \& Schneider P. [astro-ph/0608064].
+
+\bibitem{Percival2014}%[Percival et al.(2014)]
+Percival, W.J., Ross, A.J., \& S\'{a}nchez, A.G., et al. 2014, MNRAS, 439, 2531
+
+\bibitem{LB2002}%[Lewis \& Bridle (2002)]
+Lewis, A., \& Bridle, S. 2002, Phys. Rev. D, 66, 103511
+
+\bibitem{Planck2015}%[Ade et al. (2015)]
+Ade, P.A.R., Aghanim, N., \& Arnaud, M., et al. 2016, A\&A, 594, A13
+
+\bibitem{Anderson2013}%[Anderson et al.(2013)]
 Anderson, L., Aubourg, \'E., \& Bailey, S. et al. 2014, MNRAS, 441, 24
 
-%\bibitem[Bassett et al.(2002)]{Bassett2002}
-%Bassett, B.A., Kunz, M., Silk, J., \& Ungarelli, C. 2002, MNRAS, 336, 1217
+\bibitem{6dFGS}%[Beutler et al.(2011)]
+Beutler, F., Blake, C., \& Colless, M., et al. 2011, MNRAS, 416, 3017
 
-\bibitem[Ballinger, Peacock \& Heavens 1996]{Ballinger1996}
-Ballinger, W.E., Peacock, J.A., \& Heavens, A.F. 1996, MNRAS, 282, 877
+\bibitem{MGS}%[Ross et al.(2015)]
+Ross, A.J., Samushia, L., \& Howlett, C., et al. 2015, MNRAS, 449, 835
 
-\bibitem[Betoule et al.(2014)]{JLA}
+\bibitem{JLA}%[Betoule et al.(2014)]
 Betoule, M., Kessler, R., \& Guy, J., et al. 2014, A\&A, 568, 32
 
-\bibitem[Beutler et al.(2011)]{6dFGS}
-Beutler, F., Blake, C., \& Colless, M., et al. 2011, MNRAS, 416, 3017
+\bibitem{Riess2011}%[Riess et al.(2011)]
+Riess, A.G., Macri, L., \& Casertano, S., et al. 2011, ApJ, 730, 119
 
-\bibitem[Beutler et al.(2013)]{Beutler2013}
-Beutler, F., Saito, S., \& Seo, H.-J., et al. 2013, MNRAS, 443, 1065
-
-\bibitem[Beutler et al.(2016)]{Beutler2016}
-Beutler, F., Seo, H.-J., \& Saito, S., et al. 2016,
-arXiv:1607.03150
-
-\bibitem[Blake et al.(2011)]{Blake2011}
-Blake, C., Glazebrook, K., \& Davis, T. M., 2011, MNRAS, 418, 1725
-
-\bibitem[Blake et al.(2013)]{WiggleZtopoloy}
-Blake, C., James, J.B., \& Poole, G.B. 2013, MNRAS, 437, 2488
-
-\bibitem[Bolton et al.(2012)]{Bolton2012}
-Bolton, A.S., Schlegel, \& D.J., Aubourg E., et al. 2012, AJ, 144, 144
-
-\bibitem[Boylan-Kolchin et al.(2008)]{B08}
-Boylan-Kolchin, M., Ma, C.-P., \& Quataert, E. 2008, MNRAS, 383, 93
-
-%\bibitem[Bueno Belloso et al. (2012)]{BB2012}
-%Bueno Belloso, A., Pettinari, G.W., Meures, N., \& Percival, W.J. 2012, Phys. Rev. D, 86, 023530
-
-%\bibitem[Chevallier \& Polarski(2001)]{CP2001}
-%Chevallier, M., Polarski, D. 2001, Int. J. Mod. Phys. D, 10, 213
-
-%\bibitem[Choi et al.(2010)]{choi 2010}
-%Choi, Y.-Y., Park, C., Kim, J., Gott, J.R., 
-%Weinberg, D.H., Vogeley, M.S., \& Kim, S.S. 2010, ApJS, 190, 181
-
-\bibitem[Christensen et al.(2001)]{Bayesian}
-Christensen, N., Meyer, R., Knox, L., \& Luey, B. 2001, Class. Quant. Grav., 18, 2677
-
-%\bibitem[Chuang et al.(2013)]{Chuang2013}
-%Chuang, C.-H., Prada, F., Beutler, F., et al. 2013, arXiv:1312.4889
-
-\bibitem[Chuang \& Wang(2012)]{ChuangWang2012}
-Chuang, C.-H., \& Wang, Y. 2012, MNRAS, 426, 226
-
-%\bibitem[Corasaniti \& Copeland(2003)]{Corasaniti2003}
-%Corasaniti, P.S., Copeland, E.J. 2003, Phys. Rev. D, 67, 063521
-
-%eBOSS: 
-%http://arxiv.org/abs/1508.04473
-\bibitem[Dawson et al.(2015)]{eBOSS}
-Dawson, K.S., Kneib, J.P., \& Percival, W.J., et al. 2015, accepted AJ
-
-\bibitem[Dawson et al.(2012)]{Dawson et al. 2012}
-Dawson, K.S., Schlegel, D.J., \& Ahn, C.P., et al. 2012, AJ, 145, 10
-
-\bibitem[Efstathiou (2014)]{E14H0}
+\bibitem{E14H0}%[Efstathiou (2014)]
 Efstathiou, G. 2014, MNRAS, 440, 1138
 
-\bibitem[Eisenstein et al.(2011)]{Eisenstein et al. 2011}
-Eisenstein, D.J.,  Weinberg, D.H., \& Agolet, E., et al. 2011, AJ, 142, 72
+%\bibitem{Lee12}
+%\bibinfo{author}{Lee}, E.~J., {Murray}, N., {Rahman}, M. 
+%\newblock \bibinfo{title}{Milky Way Star-forming Complexes and the Turbulent Motion of the Galaxy's Molecular Gas.}
+%\newblock{\it Astrophys. \ J.}{\bf\, 752}, 146-159 (2012).
 
-\bibitem[Feldman, Kaiser \& Peacock (1994)]{1994ApJ...426...23F} 
-Feldman, H.A., Kaiser, N., \& Peacock, J.A.\ 1994, ApJ, 426, 23
+%%%% For methods
 
-\bibitem[Fukugita et al. (1996)]{Fukugita1996}
-Fukugita, M., Ichikawa, T., \& Gunn, J.E., et al. 1996, AJ, 111, 1748
-%Publication:	
-%Astronomical Journal v.111, p.1748
-
-%\bibitem[Gingold \& Monaghan(1977)]{GM1977}
-%Gingold, R.A., \& Monaghan, J.J. 1977, MNRAS, 181, 375
-
-%\bibitem[Gott et al.(2009)]{gott 2009}
-%Gott, J.R., Choi, Y.-Y., Park, C., \& Kim, J. 2009, ApJ, 695, L45
-
-%\bibitem[Gott et al.(2008)]{gott 2008}
-%Gott, J.R., Hambrick, D.C., Vogeley, M.S., Kim, J., Park, C., Choi, Y.-Y.,
-%Cen, R., Ostriker, J.P., \& Nagamine, K. 2008, ApJ, 675, 16
-
-\bibitem[Gunn et al. (1998)]{Gunn1998}	
-Gunn, J.E., Carr, M., \& Rockosi, C. et al. 1998, AJ, 116, 3040
-
-\bibitem[Gunn et al.(2006)]{Gunn et al. 2006}
-Gunn, J.E., Siegmund, W.A., \& Mannery, E.J., et al. 2006, AJ, 131, 2332
-
-\bibitem[Guzzo et al.(2008)]{Guzzo2008}
-Guzzo, L., Pierleoni, M., \& Meneux, B., et al. 2008, Nature, 451, 541
-
-\bibitem[Hartlap et al.(2006)]{Hartlap}
-Hartlap J., Simon P. \& Schneider P. [astro-ph/0608064].
-
-\bibitem[Hong et al.(2016)]{hong2016}
-Hong, S.E., Park, C.,\&  Kim, J. 2016, ApJ, 823, 103
-
-\bibitem[Jackson (1972)]{FOG}
-Jackson, J., 1972, MNRAS, 156, 1
-
-\bibitem[Jennings et al.(2011)]{Jennings2011}
-Jennings, E., Baugh, C.M., \& Pascoli, S. 2011, MNRAS, 420, 1079
-
-%\bibitem[Jeong et al.(2014)]{Jeong2014}
-%Jeong, D., Dai, L., Kamionkowski, M., \& Szalay, A.S. 2014, arXiv:1408.4648
-
-\bibitem[Jiang et al.(2008)]{jiang2008}
-Jiang, C.Y., Jing, Y. P., \& Faltenbacher, A., et al. 2008, ApJ, 675, 1095
-
-\bibitem[Kaiser (1987)]{Kaiser1987}
-Kaiser, N. 1987, MNRAS, 227, 1
-
-\bibitem[Kim \& Park(2006)]{kim and park 2006}
-Kim, J., \& Park, C. 2006, ApJ, 639, 600
-
-\bibitem[Kim et al.(2009)]{2009ApJ...701.1547K} 
-Kim, J., Park, C., Gott, J.R., III, \& Dubinski, J.\ 2009, ApJ, 701, 1547
-
-\bibitem[Kim et al.(2015)]{hr4}
-Kim, J., Park, C., L'Huillier, B., \& Hong, S. E. 2015, JKAS, 48, 213
-
-\bibitem[Kim et al.(2011)]{horizonrun}
-Kim, J., Park, C., Rossi, G., Lee, S.M., \& Gott, J.R. 2011, JKAS, 44, 217
-
-\bibitem[Kitaura et al.(2015)]{MDPATCHY}
-Kitaura, F.S., Rodrı\'{i}guez-Torres, S., Chuang, C.-H., et al. arXiv:1509.06400
-
-\bibitem[Komatsu et al.(2011)]{komatsu 2011}
+\bibitem{komatsu2011}%[Komatsu et al.(2011)]
 Komatsu, E., Smith, K. M., \& Dunkley, J., et al. 2011, ApJS, 192, 18
-
-\bibitem[Lacey \& Cole(1993)]{LC93}
-Lacey, C., \& Cole, S. 1993, MNRAS, 262, 627
-
-\bibitem[Landy \& Szalay(1993)]{1993ApJ...412...64L} 
-Landy, S.D., \& Szalay, A.S.\ 1993, ApJ, 412, 64
-
-%EUCLID:
-%http://arxiv.org/abs/1110.3193
-\bibitem[Laureijs et al.(2011)]{EUCLID}
-Laureijs, R., Amiaux, J., \& Arduini, S., et al. 2011, arXiv:1110.3193
-
-\bibitem[Lavaux \& Wandelt(2012)]{LavausWandelt1995}
-Lavaux, G., \& Wandelt, B.D. 2012, ApJ, 754, 109
-
-%\bibitem[Levi et al.(2013)]{2013arXiv1308.0847L} 
-%Levi, M., Bebek, C., Beers, T., et al.\ 2013, arXiv:1308.0847
-
-\bibitem[Lewis \& Bridle (2002)]{LB2002}
-Lewis, A., \& Bridle, S. 2002, Phys. Rev. D, 66, 103511
-
-\bibitem[L'Huillier et al.(2014)]{2014NewA...30...79L} 
-L'Huillier, B., Park, C., \& Kim, J.\ 2014, New Astronomy, 30, 79
-
-\bibitem[Li et al.(2011)]{Li2011}
-Li, M., Li, X.-D., Wang, S., \& Wang, Y. 2011, Commun. Theor. Phys., 56, 525
-
-\bibitem[Li et al.(2014)]{Li2014}
-Li, X.-D., Park, C., Forero-Romero, J., \& Kim, J. 2014, ApJ, 796, 137
-
-\bibitem[Li et al.(2015)]{Li2015}
-Li, X.-D., Park, C., Sabiu, C.G., \& Kim, J. 2015, MNRAS, 450, 807
-
-\bibitem[Li et al.(2016)]{Li2016}
-Li, X.-D., Park, C., \& Sabiu, C.G., et al. 2016, ApJ, 832, 103
-
-%\bibitem[Linder(2003)]{Linder2003}
-%Linder, E.V. 2003, Phys. Rev. Lett., 90, 091301
-
-\bibitem[Linder et al.(2014)]{Linder2013}
-Linder, E.V., Minji, O., Okumura, T., Sabiu, C.G., \& Song, Y.-S. 2014, Phys. Rev. D, 89, 063525
-
-\bibitem[L{\'o}pez-Corredoira(2014)]{2014ApJ...781...96L} 
-L{\'o}pez-Corredoira, M.\ 2014, ApJ, 781, 96
-
-\bibitem[Mao et al. (2016)]{Qingqing2016}
-Mao, Q., Berlind, A.A., Scherrer, R.J., et al. 2016, submitted to ApJ
-
-\bibitem[Marinoni \& Buzzi(2010)]{Marinoni2010}
-Marinoni, C., \& Buzzi, A. 2010, Nature, 468, 539
-
-\bibitem[Matsubara \& Suto(1996)]{Matsubara1996}
-Matsubara T., \& Suto, Y. 1996, ApJ, 470, L1
-
-\bibitem[McCavana et al.(2012)]{M12}
-McCavana, T., Micic, M., Lewis, G. F., et al. 2012, MNRAS, 424, 361
-
-\bibitem[Morandi \& Sun (2016)]{MS2016}
-Morandi, A., \& Sun, M. arXiv:1601.03741
-
-\bibitem[Outram et al.(2004)]{Outram2004}
-Outram, P.J., Shanks, T., Boyle, B.J., Croom, S.M., Hoyle, F., Loaring, N.S., 
-Miller, L., \& Smith, R.J. 2004, MNRAS, 348, 745
-
-%\bibitem[Parejko et al.(2013)]{Parejko2013}
-%Parejko, J. K., Sunayama, T., Padmanabhan, N., et al. 2013, MNRAS, 429, 98
-
-\bibitem[Parejko et al.(2013)]{Parejko2013}
-Parejko J.K., et al., 2013, MNRAS, 429, 98
-
-\bibitem[Parihar et al. (2014)]{CMASSLSS2014}
-Parihar, P., Vogeley, M.S., \& Gott, J.R., et al. 2014, ApJ, 796, 86
-
-\bibitem[Park et al.(2005)]{park 2005}
-Park, C., Kim, J., \& Gott, J.R. 2005, ApJ, 633, 1
-
-\bibitem[Park \& Kim(2010)]{topology}
-Park, C., \& Kim, Y.-R. 2010, ApJL, 715, L185
-
-\bibitem[Park et al. (2012)]{Park2012}
-Park, C., Choi, Y.-Y., Kim, J., Gott, J.R., Kim, S.S., \&
-Kim, K.-S. 2012, ApJ, 759, 7
-
-\bibitem[Park et al. (2015)]{Park2015}
-Park, C., Song, H., Einasto, M., Lietzen, H., \&
-Heinamaki, P. 2015, JKAS, 48, 75
-
-\bibitem[Peebles \& Ratra(2003)]{PR2003}
-Peebles, P.J.E., \& Ratra, B. 2003, Reviews of Modern Physics, 75, 559
-
-\bibitem[Percival et al.(2014)]{Percival2014}
-Percival, W.J., Ross, A.J., \& S\'{a}nchez, A.G., et al. 2014, MNRAS, 439, 2531
-
-\bibitem[Perlmutter et al.(1999)]{Perl1999}
-Perlmutter, S., Aldering, G., \& Goldhaber, G., et al. 1999, ApJ, 517, 565
-
-\bibitem[Press \& Shechter(1974)]{PS1974}
-Press, W.H., \& Schechter, P.L. 1974, ApJ, 187, 425
-
-\bibitem[Reid et al.(2012)]{Reid2012}
-Reid, B., Samushia, L., \& White, M., et al. 2012, MNRAS, 426, 2719
-
-\bibitem[Reid et al.(2016)]{Reidetal:2016}
-Reid, B., Ho, S., \& Padmanabhan, N., et al.  2016, MNRAS, 455, 1553
-
-\bibitem[Riess et al.(1998)]{Riess1998}
-Riess, A.G., Filippenko, A.V., \& Challis, P., et al. 1998, AJ, 116, 1009
-
-\bibitem[Riess et al.(2011)]{Riess2011}
-Riess, A.G., Macri, L., \& Casertano, S., et al. 2011, ApJ, 730, 119
-%A 3\% Solution: Determination of the Hubble Constant with the Hubble Space Telescope and Wide Field Camera
-
-\bibitem[Ross et al.(2012)]{2012MNRAS.424..564R} 
-Ross, A.J., Percival, W.J., \& S{\'a}nchez, A.G. et al.\ 2012, MNRAS, 424, 564
-
-\bibitem[Ross et al.(2015)]{MGS}
-Ross, A.J., Samushia, L., \& Howlett, C., et al. 2015, MNRAS, 449, 835
-
-\bibitem[Ryden(1995)]{Ryden1995}
-Ryden, B.S. 1995, ApJ, 452, 25
-
-%\bibitem[Samushia et al.(2014)]{Samushia2014}
-%Samushia, L., Reid, B. A., White, M., et al. 2014, MNRAS, 439, 3504
-
-%\bibitem[Sanchez et al.(2013)]{Sanchez2013}
-%Sanchez, A. G., Kazin, E. A., Beutler, F., et al. 2013, MNRAS, 433, 1202
-
-%\bibitem[Sutter et al.(2014)]{Sutter2014}
-%Sutter, P.M., Pisani, A., Wandelt, B.D., \& Weinberg, D.H. 2014, MNRAS, 443, 2983
-
-\bibitem[Sabiu (2013)]{kstat}
-C.G. Sabiu 2013
-https://bitbucket.org/csabiu/kstat
-http://ascl.net/code/v/1634
-
-\bibitem[Sanchez et al.(2016)]{Sanchez2016}
-Sanchez, A. G., Scoccimarro, R., \& Crocce, M., et al.
-arXiv:1607.03147
-
-\bibitem[Schlafly et al.(2010)]{Schlafly2010}
-Schlafly E.F., Finkbeiner D.P., Schlegel D.J., et al. 2010, ApJ, 725, 1175
-
-\bibitem[Schlafly \& Finkbeiner(2011)]{SF2011}
-Schlafly E.F., \& Finkbeiner D.P. 2011, ApJ, 737, 103
-
-%DESI:
-%http://arxiv.org/abs/1106.1706
-\bibitem[Schlegel et al.(2011)]{DESI}
-Schlegel, D., Abdalla, F., \& Abraham, T., et al. 2011, arXiv:1106.1706
-
-\bibitem[Smee et al.(2013)]{Smee2013}
-Smee, S.A., Gunn, J.E., \& Uomoto, A., et al. 2013, AJ, 146, 32
-
-\bibitem[Song et al.(2014)]{2014arXiv1407.2257S} 
-Song, Y.S., Sabiu, C.G., 
-Okumura, T., Oh, M., \& Linder, E.V.\ 2014, JCAP, 12, 005
-
-\bibitem[Speare et al. (2015)]{Speare2015}
-Speare, R., Gott, J.R., Kim, J., \& Park, C.
-2015, ApJ, 799, 176
-
-%\bibitem[Tojeiro \& Percival(2011)]{Tojeiro2011}
-%Tojeiro R., \& Percivial W.J. 2011, MNRAS, 417, 1114
-
-%\bibitem[Tojeiro et al.(2012)]{Tojeiro2012}
-%Tojeiro, R., Percival, W. J., Wake, D. A., et al. 2012, MNRAS, 424, 136
-
-\bibitem[Viana \& Liddle(1996)]{VL1996}
-Viana, P.T.P., \& Liddle, A.R. 1996, MNRAS, 281, 323
-
-\bibitem[Villalobos et al.(2013)]{V13}
-Villalobos, \'{A}., ́De Lucia, G., Weinmann, S.M., Borgani, S., \& Murante, G. 2013, MNRAS, 433, L49
-
-\bibitem[Weinberg (1989)]{SW1989}
-Weinberg, S. 1989, Reviews of Modern Physics, 61, 1
-
-\bibitem[White (2011)]{White2011}
-White M., et al. 2011, ApJ, 728, 126
-
-\bibitem[Yoo \& Watanabe(2012)]{2012IJMPD..2130002Y} Yoo, J., \& Watanabe, Y.\ 2012, International Journal of Modern Physics D, 21, 1230002
-
-\bibitem[York et al.(2000)]{York et al. 2000}
-York, D.G., Adelman, J., \& Anderson, J.E., et al. 2000, AJ, 120, 1579
-
-\bibitem[Zehavi et al.(2011)]{zehavi2011}
-Zehavi, I., Zheng, Z., \& Weinberg, D.H., et al. 2011, ApJ, 736, 59
 

### 2017-07-13 Draft/Draft0.8.tex
minor changes

--- 2017-07-13 Draft/Draft0.7.tex
@@
 Arman Shafieloo,$^{2}$
-Juhan Kim,$^{4,1}$
+Juhan Kim,$^{4}$
 and Sungwook E. Hong$^{2}$}
 
-  \affiliation{School of Physics, Korea Institute for Advanced Study, 85 Heogi-ro, Dongdaemun-gu, Seoul 130-722, Korea}
-  \affiliation{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 305-348, Korea}
+  \affiliation{School of Physics, Korea Institute for Advanced Study, 85 Heogi-ro, Dongdaemun-gu, Seoul 02455, Korea}
+  \affiliation{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 34055, Korea}
   \affiliation{National Astronomy Observatories, Chinese Academy of Science, Beijing, 100012, P.R.China}
-  \affiliation{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 130-722, Korea}
+  \affiliation{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 02455, Korea}
 
@@
 $\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ w_a = -0.07 \pm 0.29$ (68.3\% CL). 
-Addint our new AP measurements to the aforementioned results 
-reduces the error bars by 30-40\%,
+Adding our new AP measurements to the aforementioned results 
+reduces the error bars by $\sim$30-40\%,
 and reduces the area of $w_0-w_a$ contour by 50\%.
 The AP method can be combined with the standard BAO method,
-greatly increasing the power of ongoing and future galaxy surveys in probing dark energy.
+greatly increasing the power of ongoing and future galaxy surveys in probing dark energy, 
+improving the figure of merit constraints on $(w_0,w_a)$ by a factor of 2. 
 \end{abstract}
@@
 has allowed tight constraints to be placed on the background averaged distance scales, $D_A(z)$ and $H^{-1}(z)$.  
-Assuming an incorrect cosmological model for the coordinate transformation between redshift space and comoving space, produces residual geometric distortions in the resultant galaxy distribution. 
+Assuming an incorrect cosmological model for the coordinate transformation between redshift space and comoving space, produces residual geometric distortions in the resultant galaxy distribution, see  Fig.\ref{fig_xy}.
 These distortions are induced by the fact that measured distances along 
@@
 
-The main caveat in applying the AP test is due to the fact that 
+The main caveat in applying the AP test is that 
 the radial distances of galaxies are inferred from observed redshifts.
-Thus AP tests are inevitably affected by peculiar the motions of galaxies,
+Thus AP tests are inevitably affected by the peculiar motions of galaxies,
 which leads to apparent anisotropy in the clustering signal, even if the adopted cosmology is correct.
@@
 which is a major advance in extracting cosmological information 
-on small scales where galaxy clustering is strong and there are many independent structures.
+on small scales where galaxy clustering is strong and many independent structures exist.
 
@@
 So it was widely used in the literature to reconstruct dark energy from observations.
+Especially, the DETF figure of merit (FoM) is defined the reciprocal of the area of the error
+ellipse enclosing the 95\% confidence limit in the $w_0–w_a$ plane. 
+This quantity quantifies the progress in measuring the properties of dark energy.
+Larger FoM indicates greater accuracy.
 Fig.\ref{fig_xy} shows that redshift dependence of shape distortion is sensitive to both $w_0$ and $w_a$.
@@
 \begin{eqnarray}
- s_{\rm target} = s_{\rm fiducial} \sqrt{\alpha_{\parallel}^2 \mu_{\rm fiducial}+\alpha_{\bot}(1-\mu_{\rm fiducial}^2)}, \\
+ s_{\rm target} = s_{\rm fiducial} \sqrt{\alpha_{\parallel}^2 \mu_{\rm fiducial}+\alpha_{\bot}^2(1-\mu_{\rm fiducial}^2)}, \\
  \mu_{\rm target} = \mu_{\rm fiducial} \frac{\alpha_\parallel}
- {\sqrt{\alpha_{\parallel}^2 \mu_{\rm fiducial} +\alpha_{\bot}(1-\mu_{\rm fiducial}^2)}}
+ {\sqrt{\alpha_{\parallel}^2 \mu_{\rm fiducial} +\alpha_{\bot}^2(1-\mu_{\rm fiducial}^2)}}
 \end{eqnarray}
@@
    a fiducial cosmology $\Omega_m=0.26,\ w=-1.0$ for the measurement of 2pCF,
-   systematic effects estimated from HR4 simulations, 
-   and covariance estimated using 2,000 PATCHY mocks.
+   systematic effects estimated from Horizon Run 4 simulations, 
+   and covariance estimated using 2,000 MultiDark PATCHY mocks.
    When altering these options, the results remain robust (black contours).
@@
 the ``JLA'' SNIa sample \citep{JLA},
-and the Hubble Space Telescope measurement of $H_0=70.6\pm3.3$ \cite{Riess2011,E14H0}.
+and the Hubble Space Telescope measurement of $H_0=70.6\pm3.3$ km/s/Mpc \cite{Riess2011,E14H0}.
 These MCMC chains contain the CMB+BAO+SNIa+$H_0$ likelihood computed for $\sim$37,000 sets of cosmological parameters,
@@
 Adding our new AP constraints significantly reduces the allowable parameter space. 
-This can also be visualise as allowable bands in $w(z)$ as can be seen in the right panel of Fig.\ref{fig_con}.
+This can also be visualised as allowable bands in $w(z)$ as can be seen in the right panel of Fig.\ref{fig_con}.
 
@@
 and reduces the $w_0-w_a$ (95.4\% CL) contour by 50\%.
-This reveals the constraining power of the small scale AP effect for probing the redshift evolution of dark energy.
+This constitutes a significant increase in the figure of merit (FoM)  constraints on $(w_0, w_a)$.
+This doubling of the FoM($w_o,w_a$) comes at no additional cost or alteration to survey design, thus greatly improving the overall cost-benefit consideration of large cosmological redshift surveys.
 
 We performed a thorough test of all the possible variables in our methodology.
-Figure \ref{fig_contest} shows that 
+Fig.\ref{fig_contest} shows that 
 the result is unaffected by the line-of-sight $\mu$-cut, 
@@
 
-In summary, we previously proposed to constrain cosmological parameters via 
+We previously proposed to constrain cosmological parameters via 
 the redshift dependence of anisotropic galaxy clustering\cite{Li2016}.
@@
 
-The presented method of clustering shells can be applied to many spectroscopic galaxy surveys. 
-The method is complimentary to the BAO method and the two methods can be combined together, 
-increasing (by roughly twice) the power of ongoing and future surveys, with little to no additional cost.
+The presented method of clustering shells can be applied to many large spectroscopic galaxy surveys. 
+We show that figure of merit constraints on  $(w_0, w_a)$ can be increased by a factor of 2 when considering the small scale clustering shells information in combination with existing constraints.
+The analysis we perform requires no change to the typical survey strategy of large cosmological redshift surveys, thus we can increasing (by roughly twice) the power of ongoing and future surveys, with little to no additional cost.
 We expect this approach will play an important role in helping us unveiling the mystery of dark energy.

### 2017-07-13 Draft/Draft0.9.tex
minor changes

--- 2017-07-13 Draft/Draft0.8.tex
@@
 \title{Cosmological constraints from the redshift dependence of the Alcock-Paczynski effect: 
-constraining the linear evolution of dark energy}
+significant improvement in the dark energy figure of merit}
 
@@
 while improving upon earlier works \citep{Li2016}, 
-we present a novel use of the Alcock-Paczynski (AP) test via the small scales clustering difference between redshift bins. 
+we present a novel use of the Alcock-Paczynski (AP) test via clustering difference between redshift bins on scales of 6-40 $h^{-1}\rm Mpc$.
 This differential measure is shown to be a robust statistical tool that mitigates many systematic effects, 
 allowing for competitive and unbiased constrains to be placed on cosmological parameters.
-We find that our results, in combination with the CMB, BAO, SNIa and $H_0$ from Cepheid data yield, 
+We find that our results, in combination with the CMB, BAO, SNIa and $H_0$ from Cepheid data, yield
 $\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ w_a = -0.07 \pm 0.29$ (68.3\% CL). 
@@
 reduces the error bars by $\sim$30-40\%,
-and reduces the area of $w_0-w_a$ contour by 50\%.
-The AP method can be combined with the standard BAO method,
-greatly increasing the power of ongoing and future galaxy surveys in probing dark energy, 
-improving the figure of merit constraints on $(w_0,w_a)$ by a factor of 2. 
+%and reduces the area of $w_0-w_a$ contour by 50\%.
+and improves the dark energy figure of merit by a factor of 2. 
+The AP method can %be combined with the standard BAO method,
+greatly increase the power of ongoing and future galaxy surveys in probing dark energy.
 \end{abstract}
@@
 The  origin  of  the late-time accelerating  expansion  of  the  universe  is  one of  the  most  salient  questions  in  contemporary cosmology. 
-Theoretical explanations for this phenomena are many and range from a non-zero  vacuum energy and evolving  scalar  fields  remnant  from  the  big  bang, to modifications of Einstein's General Relativity\cite{2012IJMPD..2130002Y}.
-Considering the wealth of theoretical explanations, it is crucial to obtain precise and unbiased measurements of the expansion history of the Universe allowing us to 
+Theoretical explanations for this phenomena are many and range from a non-zero  vacuum energy and evolving  scalar  fields  remnant  from  the  big  bang, 
+to modifications of Einstein's General Relativity\cite{2012IJMPD..2130002Y}. 
+Considering the wealth of theoretical explanations, 
+it is crucial to obtain precise and unbiased measurements of the expansion history of the Universe allowing us to 
 differentiate between competing models.
@@
 has allowed tight constraints to be placed on the background averaged distance scales, $D_A(z)$ and $H^{-1}(z)$.  
-Assuming an incorrect cosmological model for the coordinate transformation between redshift space and comoving space, produces residual geometric distortions in the resultant galaxy distribution, see  Fig.\ref{fig_xy}.
+Assuming an incorrect cosmological model for the coordinate transformation between redshift space and comoving space
+produces residual geometric distortions in the resultant galaxy distribution (see  Fig.\ref{fig_xy}). 
 These distortions are induced by the fact that measured distances along 
@@
 
-In an effort to minimise RSD contamination, the shape of void regions\cite{Ryden1995,LavausWandelt1995}  has been 
+In an effort to minimize RSD contamination, the shape of void regions\cite{Ryden1995,LavausWandelt1995}  has been 
 proposed as an AP probe.
@@
 In a later work\cite{Li2015}, we developed an AP methodology 
-that utilises the redshift dependence of the galaxy 2-point correlation function (2pCF), 
+that utilizes the redshift dependence of the galaxy 2-point correlation function (2pCF), 
 measured as a function of angle between the galaxy pair and line-of-sight (LoS).
@@
 So it was widely used in the literature to reconstruct dark energy from observations.
-Especially, the DETF figure of merit (FoM) is defined the reciprocal of the area of the error
-ellipse enclosing the 95\% confidence limit in the $w_0–w_a$ plane. 
-This quantity quantifies the progress in measuring the properties of dark energy.
-Larger FoM indicates greater accuracy.
+The constraining power is usually quantified by the DETF (Dark Energy Task Force) \cite{DETF} figure of merit, 
+defined as the reciprocal of the area of the error ellipse enclosing the 95\% confidence limit (CL) in the $w_0-w_a$ plane. 
 Fig.\ref{fig_xy} shows that redshift dependence of shape distortion is sensitive to both $w_0$ and $w_a$.
@@
    \caption{\label{fig_TpCF}
-   Spliting the SDSS galaxies into six redshiftbins, and measuring the correlation function.
+   Splitting the SDSS galaxies into six redshift bins, and measuring the correlation function.
    Left panel: We split the BOSS DR12 galaxies into six redshift bins to measure the evolution of shape distortion.
@@
 with $s_{\rm min}=6 h^{-1} {\rm Mpc},\ s_{\rm max}=40 h^{-1} {\rm Mpc}$.
-We then normalise these {\em clustering shells} as 
+We then normalize these {\em clustering shells} as 
 $\hat\xi_{\Delta s}(\mu) \equiv \frac{\xi_{\Delta s}(\mu)}{\int_{0}^{\mu_{\rm max}}\xi_{\Delta s}(\mu)\ d\mu}$
@@
 However, the shape of the tilted lines remain similar at different redshifts, a fact that enables us  to mitigate the RSD effect by focusing on the redshift dependence of the anisotropic clustering signal.
-The ``correct'' cosmological model is selected by minimising the amount of redshift evolution of $\hat\xi_{\Delta s}$,
+The ``correct'' cosmological model is selected by minimizing the amount of redshift evolution of $\hat\xi_{\Delta s}$,
 via a $\chi^2$ function of 
@@
 $(\Omega_{b},\Omega_{m},\Omega_\Lambda,h,\sigma_8,n_s)$  = (0.044, 0.26, 0.74, 0.72, 0.79, 0.96). 
+As presented in \cite{Li2016}, the value of $\left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right]_{\rm sys}$
+(mainly comes from redshift evolution of RSD and galaxy bias)
+reaches 4-6\% at the highest redshift bin,
+and is minor ($\lesssim2\%$) at the other redshift bins.
 Mock galaxy samples are produced using a modified version of the one-to-one correspondence scheme \citep{hong2016}. 
@@
 are adequately corrected \citep{Hartlap,Percival2014}.
+
+\begin{figure*}
+   \centering{
+   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
+   \includegraphics[height=5cm,natwidth=6,natheight=4.5]{figCPL_b.pdf}
+   %\includegraphics[width=5.5cm,natwidth=4,natheight=4]{figCPL_b_BAOSNIaAP.pdf}
+   \includegraphics[height=5cm,natwidth=6,natheight=4.5]{figCPL_d.pdf}
+   %\includegraphics[height=8cm]{fig2b.pdf}
+%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
+%    \includegraphics[height=8cm]{smu.eps}
+   }
+   \caption{\label{fig_con}
+   Cosmological constraints on the CPL dark energy parametrization $w=w_0+w_a\frac{z}{1+z}$.
+   Left panel: 68.3\%, 95.4\% CL likelihood contours in the  $w_0-w_a$ plane.
+   %Results are consistent with $\Lambda$CDM.
+   The constrained area is significantly reduced after combined with the AP method.
+   %This shows the power of the AP method in constraining dynamical dark energy.
+   %Middle panel: $w_0-w_a$ likelihood contours using datasets of CMB+BAO, CMB+BAO+SNIa+$H_0$ and CMB+BAO+AP+$H_0$.
+   %When combined with CMB+BAO, AP method yields much tighter constraints than SNIa.
+   Right panel: Redshift evolution of $w(z)$, with/without adding the AP constraint.
+   Adding AP tightens the constraints and reduces the redshift evolution of $w$ (tilt of $w(z)$).
+   }
+\end{figure*}
+
+%Covariance matrix
+
+\begin{figure*}
+   \centering{
+   \includegraphics[width=14cm,natwidth=6,natheight=5]{fig_con_tests.pdf}
+   %\includegraphics[width=9cm,natwidth=4,natheight=4]{fig2b.pdf}
+   %\includegraphics[height=8cm]{fig2b.pdf}
+%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
+%    \includegraphics[height=8cm]{smu.eps}
+   }
+   \caption{\label{fig_contest}
+   Robustness test of the results.
+   For the ``default'' constraints (pink contours) are derived using six redshift bins, 
+   $\mu_{\rm max}=0.97$, $n_{\mu}=15-20$, $s=6-40 \rm Mpc/h$,
+   a fiducial cosmology $\Omega_m=0.26,\ w=-1.0$ for the measurement of 2pCF,
+   systematic effects estimated from Horizon Run 4 simulations, 
+   and covariance estimated using 2,000 MultiDark PATCHY mocks.
+   When altering these options, the results remain robust (black contours).
+   }
+\end{figure*}
 
@@
 $\hat\xi_{\Delta s}(\mu)$ in a non-fiducial cosmology suffers from
-an error of $\lesssim0.5\%$, which is 10 times smaller than 
-the statistical noise.
+an error of $\lesssim0.5\%$, which is 10 times smaller than the statistical noise.
 We checked that the approximate method can reproduce the results presented in \cite{Li2016} quite well.
+
+%It should be mentioned that simply using a linear interpolation to infer the values of $\xi$ in a new cosmology does {\it not} work.
+%The interpolation introduces an artificial smoothing in the inferred $\xi$, and reduces the
 
@@
 {\it Results.}---
-
-\begin{figure*}
-   \centering{
-   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
-   \includegraphics[height=6cm,natwidth=6,natheight=4.5]{figCPL_b.pdf}
-   %\includegraphics[width=5.5cm,natwidth=4,natheight=4]{figCPL_b_BAOSNIaAP.pdf}
-   \includegraphics[height=6cm,natwidth=6,natheight=4.5]{figCPL_d.pdf}
-   %\includegraphics[height=8cm]{fig2b.pdf}
-%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
-%    \includegraphics[height=8cm]{smu.eps}
-   }
-   \caption{\label{fig_con}
-   Cosmological constraints on the CPL dark energy parametrization $w=w_0+w_a\frac{z}{1+z}$.
-   Left panel: 68.3\%, 95.4\% CL likelihood contours in the  $w_0-w_a$ plane.
-   %Results are consistent with $\Lambda$CDM.
-   The constrained area is significantly reduced after combined with the AP method.
-   %This shows the power of the AP method in constraining dynamical dark energy.
-   %Middle panel: $w_0-w_a$ likelihood contours using datasets of CMB+BAO, CMB+BAO+SNIa+$H_0$ and CMB+BAO+AP+$H_0$.
-   %When combined with CMB+BAO, AP method yields much tighter constraints than SNIa.
-   Right panel: Redshift evolution of $w(z)$, with/without adding the AP constraint.
-   Adding AP tightens the constraints and reduces the redshift evolution of $w$ (tilt of $w(z)$).
-   }
-\end{figure*}
-
-%Covariance matrix
-
-\begin{figure*}
-   \centering{
-   \includegraphics[width=16cm,natwidth=6,natheight=5]{fig_con_tests.pdf}
-   %\includegraphics[width=9cm,natwidth=4,natheight=4]{fig2b.pdf}
-   %\includegraphics[height=8cm]{fig2b.pdf}
-%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
-%    \includegraphics[height=8cm]{smu.eps}
-   }
-   \caption{\label{fig_contest}
-   Robustness test of the results.
-   For the ``default'' constraints (pink contours) are derived using six redshift bins, 
-   $\mu_{\rm max}=0.97$, $n_{\mu}=15-20$, $s=6-40 \rm Mpc/h$,
-   a fiducial cosmology $\Omega_m=0.26,\ w=-1.0$ for the measurement of 2pCF,
-   systematic effects estimated from Horizon Run 4 simulations, 
-   and covariance estimated using 2,000 MultiDark PATCHY mocks.
-   When altering these options, the results remain robust (black contours).
-   }
-\end{figure*}
 
@@
 yielding constraints of %$ \Omega_m = 0.309 \pm 0.010, w_0 = -0.938 \pm 0.109, w_a = -0.38 \pm 0.41$.
-\begin{eqnarray}
- \Omega_m &=& 0.309 \pm 0.010,  \\ \nonumber
- w_0 &=& -0.938 \pm 0.109,  \\ \nonumber
- w_a &=& -0.38 \pm 0.41.
-\end{eqnarray}
+%\begin{eqnarray}
+% \Omega_m &=& 0.309 \pm 0.010,  \\ \nonumber
+% w_0 &=& -0.938 \pm 0.109,  \\ \nonumber
+% w_a &=& -0.38 \pm 0.41.
+%\end{eqnarray}
+\small
+\begin{equation}
+ \Omega_m = 0.309 \pm 0.010,\
+ w_0 = -0.938 \pm 0.109,\
+ w_a = -0.38 \pm 0.41.
+\end{equation}
+\normalsize
 %To derive the constraints combined with our AP method,
@@
 we derive the CMB+BAO+SNIa+$H_0$+AP constraints on CPL parameters, %$\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29$.
-\begin{eqnarray}
-\Omega_m &=& 0.301 \pm 0.008, \\ \nonumber
-w_0 &=& -1.042 \pm 0.067, \\ \nonumber
-w_a &=& -0.07 \pm 0.29.
-\end{eqnarray}
+%\begin{eqnarray}
+%\Omega_m &=& 0.301 \pm 0.008, \\ \nonumber
+%w_0 &=& -1.042 \pm 0.067, \\ \nonumber
+%w_a &=& -0.07 \pm 0.29.
+%\end{eqnarray}
+\small
+\begin{equation}
+ \Omega_m = 0.301 \pm 0.008,\
+ w_0 = -1.042 \pm 0.067,\
+ w_a = -0.07 \pm 0.29.
+\end{equation}
+\normalsize
 While the central values of parameters do not shift appreciably,
@@
 
-The marginalised constraints on $w_0-w_a$ are shown in the left panel of Fig.\ref{fig_con}.
+The marginalized constraints on $w_0-w_a$ are shown in the left panel of Fig.\ref{fig_con}.
 Adding our new AP constraints significantly reduces the allowable parameter space. 
-This can also be visualised as allowable bands in $w(z)$ as can be seen in the right panel of Fig.\ref{fig_con}.
+This can also be visualized as allowable bands in $w(z)$ as can be seen in the right panel of Fig.\ref{fig_con}.
 
@@
 and reduces the $w_0-w_a$ (95.4\% CL) contour by 50\%.
-This constitutes a significant increase in the figure of merit (FoM)  constraints on $(w_0, w_a)$.
-This doubling of the FoM($w_o,w_a$) comes at no additional cost or alteration to survey design, thus greatly improving the overall cost-benefit consideration of large cosmological redshift surveys.
+This constitutes a significant increase in the figure of merit constraints on $(w_0, w_a)$. 
+This doubling of the figure of merit comes at no additional cost or alteration to survey design, 
+thus greatly improving the overall cost-benefit consideration of large cosmological redshift surveys.
 
@@
 %or reduce the number of mocks to 1000.
+The result does not change significantly if we remove the highest redshift bin,
+where the estimated systematics is comparably large.
 The most striking point to note in our testing is that the 
@@
 Since it works with the redshift evolution of the anisotropic clustering signal it significantly reduces the effect of systematics. 
-It avoids the great difficulty in accurate modelling of the RSD, non-linear clustering and galaxy bias.
-It is applicable on much smaller scales, allowing for the inclusion of more $k$-modes and hence more information.
+It avoids the great difficulty in accurate modeling of the RSD, non-linear clustering and galaxy bias.
+It is applicable on much smaller clustering scales, allowing for the inclusion of more $k$-modes and hence more information.
 
-The presented method of clustering shells can be applied to many large spectroscopic galaxy surveys. 
-We show that figure of merit constraints on  $(w_0, w_a)$ can be increased by a factor of 2 when considering the small scale clustering shells information in combination with existing constraints.
-The analysis we perform requires no change to the typical survey strategy of large cosmological redshift surveys, thus we can increasing (by roughly twice) the power of ongoing and future surveys, with little to no additional cost.
+We believe that the presented method of clustering shells will be applied to many spectroscopic galaxy surveys. 
+The current figure of merit constraints on $(w_0, w_a)$ is increased by a factor of 2 
+when considering the small scale clustering shells information in combination with existing constraints. 
+The analysis we perform requires no change to the typical survey strategy of large cosmological redshift surveys, 
+thus we can increasing (by roughly twice) the power of ongoing and future surveys, with little to no additional cost.
 We expect this approach will play an important role in helping us unveiling the mystery of dark energy.
+
+\
 
@@
 We thank Stephen Appleby, Seokcheon Lee, Maurice van Putten, Graziano Rossi and Yi Wang for helpful discussions.
+
+Based on observations obtained with Planck (http://www.esa.int/Planck), 
+an ESA science mission with instruments and contributions directly funded by 
+ESA Member States, NASA, and Canada.
+
+Funding for SDSS-III has been provided by the Alfred P. Sloan Foundation, the Participating Institutions, the
+National Science Foundation, and the U.S. Department of Energy Office of Science. 
+The SDSS-III web site is http://www.sdss3.org/. 
+SDSS-III is managed by the Astrophysical Research Consortium for the Participating Institutions
+of the SDSS-III Collaboration.
 \end{acknowledgments}
@@
 
+\bibitem{DETF}
+Albrecht, A., Bernstein, G., \& Cahn, R., et al. [astro-ph/0609591].
+
 \bibitem{Reidetal:2016}%[Reid et al.(2016)]
@@
 Kim, J., Park, C., L'Huillier, B., \& Hong, S. E. 2015, JKAS, 48, 213
+
+\bibitem{komatsu2011}%[Komatsu et al.(2011)]
+Komatsu, E., Smith, K. M., \& Dunkley, J., et al. 2011, ApJS, 192, 18
 
@@
 \bibitem{Hartlap}%[Hartlap et al.(2006)]
-Hartlap J., Simon P. \& Schneider P. [astro-ph/0608064].
+Hartlap, J., Simon, P., \& Schneider, P. [astro-ph/0608064].
 
@@
 
-\bibitem{komatsu2011}%[Komatsu et al.(2011)]
-Komatsu, E., Smith, K. M., \& Dunkley, J., et al. 2011, ApJS, 192, 18
-
 \end{thebibliography}

### 2017-09-27 Draft/Draft1.0.tex
minor changes

--- 2017-07-13 Draft/Draft0.9.tex
@@
 \begin{abstract}
-We use the small scale anisotropic clustering signal of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
+We use the anisotropic clustering signal of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
 12, spanning the redshift range $0.15<z<0.69$ to place constraints on the expansion history of the Universe. 
@@
 These distortions are induced by the fact that measured distances along 
-and perpendicular to the line of sight are fundamentally different. 
+and perpendicular to the line of sight are connected with cosmological parameters differently. 
 Measuring the ratio of galaxy clustering in the radial and transverse directions provides a probe of this AP effect.
@@
    \caption{\label{fig_TpCF}
-   Splitting the SDSS galaxies into six redshift bins, and measuring the correlation function.
+   Splitting the SDSS galaxies into six redshift bins, and measuring the correlation function
+   (similar figures already presented in \cite{Li2016}).
    Left panel: We split the BOSS DR12 galaxies into six redshift bins to measure the evolution of shape distortion.
@@
    and covariance estimated using 2,000 MultiDark PATCHY mocks.
-   When altering these options, the results remain robust (black contours).
+   When we alters one of these options by using $\mu_{\rm max}=0.99$, 
+   $\mu_{\rm max}=0.85$, $n_{\mu}=15-20$, $s=8-30 \rm Mpc/h$, 
+   a fiducial cosmology of $\Omega_m=0.26,\ w=-0.6$, 
+   excluding the last redshift bin in the analysis, 
+   discarding the systematics correction, 
+   or reducing the number of mocks in the estimation of covariance matrix,
+   the results remain robust (black contours).
    }
@@
 \begin{eqnarray}
- s_{\rm target} = s_{\rm fiducial} \sqrt{\alpha_{\parallel}^2 \mu_{\rm fiducial}+\alpha_{\bot}^2(1-\mu_{\rm fiducial}^2)}, \\
+ s_{\rm target} = s_{\rm fiducial} \sqrt{\alpha_{\parallel}^2 \mu_{\rm fiducial}^2+\alpha_{\bot}^2(1-\mu_{\rm fiducial}^2)}, \\
  \mu_{\rm target} = \mu_{\rm fiducial} \frac{\alpha_\parallel}
- {\sqrt{\alpha_{\parallel}^2 \mu_{\rm fiducial} +\alpha_{\bot}^2(1-\mu_{\rm fiducial}^2)}}
+ {\sqrt{\alpha_{\parallel}^2 \mu_{\rm fiducial}^2 +\alpha_{\bot}^2(1-\mu_{\rm fiducial}^2)}}
 \end{eqnarray}
@@
 In the fiducial cosmology
-we measure $\xi(s,\mu)$ in an ultra high resolution of
+we measure $\xi(s,\mu)$ with a high resolution of
 $\Delta s = 0.2 {\rm Mpc/h}$, $\Delta \mu = 1/600$,
@@
 \normalsize
-While the central values of parameters do not shift appreciably,
+%While the central values of parameters do not shift appreciably,
+As a result of the additional constraint from our AP analysis,
 the error bars of $w_0$ and $w_a$ are reduced by 38.4\% and 29.7\%, respectively.% $$-40\%$ by adding our method into the analysis.
+It can be also noted that the central value of $w_a$ moved to zero appreciably.
 
@@
 This constitutes a significant increase in the figure of merit constraints on $(w_0, w_a)$. 
-This doubling of the figure of merit comes at no additional cost or alteration to survey design, 
+This doubling of the figure of merit comes at no additional cost or alteration to data size, 
 thus greatly improving the overall cost-benefit consideration of large cosmological redshift surveys.
@@
 where the estimated systematics is comparably large.
-The most striking point to note in our testing is that the 
-shift in contour position is very small even when we do not include the systematic correction.
-This is reassuring, since we may have worried that {\it cosmological dependence} 
-of the systematic correction could influence the final result.
+The most striking point to note in our test is that the 
+shift in contour position is very small even when %we do not include the systematic correction.
+the systematics are not corrected.
+%This is reassuring, since we may have worried that {\it cosmological dependence} 
+%of the systematic correction could influence the final result. 
+This indicates that, for the data analysis of current galaxy surveys,
+the systematic effects in our method may not be important.
+But it remains to be seen if this is true for future galaxy surveys,
+or when the cosmology dependence of the systematics effects is taken into account.
 
@@
 
-We previously proposed to constrain cosmological parameters via 
+In recent studies we have proposed to constrain cosmological parameters 
+governing the expansion history of the universe via 
 the redshift dependence of anisotropic galaxy clustering\cite{Li2016}.
 This approach enables a robust AP test on relatively small scales.
-In this paper we improved the methodology and obtained tight constraints on the CPL parametrization of dark energy.
+In this paper we improved the methodology and obtained a tight constraint 
+on the CPL parametrization of dark energy.
 %using 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
@@
 
-The AP method presented in this work has many advantages over the `traditional' galaxy clustering method.
+The AP method presented in this work has many advantages over the 
+`traditional' methods using galaxy clustering.
 Since it works with the redshift evolution of the anisotropic clustering signal it significantly reduces the effect of systematics. 
 It avoids the great difficulty in accurate modeling of the RSD, non-linear clustering and galaxy bias.
-It is applicable on much smaller clustering scales, allowing for the inclusion of more $k$-modes and hence more information.
+%It is applicable on much smaller clustering scales, allowing for the inclusion of more $k$-modes and hence more information. 
+Our method can use the galaxy clustering signal down to
+much smaller scales compared to other methods,
+providing much higher statistics.
 
-We believe that the presented method of clustering shells will be applied to many spectroscopic galaxy surveys. 
-The current figure of merit constraints on $(w_0, w_a)$ is increased by a factor of 2 
-when considering the small scale clustering shells information in combination with existing constraints. 
-The analysis we perform requires no change to the typical survey strategy of large cosmological redshift surveys, 
-thus we can increasing (by roughly twice) the power of ongoing and future surveys, with little to no additional cost.
-We expect this approach will play an important role in helping us unveiling the mystery of dark energy.
+Combining our method with the CMB+SNIa+BAO+$H_0$ datasets,
+the dark energy figure of merit is improved by a factor of 2.
+%The method can be applied to many spectroscopic galaxy surveys.
+We expect the method will play an important role in deriving cosmological constraints from future spectroscopic galaxy surveys.
 
@@
 \begin{acknowledgments}
-We thank the Korea Institute for Advanced Study for providing computing resources (KIAS Center for Advanced Computation Linux Cluster System).
+We thank Korea Institute for Advanced Study for providing computing resources (KIAS Center for Advanced Computation Linux Cluster System).
 CGS acknowledges support from the National Research Foundation (NRF,  \#2017R1D1A1B03034900). 

### 2017-09-27 Draft/Draft1.1.tex
minor changes

--- 2017-09-27 Draft/Draft1.0.tex
@@
-%\documentclass[preprint,prd,aps,amsmath,amssymb,nofootinbib]{revtex4}
-%\documentclass[prd,aps,amsmath,amssymb,nofootinbib]{revtex4}
-%\documentclass[aps,twocolumn,showpacs,floatfix,superscriptaddress]{revtex4}
-\documentclass[prl,twocolumn,superscriptaddress,aps,amsmath,amssymb,nofootinbib,altaffilletter]{revtex4}
-%\documentclass[prl,superscriptaddress,twocolumn,nopreprintnumbers,floatfix,preprintnumbers,altaffilletter]{revtex4}
+%%% On-going present
+%%
+%% Beginning of file 'sample.tex'
+%%
+%% Modified 2005 December 5
+%%
+%% This is a sample manuscript marked up using the
+%% AASTeX v5.x LaTeX 2e macros.
 
-\usepackage{graphicx}
-\usepackage{subfigure}
-\usepackage{bm}
-\usepackage{amsmath}
-\usepackage{array}
-\usepackage{multirow}
-\usepackage{float}
-\usepackage{color}
-\graphicspath{{figs/}}
+%% The first piece of markup in an AASTeX v5.x document
+%% is the \documentclass command. LaTeX will ignore
+%% any data that comes before this command.
+
+%% The command below calls the preprint style  
+%% which will produce a one-column, single-spaced document.
+%% Examples of commands for other substyles follow. Use
+%% whichever is most appropriate for your purposes.
+%%
+%%\documentclass[12pt,preprint]{aastex}
+
+%% manuscript produces a one-column, double-spaced document:
+
+%%\documentclass[manuscript]{aastex}
+
+%% preprint2 produces a double-column, single-spaced document:
+
+ %\documentclass[preprint2]{aastex}
+%\documentclass[preprint2]{aastex}
+%\documentclass[manuscript]{aastex}
+\documentclass[iop]{emulateapj}
+\renewcommand{\baselinestretch}{0.95}
+%% Sometimes a paper's abstract is too long to fit on the
+%% title page in preprint2 mode. When that is the case,
+%% use the longabstract style option.
+
+%% \documentclass[preprint2,longabstract]{aastex}
+
+%% If you want to create your own macros, you can do so
+%% using \newcommand. Your macros should appear before
+%% the \begin{document} command.
+%%
+%% If you are submitting to a journal that translates manuscripts
+%% into SGML, you need to follow certain guidelines when preparing
+%% your macros. See the AASTeX v5.x Author Guide
+%% for information.
+
+\usepackage{enumitem}
+
+\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm
+        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$~}\fi}} 
+\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}
+\def\be{\begin{equation}}
+\def\ee{\end{equation}}
+\def\ba{\begin{eqnarray}}
+\def\ea{\end{eqnarray}}
+
+%% You can insert a short comment on the title page using the command below.
+
+%\slugcomment{Not to appear in Nonlearned J., 45.}
+
+%% If you wish, you may supply running head information, although
+%% this information may be modified by the editorial offices.
+%% The left head contains a list of authors,
+%% usually a maximum of three (otherwise use et al.).  The right
+%% head is a modified title of up to roughly 44 characters.
+%% Running heads will not print in the manuscript style.
+
+%\title[]
+%{}
+
+\shorttitle{Significantly improved dark energy figure of merit from reshift dependence of AP effect}
+\shortauthors{X.-D. Li, C. Park, C.G. Sabiu, H. Park, D.H. Weinberg, J. Kim, S.E. Hong}
+
+%% This is the end of the preamble.  Indicate the beginning of the
+%% paper itself with \begin{document}.
 
 \begin{document}
+
+%% LaTeX will automatically break titles if they run longer than
+%% one line. However, you may use \\ to force a line break if
+%% you desire.
 
@@
 
-\author{ 
-Xiao-Dong Li,$^{1}$
-Cristiano G. Sabiu,$^{2}$
-Changbom Park,$^{1}$
-Yuting Wang,$^{3}$
-Gong-bo Zhao,$^{3}$
-Hyunbae Park,$^{2}$
-Arman Shafieloo,$^{2}$
-Juhan Kim,$^{4}$
-and Sungwook E. Hong$^{2}$}
+%\author{Xiao-Dong~Li\altaffilmark{1}, Changbom~Park\altaffilmark{1}, J.~E.~Forero-Romero\altaffilmark{2} and Juhan Kim%\altaffilmark{3}}
+%\affil{\altaffilmark{1}School of Physics, Korea Institute for Advanced Study, Heogiro 85, Seoul 130-722, Korea }
+%\affil{\altaffilmark{2}Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, %Colombia}
+%\affil{\altaffilmark{3}Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-%gu, Seoul 130-722, Korea }
+%\affil{\it (xiaodongli@kias.re.kr, cbp@kias.re.kr, je.forero@uniandes.edu.co, kjhan@kias.re.kr)}
 
-  \affiliation{School of Physics, Korea Institute for Advanced Study, 85 Heogi-ro, Dongdaemun-gu, Seoul 02455, Korea}
-  \affiliation{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 34055, Korea}
-  \affiliation{National Astronomy Observatories, Chinese Academy of Science, Beijing, 100012, P.R.China}
-  \affiliation{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 02455, Korea}
+%\author[Xiao-Dong~Li, Changbom~Park, Cristiano G. Sabiu, Juhan Kim and Sungwook E. Hong]
+%{ Xiao-Dong Li$^{1,\dagger}$, Changbom Park$^{1}$, Cristiano G. Sabiu$^{2}$, Juhan Kim$^{3,1,\star}$, Sungwook E. Hong$^{1}$\\
+%$^1$School of Physics, Korea Institute for Advanced Study, 85 Heogi-ro, Dongdaemun-gu, Seoul 130-722, Korea\\
+%$^2$Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 305-348, Korea\\
+%$^3$Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 130-722, Korea\\
+%$^{\dagger}$xiaodongli@kias.re.kr\\
+%$\star$Corresponding Author: ***@kasi.re.kr}
+
+\author{Xiao-Dong Li,}
+\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
+\author{Cristiano G. Sabiu,}
+\affil{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 34055, Korea}
+\author{Changbom Park,}
+\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
+\author{Yuting Wang, Gong-bo Zhao}
+\affil{National Astronomy Observatories, Chinese Academy of Science, Beijing, 100012, P.R.China}
+\author{Hyunbae Park, Arman Shafieloo,}
+\affil{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 34055, Korea}
+\author{Juhan Kim,}
+\affil{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 02455, Korea}
+\author{and Sungwook E. Hong}
+\affil{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 34055, Korea}
+
+%\altaffiltext{1}{xiaodongli@kias.re.kr}
+%\altaffiltext{2}{cbp@kias.re.kr}
+%\altaffiltext{3}{csabiu@kasi.re.kr}
+%\altaffiltext{4}{\bf Hyunbae: your email}
+\altaffiltext{1}{Corresponding Author: kjhan@kias.re.kr}
+
+% \email{xiaodongli@kias.re.kr}
+% \email{cbp@kias.re.kr}
+% \email{je.forero@uniandes.edu.co}
+
+% \author{S. Djorgovski\altaffilmark{1,2,3} and Ivan R. King\altaffilmark{1}}
+% \affil{Astronomy Department, University of California,
+%     Berkeley, CA 94720}
+%
+% \author{C. D. Biemesderfer\altaffilmark{4,5}}
+% \affil{National Optical Astronomy Observatories, Tucson, AZ 85719}
+% \email{aastex-help@aas.org}
+%
+% \and
+%
+% \author{R. J. Hanisch\altaffilmark{5}}
+% \affil{Space Telescope Science Institute, Baltimore, MD 21218}
+%
+% %% Notice that each of these authors has alternate affiliations, which
+% %% are identified by the \altaffilmark after each name.  Specify alternate
+% %% affiliation information with \altaffiltext, with one command per each
+% %% affiliation.
+%
+% \altaffiltext{1}{Visiting Astronomer, Cerro Tololo Inter-American Observatory.
+% CTIO is operated by AURA, Inc.\ under contract to the National Science
+% Foundation.}
+% \altaffiltext{2}{Society of Fellows, Harvard University.}
+% \altaffiltext{3}{present address: Center for Astrophysics,
+%     60 Garden Street, Cambridge, MA 02138}
+% \altaffiltext{4}{Visiting Programmer, Space Telescope Science Institute}
+% \altaffiltext{5}{Patron, Alonso's Bar and Grill}
+
+%% Mark off your abstract in the ``abstract'' environment. In the manuscript
+%% style, abstract will output a Received/Accepted line after the
+%% title and affiliation information. No date will appear since the author
+%% does not have this information. The dates will be filled in by the
+%% editorial office after submission.
 
@@
 allowing for competitive and unbiased constrains to be placed on cosmological parameters.
+% The Alcock-Paczynski (AP) test was performed via the redshift dependence of clustering on scales of 6-40 $h^{-1}\rm Mpc$.
+% We improve the methodology of \citep{Li2016} by significantly reducing its computation time, 
+% which enables us to explore three or more cosmological parameters.
+% We applied the improved method on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$.
 We find that our results, in combination with the CMB, BAO, SNIa and $H_0$ from Cepheid data, yield
@@
 and improves the dark energy figure of merit by a factor of 2. 
+% We carefully checked the robustness of the results.
 The AP method can %be combined with the standard BAO method,
@@
 
-\pacs{95.36.+x, 98.80.–k}
-\maketitle
+%% Keywords should appear after the \end{abstract} command. The uncommented
+%% example has been keyed in ApJ style. See the instructions to authors
+%% for the journal to which you are submitting your paper to determine
+%% what keyword punctuation is appropriate.
+
+\keywords{large-scale structure of Universe --- dark energy --- cosmological parameters}
+
+%% From the front matter, we move on to the body of the paper.
+%% In the first two sections, notice the use of the natbib \citep
+%% and \citet commands to identify citations.  The citations are
+%% tied to the reference list via symbolic KEYs. The KEY corresponds
+%% to the KEY in the \bibitem in the reference list below. We have
+%% chosen the first three characters of the first author's name plus
+%% the last two numeral of the year of publication as our KEY for
+%% each reference.
+
+%% Authors who wish to have the most important objects in their paper
+%% linked in the electronic edition to a data center may do so by tagging
+%% their objects with \objectname{} or \object{}.  Each macro takes the
+%% object name as its required argument. The optional, square-bracket
+%% argument should be used in cases where the data center identification
+%% differs from what is to be printed in the paper.  The text appearing
+%% in curly braces is what will appear in print in the published paper.
+%% If the object name is recognized by the data centers, it will be linked
+%% in the electronic edition to the object data available at the data centers
+%%
+%% Note that for sources with brackets in their names, e.g. [WEG2004] 14h-090,
+%% the brackets must be escaped with backslashes when used in the first
+%% square-bracket argument, for instance, \object[\[WEG2004\] 14h-090]{90}).
+%%  Otherwise, LaTeX will issue an error.
+
+\section{Introduction}
 
@@
 
-%\section{Introduction}
-{\it Introduction.}---
 The  origin  of  the late-time accelerating  expansion  of  the  universe  is  one of  the  most  salient  questions  in  contemporary cosmology. 
@@
 $w_0$ determines the present-day value, while parameter $w_a$ characterizes the first-order derivative of $w$ with respect to $a$. 
+The possible redshift evolution of dark energy EoS is not considered in the analysis of \cite{Li2016}.
 
@@
 
-%\section{Methodology}\label{sec:method}
-{\it Methodology.}---
+%{\bf AMTB: Please chose one kind of tense of verbs. It changes from sentences to sentences!}
+%{\bf AMTB: How many mock BOSS samples are made from HR4?}
 
+\section{Methodology}
 The spectroscopic galaxy sample of SDSS-III BOSS (Baryon Oscillation Spectroscopic Survey) has two primary catalogues:
@@
 and ``translated'' to the measurements in a ``target'' cosmology using the relations, 
-\begin{eqnarray}
+\begin{eqnarray}\label{eq:smumap}
  s_{\rm target} = s_{\rm fiducial} \sqrt{\alpha_{\parallel}^2 \mu_{\rm fiducial}^2+\alpha_{\bot}^2(1-\mu_{\rm fiducial}^2)}, \\
@@
 and values of $D_A$ and $H$ are computed in the effective redshifts of the six redshift bins.
+%The left panel of Figure \ref{fig_method} shows how 
+%$\xi(s,\mu)$ is mapped from the fiducial cosmology to another cosmology using the above relations.
 In the fiducial cosmology
@@
 a correction is applied by computing the fraction of the overlapping area.
+%\footnote{A dense grid can effectively reduce the ``edge effect'' produced when we map $\xi(s,\mu)$ from one cosmology to another.
+%The edge effect would introduce artificial correlations between nearby pixels, smooth $\xi(s,\mu)$ a little bit, 
+%reduce the value of $\chi^2$, and change the obtained cosmological constriants.
+%We found that, using $\Delta s = 1 {\rm Mpc/h}$ and $\Delta \mu = 1/120$, 
+%the cosmological constraints of \cite{Li2016} can not be properly reproduced.}.
 
@@
 We checked that the approximate method can reproduce the results presented in \cite{Li2016} quite well.
+% We checked that the approximate method can reproduce the results of precise method quite well.
+% The right panel of Figure \cite{fig_method} shows the  $\Omega_m$-$w_0$ constraints obtained 
+%  using the precise and approximate 2pCFs (here we fix $w_a=0$). 
+%  They agree with each other quite well.
+
+%\begin{figure*}
+%   \centering{
+%   \includegraphics[width=6cm]{fig_smu.eps}
+%   \includegraphics[width=10.5cm]{fig_comp.eps}
+%   }
+%   \caption{\label{fig_method}
+%   Left panel: Mapping $\xi(s,\mu)$ from the fiducial cosmology to four other cosmologies. 
+% The number counts are measured in the fiducial cosmology in a uniform grid (blue dashed.
+%  Just for illustration; the grid adopted in real analysis is much denser).
+% In the four cosmologies with $(\Omega_m,w) = (0.31,-1.5),\ (0.31,-0.5),\ (0.41,-1.0)\ \rm and\ (0.21,-1.0)$, 
+% %due to the distortion of geometry,
+% the distribution of number counts in $(s, \mu)$ space becomes the red solid grid ({\bf Check}).
+% We utilize the mapping realtion to approximate the 2pCF in vaiours cosmologies, without re-conducting the 2pCF statistics. 
+% Right panel: Cosmological constraints in the $\Omega_m$-$w_0$ plane, with the value of $w_a$ fixed as zero.
+% Results obtained using the precise 2pCFs (gray filled) 
+% and approximate 2pCFs (blue solid) 2pCFs matches each other quite well.
+%   }
+%\end{figure*}
+
+%
 
@@
 
-%\section{Results}\label{sec:results}
-{\it Results.}---
+\section{Result}
 
@@
 The derived cosmological constraints are fully consistent with a cosmological constant dark energy component having no evolution.
+%\cite{Li2016} 
 Adding the new AP method to the CMB+BAO+SNIa+$H_0$ constraints reduces the statistical errors on many parameters by $\sim$30-40\% 
@@
 %\section{Conclusion}\label{sec:conclusion}
-{\it Conclusion.}---
+\section{Conclusion}
 
@@
 on the CPL parametrization of dark energy.
+%The derived cosmological constraints are fully consistent with a cosmological constant 
+%dark energy component having no redshift evolution.
+
 %using 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
@@
 
-\
+\section*{Acknowledgments}
 
-\begin{acknowledgments}
 We thank Korea Institute for Advanced Study for providing computing resources (KIAS Center for Advanced Computation Linux Cluster System).
@@
 SDSS-III is managed by the Astrophysical Research Consortium for the Participating Institutions
-of the SDSS-III Collaboration.
-\end{acknowledgments}
+of the SDSS-III Collaboration including the University of Arizona, the Brazilian Participation Group, Brookhaven
+National Laboratory, Carnegie Mellon University, University of Florida, the French Participation Group, 
+the German Participation Group, Harvard University, the Instituto de Astrofisica de Canarias, the Michigan State/Notre
+Dame/JINA Participation Group, Johns Hopkins University, Lawrence Berkeley National Laboratory, Max Planck
+Institute for Astrophysics, Max Planck Institute for Extraterrestrial Physics, New Mexico State University, New
+York University, Ohio State University, Pennsylvania State
+University, University of Portsmouth, Princeton University,
+the Spanish Participation Group, University of Tokyo, University of Utah, Vanderbilt University, University of Virginia, 
+University of Washington, and Yale University.
 
-%% After the acknowledgments section, use the following syntax and the
-%% \facility{} macro to list the keywords of facilities used in the research
-%% for the paper.  Each keyword will be checked against the master list during
-%% copy editing.  Individual instruments or configurations can be provided
-%% in parentheses, after the keyword, but they will not be verified.
+\
 
-%{\it Facilities:} \facility{Nickel}, \facility{HST (STIS)}, \facility{CXO (ASIS)}.
+\
 
-%% Appendix material should be preceded with a single \appendix command.
-%% There should be a \section command for each appendix. Mark appendix
-%% subsections with the same markup you use in the main body of the paper.
-
-%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
-%% The equation counter will reset when it encounters the \appendix
-%% command and will number appendix equations (A1), (A2), etc.
-
-%% The reference list follows the main body and any appendices.
-%% Use LaTeX's thebibliography environment to mark up your reference list.
-%% Note \begin{thebibliography} is followed by an empty set of
-%% curly braces.  If you forget this, LaTeX will generate the error
-%% "Perhaps a missing \item?".
-%%
-%% thebibliography produces citations in the text using \bibitem-\cite
-%% cross-referencing. Each reference is preceded by a
-%% \bibitem command that defines in curly braces the KEY that corresponds
-%% to the KEY in the \cite commands (see the first section above).
-%% Make sure that you provide a unique KEY for every \bibitem or else the
-%% paper will not LaTeX. The square brackets should contain
-%% the citation text that LaTeX will insert in
-%% place of the \cite commands.
-
-%% We have used macros to produce journal name abbreviations.
-%% AASTeX provides a number of these for the more frequently-cited journals.
-%% See the Author Guide for a list of them.
-
-%% Note that the style of the \bibitem labels (in []) is slightly
-%% different from previous examples.  The natbib system solves a host
-%% of citation expression problems, but it is necessary to clearly
-%% delimit the year from the author name used in the citation.
-%% See the natbib documentation for more details and options.
-
-%\bibitem[Canizares et al.(1978)]{can78} Canizares, C. R.,
-%    Grindlay, J. E., Hiltner, W. A., Liller, W., \&
-%    McClintock, J. E.  1978, \apj, 224, 39
-
-%Wang Q H, Lindon O, Hardle W. 
-%Semiparametric regression analysis with missing response at random. 
-%J Am Stat Assoc, 2004, 99: 334－345
+\
 
 \begin{thebibliography}{}
-%\citep{Riess:1998}
-%[astro-ph/0205436].
-\bibitem{Li2016}%[Li et al.(2016)]
+
+\bibitem[Ade et al. (2015)]{Planck2015}
+Ade, P.A.R., Aghanim, N., \& Arnaud, M., et al. arXiv:1502.01589
+
+\bibitem[Alam et al.(2016)]{Alam2016}
+Alam, S., Ata, M., \& Bailey, S., et al. 2016,
+submitted to MNRAS (arXiv:1607.03155)
+
+\bibitem[Albrecht et al.(2006)]{DETF}
+Albrecht, A., Bernstein, G., \& Cahn, R., et al. 2006. [astro-ph/0609591].
+
+%\bibitem[{{Alam} {et~al}\mbox{.}(2015{\natexlab{a}}){Alam}, {Albareti},
+%  {Allende Prieto}, {Anders}, {Anderson}, {Anderton}, {Andrews}, {Armengaud},
+%  {Aubourg}, {Bailey}, \& et~al.}]{dr12}
+%{Alam} S., Albareti, F.D.,\& Allende Prieto, C., {et~al.}, 2015,  ApJS, 219, 12
+
+\bibitem[Alcock \& Paczynski(1979)]{AP1979}
+Alcock, C., \& Paczynski, B. 1979, Nature, 281, 358
+
+%\bibitem[Anderson et al.(2012)]{2012MNRAS.427.3435A} 
+%Anderson, L., Aubourg, E., Bailey, S., et al.\ 2012, MNRAS, 427, 3435
+
+\bibitem[Anderson et al.(2013)]{Anderson2013}
+Anderson, L., Aubourg, \'E., \& Bailey, S. et al. 2014, MNRAS, 441, 24
+
+%\bibitem[Bassett et al.(2002)]{Bassett2002}
+%Bassett, B.A., Kunz, M., Silk, J., \& Ungarelli, C. 2002, MNRAS, 336, 1217
+
+\bibitem[Ballinger, Peacock \& Heavens 1996]{Ballinger1996}
+Ballinger, W.E., Peacock, J.A., \& Heavens, A.F. 1996, MNRAS, 282, 877
+
+\bibitem[Betoule et al.(2014)]{JLA}
+Betoule, M., Kessler, R., \& Guy, J., et al. 2014, A\&A, 568, 32
+
+\bibitem[Beutler et al.(2011)]{6dFGS}
+Beutler, F., Blake, C., \& Colless, M., et al. 2011, MNRAS, 416, 3017
+
+%\bibitem[Beutler et al.(2013)]{Beutler2013}
+%Beutler, F., Saito, S., \& Seo, H.-J., et al. 2013, MNRAS, 443, 1065
+
+%\bibitem[Beutler et al.(2016)]{Beutler2016}
+%Beutler, F., Seo, H.-J., \& Saito, S., et al. 2016,
+%arXiv:1607.03150
+
+\bibitem[Blake et al.(2011)]{Blake2011}
+Blake, C., Glazebrook, K., \& Davis, T. M., 2011, MNRAS, 418, 1725
+
+%\bibitem[Blake et al.(2013)]{WiggleZtopoloy}
+%Blake, C., James, J.B., \& Poole, G.B. 2013, MNRAS, 437, 2488
+
+%\bibitem[Bolton et al.(2012)]{Bolton2012}
+%Bolton, A.S., Schlegel, \& D.J., Aubourg E., et al. 2012, AJ, 144, 144
+
+%\bibitem[Boylan-Kolchin et al.(2008)]{B08}
+%Boylan-Kolchin, M., Ma, C.-P., \& Quataert, E. 2008, MNRAS, 383, 93
+
+%\bibitem[Bueno Belloso et al. (2012)]{BB2012}
+%Bueno Belloso, A., Pettinari, G.W., Meures, N., \& Percival, W.J. 2012, Phys. Rev. D, 86, 023530
+
+\bibitem[Chevallier \& Polarski(2001)]{CPL_CP}
+Chevallier, M., Polarski, D. 2001, Int. J. Mod. Phys. D, 10, 213
+
+%\bibitem{CPL_CP}
+%Chevallier, M, \& Polarski, D. 2001, Int. J. Mod. Phys. D,  10, 213
+
+%\bibitem[Choi et al.(2010)]{choi 2010}
+%Choi, Y.-Y., Park, C., Kim, J., Gott, J.R., 
+%Weinberg, D.H., Vogeley, M.S., \& Kim, S.S. 2010, ApJS, 190, 181
+
+%\bibitem[Christensen et al.(2001)]{Bayesian}
+%Christensen, N., Meyer, R., Knox, L., \& Luey, B. 2001, Class. Quant. Grav., 18, 2677
+
+%\bibitem[Chuang et al.(2013)]{Chuang2013}
+%Chuang, C.-H., Prada, F., Beutler, F., et al. 2013, arXiv:1312.4889
+
+%\bibitem[Chuang \& Wang(2012)]{ChuangWang2012}
+%Chuang, C.-H., \& Wang, Y. 2012, MNRAS, 426, 226
+
+%\bibitem[Corasaniti \& Copeland(2003)]{Corasaniti2003}
+%Corasaniti, P.S., Copeland, E.J. 2003, Phys. Rev. D, 67, 063521
+
+%eBOSS: 
+%http://arxiv.org/abs/1508.04473
+%\bibitem[Dawson et al.(2015)]{eBOSS}
+%Dawson, K.S., Kneib, J.P., \& Percival, W.J., et al. 2015, accepted AJ
+
+%\bibitem[Dawson et al.(2012)]{Dawson et al. 2012}
+%Dawson, K.S., Schlegel, D.J., \& Ahn, C.P., et al. 2012, AJ, 145, 10
+
+\bibitem[Efstathiou (2014)]{E14H0}
+Efstathiou, G. 2014, MNRAS, 440, 1138
+
+%\bibitem[Eisenstein et al.(2011)]{Eisenstein et al. 2011}
+%Eisenstein, D.J.,  Weinberg, D.H., \& Agolet, E., et al. 2011, AJ, 142, 72
+
+%\bibitem[Feldman, Kaiser \& Peacock (1994)]{1994ApJ...426...23F} 
+%Feldman, H.A., Kaiser, N., \& Peacock, J.A.\ 1994, ApJ, 426, 23
+
+%\bibitem[Fukugita et al. (1996)]{Fukugita1996}
+%Fukugita, M., Ichikawa, T., \& Gunn, J.E., et al. 1996, AJ, 111, 1748
+%Publication:	
+%Astronomical Journal v.111, p.1748
+
+%\bibitem[Gingold \& Monaghan(1977)]{GM1977}
+%Gingold, R.A., \& Monaghan, J.J. 1977, MNRAS, 181, 375
+
+%\bibitem[Gott et al.(2009)]{gott 2009}
+%Gott, J.R., Choi, Y.-Y., Park, C., \& Kim, J. 2009, ApJ, 695, L45
+
+%\bibitem[Gott et al.(2008)]{gott 2008}
+%Gott, J.R., Hambrick, D.C., Vogeley, M.S., Kim, J., Park, C., Choi, Y.-Y.,
+%Cen, R., Ostriker, J.P., \& Nagamine, K. 2008, ApJ, 675, 16
+
+%\bibitem[Gunn et al. (1998)]{Gunn1998}	
+%Gunn, J.E., Carr, M., \& Rockosi, C. et al. 1998, AJ, 116, 3040
+
+%\bibitem[Gunn et al.(2006)]{Gunn et al. 2006}
+%Gunn, J.E., Siegmund, W.A., \& Mannery, E.J., et al. 2006, AJ, 131, 2332
+
+%\bibitem[Guzzo et al.(2008)]{Guzzo2008}
+%Guzzo, L., Pierleoni, M., \& Meneux, B., et al. 2008, Nature, 451, 541
+
+\bibitem[Hartlap et al.(2006)]{Hartlap}
+Hartlap J., Simon P. \& Schneider P. [astro-ph/0608064].
+
+\bibitem[Hong et al.(2016)]{hong2016}
+Hong, S.E., Park, C.,\&  Kim, J. 2016, ApJ, 823, 103
+
+%\bibitem[Jackson (1972)]{FOG}
+%Jackson, J., 1972, MNRAS, 156, 1
+
+\bibitem[Jennings et al.(2011)]{Jennings2011}
+Jennings, E., Baugh, C.M., \& Pascoli, S. 2011, MNRAS, 420, 1079
+
+%\bibitem[Jeong et al.(2014)]{Jeong2014}
+%Jeong, D., Dai, L., Kamionkowski, M., \& Szalay, A.S. 2014, arXiv:1408.4648
+
+%\bibitem[Jiang et al.(2008)]{jiang2008}
+%Jiang, C.Y., Jing, Y. P., \& Faltenbacher, A., et al. 2008, ApJ, 675, 1095
+
+%\bibitem[Kaiser (1987)]{Kaiser1987}
+%Kaiser, N. 1987, MNRAS, 227, 1
+
+%\bibitem[Kim \& Park(2006)]{kim and park 2006}
+%Kim, J., \& Park, C. 2006, ApJ, 639, 600
+
+%\bibitem[Kim et al.(2009)]{2009ApJ...701.1547K} 
+%Kim, J., Park, C., Gott, J.R., III, \& Dubinski, J.\ 2009, ApJ, 701, 1547
+
+\bibitem[Kim et al.(2015)]{HR4}
+Kim, J., Park, C., L'Huillier, B., \& Hong, S. E. 2015, JKAS, 48, 213
+
+%\bibitem[Kim et al.(2011)]{horizonrun}
+%Kim, J., Park, C., Rossi, G., Lee, S.M., \& Gott, J.R. 2011, JKAS, 44, 217
+
+\bibitem[Kitaura et al.(2015)]{MDPATCHY}
+Kitaura, F.S., Rodrı\'{i}guez-Torres, S., Chuang, C.-H., et al. arXiv:1509.06400
+
+\bibitem[Komatsu et al.(2011)]{komatsu2011}
+Komatsu, E., Smith, K. M., \& Dunkley, J., et al. 2011, ApJS, 192, 18
+
+%\bibitem[Lacey \& Cole(1993)]{LC93}
+%Lacey, C., \& Cole, S. 1993, MNRAS, 262, 627
+
+%\bibitem[Landy \& Szalay(1993)]{1993ApJ...412...64L} 
+%Landy, S.D., \& Szalay, A.S.\ 1993, ApJ, 412, 64
+
+%EUCLID:
+%http://arxiv.org/abs/1110.3193
+%\bibitem[Laureijs et al.(2011)]{EUCLID}
+%Laureijs, R., Amiaux, J., \& Arduini, S., et al. 2011, arXiv:1110.3193
+
+\bibitem[Lavaux \& Wandelt(2012)]{LavausWandelt1995}
+Lavaux, G., \& Wandelt, B.D. 2012, ApJ, 754, 109
+
+%\bibitem[Levi et al.(2013)]{2013arXiv1308.0847L} 
+%Levi, M., Bebek, C., Beers, T., et al.\ 2013, arXiv:1308.0847
+
+\bibitem[Lewis \& Bridle (2002)]{LB2002}
+Lewis, A., \& Bridle, S. 2002, Phys. Rev. D, 66, 103511
+
+%\bibitem[L'Huillier et al.(2014)]{2014NewA...30...79L} 
+%L'Huillier, B., Park, C., \& Kim, J.\ 2014, New Astronomy, 30, 79
+
+%\bibitem[Li et al.(2011)]{Li2011}
+%Li, M., Li, X.-D., Wang, S., \& Wang, Y. 2011, Commun. Theor. Phys., 56, 525
+
+\bibitem[Li et al.(2014)]{Li2014}
+Li, X.-D., Park, C., Forero-Romero, J., \& Kim, J. 2014, ApJ, 796, 137
+
+\bibitem[Li et al.(2015)]{Li2015}
+Li, X.-D., Park, C., Sabiu, C.G., \& Kim, J. 2015, MNRAS, 450, 807
+
+\bibitem[Li et al.(2016)]{Li2016}%
 Li, X.-D., Park, C., \& Sabiu, C.G., et al. 2016, ApJ, 832, 103
 
-\bibitem{2012IJMPD..2130002Y}%[Yoo \& Watanabe(2012)]
-Yoo, J., \& Watanabe, Y.\ 2012, International Journal of Modern Physics D, 21, 1230002
+\bibitem[Linder(2003)]{CPL_L}
+Linder, E.V. 2003, Phys. Rev. Lett., 90, 091301
 
-\bibitem{AP1979}%[Alcock \& Paczynski(1979)]
-Alcock, C., \& Paczynski, B. 1979, Nature, 281, 358
+%\bibitem[Linder et al.(2014)]{Linder2013}
+%Linder, E.V., Minji, O., Okumura, T., Sabiu, C.G., \& Song, Y.-S. 2014, Phys. Rev. D, 89, 063525
 
-\bibitem{Outram2004}%[Outram et al.(2004)]
+%\bibitem[L{\'o}pez-Corredoira(2014)]{2014ApJ...781...96L} 
+%L{\'o}pez-Corredoira, M.\ 2014, ApJ, 781, 96
+
+\bibitem[Mao et al. (2016)]{Qingqing2016}
+Mao, Q., Berlind, A.A., Scherrer, R.J., et al. 2016, submitted to ApJ
+
+\bibitem[Marinoni \& Buzzi(2010)]{Marinoni2010}
+Marinoni, C., \& Buzzi, A. 2010, Nature, 468, 539
+
+%\bibitem[Matsubara \& Suto(1996)]{Matsubara1996}
+%Matsubara T., \& Suto, Y. 1996, ApJ, 470, L1
+
+%\bibitem[McCavana et al.(2012)]{M12}
+%McCavana, T., Micic, M., Lewis, G. F., et al. 2012, MNRAS, 424, 361
+
+%\bibitem[Morandi \& Sun (2016)]{MS2016}
+%Morandi, A., \& Sun, M. arXiv:1601.03741
+
+\bibitem[Outram et al.(2004)]{Outram2004}
 Outram, P.J., Shanks, T., Boyle, B.J., Croom, S.M., Hoyle, F., Loaring, N.S., 
@@
 
-\bibitem{Blake2011}%[Blake et al.(2011)]
-Blake, C., Glazebrook, K., \& Davis, T. M., 2011, MNRAS, 418, 1725
+%\bibitem[Parejko et al.(2013)]{Parejko2013}
+%Parejko, J. K., Sunayama, T., Padmanabhan, N., et al. 2013, MNRAS, 429, 98
 
-\bibitem{Alam2016}%[Alam et al.(2016)]
-Alam, S., Ata, M., \& Bailey, S., et al. 2016,
-submitted to MNRAS (arXiv:1607.03155)
+%\bibitem[Parejko et al.(2013)]{Parejko2013}
+%Parejko J.K., et al., 2013, MNRAS, 429, 98
 
-\bibitem{Ballinger1996}%[Ballinger, Peacock \& Heavens 1996]
-Ballinger, W.E., Peacock, J.A., \& Heavens, A.F. 1996, MNRAS, 282, 877
+%\bibitem[Parihar et al. (2014)]{CMASSLSS2014}
+%Parihar, P., Vogeley, M.S., \& Gott, J.R., et al. 2014, ApJ, 796, 86
 
-\bibitem{Marinoni2010}%[Marinoni \& Buzzi(2010)]
-Marinoni, C., \& Buzzi, A. 2010, Nature, 468, 539
+%\bibitem[Park et al.(2005)]{park 2005}
+%Park, C., Kim, J., \& Gott, J.R. 2005, ApJ, 633, 1
 
-\bibitem{Jennings2011}%[Jennings et al.(2011)]
-Jennings, E., Baugh, C.M., \& Pascoli, S. 2011, MNRAS, 420, 1079
+%\bibitem[Park \& Kim(2010)]{topology}
+%Park, C., \& Kim, Y.-R. 2010, ApJL, 715, L185
 
-\bibitem{Ryden1995}%[Ryden(1995)]
+%\bibitem[Park et al. (2012)]{Park2012}
+%Park, C., Choi, Y.-Y., Kim, J., Gott, J.R., Kim, S.S., \&
+%Kim, K.-S. 2012, ApJ, 759, 7
+
+%\bibitem[Park et al. (2015)]{Park2015}
+%Park, C., Song, H., Einasto, M., Lietzen, H., \&
+%Heinamaki, P. 2015, JKAS, 48, 75
+
+%\bibitem[Peebles \& Ratra(2003)]{PR2003}
+%Peebles, P.J.E., \& Ratra, B. 2003, Reviews of Modern Physics, 75, 559
+
+\bibitem[Percival et al.(2014)]{Percival2014}
+Percival, W.J., Ross, A.J., \& S\'{a}nchez, A.G., et al. 2014, MNRAS, 439, 2531
+
+%\bibitem[Perlmutter et al.(1999)]{Perl1999}
+%Perlmutter, S., Aldering, G., \& Goldhaber, G., et al. 1999, ApJ, 517, 565
+
+%\bibitem[Press \& Shechter(1974)]{PS1974}
+%Press, W.H., \& Schechter, P.L. 1974, ApJ, 187, 425
+
+%\bibitem[Reid et al.(2012)]{Reid2012}
+%Reid, B., Samushia, L., \& White, M., et al. 2012, MNRAS, 426, 2719
+
+\bibitem[Reid et al.(2016)]{Reidetal:2016}
+Reid, B., Ho, S., \& Padmanabhan, N., et al.  2016, MNRAS, 455, 1553
+
+%\bibitem[Riess et al.(1998)]{Riess1998}
+%Riess, A.G., Filippenko, A.V., \& Challis, P., et al. 1998, AJ, 116, 1009
+
+\bibitem[Riess et al.(2011)]{Riess2011}
+Riess, A.G., Macri, L., \& Casertano, S., et al. 2011, ApJ, 730, 119
+A 3\% Solution: Determination of the Hubble Constant with the Hubble Space Telescope and Wide Field Camera
+
+%\bibitem[Ross et al.(2012)]{2012MNRAS.424..564R} 
+%Ross, A.J., Percival, W.J., \& S{\'a}nchez, A.G. et al.\ 2012, MNRAS, 424, 564
+
+\bibitem[Ross et al.(2015)]{MGS}
+Ross, A.J., Samushia, L., \& Howlett, C., et al. 2015, MNRAS, 449, 835
+
+\bibitem[Ryden(1995)]{Ryden1995}
 Ryden, B.S. 1995, ApJ, 452, 25
 
-\bibitem{LavausWandelt1995}%[Lavaux \& Wandelt(2012)]
-Lavaux, G., \& Wandelt, B.D. 2012, ApJ, 754, 109
+%%\bibitem[Samushia et al.(2014)]{Samushia2014}
+%Samushia, L., Reid, B. A., White, M., et al. 2014, MNRAS, 439, 3504
 
-\bibitem{Qingqing2016}%[Mao et al. (2016)]
-Mao, Q., Berlind, A.A., Scherrer, R.J., et al. 2016, submitted to ApJ
+%\bibitem[Sanchez et al.(2013)]{Sanchez2013}
+%Sanchez, A. G., Kazin, E. A., Beutler, F., et al. 2013, MNRAS, 433, 1202
 
-\bibitem{Li2014}%[Li et al.(2014)]
-Li, X.-D., Park, C., Forero-Romero, J., \& Kim, J. 2014, ApJ, 796, 137
+%\bibitem[Sutter et al.(2014)]{Sutter2014}
+%Sutter, P.M., Pisani, A., Wandelt, B.D., \& Weinberg, D.H. 2014, MNRAS, 443, 2983
 
-\bibitem{Li2015}%[Li et al.(2015)]
-Li, X.-D., Park, C., Sabiu, C.G., \& Kim, J. 2015, MNRAS, 450, 807
+%\bibitem[Sanchez et al.(2016)]{Sanchez2016}
+%Sanchez, A. G., Scoccimarro, R., \& Crocce, M., et al.
+%arXiv:1607.03147
 
-\bibitem{CPL_CP}
-Chevallier, M, \& Polarski, D. 2001, Int. J. Mod. Phys. D,  10, 213
+%\bibitem[Schlafly et al.(2010)]{Schlafly2010}
+%Schlafly E.F., Finkbeiner D.P., Schlegel D.J., et al. 2010, ApJ, 725, 1175
 
-\bibitem{CPL_L}
-Linder, E. V. 2003, Phys. Rev. Lett, 90, 091301
+%\bibitem[Schlafly \& Finkbeiner(2011)]{SF2011}
+%Schlafly E.F., \& Finkbeiner D.P. 2011, ApJ, 737, 103
 
-\bibitem{DETF}
-Albrecht, A., Bernstein, G., \& Cahn, R., et al. [astro-ph/0609591].
+%DESI:
+%http://arxiv.org/abs/1106.1706
+%\bibitem[Schlegel et al.(2011)]{DESI}
+%Schlegel, D., Abdalla, F., \& Abraham, T., et al. 2011, arXiv:1106.1706
 
-\bibitem{Reidetal:2016}%[Reid et al.(2016)]
-Reid, B., Ho, S., \& Padmanabhan, N., et al.  2016, MNRAS, 455, 1553
+%\bibitem[Smee et al.(2013)]{Smee2013}
+%Smee, S.A., Gunn, J.E., \& Uomoto, A., et al. 2013, AJ, 146, 32
 
-\bibitem{HR4}%[Kim et al.(2015)]
-Kim, J., Park, C., L'Huillier, B., \& Hong, S. E. 2015, JKAS, 48, 213
+%\bibitem[Song et al.(2014)]{2014arXiv1407.2257S} 
+%Song, Y.S., Sabiu, C.G., 
+%Okumura, T., Oh, M., \& Linder, E.V.\ 2014, JCAP, 12, 005
 
-\bibitem{komatsu2011}%[Komatsu et al.(2011)]
-Komatsu, E., Smith, K. M., \& Dunkley, J., et al. 2011, ApJS, 192, 18
+%\bibitem[Speare et al. (2015)]{Speare2015}
+%Speare, R., Gott, J.R., Kim, J., \& Park, C.
+%2015, ApJ, 799, 176
 
-\bibitem{hong2016}%[Hong et al.(2016)]
-Hong, S.E., Park, C.,\&  Kim, J. 2016, ApJ, 823, 103
+%\bibitem[Tojeiro \& Percival(2011)]{Tojeiro2011}
+%Tojeiro R., \& Percivial W.J. 2011, MNRAS, 417, 1114
 
-\bibitem{MDPATCHY}%[Kitaura et al.(2015)]
-Kitaura, F.S., Rodriguez-Torres, S., Chuang, C.-H., et al.2016, MNRAS, 456, 4156
+%\bibitem[Tojeiro et al.(2012)]{Tojeiro2012}
+%Tojeiro, R., Percival, W. J., Wake, D. A., et al. 2012, MNRAS, 424, 136
 
-\bibitem{Hartlap}%[Hartlap et al.(2006)]
-Hartlap, J., Simon, P., \& Schneider, P. [astro-ph/0608064].
+%\bibitem[Viana \& Liddle(1996)]{VL1996}
+%Viana, P.T.P., \& Liddle, A.R. 1996, MNRAS, 281, 323
 
-\bibitem{Percival2014}%[Percival et al.(2014)]
-Percival, W.J., Ross, A.J., \& S\'{a}nchez, A.G., et al. 2014, MNRAS, 439, 2531
+%\bibitem[Villalobos et al.(2013)]{V13}
+%Villalobos, \'{A}., ́De Lucia, G., Weinmann, S.M., Borgani, S., \& Murante, G. 2013, MNRAS, 433, L49
 
-\bibitem{LB2002}%[Lewis \& Bridle (2002)]
-Lewis, A., \& Bridle, S. 2002, Phys. Rev. D, 66, 103511
+%\bibitem[Weinberg (1989)]{SW1989}
+%Weinberg, S. 1989, Reviews of Modern Physics, 61, 1
 
-\bibitem{Planck2015}%[Ade et al. (2015)]
-Ade, P.A.R., Aghanim, N., \& Arnaud, M., et al. 2016, A\&A, 594, A13
+%\bibitem[White (2011)]{White2011}
+%White M., et al. 2011, ApJ, 728, 126
 
-\bibitem{Anderson2013}%[Anderson et al.(2013)]
-Anderson, L., Aubourg, \'E., \& Bailey, S. et al. 2014, MNRAS, 441, 24
+\bibitem[Yoo \& Watanabe(2012)]{2012IJMPD..2130002Y}%
+Yoo, J., \& Watanabe, Y.\ 2012, International Journal of Modern Physics D, 21, 1230002
 
-\bibitem{6dFGS}%[Beutler et al.(2011)]
-Beutler, F., Blake, C., \& Colless, M., et al. 2011, MNRAS, 416, 3017
+%\bibitem[York et al.(2000)]{York et al. 2000}
+%York, D.G., Adelman, J., \& Anderson, J.E., et al. 2000, AJ, 120, 1579
 
-\bibitem{MGS}%[Ross et al.(2015)]
-Ross, A.J., Samushia, L., \& Howlett, C., et al. 2015, MNRAS, 449, 835
-
-\bibitem{JLA}%[Betoule et al.(2014)]
-Betoule, M., Kessler, R., \& Guy, J., et al. 2014, A\&A, 568, 32
-
-\bibitem{Riess2011}%[Riess et al.(2011)]
-Riess, A.G., Macri, L., \& Casertano, S., et al. 2011, ApJ, 730, 119
-
-\bibitem{E14H0}%[Efstathiou (2014)]
-Efstathiou, G. 2014, MNRAS, 440, 1138
-
-%\bibitem{Lee12}
-%\bibinfo{author}{Lee}, E.~J., {Murray}, N., {Rahman}, M. 
-%\newblock \bibinfo{title}{Milky Way Star-forming Complexes and the Turbulent Motion of the Galaxy's Molecular Gas.}
-%\newblock{\it Astrophys. \ J.}{\bf\, 752}, 146-159 (2012).
-
-%%%% For methods
+%\bibitem[Zehavi et al.(2011)]{zehavi2011}
+%Zehavi, I., Zheng, Z., \& Weinberg, D.H., et al. 2011, ApJ, 736, 59
 

### 2017-09-27 Draft/Draft1.2.tex
minor changes

--- 2017-09-27 Draft/Draft1.1.tex
@@
 12, spanning the redshift range $0.15<z<0.69$ to place constraints on the expansion history of the Universe. 
-Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$,
-while improving upon earlier works \citep{Li2016},
-we present a novel use of the Alcock-Paczynski (AP) test via clustering difference between redshift bins on scales of 6-40 $h^{-1}\rm Mpc$.
-This differential measure is shown to be a robust statistical tool that mitigates many systematic effects, 
-allowing for competitive and unbiased constrains to be placed on cosmological parameters.
-% The Alcock-Paczynski (AP) test was performed via the redshift dependence of clustering on scales of 6-40 $h^{-1}\rm Mpc$.
-% We improve the methodology of \citep{Li2016} by significantly reducing its computation time, 
-% which enables us to explore three or more cosmological parameters.
-% We applied the improved method on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$.
-We find that our results, in combination with the CMB, BAO, SNIa and $H_0$ from Cepheid data, yield
+%Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$,
+%while improving upon earlier works \citep{Li2016},
+%we present a novel use of the Alcock-Paczynski (AP) test via clustering difference between redshift bins on scales of 6-40 $h^{-1}\rm Mpc$.
+%This differential measure is shown to be a robust statistical tool that mitigates many systematic effects, 
+%allowing for competitive and unbiased constrains to be placed on cosmological parameters.
+The Alcock-Paczynski (AP) test was performed via the redshift dependence of clustering on scales of 6-40 $h^{-1}\rm Mpc$.
+We improve the methodology of \cite{Li2016} by significantly reducing its computation time. 
+This enables us to efficiently explore three or more cosmological parameters.
+We then apply the improved method on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$.
+In combination with the CMB, BAO, SNIa and $H_0$ from Cepheid data, we obtain
 $\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ w_a = -0.07 \pm 0.29$ (68.3\% CL). 
@@
 and improves the dark energy figure of merit by a factor of 2. 
-% We carefully checked the robustness of the results.
-The AP method can %be combined with the standard BAO method,
-greatly increase the power of ongoing and future galaxy surveys in probing dark energy.
+We checked the robustness of the results.
+%The AP method may %be combined with the standard BAO method,
+%greatly increase the power of ongoing and future galaxy surveys in probing dark energy.
 \end{abstract}
@@
    \centering{
-   \includegraphics[width=14cm,natwidth=6,natheight=5]{fig_con_tests.pdf}
+   \includegraphics[width=18cm,natwidth=6,natheight=5]{fig_con_tests.pdf}
    %\includegraphics[width=9cm,natwidth=4,natheight=4]{fig2b.pdf}
@@
 
-%\begin{figure*}
-%   \centering{
-%   \includegraphics[width=6cm]{fig_smu.eps}
-%   \includegraphics[width=10.5cm]{fig_comp.eps}
-%   }
-%   \caption{\label{fig_method}
-%   Left panel: Mapping $\xi(s,\mu)$ from the fiducial cosmology to four other cosmologies. 
-% The number counts are measured in the fiducial cosmology in a uniform grid (blue dashed.
-%  Just for illustration; the grid adopted in real analysis is much denser).
-% In the four cosmologies with $(\Omega_m,w) = (0.31,-1.5),\ (0.31,-0.5),\ (0.41,-1.0)\ \rm and\ (0.21,-1.0)$, 
-% %due to the distortion of geometry,
-% the distribution of number counts in $(s, \mu)$ space becomes the red solid grid ({\bf Check}).
-% We utilize the mapping realtion to approximate the 2pCF in vaiours cosmologies, without re-conducting the 2pCF statistics. 
-% Right panel: Cosmological constraints in the $\Omega_m$-$w_0$ plane, with the value of $w_a$ fixed as zero.
-% Results obtained using the precise 2pCFs (gray filled) 
-% and approximate 2pCFs (blue solid) 2pCFs matches each other quite well.
-%   }
-%\end{figure*}
+\begin{figure*}
+   \centering{
+   \includegraphics[width=6cm]{fig_smu.eps}
+   \includegraphics[width=10.5cm]{fig_comp.eps}
+   }
+   \caption{\label{fig_method}
+   Left panel: Mapping $\xi(s,\mu)$ from the fiducial cosmology to four other cosmologies. 
+ The number counts are measured in the fiducial cosmology in the blue dashed grid (for illustration purpose 
+  the grid shown here is much sparser than the grid adopted in real analysis).
+ In the four cosmologies with $(\Omega_m,w) = (0.31,-1.5),\ (0.31,-0.5),\ (0.41,-1.0)\ \rm and\ (0.21,-1.0)$, 
+ %due to the distortion of geometry,
+ the distribution of number counts in $(s, \mu)$ space becomes the red solid grid.
+ We utilize the mapping realtion to infer the 2pCFs in vaiours cosmologies without re-conducting the 2pCF statistics. 
+ Right panel: Cosmological constraints in the $\Omega_m$-$w_0$ plane, with the value of $w_a$ fixed as zero.
+ Results obtained using the precise 2pCFs (gray filled) 
+ and approximate 2pCFs (blue solid) 2pCFs agree with each other quite well.
+   }
+\end{figure*}
 
@@
 
-We performed a thorough test of all the possible variables in our methodology.
+We performed a test of all the possible variables in our methodology.
 Fig.\ref{fig_contest} shows that 
@@
 The most striking point to note in our test is that the 
-shift in contour position is very small even when %we do not include the systematic correction.
+shift in contour position is not significant even when %we do not include the systematic correction.
 the systematics are not corrected.
@@
 on the CPL parametrization of dark energy.
-%The derived cosmological constraints are fully consistent with a cosmological constant 
-%dark energy component having no redshift evolution.
+The derived cosmological constraints are fully consistent with a cosmological constant 
+dark energy component having no redshift evolution.
 
@@
 providing much higher statistics.
+
+%Yet there are still issues demanding more investigations.
+In this analysis, the systematic effects and the covariance matrices are estimated using simulations performed in a certain cosmology.
+Their cosmological dependence needs to be investigated in future works to guarantee the robustness of the method.
 

### 2017-09-27 Draft/Draft1.3.tex
minor changes

--- 2017-09-27 Draft/Draft1.2.tex
@@
 %\altaffiltext{4}{\bf Hyunbae: your email}
-\altaffiltext{1}{Corresponding Author: kjhan@kias.re.kr}
+%\altaffiltext{1}{Corresponding Author: kjhan@kias.re.kr}
 
@@
 %allowing for competitive and unbiased constrains to be placed on cosmological parameters.
-The Alcock-Paczynski (AP) test was performed via the redshift dependence of clustering on scales of 6-40 $h^{-1}\rm Mpc$.
+The Alcock-Paczynski (AP) test was performed via the redshift dependence of clustering on scales of 6--40 $h^{-1}\rm Mpc$.
 We improve the methodology of \cite{Li2016} by significantly reducing its computation time. 
@@
    The distance dependence of the shape distortion in four wrongly assumed cosmologies.
-   Assuming a true cosmology of $\Omega_m=0.31$, $w=-1$.
+   Assuming a true cosmology of $\Omega_m=0.26$, $w=-1$.
    There are four perfect squares with their true shapes plotted in blue dashed lines.
@@
 Assuming an incorrect cosmological model for the coordinate transformation between redshift space and comoving space
-produces residual geometric distortions in the resultant galaxy distribution (see  Fig.\ref{fig_xy}). 
+produces residual geometric distortions in the resultant galaxy distribution (see  Figure \ref{fig_xy}). 
 These distortions are induced by the fact that measured distances along 
@@
 the anisotropy in the clustering signal has a clear redshift dependence
-(as an illustration, Fig.\ref{fig_xy} shows how the shape distortion of objects varies with distance (i.e., redshift) 
+(as an illustration, Figure \ref{fig_xy} shows how the shape distortion of objects varies with distance (i.e., redshift) 
 when incorrect cosmologies are used to infer distances).
@@
 defined as the reciprocal of the area of the error ellipse enclosing the 95\% confidence limit (CL) in the $w_0-w_a$ plane. 
-Fig.\ref{fig_xy} shows that redshift dependence of shape distortion is sensitive to both $w_0$ and $w_a$.
+Figure \ref{fig_xy} shows that redshift dependence of shape distortion is sensitive to both $w_0$ and $w_a$.
 So we expect these two parameters effectively constrained by our method.
@@
 \section{Methodology}
+
+\subsection{Quantifying the redshift dependece of AP distortion}
+
 The spectroscopic galaxy sample of SDSS-III BOSS (Baryon Oscillation Spectroscopic Survey) has two primary catalogues:
@@
 $0.150<z_1<0.274<z_2<0.351<z_3<0.430<z_4<0.511<z_5<0.572<z_6<0.693$.
-The number density of galaxies and the redshift binning scheme is plotted in the left panel of Fig.\ref{fig_TpCF}.
+The number density of galaxies and the redshift binning scheme is plotted in the left panel of Figure \ref{fig_TpCF}.
 
@@
 
+\begin{figure*}
+   \centering{
+   \includegraphics[width=16cm]{fig_smu.eps}
+%   \includegraphics[width=10.5cm]{fig_comp.eps}
+   }
+   \caption{\label{fig_method}
+   Mapping $\xi(s,\mu)$ from the fiducial cosmology (taken as the $\Omega_m=0.26$ $\Lambda$CDM cosmology) to other cosmologies. 
+ The number counts are measured in the fiducial cosmology in the blue dashed grid.
+ In the four cosmologies with $(w_0,w_a) = (-1.5,0),\ (-0.5,0),\ (-1,2)\ \rm and\ (-1,-2)$,
+ %due to the distortion of geometry,
+ according to Equation \ref{eq:smumap},
+ the distribution of measured number counts in $(s, \mu)$ space becomes the red solid grid,
+ To ensure the accuracy, we count the number of pairs in 5 times smaller pixels (the small red pixels), 
+ and group them together to infer the values of $\xi(s, \mu)$ in blue dashed grid.
+ For illustration purpose, 
+  the blue and red grids are all 10 times sparser than the grids adopted in real analysis.
+}
+\end{figure*}
+
+\begin{figure*}
+   \centering{
+   \includegraphics[width=8.5cm]{fig_comp.eps}
+   \includegraphics[width=8.5cm]{fig_IO.eps}
+   }
+   \caption{\label{fig_Check}
+ Left panel: Cosmological constraints from the BOSS DR12 galaxies, in the $\Omega_m$-$w_0$ plane. 
+ The value of $w_a$ is fixed as zero.
+ Results obtained using the precise 2pCFs (cyan filled) 
+ and approximate 2pCFs (blue solid) agree with each other quite well.
+ Right panel: Input-output test of the methodology using four sets of HR4 mock catalogues.
+ The approximate 2pCFs are used in the analysis.
+ The simulation cosmology, $\Omega_m=0.26$ $\Lambda$CDM, is marked by the black plus.
+ The inferred cosmological constraints from the method, shown in the cygan contours, are consistent with the input cosmology.
+   }
+\end{figure*}
+
 Following our previous methodology \citep{Li2016}, the information of small-scale anisotropic clustering is computed.
@@
 
-The right panel of Fig.\ref{fig_TpCF} shows the contour map of $\xi(s,\mu)$ measured in the six redshift bins.
+The right panel of Figure \ref{fig_TpCF} shows the contour map of $\xi(s,\mu)$ measured in the six redshift bins.
 The contour lines are not horizontal due to the effects of peculiar velocity,
@@
    %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
-   \includegraphics[height=5cm,natwidth=6,natheight=4.5]{figCPL_b.pdf}
+   \includegraphics[width=8cm,natwidth=6,natheight=4.5]{figCPL_b.pdf}
    %\includegraphics[width=5.5cm,natwidth=4,natheight=4]{figCPL_b_BAOSNIaAP.pdf}
-   \includegraphics[height=5cm,natwidth=6,natheight=4.5]{figCPL_d.pdf}
+   \includegraphics[width=8cm,natwidth=6,natheight=4.5]{figCPL_d.pdf}
    %\includegraphics[height=8cm]{fig2b.pdf}
@@
 
+\subsection{Approximating the 2pCFs in cosmologies other than the fiducial one}
+
 In our earlier work\cite{Li2016}, the likelihood contour of $\Omega_m-w$ was constructed by
@@
 and values of $D_A$ and $H$ are computed in the effective redshifts of the six redshift bins.
-%The left panel of Figure \ref{fig_method} shows how 
-%$\xi(s,\mu)$ is mapped from the fiducial cosmology to another cosmology using the above relations.
 In the fiducial cosmology
@@
 in large pixels of $\Delta s = 1 {\rm Mpc/h}$, $\Delta \mu = 1/120$.
-%in the fiducial cosmology and group the bins in the target cosmology.
 In the case when one small pixel belongs to more than one larger pixel,
 a correction is applied by computing the fraction of the overlapping area.
+%in the fiducial cosmology and group the bins in the target cosmology.
 %\footnote{A dense grid can effectively reduce the ``edge effect'' produced when we map $\xi(s,\mu)$ from one cosmology to another.
@@
 
-We found when using the approximate method the computed 
-$\hat\xi_{\Delta s}(\mu)$ in a non-fiducial cosmology suffers from
-an error of $\lesssim0.5\%$, which is 10 times smaller than the statistical noise.
-We checked that the approximate method can reproduce the results presented in \cite{Li2016} quite well.
-% We checked that the approximate method can reproduce the results of precise method quite well.
-% The right panel of Figure \cite{fig_method} shows the  $\Omega_m$-$w_0$ constraints obtained 
-%  using the precise and approximate 2pCFs (here we fix $w_a=0$). 
-%  They agree with each other quite well.
-
-\begin{figure*}
-   \centering{
-   \includegraphics[width=6cm]{fig_smu.eps}
-   \includegraphics[width=10.5cm]{fig_comp.eps}
-   }
-   \caption{\label{fig_method}
-   Left panel: Mapping $\xi(s,\mu)$ from the fiducial cosmology to four other cosmologies. 
- The number counts are measured in the fiducial cosmology in the blue dashed grid (for illustration purpose 
-  the grid shown here is much sparser than the grid adopted in real analysis).
- In the four cosmologies with $(\Omega_m,w) = (0.31,-1.5),\ (0.31,-0.5),\ (0.41,-1.0)\ \rm and\ (0.21,-1.0)$, 
- %due to the distortion of geometry,
- the distribution of number counts in $(s, \mu)$ space becomes the red solid grid.
- We utilize the mapping realtion to infer the 2pCFs in vaiours cosmologies without re-conducting the 2pCF statistics. 
- Right panel: Cosmological constraints in the $\Omega_m$-$w_0$ plane, with the value of $w_a$ fixed as zero.
- Results obtained using the precise 2pCFs (gray filled) 
- and approximate 2pCFs (blue solid) 2pCFs agree with each other quite well.
-   }
-\end{figure*}
+The above procedure is illustrated in Figure \ref{fig_method}.
+Using the relations given by Equation \ref{eq:smumap},
+we obtained the distribution of number counts in cosmologies other than the fiducial cosmology.
+To ensure the accuracy of mapping, the number counting is conducted using 5 times smaller pixels (the small red pixels), 
+and grouped together to infer the number counts in the standard resolution (the large blue dashed pixels).
+
+%We checked that the approximate method can reproduce the results presented in \cite{Li2016} quite well.
+
+The approximation procedure only introduces a $\lesssim0.5\%$ error in the $\hat\xi_{\Delta s}(\mu)$, 
+which is 10 times smaller than the noise of $\hat\xi_{\Delta s}(\mu)$.
+We checked that the approximate method can reproduce the results of precise method quite well.
+The left panel of Figure \ref{fig_Check} shows the  $\Omega_m$-$w_0$ constraints obtained 
+  using the precise and approximate 2pCFs (here we fix $w_a=0$). 
+They agree with each other quite well.
+
+To further check the robustness of the approximate method, 
+we did an input-output test using the four sets of HR4 mock catalogues \cite{HR4}.
+The results are shown in the right panel of Figure \ref{fig_Check}. 
+The input cosmology is the simulation cosmology, i.e. $\Omega_m=0.26$ $\Lambda$CDM.
+It lies within the 1$\sigma$ conour of the inferred constraints.
 
@@
 
-\section{Result}
+\section{Results}
 
@@
 %of the systematic correction could influence the final result. 
+%This suggest that the CPL constraints reported are robust.
 This indicates that, for the data analysis of current galaxy surveys,

### 2017-09-27 scp.sh

@@ -1,9 +1,11 @@
 
 #scp -r xiaodongli@baekdu.kias.re.kr:~/boss2pcf/data/DR12v4-CMASS-N/xyzw.finesplitted/data*.2pcf ./
 #dataran.xyzw.1of3.cosmo-converted.om0.2100_w-0.7000.rmax51.51rbins.120mubins.rr
-for om in 0.1100 0.2100 0.2600 0.3100 0.4100
+for om in 0.26
 do
-for w in  0.0000 -0.5000 -1.0000 -1.5000 -2.5000
+for w in  -1.0
+do
+for wa in -2.0000 -1.0000
 do
 for ibin in 1 2 3
 do
@@ -11,7 +13,9 @@ for catname in DR12v4-CMASS DR12v4-LOWZ
 do
 	mkdir -p $catname/xyzw.binsplitted/
 	#sshpass -p lx821118 scp -r xiaodongli@baekdu.kias.re.kr:~/boss2pcf/data/$catname/xyzw.binsplitted/data.xyzw.${ibin}of3.cosmo-converted.om${om}_w${w}.rmax51.51rbins.120mubins.2pcf /home/xiaodongli/SparseFilaments/data/local_input/boss2pcf/data/$catname/xyzw.binsplitted/
-	sshpass -p lx821118 scp -r xiaodongli@baekdu.kias.re.kr:~/boss2pcf/data/$catname/xyzw.binsplitted/data.xyzw.${ibin}of3.cosmo-converted.om${om}_w${w}.rmax*.*rbins.*mubins.2pcf /home/xiaodongli/SparseFilaments/data/input/boss2pcf/data/${catname}_Files/xyzw.binsplitted/
+	#sshpass -p lx821118 scp -r xiaodongli@baekdu.kias.re.kr:~/boss2pcf/data/$catname/xyzw.binsplitted/data.xyzw.${ibin}of3.cosmo-converted.om${om}_w${w}.rmax*.*rbins.*mubins.2pcf /home/xiaodongli/SparseFilaments/data/input/boss2pcf/data/${catname}_Files/xyzw.binsplitted/
[…]

### 2017-09-27 src/AP_Rhct.f90

@@ -1,5 +1,17 @@
 
 
+!Rhct
+! Sys-corred:      16.0076275       26.95636 56       12.7971764       13.1067686       19.3084583       88.176397148907327     
+! Sys-uncorred:    16.5017948       23.0967922       12.0079880       11.4178925       14.0837126       77.108180501000902
+
+! LCDM model. om =   0.27   &nbs p;
+
+! Sys-corred:      14.0279408       21.7550316       11.8282537       10.6070719       12.7000446       70.918342580960200     
+! param  mean           sddev          lower1         upper1         lower2         upper2         lower3         upper3
+!    1  0.2774861E+00  0.2212044E-01  0.2600098E+00  0.2961426E+00  0.2395020E+00  0.3320312E+00  0.2160645E+00  0.3835449E+00   \Omega_m
+
+! Sys-uncorred:    14.5382814       18.5175323       12.0481081       9.10813332       11.9272099       66.1392657 22333093  
+
 program main
 use LSS_ximu_tests
 USE de_model_init

### 2017-11-03 Draft/Draft1.4.tex
minor changes

--- 2017-09-27 Draft/Draft1.3.tex
@@
 \author{Xiao-Dong Li,}
-\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
+\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 02455, Korea}
 \author{Cristiano G. Sabiu,}
@@
 \author{Changbom Park,}
-\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
+\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 02455, Korea}
 \author{Yuting Wang, Gong-bo Zhao}
@@
 \begin{abstract}
-We use the anisotropic clustering signal of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
-12, spanning the redshift range $0.15<z<0.69$ to place constraints on the expansion history of the Universe. 
+We perform the Alcock-Paczynski (AP) test via the redshift dependence of clustering on scales of 6--40 $h^{-1}\rm Mpc$
+to place constraints on the expansion history of the Universe.
+We use 1,133,326 galaxies Sloan Digital Sky Survey Data Release 12 galaxies, spanning the redshift range $0.15<z<0.69$.
 %Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$,
@@
 %allowing for competitive and unbiased constrains to be placed on cosmological parameters.
-The Alcock-Paczynski (AP) test was performed via the redshift dependence of clustering on scales of 6--40 $h^{-1}\rm Mpc$.
-We improve the methodology of \cite{Li2016} by significantly reducing its computation time. 
-This enables us to efficiently explore three or more cosmological parameters.
+We improve the methodology of Li et al. to efficiently explore three or more cosmological parameters.
 We then apply the improved method on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$.
@@
 
+%\begin{figure*}
+%   \centering{
+%   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
+%   \includegraphics[height=6.5cm]{fig_nbar.eps}
+%   \includegraphics[width=9.0cm,]{fig_2pcf.eps}
+%   }
+%   \caption{\label{fig_TpCF}
+%   Splitting the SDSS galaxies into six redshift bins, and measuring the correlation function
+%   (similar figures already presented in \cite{Li2016}).
+%   Left panel: We split the BOSS DR12 galaxies into six redshift bins to measure the evolution of shape distortion.
+%   The blue and green solid histograms show the redshift density distribution of LOWZ and CMASS galaxies in the $\Omega_m=0.31$ $\Lambda$CDM. 
+%   The vertical dashed lines define the six redshift bins that are used to cut the samples.
+%   The number of LOWZ/CMASS galaxies in the three low/high redshift bins are listed.
+%   Right panel: 2D contour map of measured $\xi$ as a function of $\mu$ and $s$, from the six redshift bins of LOWZ and CMASS samples, 
+%      in the cosmology of $\Omega_m=0.31$ $\Lambda$CDM model.
+%    The black dashed lines mark the clustering region 6-40\ Mpc/h studied in the AP method.
+%    The six contour maps have rather similar appearance, implying small redshift evolution of $\xi$ from RSD.
+%   }
+%\end{figure*}
+
+\begin{figure*}
+   \centering{
+   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
+   \includegraphics[width=18cm]{fig_fan.eps}
+   %\includegraphics[width=9.0cm]{fig_2pcf.eps}
+   %\includegraphics[width=8.5cm]{fig_fan_2.eps}
+   }
+   \caption{\label{fig_fan}
+   %We split the BOSS DR12 galaxies into six redshift bins to measure the evolution of shape distortion.
+   A patch of BOSS DR12 glaxies located in the fan shape region $\rm 140^\circ < RA < 170 ^\circ$, $\rm 10^\circ < DEC < 13 ^\circ$.
+   We split the sample into six non-overlapping redshift bins
+   (marked by the light green rings) in order to probing the redshift evolution of anisotropic clustering.
+   In the left and right panels, we plot the galaxies postions computed in two cosmologies: the $\Omega_m$=0.26 $\Lambda$CDM, 
+   and a dynamical dark energy cosmology with $\Omega_m=0.26,\ w_0=-1,\ w_a=-2$.
+   The redshifts and comoving distances (in unit of $h^{-1}\rm Mpc$) of the redshift bins are listed.
+   %The shape of structures look different in these two cosmologies. 
+   In the dynamical dark energy cosmology, we see apprent relative stretch of structures compared with the $\Lambda$CDM cosmology.
+   The stretch is not significant in the first redshift bin, and becomes large in the higher redshift bins.
+   We use this phenomena to discover the AP effect and place constraints on cosmologies.
+   %By investigating how the anosotropy of galaxy distribution evolves in the six redshift bins,
+   %we are able to distinguish different cosmologies.
+   %The obtained galaxy distribution is different.
+   %
+   %The blue and green solid histograms show the redshift density distribution of LOWZ and CMASS galaxies in the $\Omega_m=0.31$ $\Lambda$CDM. 
+   %The vertical dashed lines define the six redshift bins that are used to cut the samples.
+   %The number of LOWZ/CMASS galaxies in the three low/high redshift bins are listed.
+   %Right panel: 2D contour map of measured $\xi$ as a function of $\mu$ and $s$, from the six redshift bins of LOWZ and CMASS samples, 
+   %   in the cosmology of $\Omega_m=0.31$ $\Lambda$CDM model.
+   % The black dashed lines mark the clustering region 6-40\ Mpc/h studied in the AP method.
+   % The six contour maps have rather similar appearance, implying small redshift evolution of $\xi$ from RSD.
+   }
+\end{figure*}
+
 The  origin  of  the late-time accelerating  expansion  of  the  universe  is  one of  the  most  salient  questions  in  contemporary cosmology. 
 Theoretical explanations for this phenomena are many and range from a non-zero  vacuum energy and evolving  scalar  fields  remnant  from  the  big  bang, 
-to modifications of Einstein's General Relativity\cite{2012IJMPD..2130002Y}. 
+to modifications of Einstein's General Relativity \citep{2012IJMPD..2130002Y}. 
 Considering the wealth of theoretical explanations, 
@@
 
-The symmetry properties of galaxy pairs\cite{Marinoni2010}  could also be used to probe the AP effect;
+The symmetry properties of galaxy pairs\citep{Marinoni2010}  could also be used to probe the AP effect;
 however, since the peculiar velocity distorts the redshifts and changes the apparent tilt angles of galaxy pairs,
@@
 
-In an effort to minimize RSD contamination, the shape of void regions\cite{Ryden1995,LavausWandelt1995}  has been 
-proposed as an AP probe.
-This approach has the advantage that the void regions are easier to model compared with dense regions, but has limitations in that it utilizes only low density regions of the LSS and requires large samples to achieve competitive constraints \citep{Qingqing2016}.
+In an effort to minimize RSD contamination, the shape of void regions\citep{Ryden1995,LavausWandelt1995}  has been 
+proposed as an AP probe. This approach has the advantage that the void regions are easier to model compared with dense regions, 
+but has limitations in that it utilizes only low density regions of the LSS and requires large samples to achieve competitive constraints \citep{Qingqing2016}.
 
@@
 
-Previously, we proposed to use the {\it redshift dependence} of the AP distortion\cite{Li2014} as a way of mitigating the RSD effect.
+Previously, we proposed to use the {\it redshift dependence} of the AP distortion\citep{Li2014} as a way of mitigating the RSD effect. 
 The clustering anisotropies produced by RSD are, although large, close to uniform in magnitude over a wide range in redshift.  
@@
 when incorrect cosmologies are used to infer distances).
-In a later work\cite{Li2015}, we developed an AP methodology 
+In \cite{Li2015}, we developed an AP methodology 
 that utilizes the redshift dependence of the galaxy 2-point correlation function (2pCF), 
 measured as a function of angle between the galaxy pair and line-of-sight (LoS).
+
+\begin{figure*}
+   \centering{
+   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
+   \includegraphics[width=8.95cm]{fig_xi_cosmo1.eps}
+   \includegraphics[width=8.95cm]{fig_xi_cosmo2.eps}
+   }
+   \caption{\label{fig_xi}
+   $\hat\xi_{\Delta s}(\mu)$ measured from BOSS DR12 galaxies, in six redshift bins (three in LOWZ and three in CMASS).
+   This time we adopt the $\Omega_m=0.26$ $\Lambda$CDM cosmology and a more dark energy dominated cosmology, $\Omega_m=$0.11.
+   The measurement in each redshift bin and the redshift evolution with respective to the measurement in first bin of LOWZ are shown.
+   For comparison, the measurements in the HR4 mock catalogues (always in the $\Omega_m=0.26$ $\Lambda$CDM cosmology) are also plotted in green color.
+   The simulation results can match the shape of curves measured from real observational data, 
+   indicating that the FoG and Kaiser effects are well reproduced.
+   In the cosmology $\Omega_m$=0.11 cosmology, the shapes of $\hat\xi_{\Delta s}(\mu)$ are different from the $\Omega_m=0.26$ cosmology results,
+   and the amount of difference changes with redshift.
+   A large redshift evolution of $\hat\xi_{\Delta s}(\mu)$ is detected in this cosmology, 
+   indicating that it is not likely to be the underlying true cosmology of our universe.
+   For the $\Omega_m$=0.11 cosmology, we also plot the approximate 2pCFs (red dashed lines) 
+     inferred using the technique described in Sec. \ref{sec:approx_2pcf}.
+   The error induced in the approximate procedure is $\lesssim0.5\%$.
+   }
+\end{figure*}
 
@@
 or indeed any appropriately chosen parametric or non-parametric decomposition of the cosmic expansion history. 
-However, as a first step, in this paper we will focus on the widely used Chevallier-Polarski-Linder (CPL) parametrization\cite{CPL_CP,CPL_L},
+However, as a first step, in this paper we will focus on the widely used Chevallier-Polarski-Linder (CPL) parametrization\citep{CPL_CP,CPL_L},
 \begin{equation}
@@
 the bounded behavior at high redshift, 
-and the ability to accurately reconstruct many dark energy theories\cite{CPL_L}. 
+and the ability to accurately reconstruct many dark energy theories\citep{CPL_L}. 
 So it was widely used in the literature to reconstruct dark energy from observations.
-The constraining power is usually quantified by the DETF (Dark Energy Task Force) \cite{DETF} figure of merit, 
+The constraining power is usually quantified by the DETF (Dark Energy Task Force) \citep{DETF} figure of merit, 
 defined as the reciprocal of the area of the error ellipse enclosing the 95\% confidence limit (CL) in the $w_0-w_a$ plane. 
@@
 and the CMASS sample covers a higher redshift ($0.4\lesssim z \lesssim 0.7$),
-targeted to be an approximately stellar mass limited sample of massive, luminous galaxies \cite{Reidetal:2016}.
+targeted to be an approximately stellar mass limited sample of massive, luminous galaxies \citep{Reidetal:2016}.
 In the clustering analysis we use 1,133,326 galaxies, split into six, non-overlapping redshift bins, 
 $0.150<z_1<0.274<z_2<0.351<z_3<0.430<z_4<0.511<z_5<0.572<z_6<0.693$.
-The number density of galaxies and the redshift binning scheme is plotted in the left panel of Figure \ref{fig_TpCF}.
-
-\begin{figure*}
-   \centering{
-   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
-   \includegraphics[height=6.5cm]{fig_nbar.eps}
-   \includegraphics[width=9.0cm,]{fig_2pcf.eps}
-   }
-   \caption{\label{fig_TpCF}
-   Splitting the SDSS galaxies into six redshift bins, and measuring the correlation function
-   (similar figures already presented in \cite{Li2016}).
-   Left panel: We split the BOSS DR12 galaxies into six redshift bins to measure the evolution of shape distortion.
-   The blue and green solid histograms show the redshift density distribution of LOWZ and CMASS galaxies in the $\Omega_m=0.31$ $\Lambda$CDM. 
-   The vertical dashed lines define the six redshift bins that are used to cut the samples.
-   The number of LOWZ/CMASS galaxies in the three low/high redshift bins are listed.
-   Right panel: 2D contour map of measured $\xi$ as a function of $\mu$ and $s$, from the six redshift bins of LOWZ and CMASS samples, 
-      in the cosmology of $\Omega_m=0.31$ $\Lambda$CDM model.
-    The black dashed lines mark the clustering region 6-40\ Mpc/h studied in the AP method.
-    The six contour maps have rather similar appearance, implying small redshift evolution of $\xi$ from RSD.
-   }
-\end{figure*}
-
-\begin{figure*}
-   \centering{
-   \includegraphics[width=16cm]{fig_smu.eps}
-%   \includegraphics[width=10.5cm]{fig_comp.eps}
-   }
-   \caption{\label{fig_method}
-   Mapping $\xi(s,\mu)$ from the fiducial cosmology (taken as the $\Omega_m=0.26$ $\Lambda$CDM cosmology) to other cosmologies. 
- The number counts are measured in the fiducial cosmology in the blue dashed grid.
- In the four cosmologies with $(w_0,w_a) = (-1.5,0),\ (-0.5,0),\ (-1,2)\ \rm and\ (-1,-2)$,
- %due to the distortion of geometry,
- according to Equation \ref{eq:smumap},
- the distribution of measured number counts in $(s, \mu)$ space becomes the red solid grid,
- To ensure the accuracy, we count the number of pairs in 5 times smaller pixels (the small red pixels), 
- and group them together to infer the values of $\xi(s, \mu)$ in blue dashed grid.
- For illustration purpose, 
-  the blue and red grids are all 10 times sparser than the grids adopted in real analysis.
-}
-\end{figure*}
-
-\begin{figure*}
-   \centering{
-   \includegraphics[width=8.5cm]{fig_comp.eps}
-   \includegraphics[width=8.5cm]{fig_IO.eps}
-   }
-   \caption{\label{fig_Check}
- Left panel: Cosmological constraints from the BOSS DR12 galaxies, in the $\Omega_m$-$w_0$ plane. 
- The value of $w_a$ is fixed as zero.
- Results obtained using the precise 2pCFs (cyan filled) 
- and approximate 2pCFs (blue solid) agree with each other quite well.
- Right panel: Input-output test of the methodology using four sets of HR4 mock catalogues.
- The approximate 2pCFs are used in the analysis.
- The simulation cosmology, $\Omega_m=0.26$ $\Lambda$CDM, is marked by the black plus.
- The inferred cosmological constraints from the method, shown in the cygan contours, are consistent with the input cosmology.
-   }
-\end{figure*}
-
-Following our previous methodology \citep{Li2016}, the information of small-scale anisotropic clustering is computed.
+The edges are determined so that the number of galaxies are roughly the same in different redshift bins 
+(for LOWZ and CMASS samples, respectively).
+
+%The number density of galaxies and the redshift binning scheme is plotted in the left panel of Figure \ref{fig_TpCF}.
+
+Figure \ref{fig_fan} shows the positions of a patch of 10,976 BOSS DR12 glaxies,
+computed in the $\Omega_m$=0.26 $\Lambda$CDM cosmology and a dynamical dark energy cosmology with $\Omega_m=0.26,\ w_0=-1,\ w_a=-2$.
+The shape of structures look different in these two cosmologies. 
+In the later cosmology, there is apprent stretch of structures, 
+and the degree of compression becomes more significant in higher redshift bins.
+By investigating how the anosotropy of galaxy distribution evolves in the six redshift bins,
+we are able to distinguish this cosmology from the $\Lambda$CDM cosmology.
+
+Following our previous methodology \citep{Li2016}, the information of small-scale anisotropic clustering is computed as 
 %\footnote{These correlations were computed using the public code \texttt{KSTAT} \citep{kstat}.} 
-as $\xi_{\Delta s} (\mu) \equiv \int_{s_{\rm min}}^{s_{\rm max}} \xi (s,\mu)\ ds$, 
+\begin{equation}
+\xi_{\Delta s} (\mu) \equiv \int_{s_{\rm min}}^{s_{\rm max}} \xi (s,\mu)\ ds,
+\end{equation}
 with $s_{\rm min}=6 h^{-1} {\rm Mpc},\ s_{\rm max}=40 h^{-1} {\rm Mpc}$.
 We then normalize these {\em clustering shells} as 
-$\hat\xi_{\Delta s}(\mu) \equiv \frac{\xi_{\Delta s}(\mu)}{\int_{0}^{\mu_{\rm max}}\xi_{\Delta s}(\mu)\ d\mu}$
+\begin{equation}
+\hat\xi_{\Delta s}(\mu) \equiv \frac{\xi_{\Delta s}(\mu)}{\int_{0}^{\mu_{\rm max}}\xi_{\Delta s}(\mu)\ d\mu}
+\end{equation}
 to nullify the amplitude information of the clustering signal, 
 which is not associated with the Alcock-Paczynski test and is mostly sensitive to the galaxy bias.
-
-The right panel of Figure \ref{fig_TpCF} shows the contour map of $\xi(s,\mu)$ measured in the six redshift bins.
-The contour lines are not horizontal due to the effects of peculiar velocity,
-and the RSD effect clearly manifest itself through the tilting of contour lines.
-However, the shape of the tilted lines remain similar at different redshifts, a fact that enables us  to mitigate the RSD effect by focusing on the redshift dependence of the anisotropic clustering signal.
+%The right panel of Figure \ref{fig_TpCF} shows the contour map of $\xi(s,\mu)$ measured in the six redshift bins.
+%The contour lines are not horizontal due to the effects of peculiar velocity,
+%and the RSD effect clearly manifest itself through the tilting of contour lines.
+%However, the shape of the tilted lines remain similar at different redshifts, a fact that enables us  to mitigate the RSD effect by focusing on the redshift dependence of the anisotropic clustering signal.
 The ``correct'' cosmological model is selected by minimizing the amount of redshift evolution of $\hat\xi_{\Delta s}$,
@@
 We use a number of $n_{\mu}$=20, 21, ... 25 bins for the value of $\hat\xi_{\Delta s}(\mu)$ at $0<\mu<\mu_{\rm max}$.
-For the removal of fiber collision and the strong FoG effect near the LOS we take a cut $\mu_{\rm max} = 0.97$.
-
-Systematics effects are estimated using mock catalogues derived from Horizon Run 4 (HR4) \cite{HR4},
+For the removal of fiber collision and the strong finger of god (FoG) effect \citep{FOG} near the LOS we take a cut $\mu_{\rm max} = 0.97$.
+
+Systematics effects are estimated using mock catalogues derived from Horizon Run 4 (HR4) \citep{HR4},
 an N-body simulation with box size $L={3150}$ $h^{-1}$Mpc, number of particles $6300^3$,   
@@
 $(\Omega_{b},\Omega_{m},\Omega_\Lambda,h,\sigma_8,n_s)$  = (0.044, 0.26, 0.74, 0.72, 0.79, 0.96). 
+Mock galaxy samples are produced using a modified version of the one-to-one correspondence scheme \citep{hong2016}. 
 As presented in \cite{Li2016}, the value of $\left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right]_{\rm sys}$
@@
 and is minor ($\lesssim2\%$) at the other redshift bins.
-Mock galaxy samples are produced using a modified version of the one-to-one correspondence scheme \citep{hong2016}. 
+
 The covariance matrix, ${\bf Cov}$, is computed from the 2,000 sets of MultiDark PATCHY mock catalogues \citep{MDPATCHY}.
@@
 
+The MultiDark PATCHY  mocks are produced using approximate gravity solvers and analytical-statistical biasing models.
+They were calibrated to the BigMultiDark N-body simulation \citep{K2014}, which 
+uses $3\,840^3$ particles in a volume of $(2.5h^{-1}\rm Gpc)^3$,
+assuming a $\Lambda$CDM cosmology with 
+$(\Omega_{b},\Omega_{m},h,\sigma_8,n_s)$  = (0.048206, 0.307115, 0.6777, 0.8288, 0.9611). 
+%$\Omega_m = 0.307115$, $\Omega_b = 0.048206$, $\sigma_8 = 0.8288$, $n_s = 0.9611$, and $H_0 = 67.77 {\rm km}\ s^{-1} {\rm Mpc}^{-1}$.
+The mock surveys can well reproduce the number density, 
+selection function, survey geometry, and 2pCF measurement of the BOSS DR12 catalogues.
+They have been adopted for statistical analysis of BOSS data in a series of works (see \cite{Alam2016} and references therein).
+
 \begin{figure*}
    \centering{
-   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
-   \includegraphics[width=8cm,natwidth=6,natheight=4.5]{figCPL_b.pdf}
-   %\includegraphics[width=5.5cm,natwidth=4,natheight=4]{figCPL_b_BAOSNIaAP.pdf}
-   \includegraphics[width=8cm,natwidth=6,natheight=4.5]{figCPL_d.pdf}
-   %\includegraphics[height=8cm]{fig2b.pdf}
-%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
-%    \includegraphics[height=8cm]{smu.eps}
-   }
-   \caption{\label{fig_con}
-   Cosmological constraints on the CPL dark energy parametrization $w=w_0+w_a\frac{z}{1+z}$.
-   Left panel: 68.3\%, 95.4\% CL likelihood contours in the  $w_0-w_a$ plane.
-   %Results are consistent with $\Lambda$CDM.
-   The constrained area is significantly reduced after combined with the AP method.
-   %This shows the power of the AP method in constraining dynamical dark energy.
-   %Middle panel: $w_0-w_a$ likelihood contours using datasets of CMB+BAO, CMB+BAO+SNIa+$H_0$ and CMB+BAO+AP+$H_0$.
-   %When combined with CMB+BAO, AP method yields much tighter constraints than SNIa.
-   Right panel: Redshift evolution of $w(z)$, with/without adding the AP constraint.
-   Adding AP tightens the constraints and reduces the redshift evolution of $w$ (tilt of $w(z)$).
+   \includegraphics[width=12cm]{fig_smu.eps}
+%   \includegraphics[width=10.5cm]{fig_comp.eps}
+   }
+   \caption{\label{fig_method}
+   Mapping $\xi(s,\mu)$ from the fiducial cosmology (taken as the $\Omega_m=0.26$ $\Lambda$CDM cosmology) to other cosmologies. 
+ The number counts are measured in the fiducial cosmology in the blue dashed grid.
+ In the four cosmologies with $(w_0,w_a) = (-1.5,0),\ (-0.5,0),\ (-1,2)\ \rm and\ (-1,-2)$,
+ %due to the distortion of geometry,
+ according to Equation \ref{eq:smumap},
+ the distribution of measured number counts in $(s, \mu)$ space becomes the red solid grid,
+ To ensure the accuracy, we count the number of pairs in 5 times smaller pixels (the small red pixels), 
+ and group them together to infer the values of $\xi(s, \mu)$ in blue dashed pixels.
+ For illustration purpose, 
+  the blue and red grids are all 10 times sparser than the grids adopted in the real analysis.
 }
 \end{figure*}
-
-%Covariance matrix
 
@@
    \centering{
-   \includegraphics[width=18cm,natwidth=6,natheight=5]{fig_con_tests.pdf}
-   %\includegraphics[width=9cm,natwidth=4,natheight=4]{fig2b.pdf}
-   %\includegraphics[height=8cm]{fig2b.pdf}
-%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
-%    \includegraphics[height=8cm]{smu.eps}
-   }
-   \caption{\label{fig_contest}
-   Robustness test of the results.
-   For the ``default'' constraints (pink contours) are derived using six redshift bins, 
-   $\mu_{\rm max}=0.97$, $n_{\mu}=15-20$, $s=6-40 \rm Mpc/h$,
-   a fiducial cosmology $\Omega_m=0.26,\ w=-1.0$ for the measurement of 2pCF,
-   systematic effects estimated from Horizon Run 4 simulations, 
-   and covariance estimated using 2,000 MultiDark PATCHY mocks.
-   When we alters one of these options by using $\mu_{\rm max}=0.99$, 
-   $\mu_{\rm max}=0.85$, $n_{\mu}=15-20$, $s=8-30 \rm Mpc/h$, 
-   a fiducial cosmology of $\Omega_m=0.26,\ w=-0.6$, 
-   excluding the last redshift bin in the analysis, 
-   discarding the systematics correction, 
-   or reducing the number of mocks in the estimation of covariance matrix,
-   the results remain robust (black contours).
+   \includegraphics[width=8.5cm]{fig_IO.eps}
+   \includegraphics[width=8.5cm]{fig_comp.eps}
+   }
+   \caption{\label{fig_Check}
+ Left panel: Input-output test of the methodology using four sets of mock catalogues of BOSS DR12 galaxies constructed from the HR4 simulation.
+ The approximate 2pCFs are adopted in the analysis.
+ The simulation cosmology, $\Omega_m=0.26$ $\Lambda$CDM, is marked by the black plus.
+ The inferred cosmological constraints from the method, shown in the cygan contours, are consistent with the input cosmology.
+ Right panel: Cosmological constraints from the BOSS DR12 galaxies, assuming a $w$CDM cosmology 
+ (i.e., the value of $w_a$ fixed as zero).
+ Results obtained using the precise 2pCFs (cyan filled) 
+ and approximate 2pCFs (red dashed) agree with each other quite well.
+ The computation of precise 2pCFs is very expensive,
+ so the comparison was done on a coarse grid of cosmological parameters with $\delta \Omega_m=0.025,\ \delta w=0.05$.
    }
@@
 
-\subsection{Approximating the 2pCFs in cosmologies other than the fiducial one}
-
-In our earlier work\cite{Li2016}, the likelihood contour of $\Omega_m-w$ was constructed by
+As an illustration,
+Figure \ref{fig_xi} shows how we us the above procedure to distinguish different cosmologies.
+Here we plot the value of $\hat\xi_{\Delta s}(\mu)$, as long as its redshift evolution, 
+measured from the BOSS DR12 galaxies in six redshift bins.
+Two $\Lambda$CDM cosmologies are adopted, 
+one with $\Omega_m=0.26$, and the other with obviously wrong value of $\Omega_m=0.11$.
+
+The shape of $\hat \xi_{\Delta s}(\mu)$ is far away from a flat curve, 
+due to the apparent anisotropy produced by the peculiar montion of galaxies.
+In the $\Omega_m=0.11$ cosmology, 
+the shapes of $\hat\xi_{\Delta s}(\mu)$ are different from the measurements in the $\Omega_m=0.26$ cosmology,
+and the amount of difference systematically evolves with redshift.
+So we observe a large redshift evolution of $\hat\xi_{\Delta s}(\mu)$, 
+indicating that it is not likely to be the underlying true cosmology of our universe.
+
+The green curves denote the 2pCFS measured from the HR4 mock catalogues
+(we always plot the {\it correct} measurement in the simulation cosmology, i.e. the $\Omega_m=0.26$ $\Lambda$CDM).
+%The small redshift evolution of $\hat \xi_{\Delta s}(\mu)$
+The simulation results can well match the results from real observational data,
+indicating that the FoG \citep{FOG} and Kaiser \citep{Kaiser1987} effects are both well reproduced.
+Since there is no AP effect in the simulation measurements,
+all detected redshift evolution should be due to effects other than the cosmological effect; 
+so they are adopted as an estimation of the systematic effects of the method.
+The amount of systematics reaches 4-6\% in the 6th redshift bin,
+and is much smaller ($\lesssim2\%$) in the other bins.
+
+\subsection{Approximating the 2pCFs in cosmologies other than the fiducial one}\label{sec:approx_2pcf}
+
+In our earlier work\citep{Li2016}, the likelihood contour of $\Omega_m-w$ was constructed by
 measuring the 2PCF 3,375 times,
@@
 %with $0.06\leq \Omega_m\leq 0.41$, $-1.5 \leq w \leq -0.4$.
-This procedure took 1 month using 500 cores of the KIAS {\texttt {baekdu}} cluster.
+This procedure took 1 month using 500 cores of the Korea Institute for Advanced Study {\texttt {baekdu}} cluster.
 It would be computationally intractable to attempt a full MCMC of all relevant cosmological parameters using this approach. 
@@
 In the case when one small pixel belongs to more than one larger pixel,
-a correction is applied by computing the fraction of the overlapping area.
+a correction is applied by computing the fraction of the overlapping area
 %in the fiducial cosmology and group the bins in the target cosmology.
-%\footnote{A dense grid can effectively reduce the ``edge effect'' produced when we map $\xi(s,\mu)$ from one cosmology to another.
+\footnote{A denser grid can significantly reduce the edge effect;
+if we use Equation \ref{eq:smumap} to do a simple interpolation on a grid with same resoultion does not work,
+the edge effect is so large that the derived cosmological constraints suffer from a significant error.}
 %The edge effect would introduce artificial correlations between nearby pixels, smooth $\xi(s,\mu)$ a little bit, 
@@
 
-The approximation procedure only introduces a $\lesssim0.5\%$ error in the $\hat\xi_{\Delta s}(\mu)$, 
+Figure \ref{fig_xi} plots the approximate 2pCFS in the $\Omega_m=0.11$ $\Lambda$CDM cosmology.
+We find that, the approximation procedure only introduces a $\lesssim0.5\%$ error in the $\hat\xi_{\Delta s}(\mu)$, 
 which is 10 times smaller than the noise of $\hat\xi_{\Delta s}(\mu)$.
-We checked that the approximate method can reproduce the results of precise method quite well.
-The left panel of Figure \ref{fig_Check} shows the  $\Omega_m$-$w_0$ constraints obtained 
-  using the precise and approximate 2pCFs (here we fix $w_a=0$). 
-They agree with each other quite well.
-
-To further check the robustness of the approximate method, 
-we did an input-output test using the four sets of HR4 mock catalogues \cite{HR4}.
-The results are shown in the right panel of Figure \ref{fig_Check}. 
+So we expect that the approximate method can reproduce the results of precise method quite well.
+
+An input-output test was performed using the four sets of mock catalogues of BOSS DR12 galaxies constructed from HR4 \citep{HR4}.
+The results are shown in the left panel of Figure \ref{fig_Check}. 
 The input cosmology is the simulation cosmology, i.e. $\Omega_m=0.26$ $\Lambda$CDM.
 It lies within the 1$\sigma$ conour of the inferred constraints.
+The right panel of Figure \ref{fig_Check} shows the cosmological constraints in case of fixing $w_a$ as 0 (hereafter $w$CDM).
+Results obtained using the precise and approximate 2pCFs agree quite well with each other.
 
@@
 
-\section{Results}
-
-The Planck team has released the {\texttt {COSMOMC}} \citep{LB2002} outputs of four MCMC ``chains'' in the CPL model, 
+\section{Cosmoligical constraints}
+
+The Planck team has released the {\texttt {COSMOMC}} \citep{LB2002} outputs of four Markov Chain Monte Carlo (MCMC) 
+``chains'' in the CPL model, 
 using a combination of four datasets:
-the full-mission Planck observations of CMB temperature and polarization anisotropies \cite{Planck2015},
+the full-mission Planck observations of CMB temperature and polarization anisotropies \citep{Planck2015},
 the BAO distance priors measured from SDSS DR11 \citep{Anderson2013}, 6dFGS \citep{6dFGS} and SDSS MGS \citep{MGS},
 the ``JLA'' SNIa sample \citep{JLA},
-and the Hubble Space Telescope measurement of $H_0=70.6\pm3.3$ km/s/Mpc \cite{Riess2011,E14H0}.
-These MCMC chains contain the CMB+BAO+SNIa+$H_0$ likelihood computed for $\sim$37,000 sets of cosmological parameters,
-yielding constraints of %$ \Omega_m = 0.309 \pm 0.010, w_0 = -0.938 \pm 0.109, w_a = -0.38 \pm 0.41$.
-%\begin{eqnarray}
-% \Omega_m &=& 0.309 \pm 0.010,  \\ \nonumber
-% w_0 &=& -0.938 \pm 0.109,  \\ \nonumber
-% w_a &=& -0.38 \pm 0.41.
-%\end{eqnarray}
-\small
-\begin{equation}
- \Omega_m = 0.309 \pm 0.010,\
- w_0 = -0.938 \pm 0.109,\
- w_a = -0.38 \pm 0.41.
-\end{equation}
-\normalsize
+and the Hubble Space Telescope measurement of $H_0=70.6\pm3.3$ km/s/Mpc \citep{Riess2011,E14H0}.
+These MCMC chains contain the CMB+BAO+SNIa+$H_0$ likelihood computed for $\sim$37,000 sets of cosmological parameters.
 %To derive the constraints combined with our AP method,
@@
 %To do this, we splited the 1,133,326 galaxies from the SDSS DR12 into six redshift bins,
-%measured the 2pCF (on scales of 6-40 $h^{-1}$Mpc) in these redshift bins (see Fig.\ref{fig_nbar}).
+%measured the 2pCF (on scales of 6-40 $h^{-1}$Mpc) in these redshift bins (see Figure \ref{fig_nbar}).
 %This enables us investigating the redshift evolution of anisotropic clustering.
@@
 while also multiply the sample weights by our likelihoods, 
-we derive the CMB+BAO+SNIa+$H_0$+AP constraints on CPL parameters, %$\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29$.
-%\begin{eqnarray}
-%\Omega_m &=& 0.301 \pm 0.008, \\ \nonumber
-%w_0 &=& -1.042 \pm 0.067, \\ \nonumber
-%w_a &=& -0.07 \pm 0.29.
-%\end{eqnarray}
-\small
-\begin{equation}
- \Omega_m = 0.301 \pm 0.008,\
- w_0 = -1.042 \pm 0.067,\
- w_a = -0.07 \pm 0.29.
-\end{equation}
-\normalsize
+we derive the CMB+BAO+SNIa+$H_0$+AP constraints on CPL parameters. %$\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29$.
+
+\subsection{Results}
+
+\begin{figure*}
+   \centering{
+   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
+   \includegraphics[width=8.3cm,natwidth=8,natheight=8]{figCPL_a1.pdf}
+   %\includegraphics[width=5.5cm,natwidth=4,natheight=4]{figCPL_b_BAOSNIaAP.pdf}
+   \includegraphics[width=8.3cm,natwidth=8,natheight=8]{figCPL_a2.pdf}
+   %\includegraphics[width=18cm,natwidth=16,natheight=7]{figCPL_d.pdf}
+   %\includegraphics[height=8cm]{fig2b.pdf}
+%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
+%    \includegraphics[height=8cm]{smu.eps}
+   }
+   \caption{\label{fig_con}
+   Cosmological constraints on the CPL dark energy parametrization $w=w_0+w_a\frac{z}{1+z}$.
+   68.3\%, 95.4\% CL likelihood contours in the $\Omega_m-w_0$  and $w_0-w_a$ planes are plotted in the left and right panels, respectively.
+   Results from the AP method alone (brown filled), CMB+BAO (cygan filled), CMB+BAO+SNIa+$H_0$ (blue filled)
+   and CMB+BAO+SNIa+$H_0$+AP (magenta filled) are shown.
+   To see the effect of systematic effect, we also plot the AP alone and CMB+BAO+SNIa+$H_0$+AP constraints 
+   before conducting the systematics correction procedure (the gray solid and black dashed lines, labeled by ``with sys'').
+   %The AP method leads to competitive constraints on the cosmological parameters.
+   Adding the AP method to the combination of CMB+BAO+SNIa+$H_0$ reduces the contour area by about 50\%. %significantly reduced the area of contour.
+   Systematics does not have significant influence on the results.% are less affected by systematics effect.
+   %If we discard the systematics correction, there is half-$\sigma$ shift of the AP alone contour.
+   %The combined constraints are less affected.
+   %This suggests that, for the data analysis of current galaxy surveys,
+   %the systematic effects in our method is not significant.
+   %This shows the power of the AP method in constraining dynamical dark energy.
+   %Middle panel: $w_0-w_a$ likelihood contours using datasets of CMB+BAO, CMB+BAO+SNIa+$H_0$ and CMB+BAO+AP+$H_0$.
+   %When combined with CMB+BAO, AP method yields much tighter constraints than SNIa.
+   %Right panel: Redshift evolution of $w(z)$, with/without adding the AP constraint.
+   %Adding AP tightens the constraints and reduces the redshift evolution of $w$ (tilt of $w(z)$).
+   }
+\end{figure*}
+
+\begin{figure*}
+   \centering{
+   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
+   %\includegraphics[width=8cm,natwidth=6,natheight=4.5]{figCPL_b.pdf}
+   %\includegraphics[width=5.5cm,natwidth=4,natheight=4]{figCPL_b_BAOSNIaAP.pdf}
+   \includegraphics[width=11cm,natwidth=9,natheight=7]{figCPL_d.pdf}
+   %\includegraphics[height=8cm]{fig2b.pdf}
+%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
+%    \includegraphics[height=8cm]{smu.eps}
+   }
+   \caption{\label{fig_wz}
+   %Cosmological constraints on the CPL dark energy parametrization $w=w_0+w_a\frac{z}{1+z}$.
+   %Left panel: 68.3\%, 95.4\% CL likelihood contours in the  $w_0-w_a$ plane.
+   %Results are consistent with $\Lambda$CDM.
+   %The constrained area is significantly reduced after combined with the AP method.
+   %This shows the power of the AP method in constraining dynamical dark energy.
+   %Middle panel: $w_0-w_a$ likelihood contours using datasets of CMB+BAO, CMB+BAO+SNIa+$H_0$ and CMB+BAO+AP+$H_0$.
+   %When combined with CMB+BAO, AP method yields much tighter constraints than SNIa.
+   Derived redshift evolution of $w(z)$, with/without adding the AP constraint.
+   The 68.3\% and 95.4\% CL regions are plotted.
+   Adding the AP method tightens the constraints and reduces the redshift evolution of $w$ (the tilt of $w(z)$).
+   There is no significant change in the results if we disgard the systematics correction procedure in the AP method analysis.
+   }
+\end{figure*}
+
 %While the central values of parameters do not shift appreciably,
-As a result of the additional constraint from our AP analysis,
-the error bars of $w_0$ and $w_a$ are reduced by 38.4\% and 29.7\%, respectively.% $$-40\%$ by adding our method into the analysis.
-It can be also noted that the central value of $w_a$ moved to zero appreciably.
-
-The marginalized constraints on $w_0-w_a$ are shown in the left panel of Fig.\ref{fig_con}.
-Adding our new AP constraints significantly reduces the allowable parameter space. 
-This can also be visualized as allowable bands in $w(z)$ as can be seen in the right panel of Fig.\ref{fig_con}.
-
-The derived cosmological constraints are fully consistent with a cosmological constant dark energy component having no evolution.
+%Covariance matrix
+
+Figure \ref{fig_con} shows the 68.3\% and 95.4\% CL likelihood contours in the $\Omega_m-w_0$  and $w_0-w_a$ planes,
+derived from the AP method alone, CMB+BAO, CMB+BAO+SNIa+$H_0$
+and CMB+BAO+SNIa+$H_0$+AP, respectively.
+The overlapping of different contours suggest that they are consistent with each other.
+
+Using AP method alone, we can lead to effective constraints on the parameter space in the $\Omega_m-w_0$ plan.
+Due to the inclusion of one extra free parameter, 
+the constrained area becomes larger than $w$CDM result \citep{Li2016}.
+Given the current galaxy surveys it is difficult to effectively constrain $w_a$ using only one technique.
+We have to combine various techniques.
+
+Combinig the four external techniques, i.e. CMB+BAO+SNIa+$H_0$, leads to effective constraints on all parameters.
+The statistical mean values and 68.3\% uncertainties of these parameters are
+\begin{eqnarray}
+&\Omega_m = 0.309 \pm 0.010,\\
+&w_0 = -0.938 \pm 0.109,\\
+&w_a = -0.38 \pm 0.41,
+\end{eqnarray}
+while adding our AP method to this combination further tightens the constraints and yield to
+\begin{eqnarray}
+&\Omega_m = 0.301 \pm 0.008,\\
+&w_0 = -1.042 \pm 0.067,\\
+&w_a = -0.07 \pm 0.29.
+\end{eqnarray}
+The error bars are dramatically reduced by 30-40\%.
+The contour areas are reduced by 50\%, i.e., the dark energy figure of merit was improved by 100\%. 
+Notice that the AP constraints come from the BOSS DR12 data, which is already used in the BAO analysis.
+So the doubling of the figure of merit comes at no additional cost or alteration to data size,
+thus greatly improving the overall cost-benefit of large cosmological redshift surveys.
+
+It can be also noted that, after adding the AP method, the central value of $w_a$ moved to zero appreciably.
+This means the result becomes more consistent with a cosmological constant dark energy component having no evolution.
+Figure \ref{fig_wz} shows the redshift evolution of $w(z)$ derived from the cosmological constraints.
+Adding AP tightens the constraints and reduces the redshift evolution of $w$ (tilt of $w(z)$).
+
+\begin{figure*}
+   \centering{
+   \includegraphics[width=18cm,natwidth=6,natheight=5]{fig_con_tests.pdf}
+   %\includegraphics[width=9cm,natwidth=4,natheight=4]{fig2b.pdf}
+   %\includegraphics[height=8cm]{fig2b.pdf}
+%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
+%    \includegraphics[height=8cm]{smu.eps}
+   }
+   \caption{\label{fig_contest}
+   Robustness test of the results.
+   For the ``default'' constraints (pink contours) are derived using six redshift bins, 
+   $\mu_{\rm max}=0.97$, $n_{\mu}=20-25$, $s=6-40 \rm Mpc/h$,
+   a fiducial cosmology $\Omega_m=0.26,\ w=-1.0$ for the measurement of 2pCF,
+   systematic effects estimated from Horizon Run 4 simulations, 
+   and covariance estimated using 2,000 MultiDark PATCHY mocks.
+   When we alters one of these options by using $\mu_{\rm max}=0.99$, 
+   $\mu_{\rm max}=0.85$, $n_{\mu}=15-20$, $s=6-35 \rm Mpc/h$, $s=6-45 \rm Mpc/h$,  
+   a fiducial cosmology of $\Omega_m=0.26,\ w=-0.6$, 
+   excluding the last redshift bin in the analysis, 
+   or reducing the number of mocks in the estimation of covariance matrix,
+   the results remain robust (black contours).
+   }
+\end{figure*}
+
+\subsection{Robustness}
+
+To see the effect of systematic effect, in Figure \ref{fig_con,fig_wz} we also plot the AP alone and CMB+BAO+SNIa+$H_0$+AP constraints 
+before conducting the systematics correction procedure.
+If we discard the systematics correction, there is a half-$\sigma$ shift of the AP alone constraints,
+and the combined constraints are almost unaffected
+since the direction of shift is orthogonal to the direction of CMB+BAO+SNIa+$H_0$ contour.
+This indicates that, for the data analysis of current galaxy surveys,
+the systematic effects in our method is not significant.
+But it remains to be seen if this is true for future galaxy surveys,
+or when the cosmology dependence of the systematics effects is taken into account.
+The results are less affected by systematics.
 %\cite{Li2016}
-Adding the new AP method to the CMB+BAO+SNIa+$H_0$ constraints reduces the statistical errors on many parameters by $\sim$30-40\% 
-and reduces the $w_0-w_a$ (95.4\% CL) contour by 50\%.
-This constitutes a significant increase in the figure of merit constraints on $(w_0, w_a)$. 
-This doubling of the figure of merit comes at no additional cost or alteration to data size, 
-thus greatly improving the overall cost-benefit consideration of large cosmological redshift surveys.
-
-We performed a test of all the possible variables in our methodology.
-Fig.\ref{fig_contest} shows that 
+
+Finally, we performed a test of all the possible variables in our methodology.
+Figure \ref{fig_contest} shows that 
 the result is unaffected by the line-of-sight $\mu$-cut, 
-the number of angular bins, 
-the range of radial integration and the choice of fiducial cosmology. 
+the range of radial integration, 
+the choice of fiducial cosmology in the mapping of $\xi(s,\mu)$,
+and the number of mocks.
+Reduces the number of angular bins weakens the constraints a little bit,
+and enlarges the contour towards the lower-right direction 
+(the upper-left boundary is determined by the CMB+BAO+SNIa+$H_0$ constraints, so it is unaffected).
 %we adopt $\mu_{\rm max}=0.99\ (0.85)$ to include more (less) regions near the LOS,
@@
 where the estimated systematics is comparably large.
-The most striking point to note in our test is that the 
-shift in contour position is not significant even when %we do not include the systematic correction.
-the systematics are not corrected.
-%This is reassuring, since we may have worried that {\it cosmological dependence} 
-%of the systematic correction could influence the final result. 
-%This suggest that the CPL constraints reported are robust.
-This indicates that, for the data analysis of current galaxy surveys,
-the systematic effects in our method may not be important.
-But it remains to be seen if this is true for future galaxy surveys,
-or when the cosmology dependence of the systematics effects is taken into account.
+This further justifies our conclusion that, the effect of systematics is not significant in this analysis.
 
@@
 governing the expansion history of the universe via 
-the redshift dependence of anisotropic galaxy clustering\cite{Li2016}.
+the redshift dependence of anisotropic galaxy clustering\citep{Li2016}.
 This approach enables a robust AP test on relatively small scales.
@@
 %Yet there are still issues demanding more investigations.
-In this analysis, the systematic effects and the covariance matrices are estimated using simulations performed in a certain cosmology.
-Their cosmological dependence needs to be investigated in future works to guarantee the robustness of the method.
-
-Combining our method with the CMB+SNIa+BAO+$H_0$ datasets,
+In this analysis, we find the systematic effects do not significantly affect the derived cosmological constraints.
+But it remains to be seen if this is true for future galaxy surveys,
+or when the cosmology dependence of the systematics effects is taken into account.
+Espeically, the systematic effects are estimated using simulations performed in a certain cosmology.
+The cosmological dependence remains to be investigated in future works.
+
+In this analysis, combining our method with the CMB+SNIa+BAO+$H_0$ datasets,
 the dark energy figure of merit is improved by a factor of 2.
 %The method can be applied to many spectroscopic galaxy surveys.
+This indicates the great power of the method in constraining the cosmic expansion history and probing the properties of dark energy.
 We expect the method will play an important role in deriving cosmological constraints from future spectroscopic galaxy surveys.
@@
 
-%\bibitem[Jackson (1972)]{FOG}
-%Jackson, J., 1972, MNRAS, 156, 1
+\bibitem[Jackson (1972)]{FOG}
+Jackson, J., 1972, MNRAS, 156, 1
 
@@
 
-%\bibitem[Kaiser (1987)]{Kaiser1987}
-%Kaiser, N. 1987, MNRAS, 227, 1
+\bibitem[Kaiser (1987)]{Kaiser1987}
+Kaiser, N. 1987, MNRAS, 227, 1
 
@@
 Kitaura, F.S., Rodrı\'{i}guez-Torres, S., Chuang, C.-H., et al. arXiv:1509.06400
+
+\bibitem[Klypin et al.(2016)]{K2014}
+Klypin, A., Yepes, G., Gottlober, S., Prada, F., \& Hess, S. 2016,
+MNRAS, 457, 4340%
 

### 2017-11-03 Draft/Draft1.5.tex
minor changes

--- 2017-11-03 Draft/Draft1.4.tex
@@
 \begin{abstract}
-We perform the Alcock-Paczynski (AP) test via the redshift dependence of clustering on scales of 6--40 $h^{-1}\rm Mpc$
+We perform the Alcock-Paczynski (AP) test via the redshift dependence of clustering on scales of 6 -- 40 $h^{-1}\rm Mpc$
 to place constraints on the expansion history of the Universe.
@@
 We improve the methodology of Li et al. to efficiently explore three or more cosmological parameters.
-We then apply the improved method on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$.
+We then apply the improved method on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a{z}/({1+z})$.
 In combination with the CMB, BAO, SNIa and $H_0$ from Cepheid data, we obtain
-$\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ w_a = -0.07 \pm 0.29$ (68.3\% CL). 
+$\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ $ and $w_a = -0.07 \pm 0.29$ (68.3\% CL). 
 Adding our new AP measurements to the aforementioned results 
-reduces the error bars by $\sim$30-40\%,
+reduces the error bars by $\sim$30 -- 40\%,
 %and reduces the area of $w_0-w_a$ contour by 50\%.
@@
    %We split the BOSS DR12 galaxies into six redshift bins to measure the evolution of shape distortion.
-   A patch of BOSS DR12 glaxies located in the fan shape region $\rm 140^\circ < RA < 170 ^\circ$, $\rm 10^\circ < DEC < 13 ^\circ$.
+   A patch of BOSS DR12 galaxies located in the fan shape region $\rm 140^\circ < RA < 170 ^\circ$, $\rm 10^\circ < DEC < 13 ^\circ$.
    We split the sample into six non-overlapping redshift bins
    (marked by the light green rings) in order to probing the redshift evolution of anisotropic clustering.
-   In the left and right panels, we plot the galaxies postions computed in two cosmologies: the $\Omega_m$=0.26 $\Lambda$CDM, 
+   In the left and right panels, we plot the galaxies positions computed in two cosmologies: the $\Omega_m$=0.26 $\Lambda$CDM, 
    and a dynamical dark energy cosmology with $\Omega_m=0.26,\ w_0=-1,\ w_a=-2$.
@@
    %The shape of structures look different in these two cosmologies. 
-   In the dynamical dark energy cosmology, we see apprent relative stretch of structures compared with the $\Lambda$CDM cosmology.
+   In the dynamical dark energy cosmology, we see apparent relative stretch of structures compared with the $\Lambda$CDM cosmology.
    The stretch is not significant in the first redshift bin, and becomes large in the higher redshift bins.
@@
 The  origin  of  the late-time accelerating  expansion  of  the  universe  is  one of  the  most  salient  questions  in  contemporary cosmology. 
-Theoretical explanations for this phenomena are many and range from a non-zero  vacuum energy and evolving  scalar  fields  remnant  from  the  big  bang, 
+Theoretical explanations for this phenomena are numerous and range from a non-zero  vacuum energy, an evolving  scalar  field  remnant  from  the  big  bang, 
 to modifications of Einstein's General Relativity \citep{2012IJMPD..2130002Y}. 
@@
 These distortions are induced by the fact that measured distances along 
-and perpendicular to the line of sight are connected with cosmological parameters differently. 
-Measuring the ratio of galaxy clustering in the radial and transverse directions provides a probe of this AP effect.
+and perpendicular to the line of sight depend on the given cosmological parameters. 
+Therefore, measuring the ratio of galaxy clustering in the radial and transverse directions provides a probe of this AP effect.
 
@@
 
-The symmetry properties of galaxy pairs\citep{Marinoni2010}  could also be used to probe the AP effect;
+The symmetry properties of galaxy pairs \citep{Marinoni2010}  could also be used to probe the AP effect;
 however, since the peculiar velocity distorts the redshifts and changes the apparent tilt angles of galaxy pairs,
@@
 
-In an effort to minimize RSD contamination, the shape of void regions\citep{Ryden1995,LavausWandelt1995}  has been 
+In an effort to minimize RSD contamination, the shape of void regions \citep{Ryden1995,LavausWandelt1995}  has been 
 proposed as an AP probe. This approach has the advantage that the void regions are easier to model compared with dense regions, 
-but has limitations in that it utilizes only low density regions of the LSS and requires large samples to achieve competitive constraints \citep{Qingqing2016}.
+but has limitations in that it utilizes only low density regions of the LSS and requires large samples to attain statistical significances and achieve competitive constraints \citep{Qingqing2016}.
 
@@
 
-Previously, we proposed to use the {\it redshift dependence} of the AP distortion\citep{Li2014} as a way of mitigating the RSD effect. 
+Previously, we proposed to use the {\it redshift dependence} of the AP distortion \citep{Li2014} as a way of mitigating the RSD effect. 
 The clustering anisotropies produced by RSD are, although large, close to uniform in magnitude over a wide range in redshift.  
-However, if cosmological parameters are incorrectly chosen resulting in an AP effect, 
+However, if cosmological parameters are incorrectly chosen to change the AP effect, 
 the anisotropy in the clustering signal has a clear redshift dependence
-(as an illustration, Figure \ref{fig_xy} shows how the shape distortion of objects varies with distance (i.e., redshift) 
+(as an illustration, Figure \ref{fig_xy} shows how the shape distortion of objects varies with distance, i.e., redshift, 
 when incorrect cosmologies are used to infer distances).
@@
 
-In an earlier work\citep{Li2016} we applied this AP method to galaxies from the 3rd incarnation of the Sloan Digital Sky Survey (SDSS-III). 
+In an earlier work \citep{Li2016} we applied this AP method to galaxies from the 3rd incarnation of the Sloan Digital Sky Survey (SDSS-III). 
 Combining the method with measurements of the Cosmic Microwave Background (CMB), type Ia supernovae (SNIa), 
@@
 
-In this paper, we continue to develop our previous methodology and proceed to infer the constraints on dynamical dark energy. 
-We will present a slightly improved methodology to that of our previous work\citep{Li2016}, 
+In this paper, we continue to develop our previous methodology and proceed to set the constraints on dynamical dark energy. 
+We will present an improved methodology compared to that of our previous work \citep{Li2016}, 
 allowing for faster likelihood estimation and thus the exploration of larger, higher dimensional parameter spaces. 
@@
 \end{equation}
-This parametrization characterizes dark energy equation-of-state (EoS) by two free parameters.
+This parametrization characterizes the dark energy equation-of-state (EoS) by two free parameters;
 $w_0$ determines the present-day value, while parameter $w_a$ characterizes the first-order derivative of $w$ with respect to $a$. 
@@
 the bounded behavior at high redshift, 
-and the ability to accurately reconstruct many dark energy theories\citep{CPL_L}. 
-So it was widely used in the literature to reconstruct dark energy from observations.
-The constraining power is usually quantified by the DETF (Dark Energy Task Force) \citep{DETF} figure of merit, 
-defined as the reciprocal of the area of the error ellipse enclosing the 95\% confidence limit (CL) in the $w_0-w_a$ plane. 
-Figure \ref{fig_xy} shows that redshift dependence of shape distortion is sensitive to both $w_0$ and $w_a$.
-So we expect these two parameters effectively constrained by our method.
+and the ability to accurately reconstruct many dark energy theories \citep{CPL_L}. 
+%So it was widely used in the literature to reconstruct dark energy from observations.
+The constraining power is usually quantified by the DETF  \citep[Dark Energy Task Force;][]{DETF} figure of merit, 
+defined as the reciprocal of the area of the error ellipse enclosing the 95\% confidence limit (CL) in the $w_0 - w_a$ plane. 
+Figure \ref{fig_xy} shows that the redshift dependence of the shape distortion is sensitive to both $w_0$ and $w_a$.
+Thus we expect that these two parameters will be effectively constrained by our method.
 
@@
 
-\subsection{Quantifying the redshift dependece of AP distortion}
+\subsection{Quantifying the redshift dependence of the AP distortion}
 
@@
 
-Figure \ref{fig_fan} shows the positions of a patch of 10,976 BOSS DR12 glaxies,
+Figure \ref{fig_fan} shows the positions of a patch of 10,976 BOSS DR12 galaxies,
 computed in the $\Omega_m$=0.26 $\Lambda$CDM cosmology and a dynamical dark energy cosmology with $\Omega_m=0.26,\ w_0=-1,\ w_a=-2$.
 The shape of structures look different in these two cosmologies. 
-In the later cosmology, there is apprent stretch of structures, 
+In the later cosmology, there is apparent stretch of structures, 
 and the degree of compression becomes more significant in higher redshift bins.
-By investigating how the anosotropy of galaxy distribution evolves in the six redshift bins,
+By investigating how the anisotropy of galaxy distribution evolves in the six redshift bins,
 we are able to distinguish this cosmology from the $\Lambda$CDM cosmology.
@@
 \end{equation}
-with $s_{\rm min}=6 h^{-1} {\rm Mpc},\ s_{\rm max}=40 h^{-1} {\rm Mpc}$.
+with $s_{\rm min}=6 h^{-1} {\rm Mpc},$ and $s_{\rm max}=40 h^{-1} {\rm Mpc}$.
 We then normalize these {\em clustering shells} as 
@@
 where ${\bf p}(z_i,\mu_{j})$ is the redshift evolution of clustering with respect to the lowest redshift bin,
-while subtracting systematic effects:
+while subtracting systematic effects as
 \begin{eqnarray}
@@
 
-Systematics effects are estimated using mock catalogues derived from Horizon Run 4 (HR4) \citep{HR4},
-an N-body simulation with box size $L={3150}$ $h^{-1}$Mpc, number of particles $6300^3$,   
-initial redshift $z_{i}=100$, and WMAP5\citep{komatsu2011} cosmological parameters 
+Systematics effects are estimated using mock catalogues derived from Horizon Run 4 \citep[HR4;][]{HR4},
+an N-body simulation with a box size of $L={3150}$ $h^{-1}$Mpc, the number of particles $6300^3$,   
+initial redshift of $z_{i}=100$, and the WMAP5\citep{komatsu2011} cosmological parameters 
 $(\Omega_{b},\Omega_{m},\Omega_\Lambda,h,\sigma_8,n_s)$  = (0.044, 0.26, 0.74, 0.72, 0.79, 0.96). 
@@
 (mainly comes from redshift evolution of RSD and galaxy bias)
-reaches 4-6\% at the highest redshift bin,
+reaches 4 -- 6\% at the highest redshift bin,
 and is minor ($\lesssim2\%$) at the other redshift bins.
@@
 selection function, survey geometry, and 2pCF measurement of the BOSS DR12 catalogues.
-They have been adopted for statistical analysis of BOSS data in a series of works (see \cite{Alam2016} and references therein).
+They have been adopted for statistical analysis of BOSS data in a series of works \citep[see][and references therein]{Alam2016}.
 
@@
  The simulation cosmology, $\Omega_m=0.26$ $\Lambda$CDM, is marked by the black plus.
- The inferred cosmological constraints from the method, shown in the cygan contours, are consistent with the input cosmology.
+ The inferred cosmological constraints from the method, shown in the cyan contours, are consistent with the input cosmology.
  Right panel: Cosmological constraints from the BOSS DR12 galaxies, assuming a $w$CDM cosmology 
@@
 The shape of $\hat \xi_{\Delta s}(\mu)$ is far away from a flat curve, 
-due to the apparent anisotropy produced by the peculiar montion of galaxies.
+due to the apparent anisotropy produced by the peculiar motion of galaxies.
 In the $\Omega_m=0.11$ cosmology, 
@@
 so they are adopted as an estimation of the systematic effects of the method.
-The amount of systematics reaches 4-6\% in the 6th redshift bin,
+The amount of systematics reaches 4 -- 6\% in the 6th redshift bin,
 and is much smaller ($\lesssim2\%$) in the other bins.
@@
 
-In our earlier work\citep{Li2016}, the likelihood contour of $\Omega_m-w$ was constructed by
+In our earlier work \citep{Li2016}, the likelihood contour of $\Omega_m - w$ was constructed by
 measuring the 2PCF 3,375 times,
@@
 %with $0.06\leq \Omega_m\leq 0.41$, $-1.5 \leq w \leq -0.4$.
-This procedure took 1 month using 500 cores of the Korea Institute for Advanced Study {\texttt {baekdu}} cluster.
+This procedure took 1 month using 500 cores of the Korea Institute for Advanced Study {\texttt {Baekdu}} cluster.
 It would be computationally intractable to attempt a full MCMC of all relevant cosmological parameters using this approach. 
@@
 $\alpha_{\parallel}\equiv H_{\rm fiducial}/H_{\rm target}$.
-and values of $D_A$ and $H$ are computed in the effective redshifts of the six redshift bins.
+and $D_A$ and $H$ are computed in the effective redshifts of the six redshift bins.
 In the fiducial cosmology
@@
 %to obtain the accurate number counts 
-and these small ``pixels'' are grouped to infer 
+and later these small ``pixels'' are grouped to infer 
 the number counts in other cosmologies, 
-in large pixels of $\Delta s = 1 {\rm Mpc/h}$, $\Delta \mu = 1/120$.
+in large pixels of $\Delta s = 1 {\rm Mpc/h}$ and $\Delta \mu = 1/120$.
 In the case when one small pixel belongs to more than one larger pixel,
@@
 \footnote{A denser grid can significantly reduce the edge effect;
-if we use Equation \ref{eq:smumap} to do a simple interpolation on a grid with same resoultion does not work,
+if we use Equation \ref{eq:smumap} to do a simple interpolation on a grid with same resolution does not work,
 the edge effect is so large that the derived cosmological constraints suffer from a significant error.}
@@
 The input cosmology is the simulation cosmology, i.e. $\Omega_m=0.26$ $\Lambda$CDM.
-It lies within the 1$\sigma$ conour of the inferred constraints.
+It lies within the 1$\sigma$ contour of the inferred constraints.
 The right panel of Figure \ref{fig_Check} shows the cosmological constraints in case of fixing $w_a$ as 0 (hereafter $w$CDM).
@@
 
-%
-
 %It should be mentioned that simply using a linear interpolation to infer the values of $\xi$ in a new cosmology does {\it not} work.
@@
 
-\section{Cosmoligical constraints}
+\section{Cosmological constraints}
 
@@
 the full-mission Planck observations of CMB temperature and polarization anisotropies \citep{Planck2015},
-the BAO distance priors measured from SDSS DR11 \citep{Anderson2013}, 6dFGS \citep{6dFGS} and SDSS MGS \citep{MGS},
+the BAO distance priors measured from SDSS DR11 \citep{Anderson2013}, 6dFGS \citep{6dFGS}, SDSS MGS \citep{MGS},
 the ``JLA'' SNIa sample \citep{JLA},
@@
    Cosmological constraints on the CPL dark energy parametrization $w=w_0+w_a\frac{z}{1+z}$.
-   68.3\%, 95.4\% CL likelihood contours in the $\Omega_m-w_0$  and $w_0-w_a$ planes are plotted in the left and right panels, respectively.
-   Results from the AP method alone (brown filled), CMB+BAO (cygan filled), CMB+BAO+SNIa+$H_0$ (blue filled)
+   68.3\%, 95.4\% CL likelihood contours in the $\Omega_m - w_0$  and $w_0 - w_a$ planes are plotted in the left and right panels, respectively.
+   Results from the AP method alone (brown filled), CMB+BAO (cyan filled), CMB+BAO+SNIa+$H_0$ (blue filled)
    and CMB+BAO+SNIa+$H_0$+AP (magenta filled) are shown.
@@
    Adding the AP method tightens the constraints and reduces the redshift evolution of $w$ (the tilt of $w(z)$).
-   There is no significant change in the results if we disgard the systematics correction procedure in the AP method analysis.
+   There is no significant change in the results if we discard the systematics correction procedure in the AP method analysis.
    }
@@
 
-Figure \ref{fig_con} shows the 68.3\% and 95.4\% CL likelihood contours in the $\Omega_m-w_0$  and $w_0-w_a$ planes,
+Figure \ref{fig_con} shows the 68.3\% and 95.4\% CL likelihood contours in the $\Omega_m - w_0$  and $w_0 - w_a$ planes,
 derived from the AP method alone, CMB+BAO, CMB+BAO+SNIa+$H_0$
@@
 
-Using AP method alone, we can lead to effective constraints on the parameter space in the $\Omega_m-w_0$ plan.
+Using the AP method alone can lead to effective constraints on the parameter space in the $\Omega_m-w_0$ plane.
 Due to the inclusion of one extra free parameter, 
-the constrained area becomes larger than $w$CDM result \citep{Li2016}.
-Given the current galaxy surveys it is difficult to effectively constrain $w_a$ using only one technique.
-We have to combine various techniques.
-
-Combinig the four external techniques, i.e. CMB+BAO+SNIa+$H_0$, leads to effective constraints on all parameters.
+the constrained area becomes larger than the $w$CDM result \citep{Li2016}.
+Given current galaxy surveys it is difficult to effectively constrain $w_a$ using only one technique.
+%We have to combine various techniques.
+
+Combining the four external techniques, i.e. CMB+BAO+SNIa+$H_0$, leads to effective constraints on all parameters.
 The statistical mean values and 68.3\% uncertainties of these parameters are
@@
 \end{eqnarray}
-The error bars are dramatically reduced by 30-40\%.
+The error bars are dramatically reduced by 30 -- 40\%.
 The contour areas are reduced by 50\%, i.e., the dark energy figure of merit was improved by 100\%. 
@@
 So the doubling of the figure of merit comes at no additional cost or alteration to data size,
-thus greatly improving the overall cost-benefit of large cosmological redshift surveys.
-
-It can be also noted that, after adding the AP method, the central value of $w_a$ moved to zero appreciably.
+thus greatly improves the overall cost-benefit of large cosmological redshift surveys.
+
+It can be also noted that, after adding the AP method, the central value of $w_a$ moved significantly towards zero.
 This means the result becomes more consistent with a cosmological constant dark energy component having no evolution.
@@
    For the ``default'' constraints (pink contours) are derived using six redshift bins, 
-   $\mu_{\rm max}=0.97$, $n_{\mu}=20-25$, $s=6-40 \rm Mpc/h$,
+   $\mu_{\rm max}=0.97$, $n_{\mu}=20-25$, $s=6 - 40 \rm Mpc/h$,
    a fiducial cosmology $\Omega_m=0.26,\ w=-1.0$ for the measurement of 2pCF,
@@
    When we alters one of these options by using $\mu_{\rm max}=0.99$, 
-   $\mu_{\rm max}=0.85$, $n_{\mu}=15-20$, $s=6-35 \rm Mpc/h$, $s=6-45 \rm Mpc/h$,  
+   $\mu_{\rm max}=0.85$, $n_{\mu}=15-20$, $s=6 - 35 \rm Mpc/h$, $s=6 - 45 \rm Mpc/h$,  
    a fiducial cosmology of $\Omega_m=0.26,\ w=-0.6$, 
@@
 
-To see the effect of systematic effect, in Figure \ref{fig_con,fig_wz} we also plot the AP alone and CMB+BAO+SNIa+$H_0$+AP constraints 
+The effect of our systematic correction can be see in Figures \ref{fig_con} and \ref{fig_wz} where we plot the AP constraints alone and CMB+BAO+SNIa+$H_0$+AP combined constraints 
 before conducting the systematics correction procedure.
@@
 or when the cosmology dependence of the systematics effects is taken into account.
-The results are less affected by systematics.
+%The results are less affected by systematics.
 %\cite{Li2016}
@@
 governing the expansion history of the universe via 
-the redshift dependence of anisotropic galaxy clustering\citep{Li2016}.
+the redshift dependence of anisotropic galaxy clustering \citep{Li2016}.
 This approach enables a robust AP test on relatively small scales.
@@
 %Yet there are still issues demanding more investigations.
-In this analysis, we find the systematic effects do not significantly affect the derived cosmological constraints.
+In this analysis, we find that the systematic effects do not significantly affect the derived cosmological constraints.
 But it remains to be seen if this is true for future galaxy surveys,
 or when the cosmology dependence of the systematics effects is taken into account.
-Espeically, the systematic effects are estimated using simulations performed in a certain cosmology.
+Especially, the systematic effects are estimated using simulations performed in a certain cosmology.
 The cosmological dependence remains to be investigated in future works.

### 2017-11-03 Draft/Draft1.6.tex
minor changes

--- 2017-11-03 Draft/Draft1.5.tex
@@
 \shorttitle{Significantly improved dark energy figure of merit from reshift dependence of AP effect}
-\shortauthors{X.-D. Li, C. Park, C.G. Sabiu, H. Park, D.H. Weinberg, J. Kim, S.E. Hong}
+\shortauthors{X.-D. Li, C.G. Sabiu, C. Park, Y. Wang, G.-B. Zhao, H. Park, A. Shafieloo, J. Kim, S.E. Hong}
 
@@
 to place constraints on the expansion history of the Universe.
-We use 1,133,326 galaxies Sloan Digital Sky Survey Data Release 12 galaxies, spanning the redshift range $0.15<z<0.69$.
+We use the 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 12, 
+spanning the redshift range $0.15<z<0.69$.
 %Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$,
@@
 %allowing for competitive and unbiased constrains to be placed on cosmological parameters.
-We improve the methodology of Li et al. to efficiently explore three or more cosmological parameters.
-We then apply the improved method on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a{z}/({1+z})$.
+We improve the methodology of Li et al. to enable efficient exploring of three or more cosmological parameters,
+and apply it to the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a{z}/({1+z})$.
 In combination with the CMB, BAO, SNIa and $H_0$ from Cepheid data, we obtain
@@
 Adding our new AP measurements to the aforementioned results 
-reduces the error bars by $\sim$30 -- 40\%,
+reduces the error bars by $\sim$30 -- 40\%
 %and reduces the area of $w_0-w_a$ contour by 50\%.
 and improves the dark energy figure of merit by a factor of 2. 
-We checked the robustness of the results.
+We check the robustness of the results.
 %The AP method may %be combined with the standard BAO method,
@@
    \caption{\label{fig_xy}
-   The distance dependence of the shape distortion in four wrongly assumed cosmologies.
-   Assuming a true cosmology of $\Omega_m=0.26$, $w=-1$.
+   The distance dependence of the shape distortion in four wrongly assumed cosmologies,
+   assuming a true cosmology of $\Omega_m=0.26$, $w=-1$.
    There are four perfect squares with their true shapes plotted in blue dashed lines.
@@
    %We split the BOSS DR12 galaxies into six redshift bins to measure the evolution of shape distortion.
-   A patch of BOSS DR12 galaxies located in the fan shape region $\rm 140^\circ < RA < 170 ^\circ$, $\rm 10^\circ < DEC < 13 ^\circ$.
-   We split the sample into six non-overlapping redshift bins
-   (marked by the light green rings) in order to probing the redshift evolution of anisotropic clustering.
+   A patch of SDSS BOSS DR12 galaxies in the fan shape region $\rm 140^\circ < RA < 170 ^\circ$, $\rm 10^\circ < DEC < 13 ^\circ$,
+   split into six non-overlapping redshift bins (marked by the light green rings) in order to probing the redshift evolution of anisotropic clustering.
    In the left and right panels, we plot the galaxies positions computed in two cosmologies: the $\Omega_m$=0.26 $\Lambda$CDM, 
    and a dynamical dark energy cosmology with $\Omega_m=0.26,\ w_0=-1,\ w_a=-2$.
-   The redshifts and comoving distances (in unit of $h^{-1}\rm Mpc$) of the redshift bins are listed.
+   Redshifts and comoving distances (in unit of $h^{-1}\rm Mpc$) of the edges of redshift bins are listed.
    %The shape of structures look different in these two cosmologies. 
-   In the dynamical dark energy cosmology, we see apparent relative stretch of structures compared with the $\Lambda$CDM cosmology.
-   The stretch is not significant in the first redshift bin, and becomes large in the higher redshift bins.
+   In the dynamical dark energy cosmology, we see relative stretch of structures compared with the $\Lambda$CDM cosmology.
+   The stretch is not significant in the first redshift bin, and becomes large in high redshift bins.
    We use this phenomena to discover the AP effect and place constraints on cosmologies.
@@
 The clustering anisotropies produced by RSD are, although large, close to uniform in magnitude over a wide range in redshift.  
-However, if cosmological parameters are incorrectly chosen to change the AP effect, 
+However, if cosmological parameters are incorrectly chosen and there exists the AP effect, 
 the anisotropy in the clustering signal has a clear redshift dependence
-(as an illustration, Figure \ref{fig_xy} shows how the shape distortion of objects varies with distance, i.e., redshift, 
+(as an illustration, Figure \ref{fig_xy} shows how the shape distortion varies with distance, i.e., redshift, 
 when incorrect cosmologies are used to infer distances).
 In \cite{Li2015}, we developed an AP methodology 
-that utilizes the redshift dependence of the galaxy 2-point correlation function (2pCF), 
+that utilizes the redshift dependence of the galaxy 2-point correlation function (2PCF), 
 measured as a function of angle between the galaxy pair and line-of-sight (LoS).
@@
    \caption{\label{fig_xi}
-   $\hat\xi_{\Delta s}(\mu)$ measured from BOSS DR12 galaxies, in six redshift bins (three in LOWZ and three in CMASS).
-   This time we adopt the $\Omega_m=0.26$ $\Lambda$CDM cosmology and a more dark energy dominated cosmology, $\Omega_m=$0.11.
-   The measurement in each redshift bin and the redshift evolution with respective to the measurement in first bin of LOWZ are shown.
-   For comparison, the measurements in the HR4 mock catalogues (always in the $\Omega_m=0.26$ $\Lambda$CDM cosmology) are also plotted in green color.
-   The simulation results can match the shape of curves measured from real observational data, 
-   indicating that the FoG and Kaiser effects are well reproduced.
-   In the cosmology $\Omega_m$=0.11 cosmology, the shapes of $\hat\xi_{\Delta s}(\mu)$ are different from the $\Omega_m=0.26$ cosmology results,
-   and the amount of difference changes with redshift.
-   A large redshift evolution of $\hat\xi_{\Delta s}(\mu)$ is detected in this cosmology, 
+   $\hat\xi_{\Delta s}(\mu)$ measured from the SDSS BOSS DR12 galaxies in six redshift bins (three in LOWZ and three in CMASS),
+   assuming the $\Omega_m=0.26$ $\Lambda$CDM cosmology and a more dark energy dominated cosmology, $\Omega_m=$0.11 $\Lambda$CDM.
+   Measurements in the six redshift bins and their redshift evolution with respective to the first bin of LOWZ are plotted.
+   In the $\Omega_m$=0.11 cosmology, the shapes of $\hat\xi_{\Delta s}(\mu)$ are different from the $\Omega_m=0.26$ cosmology results,
+   and the amount of difference changes with redshift;
+   a large redshift evolution of $\hat\xi_{\Delta s}(\mu)$ is detected in this cosmology, 
    indicating that it is not likely to be the underlying true cosmology of our universe.
-   For the $\Omega_m$=0.11 cosmology, we also plot the approximate 2pCFs (red dashed lines) 
+   The measurements in the HR4 mock catalogues (always in the $\Omega_m=0.26$ $\Lambda$CDM cosmology; plotted in green color)
+   can match the shape of curves measured from real observational data, 
+   indicating that the simulation well reproduces the FoG and Kaiser effects.
+   For the $\Omega_m$=0.11 cosmology, we also plot the approximate 2PCFs (red dashed lines) 
    inferred using the technique described in Sec. \ref{sec:approx_2pcf}.
-   The error induced in the approximate procedure is $\lesssim0.5\%$.
+   The error induced in the approximation procedure is very small.
    }
@@
 
-In an earlier work \citep{Li2016} we applied this AP method to galaxies from the 3rd incarnation of the Sloan Digital Sky Survey (SDSS-III). 
+In an earlier work (Li et al. 2016, hereafter L16) we applied this AP method to galaxies from the 3rd incarnation of the Sloan Digital Sky Survey (SDSS-III). 
 Combining the method with measurements of the Cosmic Microwave Background (CMB), type Ia supernovae (SNIa), 
@@
 In this paper, we continue to develop our previous methodology and proceed to set the constraints on dynamical dark energy. 
-We will present an improved methodology compared to that of our previous work \citep{Li2016}, 
+We will present an improved methodology compared to L16, 
 allowing for faster likelihood estimation and thus the exploration of larger, higher dimensional parameter spaces. 
@@
 $w_0$ determines the present-day value, while parameter $w_a$ characterizes the first-order derivative of $w$ with respect to $a$. 
-The possible redshift evolution of dark energy EoS is not considered in the analysis of \cite{Li2016}.
+The possible redshift evolution of dark energy EoS is not considered in the analysis of L16.
 
@@
 defined as the reciprocal of the area of the error ellipse enclosing the 95\% confidence limit (CL) in the $w_0 - w_a$ plane.
-Figure \ref{fig_xy} shows that the redshift dependence of the shape distortion is sensitive to both $w_0$ and $w_a$.
-Thus we expect that these two parameters will be effectively constrained by our method.
+
+Figure \ref{fig_xy} illustrates the AP effect in wrong cosmologies.
+A redshift dependence of shape distortion is observed in case of adopting wrong values of $w_0$ and $w_a$,
+thus we expect that these two parameters will be effectively constrained by our method.
 
@@
 
-Figure \ref{fig_fan} shows the positions of a patch of 10,976 BOSS DR12 galaxies,
-computed in the $\Omega_m$=0.26 $\Lambda$CDM cosmology and a dynamical dark energy cosmology with $\Omega_m=0.26,\ w_0=-1,\ w_a=-2$.
+Figure \ref{fig_fan} shows a patch of 10,976 BOSS DR12 galaxies,
+whose positions are computed in the $\Omega_m$=0.26 $\Lambda$CDM cosmology 
+and a dynamical dark energy cosmology with $\Omega_m=0.26,\ w_0=-1,\ w_a=-2$.
 The shape of structures look different in these two cosmologies. 
@@
 
-Following our previous methodology \citep{Li2016}, the information of small-scale anisotropic clustering is computed as 
+Following our previous methodology, the information of small-scale anisotropic clustering is computed as 
 %\footnote{These correlations were computed using the public code \texttt{KSTAT} \citep{kstat}.} 
@@
 to nullify the amplitude information of the clustering signal, 
-which is not associated with the Alcock-Paczynski test and is mostly sensitive to the galaxy bias.
+which is not associated with the AP test and is mostly sensitive to the galaxy bias.
 %The right panel of Figure \ref{fig_TpCF} shows the contour map of $\xi(s,\mu)$ measured in the six redshift bins.
@@
 Mock galaxy samples are produced using a modified version of the one-to-one correspondence scheme \citep{hong2016}. 
-As presented in \cite{Li2016}, the value of $\left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right]_{\rm sys}$
-(mainly comes from redshift evolution of RSD and galaxy bias)
-reaches 4 -- 6\% at the highest redshift bin,
-and is minor ($\lesssim2\%$) at the other redshift bins.
+%As presented in \cite{Li2016}, the value of $\left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right]_{\rm sys}$
+%(mainly comes from redshift evolution of RSD and galaxy bias)
+%reaches 4 -- 6\% at the highest redshift bin,
+%and is minor ($\lesssim2\%$) at the other redshift bins.
 
@@
 The mock surveys can well reproduce the number density, 
-selection function, survey geometry, and 2pCF measurement of the BOSS DR12 catalogues.
+selection function, survey geometry, and 2PCF measurement of the BOSS DR12 catalogues.
 They have been adopted for statistical analysis of BOSS data in a series of works \citep[see][and references therein]{Alam2016}.
@@
    \caption{\label{fig_method}
-   Mapping $\xi(s,\mu)$ from the fiducial cosmology (taken as the $\Omega_m=0.26$ $\Lambda$CDM cosmology) to other cosmologies. 
- The number counts are measured in the fiducial cosmology in the blue dashed grid.
- In the four cosmologies with $(w_0,w_a) = (-1.5,0),\ (-0.5,0),\ (-1,2)\ \rm and\ (-1,-2)$,
- %due to the distortion of geometry,
- according to Equation \ref{eq:smumap},
- the distribution of measured number counts in $(s, \mu)$ space becomes the red solid grid,
- To ensure the accuracy, we count the number of pairs in 5 times smaller pixels (the small red pixels), 
- and group them together to infer the values of $\xi(s, \mu)$ in blue dashed pixels.
- For illustration purpose, 
-  the blue and red grids are all 10 times sparser than the grids adopted in the real analysis.
+ Mapping $\xi(s,\mu)$ from the fiducial cosmology (taken as the $\Omega_m=0.26$ $\Lambda$CDM cosmology) to four other cosmologies,
+   $(w_0,w_a) = (-1.5,0),\ (-0.5,0),\ (-1,2)\ \rm and\ (-1,-2)$.
+ The number counts are measured in the fiducial cosmology in the blue dashed grid;
+ %In the four cosmologies,  %due to the distortion of geometry,
+ in other cosmologies their distribution becomes the red solid grid (according to Equation \ref{eq:smumap}).
+ We use this relation to obtain $\xi(s,\mu)$ in these non-fiducial cosmology without re-measuring the number counts.
+ To enhance the accuracy, we count the number of galaxy pairs in 5 times smaller pixels (the small red pixels), 
+ and group them together to infer the values of $\xi(s, \mu)$ in the blue dashed pixels
+ (for illustration purpose, the blue and red grids are 10 times sparser than the grids adopted in the real analysis).
 }
@@
    \caption{\label{fig_Check}
- Left panel: Input-output test of the methodology using four sets of mock catalogues of BOSS DR12 galaxies constructed from the HR4 simulation.
- The approximate 2pCFs are adopted in the analysis.
- The simulation cosmology, $\Omega_m=0.26$ $\Lambda$CDM, is marked by the black plus.
- The inferred cosmological constraints from the method, shown in the cyan contours, are consistent with the input cosmology.
+ Left panel: Input-output test of the AP methodology using four sets of BOSS DR12 galaxy mock catalogues constructed from the HR4 simulation.
+ The approximate 2PCFs are adopted in the analysis.
+ The inferred cosmological constraints from the method, shown in the cyan contours, are consistent with the input cosmology
+ (the simulation cosmology, i.e. the $\Omega_m=0.26$ $\Lambda$CDM; marked by the black plus).
  Right panel: Cosmological constraints from the BOSS DR12 galaxies, assuming a $w$CDM cosmology 
  (i.e., the value of $w_a$ fixed as zero).
- Results obtained using the precise 2pCFs (cyan filled) 
- and approximate 2pCFs (red dashed) agree with each other quite well.
- The computation of precise 2pCFs is very expensive,
- so the comparison was done on a coarse grid of cosmological parameters with $\delta \Omega_m=0.025,\ \delta w=0.05$.
+ Results obtained using the precise 2PCFs (cyan filled) 
+ and approximate 2PCFs (red dashed) agree with each other quite well.
    }
@@
 
-The green curves denote the 2pCFS measured from the HR4 mock catalogues
-(we always plot the {\it correct} measurement in the simulation cosmology, i.e. the $\Omega_m=0.26$ $\Lambda$CDM).
+The green curves denote the 2PCFS measured from the HR4 mock catalogues
+(we plot the {\it correct} measurement in the simulation cosmology, i.e. the $\Omega_m=0.26$ $\Lambda$CDM).
 %The small redshift evolution of $\hat \xi_{\Delta s}(\mu)$
@@
 
-\subsection{Approximating the 2pCFs in cosmologies other than the fiducial one}\label{sec:approx_2pcf}
-
-In our earlier work \citep{Li2016}, the likelihood contour of $\Omega_m - w$ was constructed by
+\subsection{Approximating the 2PCFs in cosmologies other than the fiducial one}\label{sec:approx_2pcf}
+
+In L16, the likelihood contour of $\Omega_m - w$ was constructed by
 measuring the 2PCF 3,375 times,
@@
 %with $0.06\leq \Omega_m\leq 0.41$, $-1.5 \leq w \leq -0.4$.
-This procedure took 1 month using 500 cores of the Korea Institute for Advanced Study {\texttt {Baekdu}} cluster.
+This procedure took $\sim$1 month using 500 cores of the Korea Institute for Advanced Study {\texttt {Baekdu}} cluster.
 It would be computationally intractable to attempt a full MCMC of all relevant cosmological parameters using this approach. 
@@
 
-In detail, the number of pairs are only counted in a fiducial cosmology
+In detail, the number of galaxy pairs are only counted in a fiducial cosmology
 -- which is taken as the $\Omega_m=0.26$ $\Lambda$CDM --
-and ``translated'' to the measurements in a ``target'' cosmology using the relations, 
+and ``translated'' to the measurements in a ``target'' cosmology using the following relations, 
 \begin{eqnarray}\label{eq:smumap}
@@
 %in the fiducial cosmology and group the bins in the target cosmology.
-\footnote{A denser grid can significantly reduce the edge effect;
-if we use Equation \ref{eq:smumap} to do a simple interpolation on a grid with same resolution does not work,
-the edge effect is so large that the derived cosmological constraints suffer from a significant error.}
+\footnote{A dense grid of $\Delta s = 0.2 {\rm Mpc/h}$, $\Delta \mu = 1/600$ can significantly reduce the edge effect;
+if we use Equation \ref{eq:smumap} to do a simple interpolation on a $\Delta s = 1 {\rm Mpc/h}$, $\Delta \mu = 1/120$  grid,
+the edge effect becomes so large that the derived cosmological constraints suffer from a significant error.}
 %The edge effect would introduce artificial correlations between nearby pixels, smooth $\xi(s,\mu)$ a little bit, 
@@
 
-Figure \ref{fig_xi} plots the approximate 2pCFS in the $\Omega_m=0.11$ $\Lambda$CDM cosmology.
+Figure \ref{fig_xi} plots the approximate 2PCFS in the $\Omega_m=0.11$ $\Lambda$CDM cosmology.
 We find that, the approximation procedure only introduces a $\lesssim0.5\%$ error in the $\hat\xi_{\Delta s}(\mu)$, 
-which is 10 times smaller than the noise of $\hat\xi_{\Delta s}(\mu)$.
-So we expect that the approximate method can reproduce the results of precise method quite well.
-
+which is 10 times smaller than the intrinsic noise (the possion noise and cosmic variance) in $\hat\xi_{\Delta s}(\mu)$.
+%So we expect that the approximate method can reproduce the results of precise method quite well.
+So it should be precise enough to use the approximate 2PCF in the statistical analysis.
+
+We did a series of tests to check the reliability of using the approximate 2PCF in the cosmological analysis.
 An input-output test was performed using the four sets of mock catalogues of BOSS DR12 galaxies constructed from HR4 \citep{HR4}.
@@
 It lies within the 1$\sigma$ contour of the inferred constraints.
-The right panel of Figure \ref{fig_Check} shows the cosmological constraints in case of fixing $w_a$ as 0 (hereafter $w$CDM).
-Results obtained using the precise and approximate 2pCFs agree quite well with each other.
+The right panel of Figure \ref{fig_Check} displays the cosmological constraints from real observational data
+in case of fixing $w_a$ as 0 (hereafter $w$CDM).
+Results obtained using the precise and approximate 2PCFs agree quite well with each other
+\footnote{Here we are using a coarse grid of cosmological parameters with $\delta \Omega_m=0.025,\ \delta w=0.05$.
+The computation of precise 2PCFs is very expensive.}.
 
@@
 the full-mission Planck observations of CMB temperature and polarization anisotropies \citep{Planck2015},
-the BAO distance priors measured from SDSS DR11 \citep{Anderson2013}, 6dFGS \citep{6dFGS}, SDSS MGS \citep{MGS},
+the BAO distance priors measured from SDSS DR11 \citep{Anderson2013}, 6dFGS \citep{6dFGS} and SDSS MGS \citep{MGS},
 the ``JLA'' SNIa sample \citep{JLA},
@@
    \caption{\label{fig_con}
-   Cosmological constraints on the CPL dark energy parametrization $w=w_0+w_a\frac{z}{1+z}$.
+   Cosmological constraints on the CPL dark energy parametrization $w=w_0+w_a {z}/{(1+z)}$.
    68.3\%, 95.4\% CL likelihood contours in the $\Omega_m - w_0$  and $w_0 - w_a$ planes are plotted in the left and right panels, respectively.
@@
    %The AP method leads to competitive constraints on the cosmological parameters.
-   Adding the AP method to the combination of CMB+BAO+SNIa+$H_0$ reduces the contour area by about 50\%. %significantly reduced the area of contour.
+   Adding our AP method to the CMB+BAO+SNIa+$H_0$ combination reduces the contour area by about 50\%. %significantly reduced the area of contour.
    Systematics does not have significant influence on the results.% are less affected by systematics effect.
@@
    %When combined with CMB+BAO, AP method yields much tighter constraints than SNIa.
-   Derived redshift evolution of $w(z)$, with/without adding the AP constraint.
+   Derived redshift evolution of $w(z)$, with/without adding the AP method.
    The 68.3\% and 95.4\% CL regions are plotted.
@@
 
-Using the AP method alone can lead to effective constraints on the parameter space in the $\Omega_m-w_0$ plane.
+Using the AP method alone can lead to effective constraints on the $\Omega_m-w_0$ parameter space.
 Due to the inclusion of one extra free parameter, 
-the constrained area becomes larger than the $w$CDM result \citep{Li2016}.
+the constrained area becomes larger than the $w$CDM result.
 Given current galaxy surveys it is difficult to effectively constrain $w_a$ using only one technique.
@@
 \end{eqnarray}
-The error bars are dramatically reduced by 30 -- 40\%.
-The contour areas are reduced by 50\%, i.e., the dark energy figure of merit was improved by 100\%. 
+The error bars are dramatically reduced by 30 -- 40\%,
+and the contour areas are reduced by 50\%, i.e., the dark energy figure of merit was improved by 100\%. 
 Notice that the AP constraints come from the BOSS DR12 data, which is already used in the BAO analysis.
 So the doubling of the figure of merit comes at no additional cost or alteration to data size,
-thus greatly improves the overall cost-benefit of large cosmological redshift surveys.
+thus greatly improves the overall cost-benefit of the large cosmological redshift surveys.
 
@@
    Robustness test of the results.
-   For the ``default'' constraints (pink contours) are derived using six redshift bins, 
+   The ``default'' constraints (magenta contours) are derived using six redshift bins, 
    $\mu_{\rm max}=0.97$, $n_{\mu}=20-25$, $s=6 - 40 \rm Mpc/h$,
-   a fiducial cosmology $\Omega_m=0.26,\ w=-1.0$ for the measurement of 2pCF,
+   a fiducial cosmology $\Omega_m=0.26,\ w=-1.0$ for the approximation of 2PCF,
    systematic effects estimated from Horizon Run 4 simulations, 
@@
 
-The effect of our systematic correction can be see in Figures \ref{fig_con} and \ref{fig_wz} where we plot the AP constraints alone and CMB+BAO+SNIa+$H_0$+AP combined constraints 
+The effect of our systematic correction can be seen in Figures \ref{fig_con} and \ref{fig_wz} 
+where we plot the AP alone and CMB+BAO+SNIa+$H_0$+AP combined constraints 
 before conducting the systematics correction procedure.
-If we discard the systematics correction, there is a half-$\sigma$ shift of the AP alone constraints,
-and the combined constraints are almost unaffected
-since the direction of shift is orthogonal to the direction of CMB+BAO+SNIa+$H_0$ contour.
+If we discard the systematics correction, there is a half-$\sigma$ shift of the AP alone constraints;
+since the direction of shift is orthogonal to the direction of CMB+BAO+SNIa+$H_0$ contour,
+the combined constraints are almost unaffected.
 This indicates that, for the data analysis of current galaxy surveys,
@@
 governing the expansion history of the universe via 
-the redshift dependence of anisotropic galaxy clustering \citep{Li2016}.
+the redshift dependence of anisotropic galaxy clustering \citep{Li2014,Li2015,Li2016}.
 This approach enables a robust AP test on relatively small scales.
@@
 In this analysis, we find that the systematic effects do not significantly affect the derived cosmological constraints.
-But it remains to be seen if this is true for future galaxy surveys,
-or when the cosmology dependence of the systematics effects is taken into account.
+But it remains to be seen if this is true for future galaxy surveys.
 Especially, the systematic effects are estimated using simulations performed in a certain cosmology.

### 2017-11-03 Draft/Draft1.7.tex
minor changes

--- 2017-11-03 Draft/Draft1.6.tex
@@
 
-\author{Xiao-Dong Li,}
-\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 02455, Korea}
-\author{Cristiano G. Sabiu,}
-\affil{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 34055, Korea}
-\author{Changbom Park,}
-\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 02455, Korea}
-\author{Yuting Wang, Gong-bo Zhao}
-\affil{National Astronomy Observatories, Chinese Academy of Science, Beijing, 100012, P.R.China}
-\author{Hyunbae Park, Arman Shafieloo,}
-\affil{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 34055, Korea}
-\author{Juhan Kim,}
-\affil{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 02455, Korea}
-\author{and Sungwook E. Hong}
-\affil{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 34055, Korea}
+%[Xiao-Dong~Li, Cristiano G. Sabiu, Yuting Wang, Changbom~Park, Gong-bo Zhao, Hyunbae Park, Arman Shafieloo, Juhan Kim and Sungwook E. Hong]
+\author{Xiao-Dong~Li$^{1,2}$, Cristiano G. Sabiu$^3$, Yuting Wang$^4$, Changbom~Park$^2$, Gong-bo Zhao$^4$, Hyunbae Park$^3$, Arman Shafieloo$^3$, Juhan Kim$^5$ and Sungwook E. Hong$^3$}
+%{ Xiao-Dong Li$^{1,2,\dagger}$, Changbom Park$^{1}$, Cristiano G. Sabiu$^{2}$, Juhan Kim$^{3,1,\star}$, Sungwook E. Hong$^{1}$\\
+\affil{$^1$School of Physics and Astronomy, Sun Yat-Sen University, Guangzhou 510297, P.R.China}
+\affil{$^2$School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 02455, Korea}
+\affil{$^3$Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 34055, Korea}
+\affil{$^4$National Astronomy Observatories, Chinese Academy of Science, Beijing, 100012, P.R.China}
+\affil{$^5$Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 02455, Korea}
+
+%\author{Xiao-Dong Li,}
+%\affil{School of Physics and Astronomy, SYSU TBA}
+%\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 02455, Korea}
+%\author{Cristiano G. Sabiu,}
+%\affil{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 34055, Korea}
+%\author{Changbom Park,}
+%\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 02455, Korea}
+%\author{Yuting Wang, Gong-bo Zhao}
+%\affil{National Astronomy Observatories, Chinese Academy of Science, Beijing, 100012, P.R.China}
+%\author{Hyunbae Park, Arman Shafieloo,}
+%\affil{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 34055, Korea}
+%\author{Juhan Kim,}
+%\affil{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 02455, Korea}
+%\author{and Sungwook E. Hong}
+%\affil{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 34055, Korea}
 
@@
 \begin{abstract}
-We perform the Alcock-Paczynski (AP) test via the redshift dependence of clustering on scales of 6 -- 40 $h^{-1}\rm Mpc$
+We derive tight constraints on dynamical dark energy 
+from the Alcock-Paczynski (AP) test via the redshift dependence of clustering on scales of 6 -- 40 $h^{-1}\rm Mpc$
 to place constraints on the expansion history of the Universe.
@@
    \caption{\label{fig_xy}
-   The distance dependence of the shape distortion in four wrongly assumed cosmologies,
-   assuming a true cosmology of $\Omega_m=0.26$, $w=-1$.
-   There are four perfect squares with their true shapes plotted in blue dashed lines.
-   They are measured by an observer located at the origin, and the distances are reprojected in the four wrong cosmologies.
-   The apparently distorted shapes are plotted in red solid lines.
+   %The distance dependence of the shape distortion in four wrongly assumed cosmologies,
+   %assuming a true cosmology of $\Omega_m=0.26$, $w=-1$.
+   %There are four perfect squares with their true shapes plotted in blue dashed lines.
+   %They are measured by an observer located at the origin, and the distances are reprojected in the four wrong cosmologies.
+   %The apparently distorted shapes are plotted in red solid lines.
+   Examples of the rectangular shape distorted by assuming incorrect 
+   cosmologies compared to the true fiducial cosmology $\Omega_m=0.26$ and $w=-1$.
+   The blue dashed boxes mark the reference rectangular shape
+   and the red distorted boxes are the shapes observed at the coordinate origin.
    }
@@
    %We split the BOSS DR12 galaxies into six redshift bins to measure the evolution of shape distortion.
-   A patch of SDSS BOSS DR12 galaxies in the fan shape region $\rm 140^\circ < RA < 170 ^\circ$, $\rm 10^\circ < DEC < 13 ^\circ$,
-   split into six non-overlapping redshift bins (marked by the light green rings) in order to probing the redshift evolution of anisotropic clustering.
-   In the left and right panels, we plot the galaxies positions computed in two cosmologies: the $\Omega_m$=0.26 $\Lambda$CDM, 
+   A patch of SDSS BOSS DR12 galaxies in the fan shape region of 
+   $\rm 140^\circ < R.A. < 170 ^\circ$, $\rm 10^\circ < Decl. < 13 ^\circ$,
+   split into six non-overlapping redshift bins (marked by the light green arcs) in order to probe the redshift evolution of anisotropic clustering.
+   In the left and right panels, we plot the galaxy positions computed in two cosmologies: the $\Omega_m$=0.26 $\Lambda$CDM, 
    and a dynamical dark energy cosmology with $\Omega_m=0.26,\ w_0=-1,\ w_a=-2$.
@@
    The stretch is not significant in the first redshift bin, and becomes large in high redshift bins.
-   We use this phenomena to discover the AP effect and place constraints on cosmologies.
+   We use this apparent distortion to discover the AP effect and place constraints on cosmologies.
    %By investigating how the anosotropy of galaxy distribution evolves in the six redshift bins,
@@
 Theoretical explanations for this phenomena are numerous and range from a non-zero  vacuum energy, an evolving  scalar  field  remnant  from  the  big  bang, 
-to modifications of Einstein's General Relativity \citep{2012IJMPD..2130002Y}. 
+to modifications of Einstein's General Relativity \citep{Li2011,2012IJMPD..2130002Y}. 
 Considering the wealth of theoretical explanations, 
-it is crucial to obtain precise and unbiased measurements of the expansion history of the Universe allowing us to 
+it is crucial to obtain precise and unbiased measurements of the expansion history of the Universe which allows us to 
 differentiate between competing models.
@@
 the anisotropy in the clustering signal has a clear redshift dependence
-(as an illustration, Figure \ref{fig_xy} shows how the shape distortion varies with distance, i.e., redshift, 
-when incorrect cosmologies are used to infer distances).
+(as an illustration, Figure \ref{fig_xy} shows how the shape distortion varies with distance 
+when incorrect cosmologies are used to infer distance from redshift).
 In \cite{Li2015}, we developed an AP methodology 
@@
    In the $\Omega_m$=0.11 cosmology, the shapes of $\hat\xi_{\Delta s}(\mu)$ are different from the $\Omega_m=0.26$ cosmology results,
-   and the amount of difference changes with redshift;
+   and the difference changes with redshift;
    a large redshift evolution of $\hat\xi_{\Delta s}(\mu)$ is detected in this cosmology, 
@@
    The measurements in the HR4 mock catalogues (always in the $\Omega_m=0.26$ $\Lambda$CDM cosmology; plotted in green color)
-   can match the shape of curves measured from real observational data, 
+   match the shape of curves measured from observational data, 
    indicating that the simulation well reproduces the FoG and Kaiser effects.
@@
 thus we expect that these two parameters will be effectively constrained by our method.
+There is a fare degree of degeneracy in the resulting expansion history
+between increasing $w_0$ and adopting similar $w_0$ but increased $w_1$.
 
@@
 the LOWZ sample, designed as an extension of the SDSS-I/II luminous red galaxy sample to $z\approx 0.4$ and fainter luminosities,
-and the CMASS sample covers a higher redshift ($0.4\lesssim z \lesssim 0.7$),
-targeted to be an approximately stellar mass limited sample of massive, luminous galaxies \citep{Reidetal:2016}.
+and the CMASS sample covering a higher range ($0.4\lesssim z \lesssim 0.7$),
+and made to be an approximately stellar mass limited sample of massive, luminous galaxies \citep{Reidetal:2016}.
 In the clustering analysis we use 1,133,326 galaxies, split into six, non-overlapping redshift bins, 
@@
 The shape of structures look different in these two cosmologies. 
-In the later cosmology, there is apparent stretch of structures, 
+In the latter cosmology, there is apparent stretch of structures, 
 and the degree of compression becomes more significant in higher redshift bins.
@@
 
-Following our previous methodology, the information of small-scale anisotropic clustering is computed as 
+Following our previous methodology, the information of anisotropic clustering is computed as 
 %\footnote{These correlations were computed using the public code \texttt{KSTAT} \citep{kstat}.} 
@@
 to nullify the amplitude information of the clustering signal, 
-which is not associated with the AP test and is mostly sensitive to the galaxy bias.
+which is not associated with the AP test and is mostly sensitive to the galaxy bias evolution.
 %The right panel of Figure \ref{fig_TpCF} shows the contour map of $\xi(s,\mu)$ measured in the six redshift bins.
@@
 \end{eqnarray}
-We use a number of $n_{\mu}$=20, 21, ... 25 bins for the value of $\hat\xi_{\Delta s}(\mu)$ at $0<\mu<\mu_{\rm max}$.
-For the removal of fiber collision and the strong finger of god (FoG) effect \citep{FOG} near the LOS we take a cut $\mu_{\rm max} = 0.97$.
-
-Systematics effects are estimated using mock catalogues derived from Horizon Run 4 \citep[HR4;][]{HR4},
+We use $n_{\mu}$=20, 21, ... 25 bins for the value of 
+$0<\mu<\mu_{\rm max}$.
+To reduce the fiber collision and the finger of god (FoG) effect \citep{FOG} near the LOS we take a cut $\mu_{\rm max} = 0.97$.
+
+The systematics effects are estimated using mock catalogues drawn from Horizon Run 4 \citep[HR4;][]{HR4},
 an N-body simulation with a box size of $L={3150}$ $h^{-1}$Mpc, the number of particles $6300^3$,   
@@
 
-The covariance matrix, ${\bf Cov}$, is computed from the 2,000 sets of MultiDark PATCHY mock catalogues \citep{MDPATCHY}.
+The covariance matrix, ${\bf Cov}$, is computed from the a set of 2,000 MultiDark PATCHY mock catalogues \citep{MDPATCHY}.
 The statistical bias and scattering in the likelihood function (due to the finite number of mocks in covariance estimation) 
@@
  The inferred cosmological constraints from the method, shown in the cyan contours, are consistent with the input cosmology
- (the simulation cosmology, i.e. the $\Omega_m=0.26$ $\Lambda$CDM; marked by the black plus).
+ (the simulation cosmology, i.e. the $\Omega_m=0.26$ $\Lambda$CDM; marked by the black plus sign).
  Right panel: Cosmological constraints from the BOSS DR12 galaxies, assuming a $w$CDM cosmology 
@@
 
+{\bf TBA}
 As an illustration,
@@
 
-The shape of $\hat \xi_{\Delta s}(\mu)$ is far away from a flat curve, 
+The shape of $\hat \xi_{\Delta s}(\mu)$ is very different from a flat curve, 
 due to the apparent anisotropy produced by the peculiar motion of galaxies.
@@
 %The small redshift evolution of $\hat \xi_{\Delta s}(\mu)$
-The simulation results can well match the results from real observational data,
+The simulation results can well match the results from observational data,
 indicating that the FoG \citep{FOG} and Kaiser \citep{Kaiser1987} effects are both well reproduced.
@@
 %We checked that the approximate method can reproduce the results presented in \cite{Li2016} quite well.
-
+{\bf TBA}
 Figure \ref{fig_xi} plots the approximate 2PCFS in the $\Omega_m=0.11$ $\Lambda$CDM cosmology.
@@
    \caption{\label{fig_con}
-   Cosmological constraints on the CPL dark energy parametrization $w=w_0+w_a {z}/{(1+z)}$.
-   68.3\%, 95.4\% CL likelihood contours in the $\Omega_m - w_0$  and $w_0 - w_a$ planes are plotted in the left and right panels, respectively.
-   Results from the AP method alone (brown filled), CMB+BAO (cyan filled), CMB+BAO+SNIa+$H_0$ (blue filled)
+   Cosmological parameter constraints on the CPL dark energy parametrization $w=w_0+w_a {z}/{(1+z)}$.
+   The 68.3\%, 95.4\% CL likelihood contours in the $\Omega_m - w_0$  and $w_0 - w_a$ planes are plotted in the left and right panels, respectively.
+   %Results from the AP method alone (brown filled), CMB+BAO (cyan filled), CMB+BAO+SNIa+$H_0$ (blue filled)
+   Results from CMB+BAO (cyan filled), CMB+BAO+SNIa+$H_0$ (blue filled)
    and CMB+BAO+SNIa+$H_0$+AP (magenta filled) are shown.
-   To see the effect of systematic effect, we also plot the AP alone and CMB+BAO+SNIa+$H_0$+AP constraints 
-   before conducting the systematics correction procedure (the gray solid and black dashed lines, labeled by ``with sys'').
+   %To see the effect of systematic effect, we also plot the AP alone and CMB+BAO+SNIa+$H_0$+AP constraints 
+   %before conducting the systematics correction procedure (the gray solid and black dashed lines, labeled by ``with sys'').
    %The AP method leads to competitive constraints on the cosmological parameters.
-   Adding our AP method to the CMB+BAO+SNIa+$H_0$ combination reduces the contour area by about 50\%. %significantly reduced the area of contour.
-   Systematics does not have significant influence on the results.% are less affected by systematics effect.
+   Adding our AP method to the CMB+BAO+SNIa+$H_0$ combination reduces the contour area by as much as 50\%. %significantly reduced the area of contour.
+   %Systematics does not have significant influence on the results.% are less affected by systematics effect.
    %If we discard the systematics correction, there is half-$\sigma$ shift of the AP alone contour.
@@
    %When combined with CMB+BAO, AP method yields much tighter constraints than SNIa.
-   Derived redshift evolution of $w(z)$, with/without adding the AP method.
-   The 68.3\% and 95.4\% CL regions are plotted.
+   %Derived redshift evolution of $w(z)$, with/without adding the AP method.
+   Derived redshift evolution of $w(z)$, the 68.3\% and 95.4\% CL regions are plotted.
    Adding the AP method tightens the constraints and reduces the redshift evolution of $w$ (the tilt of $w(z)$).
-   There is no significant change in the results if we discard the systematics correction procedure in the AP method analysis.
+   %There is no significant change in the results if we discard the systematics correction procedure in the AP method analysis.
    }
@@
 Figure \ref{fig_con} shows the 68.3\% and 95.4\% CL likelihood contours in the $\Omega_m - w_0$  and $w_0 - w_a$ planes,
-derived from the AP method alone, CMB+BAO, CMB+BAO+SNIa+$H_0$
-and CMB+BAO+SNIa+$H_0$+AP, respectively.
+derived from the CMB+BAO, CMB+BAO+SNIa+$H_0$ and CMB+BAO+SNIa+$H_0$+AP, respectively.
 The overlapping of different contours suggest that they are consistent with each other.
 
-Using the AP method alone can lead to effective constraints on the $\Omega_m-w_0$ parameter space.
-Due to the inclusion of one extra free parameter, 
-the constrained area becomes larger than the $w$CDM result.
-Given current galaxy surveys it is difficult to effectively constrain $w_a$ using only one technique.
+%Using the AP method alone can lead to effective constraints on the $\Omega_m-w_0$ parameter space.
+%Due to the inclusion of one extra free parameter, 
+%the constrained area becomes larger than the $w$CDM result.
+%Given current galaxy surveys it is difficult to effectively constrain $w_a$ using only one technique.
 %We have to combine various techniques.
 
+We can not derive effective constraint on the parameter space from a combination of CMB+BAO.
 Combining the four external techniques, i.e. CMB+BAO+SNIa+$H_0$, leads to effective constraints on all parameters.
@@
    The ``default'' constraints (magenta contours) are derived using six redshift bins, 
-   $\mu_{\rm max}=0.97$, $n_{\mu}=20-25$, $s=6 - 40 \rm Mpc/h$,
+   $\mu_{\rm max}=0.97$, $s=6 - 40 \rm Mpc/h$,
    a fiducial cosmology $\Omega_m=0.26,\ w=-1.0$ for the approximation of 2PCF,
@@
    and covariance estimated using 2,000 MultiDark PATCHY mocks.
-   When we alters one of these options by using $\mu_{\rm max}=0.99$, 
-   $\mu_{\rm max}=0.85$, $n_{\mu}=15-20$, $s=6 - 35 \rm Mpc/h$, $s=6 - 45 \rm Mpc/h$,  
+   When we alters one of these options by discarding the systematic correction, 
+   using $\mu_{\rm max}=0.99$, 
+   $\mu_{\rm max}=0.85$, $s=6 - 35 \rm Mpc/h$, $s=6 - 45 \rm Mpc/h$,  
    a fiducial cosmology of $\Omega_m=0.26,\ w=-0.6$, 
@@
 
+\begin{figure*}
+   \centering{
+   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
+   %\includegraphics[width=8cm,natwidth=6,natheight=4.5]{figCPL_b.pdf}
+   %\includegraphics[width=5.5cm,natwidth=4,natheight=4]{figCPL_b_BAOSNIaAP.pdf}
+   \includegraphics[width=11cm,natwidth=9,natheight=7]{figCPL_d_withsys.pdf}
+   %\includegraphics[height=8cm]{fig2b.pdf}
+%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
+%    \includegraphics[height=8cm]{smu.eps}
+   }
+   \caption{\label{fig_wz_sys}
+   %Cosmological constraints on the CPL dark energy parametrization $w=w_0+w_a\frac{z}{1+z}$.
+   %Left panel: 68.3\%, 95.4\% CL likelihood contours in the  $w_0-w_a$ plane.
+   %Results are consistent with $\Lambda$CDM.
+   %The constrained area is significantly reduced after combined with the AP method.
+   %This shows the power of the AP method in constraining dynamical dark energy.
+   %Middle panel: $w_0-w_a$ likelihood contours using datasets of CMB+BAO, CMB+BAO+SNIa+$H_0$ and CMB+BAO+AP+$H_0$.
+   %When combined with CMB+BAO, AP method yields much tighter constraints than SNIa.
+   %Derived redshift evolution of $w(z)$, with/without adding the AP method.
+   Derived redshift evolution of $w(z)$ from CMB+BAO+SNIa+$H_0$+AP.
+   %Adding the AP method tightens the constraints and reduces the redshift evolution of $w$ (the tilt of $w(z)$).
+   There is no significant change if we discard the systematics correction procedure in the AP method analysis.
+   }
+\end{figure*}
+
 \subsection{Robustness}
 
-The effect of our systematic correction can be seen in Figures \ref{fig_con} and \ref{fig_wz} 
-where we plot the AP alone and CMB+BAO+SNIa+$H_0$+AP combined constraints 
-before conducting the systematics correction procedure.
-If we discard the systematics correction, there is a half-$\sigma$ shift of the AP alone constraints;
-since the direction of shift is orthogonal to the direction of CMB+BAO+SNIa+$H_0$ contour,
-the combined constraints are almost unaffected.
+%The effect of our systematic correction can be seen in Figures \ref{fig_con} and \ref{fig_wz} 
+%where we plot the AP alone and CMB+BAO+SNIa+$H_0$+AP combined constraints 
+%before conducting the systematics correction procedure.
+Figure \ref{fig_contest} and \ref{fig_wz_sys} show that,
+if we discard the systematics correction, %there is a half-$\sigma$ shift of the AP alone constraints;
+%since the direction of shift is orthogonal to the direction of CMB+BAO+SNIa+$H_0$ contour,
+the derived constraints are almost unaffected.
 This indicates that, for the data analysis of current galaxy surveys,
@@
 
-Finally, we performed a test of all the possible variables in our methodology.
-Figure \ref{fig_contest} shows that 
+%Finally, we performed a test of all the possible variables in our methodology.
+Furthermore, Figure \ref{fig_contest} shows that 
 the result is unaffected by the line-of-sight $\mu$-cut, 
@@
 and the number of mocks.
-Reduces the number of angular bins weakens the constraints a little bit,
-and enlarges the contour towards the lower-right direction 
-(the upper-left boundary is determined by the CMB+BAO+SNIa+$H_0$ constraints, so it is unaffected).
+%Reduces the number of angular bins weakens the constraints a little bit,
+%and enlarges the contour towards the lower-right direction 
+%(the upper-left boundary is determined by the CMB+BAO+SNIa+$H_0$ constraints, so it is unaffected).
 %we adopt $\mu_{\rm max}=0.99\ (0.85)$ to include more (less) regions near the LOS,
@@
 
-%\bibitem[Li et al.(2011)]{Li2011}
-%Li, M., Li, X.-D., Wang, S., \& Wang, Y. 2011, Commun. Theor. Phys., 56, 525
+\bibitem[Li et al.(2011)]{Li2011}
+Li, M., Li, X.-D., Wang, S., \& Wang, Y. 2011, Commun. Theor. Phys., 56, 525
 

### 2017-11-03 Draft/Draft1.8.tex
minor changes

--- 2017-11-03 Draft/Draft1.7.tex
@@
 %[Xiao-Dong~Li, Cristiano G. Sabiu, Yuting Wang, Changbom~Park, Gong-bo Zhao, Hyunbae Park, Arman Shafieloo, Juhan Kim and Sungwook E. Hong]
-\author{Xiao-Dong~Li$^{1,2}$, Cristiano G. Sabiu$^3$, Yuting Wang$^4$, Changbom~Park$^2$, Gong-bo Zhao$^4$, Hyunbae Park$^3$, Arman Shafieloo$^3$, Juhan Kim$^5$ and Sungwook E. Hong$^3$}
+\author{Xiao-Dong~Li$^{1,2,4}$, Cristiano G. Sabiu$^3$, Yuting Wang$^4$, Changbom~Park$^2$, Gong-bo Zhao$^4$, Hyunbae Park$^3$, Arman Shafieloo$^3$, Juhan Kim$^5$ and Sungwook E. Hong$^3$}
 %{ Xiao-Dong Li$^{1,2,\dagger}$, Changbom Park$^{1}$, Cristiano G. Sabiu$^{2}$, Juhan Kim$^{3,1,\star}$, Sungwook E. Hong$^{1}$\\
@@
 We derive tight constraints on dynamical dark energy 
-from the Alcock-Paczynski (AP) test via the redshift dependence of clustering on scales of 6 -- 40 $h^{-1}\rm Mpc$
+from the Alcock-Paczynski (AP) test via the redshift dependence of galaxy clustering on scales of 6 -- 40 $h^{-1}\rm Mpc$
 to place constraints on the expansion history of the Universe.
@@
    $\hat\xi_{\Delta s}(\mu)$ measured from the SDSS BOSS DR12 galaxies in six redshift bins (three in LOWZ and three in CMASS),
-   assuming the $\Omega_m=0.26$ $\Lambda$CDM cosmology and a more dark energy dominated cosmology, $\Omega_m=$0.11 $\Lambda$CDM.
+   assuming the $\Omega_m=0.26$ $\Lambda$CDM cosmology and a dynamical dark energy cosmology with $\Omega_m=0.26$, $w_0=-1$ and $w_a=-2$.
    Measurements in the six redshift bins and their redshift evolution with respective to the first bin of LOWZ are plotted.
-   In the $\Omega_m$=0.11 cosmology, the shapes of $\hat\xi_{\Delta s}(\mu)$ are different from the $\Omega_m=0.26$ cosmology results,
+   In the dynamical dark energy cosmology, the shapes of $\hat\xi_{\Delta s}(\mu)$ are different from the $\Omega_m=0.26$ cosmology results,
    and the difference changes with redshift;
-   a large redshift evolution of $\hat\xi_{\Delta s}(\mu)$ is detected in this cosmology, 
-   indicating that it is not likely to be the underlying true cosmology of our universe.
+   a larger redshift evolution of $\hat\xi_{\Delta s}(\mu)$ is detected in this cosmology, 
+   indicating that it is less likely to be the underlying true cosmology of our universe.
    The measurements in the HR4 mock catalogues (always in the $\Omega_m=0.26$ $\Lambda$CDM cosmology; plotted in green color)
@@
    indicating that the simulation well reproduces the FoG and Kaiser effects.
-   For the $\Omega_m$=0.11 cosmology, we also plot the approximate 2PCFs (red dashed lines) 
+   For the dynamical dark energy cosmology, we also plot the approximate 2PCFs (red dashed lines) 
    inferred using the technique described in Sec. \ref{sec:approx_2pcf}.
@@
 
-{\bf TBA}
 As an illustration,
 Figure \ref{fig_xi} shows how we us the above procedure to distinguish different cosmologies.
-Here we plot the value of $\hat\xi_{\Delta s}(\mu)$, as long as its redshift evolution, 
+Here we plot the value of $\hat\xi_{\Delta s}(\mu)$ (upper panels) as well as its redshift evolution (lower panels), 
 measured from the BOSS DR12 galaxies in six redshift bins.
-Two $\Lambda$CDM cosmologies are adopted, 
-one with $\Omega_m=0.26$, and the other with obviously wrong value of $\Omega_m=0.11$.
+Two cosmologies are adopted, 
+one is the $\Omega_m=0.26$ $\Lambda$CDM cosmology, 
+and the other is a dynamical dark energy cosmology with $\Omega_m=0.26$, $w_0=-1$ and $w_a=-2$.
 
@@
 due to the apparent anisotropy produced by the peculiar motion of galaxies.
-In the $\Omega_m=0.11$ cosmology, 
+In the dynamical dark energy cosmology, 
 the shapes of $\hat\xi_{\Delta s}(\mu)$ are different from the measurements in the $\Omega_m=0.26$ cosmology,
 and the amount of difference systematically evolves with redshift.
-So we observe a large redshift evolution of $\hat\xi_{\Delta s}(\mu)$, 
-indicating that it is not likely to be the underlying true cosmology of our universe.
+We observe a larger redshift evolution of $\hat\xi_{\Delta s}(\mu)$ compared with $\Lambda$CDM cosmology, 
+indicating that it is less likely to be the underlying true cosmology of our universe.
 
@@
 %The small redshift evolution of $\hat \xi_{\Delta s}(\mu)$
-The simulation results can well match the results from observational data,
+The simulation results can match well the results from observational data,
 indicating that the FoG \citep{FOG} and Kaiser \citep{Kaiser1987} effects are both well reproduced.
@@
 we obtained the distribution of number counts in cosmologies other than the fiducial cosmology.
-To ensure the accuracy of mapping, the number counting is conducted using 5 times smaller pixels (the small red pixels), 
-and grouped together to infer the number counts in the standard resolution (the large blue dashed pixels).
+We ensure the accuracy of the remapping by performing the pair counting using 5 times smaller pixels (the small red pixels), 
+and regrouping these together to infer the number counts at the desired resolution (the large blue dashed pixels).
 
 %We checked that the approximate method can reproduce the results presented in \cite{Li2016} quite well.
-{\bf TBA}
-Figure \ref{fig_xi} plots the approximate 2PCFS in the $\Omega_m=0.11$ $\Lambda$CDM cosmology.
+Figure \ref{fig_xi} plots the approximate 2PCFS in the dynamical dark energycosmology.
 We find that, the approximation procedure only introduces a $\lesssim0.5\%$ error in the $\hat\xi_{\Delta s}(\mu)$, 
@@
 derived from the CMB+BAO, CMB+BAO+SNIa+$H_0$ and CMB+BAO+SNIa+$H_0$+AP, respectively.
-The overlapping of different contours suggest that they are consistent with each other.
+The overlapping of the various contours suggest that they are consistent with each other.
 
@@
 \end{eqnarray}
-while adding our AP method to this combination further tightens the constraints and yield to
+while adding our AP method to this combination further tightens the constraints leading to
 \begin{eqnarray}
@@
 The error bars are dramatically reduced by 30 -- 40\%,
-and the contour areas are reduced by 50\%, i.e., the dark energy figure of merit was improved by 100\%. 
+and the contour areas are reduced by 50\%, i.e., the dark energy figure of merit is improved by 100\%. 
 Notice that the AP constraints come from the BOSS DR12 data, which is already used in the BAO analysis.
@@
 Figure \ref{fig_wz} shows the redshift evolution of $w(z)$ derived from the cosmological constraints.
-Adding AP tightens the constraints and reduces the redshift evolution of $w$ (tilt of $w(z)$).
+Adding the new AP results tightens the constraints and reduces the redshift evolution of $w$ (tilt of $w(z)$).
 
@@
 Our method can use the galaxy clustering signal down to
-much smaller scales compared to other methods,
-providing much higher statistics.
+much smaller scales compared to other methods, thus including many more k-modes, maximising the information gain.
 

### 2017-11-03 src/AP_Rhct.f90

@@ -12,6 +12,7 @@
 
 ! Sys-uncorred:    14.5382814       18.5175323       12.0481081       9.10813332       11.9272099       66.1392657 22333093  
 
+
 program main
 use LSS_ximu_tests
 USE de_model_init
@@ -36,7 +37,7 @@ implicit none
 !!! Next step: write this for wbinned model!!!
 
   de_model_lab  = de_wcdm_lab
-  ommin=0.0;  ommax=1.0; 
+  ommin=0.2;  ommax=0.3; 
    numw0=1; numwa=1;
 !  print *, log(2.732); stop
   nowmodel = model_wcdm;   wamin=0.0;wamax=0.0;numwa=1
@@ -64,7 +65,7 @@ implicit none
   if(do_lcdm_constraint) then
     mcmcdir = '/home/xiaodongli/software/cosmomcs/12Oct_generic/chains/wcdm/'
     MCMCfilestr = 'base_lcdm_'
-    numom = 2001
+    numom = 21
   else
     mcmcdir = '/home/xiaodongli/software/cosmomcs/12Oct_generic/chains/wcdm/'
     MCMCfilestr = 'base_Rhct_'

### 2017-11-03 src/AP_ximu.f90

@@ -1,0 +1,2309 @@
+
+! 1. Plans
+
+! 1. The file system: can find all files;
+! 2. Loadin & ximu: can load in 2pcf files, and compute ximu
+! 3. Cosmo convert: convert 2pcf from 1 to another
+! 4. Covmat: compute covmat from all covmat mocks
+! 5. Chisq: load in files, compute chisqs!
+
+
+!###############################################################
+!## Module: Types, constants, tools
+module types_constants
+implicit none
+
+  integer, parameter  :: rt =  kind(1.0d0)
+  integer, parameter  :: charlen=1000
+  real(rt), parameter :: CONST_C = 299792.458 !unit: km/s
+  
+  ! Setting: The binning schemes (number of bins in the mu space )
+  !  integer, parameter :: N1=1,N2=1,mubins(N1)=(/10/); real(rt),parameter::mucuts(N2)=(/0.99_rt/)
+!  integer, parameter :: N1=36
+!  integer, parameter :: mubins(N1) = (/ 5,6,7,8,9,10,11,12,13,14,&
+!  		15,16,17,18,19,20,21,22,23,24,25,26,27,28,29,30, &
+!  		31,32,33,34,35,36,37,38,39,40 /)
+
+  integer, parameter :: N1=6, gbnumsbin = 1
+  integer, parameter :: mubins(N1) = (/ 20,21,22,23,24,25 /)
+!  integer, parameter :: mubins(N1) = (/ 11 /)
+!  integer, parameter :: mubins(N1) = (/ 10,11,12,13,14,15 /)
+!  integer, parameter :: mubins(N1) = (/ 10*gbnumsbin,11*gbnumsbin,12*gbnumsbin,13*gbnumsbin,14*gbnumsbin,15*gbnumsbin /)
+!  integer, parameter :: mubins(N1) = (/ 35,36,37,38,39,40 /)
+!  integer, parameter :: mubins(N1) = (/ 15,16,17,18,19,20 /)
+!  integer, parameter :: mubins(N1) = (/ 10,11,12,13,14,15 /)
+!  integer, parameter :: mubins(N1) = (/ 25,26,27,28,29,30 /)
+!  integer, parameter :: mubins(N1) = (/ 10,11,12,13,14,15,16,17,18,19,20 /)
+
+!  integer, parameter :: N1=6
+!  integer, parameter :: mubins(N1) = (/ 20,21,22,23,24,25 /)
+!  integer, parameter :: mubins(N1) = (/ 26,27,28,29,30 /)
+
+
[…]

### 2017-11-03 src/Make.sh

@@ -1,5 +1,5 @@
 
-#gfortran -o LSS_test LSS_main_LSS_ximu.f90 LSS_main_program.f90
-#gfortran -o LSS_test LSS_main_LSS_ximu.f90 LSS_main_program.f90
-gfortran -o AP_MCMC_wcdm AP_tools.f90 AP_MCMC_wcdm.f90 $delm
-gfortran -o AP_test AP_tools.f90 AP_test.f90 $delm
+gfortran -o LSS_test LSS_main_LSS_ximu.f90 LSS_main_program.f90
+gfortran -o LSS_test LSS_main_LSS_ximu.f90 LSS_main_program.f90
+#gfortran -o AP_MCMC_wcdm AP_tools.f90 AP_MCMC_wcdm.f90 $delm
+#gfortran -o AP_test AP_tools.f90 AP_test.f90 $delm
